% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{alignment}{%
\section{Alignment}\label{alignment}}

A typical creature in the game world has an alignment, which broadly
describes its moral and personal attitudes. Alignment is a combination
of two factors: one identifies morality (good, evil, or neutral), and
the other describes attitudes toward society and order (lawful, chaotic,
or neutral). Thus, nine distinct alignments define the possible
combinations.

These brief summaries of the nine alignments describe the typical
behavior of a creature with that alignment. Individuals might vary
significantly from that typical behavior, and few people are perfectly
and consistently faithful to the precepts of their alignment.

\textbf{Lawful good} (LG) creatures can be counted on to do the right
thing as expected by society. Gold dragons, paladins, and most dwarves
are lawful good.

\textbf{Neutral good} (NG) folk do the best they can to help others
according to their needs. Many celestials, some cloud giants, and most
gnomes are neutral good.

\textbf{Chaotic good} (CG) creatures act as their conscience directs,
with little regard for what others expect. Copper dragons, many elves,
and unicorns are chaotic good.

\textbf{Lawful neutral} (LN) individuals act in accordance with law,
tradition, or personal codes. Many monks and some wizards are lawful
neutral.

\textbf{Neutral} (N) is the alignment of those who prefer to steer clear
of moral questions and don't take sides, doing what seems best at the
time. Lizardfolk, most druids, and many humans are neutral.

\textbf{Chaotic neutral} (CN) creatures follow their whims, holding
their personal freedom above all else. Many barbarians and rogues, and
some bards, are chaotic neutral.

\textbf{Lawful evil} (LE) creatures methodically take what they want,
within the limits of a code of tradition, loyalty, or order. Devils,
blue dragons, and hobgoblins are lawful evil.

\textbf{Neutral evil} (NE) is the alignment of those who do whatever
they can get away with, without compassion or qualms. Many drow, some
cloud giants, and goblins are neutral evil.

\textbf{Chaotic evil} (CE) creatures act with arbitrary violence,
spurred by their greed, hatred, or bloodlust. Demons, red dragons, and
orcs are chaotic evil.

\hypertarget{alignment-in-the-multiverse}{%
\subsection{Alignment in the
Multiverse}\label{alignment-in-the-multiverse}}

For many thinking creatures, alignment is a moral choice. Humans,
dwarves, elves, and other humanoid races can choose whether to follow
the paths of good or evil, law or chaos. According to myth, the good-
aligned gods who created these races gave them free will to choose their
moral paths, knowing that good without free will is slavery.

The evil deities who created other races, though, made those races to
serve them. Those races have strong inborn tendencies that match the
nature of their gods. Most orcs share the violent, savage nature of the
orc gods, and are thus inclined toward evil. Even if an orc chooses a
good alignment, it struggles against its innate tendencies for its
entire life. (Even half-orcs feel the lingering pull of the orc god's
influence.)

Alignment is an essential part of the nature of celestials and fiends. A
devil does not choose to be lawful evil, and it doesn't tend toward
lawful evil, but rather it is lawful evil in its essence. If it somehow
ceased to be lawful evil, it would cease to be a devil.

Most creatures that lack the capacity for rational thought do not have
alignments---they are \textbf{unaligned} . Such a creature is incapable
of making a moral or ethical choice and acts according to its bestial
nature. Sharks are savage predators, for example, but they are not evil;
they have no alignment.

\end{document}
