% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{beyond-first-level}{%
\section{Beyond First Level}\label{beyond-first-level}}

As your character goes on adventures and overcomes challenges, he or she
gains experience, represented by experience points. A character who
reaches a specified experience point total advances in capability. This
advancement is called \textbf{gaining a level}.

When your character gains a level, his or her class often grants
additional features, as detailed in the class description. Some of these
features allow you to increase your ability scores, either increasing
two scores by 1 each or increasing one score by 2. You can't increase an
ability score above 20. In addition, every character's proficiency bonus
increases at certain levels.

Each time you gain a level, you gain 1 additional Hit Die. Roll that Hit
Die, add your Constitution modifier to the roll, and add the total to
your hit point maximum. Alternatively, you can use the fixed value shown
in your class entry, which is the average result of the die roll
(rounded up).

When your Constitution modifier increases by 1, your hit point maximum
increases by 1 for each level you have attained. For example, if your
7th level fighter has a Constitution score of 17, when he reaches 8th
level, he increases his Constitution score from 17 to 18, thus
increasing his Constitution modifier from +3 to +4. His hit point
maximum then increases by 8.

The Character Advancement table summarizes the XP you need to advance in
levels from level 1 through level 20, and the proficiency bonus for a
character of that level. Consult the information in your character's
class description to see what other improvements you gain at each level.

\hypertarget{character-advancement}{%
\paragraph{Character Advancement}\label{character-advancement}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Experience Points & Level & Proficiency Bonus\tabularnewline
\midrule
\endhead
0 & 1 & +2\tabularnewline
300 & 2 & +2\tabularnewline
900 & 3 & +2\tabularnewline
2,700 & 4 & +2\tabularnewline
6,500 & 5 & +3\tabularnewline
14,000 & 6 & +3\tabularnewline
23,000 & 7 & +3\tabularnewline
34,000 & 8 & +3\tabularnewline
48,000 & 9 & +4\tabularnewline
64,000 & 10 & +4\tabularnewline
85,000 & 11 & +4\tabularnewline
100,000 & 12 & +4\tabularnewline
120,000 & 13 & +5\tabularnewline
140,000 & 14 & +5\tabularnewline
165,000 & 15 & +5\tabularnewline
195,000 & 16 & +5\tabularnewline
225,000 & 17 & +6\tabularnewline
265,000 & 18 & +6\tabularnewline
305,000 & 19 & +6\tabularnewline
355,000 & 20 & +6\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{multiclassing}{%
\subsection{Multiclassing}\label{multiclassing}}

Multiclassing allows you to gain levels in multiple classes. Doing so
lets you mix the abilities of those classes to realize a character
concept that might not be reflected in one of the standard class
options.

With this rule, you have the option of gaining a level in a new class
whenever you advance in level, instead of gaining a level in your
current class. Your levels in all your classes are added together to
determine your character level. For example, if you have three levels in
wizard and two in fighter, you're a 5th level character.

As you advance in levels, you might primarily remain a member of your
original class with just a few levels in another class, or you might
change course entirely, never looking back at the class you left behind.
You might even start progressing in a third or fourth class. Compared to
a single class character of the same level, you'll sacrifice some focus
in exchange for versatility.

\hypertarget{prerequisites}{%
\subsubsection{Prerequisites}\label{prerequisites}}

To qualify for a new class, you must meet the ability score
prerequisites for both your current class and your new one, as shown in
the Multiclassing Prerequisites table. For example, a barbarian who
decides to multiclass into the druid class must have both Strength and
Wisdom scores of 13 or higher. Without the full training that a
beginning character receives, you must be a quick study in your new
class, having a natural aptitude that is reflected by higher than
average ability scores.

\hypertarget{multiclassing-prerequisites}{%
\paragraph{Multiclassing
Prerequisites}\label{multiclassing-prerequisites}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Class & Ability Score Minimum\tabularnewline
\midrule
\endhead
Barbarian & Strength 13\tabularnewline
Bard & Charisma 13\tabularnewline
Cleric & Wisdom 13\tabularnewline
Druid & Wisdom 13\tabularnewline
Fighter & Strength 13 or Dexterity 13\tabularnewline
Monk & Dexterity 13 and Wisdom 13\tabularnewline
Paladin & Strength 13 and Charisma 13\tabularnewline
Ranger & Dexterity 13 and Wisdom 13\tabularnewline
Rogue & Dexterity 13\tabularnewline
Sorcerer & Charisma 13\tabularnewline
Warlock & Charisma 13\tabularnewline
Wizard & Intelligence 13\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{experience-points}{%
\subsubsection{Experience Points}\label{experience-points}}

The experience point cost to gain a level is always based on your total
character level, as shown in the Character Advancement table, not your
level in a particular class. So, if you are a cleric 6/fighter 1, you
must gain enough XP to reach 8th level before you can take your second
level as a fighter or your seventh level as a cleric.

\hypertarget{hit-points-and-hit-dice}{%
\subsubsection{Hit Points and Hit Dice}\label{hit-points-and-hit-dice}}

You gain the hit points from your new class as described for levels
after 1st. You gain the 1st level hit points for a class only when you
are a 1st level character. You add together the Hit Dice granted by all
your classes to form your pool of Hit Dice. If the Hit Dice are the same
die type, you can simply pool them together. For example, both the
fighter and the paladin have a d10, so if you are a paladin 5/fighter 5,
you have ten d10 Hit Dice. If your classes give you Hit Dice of
different types, keep track of them separately. If you are a paladin
5/cleric 5, for example, you have five d10 Hit Dice and five d8 Hit
Dice.

\hypertarget{proficiency-bonus}{%
\subsubsection{Proficiency Bonus}\label{proficiency-bonus}}

Your proficiency bonus is always based on your total character level, as
shown in the Character Advancement table, not your level in a particular
class. For example, if you are a fighter 3/rogue 2, you have the
proficiency bonus of a 5th level character, which is +3.

\hypertarget{proficiencies}{%
\subsubsection{Proficiencies}\label{proficiencies}}

When you gain your first level in a class other than your initial class,
you gain only some of new class's starting proficiencies, as shown in
the Multiclassing Proficiencies table.

\hypertarget{multiclassing-proficiencies}{%
\paragraph{Multiclassing
Proficiencies}\label{multiclassing-proficiencies}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Class & Proficiencies Gained\tabularnewline
\midrule
\endhead
Barbarian & Shields, simple weapons, martial weapons\tabularnewline
Bard & Light armor, one skill of your choice, one musical instrument of
your choice\tabularnewline
Cleric & Light armor, medium armor, shields\tabularnewline
Druid & Light armor, medium armor, shields (druids will not wear armor
or use shields made of metal)\tabularnewline
Fighter & Light armor, medium armor, shields, simple weapons, martial
weapons\tabularnewline
Monk & Simple weapons, shortswords\tabularnewline
Paladin & Light armor, medium armor, shields, simple weapons, martial
weapons\tabularnewline
Ranger & Light armor, medium armor, shields, simple weapons, martial
weapons, one skill from the class's skill list\tabularnewline
Rogue & Light armor, one skill from the class's skill list, thieves'
tools\tabularnewline
Sorcerer & ---\tabularnewline
Warlock & Light armor, simple weapons\tabularnewline
Wizard & ---\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{class-features}{%
\subsubsection{Class Features}\label{class-features}}

When you gain a new level in a class, you get its features for that
level. You don't, however, receive the class's starting equipment, and a
few features have additional rules when you're multiclassing: Channel
Divinity, Extra Attack, Unarmored Defense, and Spellcasting.

\hypertarget{channel-divinity}{%
\paragraph{Channel Divinity}\label{channel-divinity}}

If you already have the Channel Divinity feature and gain a level in a
class that also grants the feature, you gain the Channel Divinity
effects granted by that class, but getting the feature again doesn't
give you an additional use of it. You gain additional uses only when you
reach a class level that explicitly grants them to you. For example, if
you are a cleric 6/paladin 4, you can use Channel Divinity twice between
rests because you are high enough level in the cleric class to have more
uses. Whenever you use the feature, you can choose any of the Channel
Divinity effects available to you from your two classes.

\hypertarget{extra-attack}{%
\paragraph{Extra Attack}\label{extra-attack}}

If you gain the Extra Attack class feature from more than one class, the
features don't add together. You can't make more than two attacks with
this feature unless it says you do (as the fighter's version of Extra
Attack does). Similarly, the warlock's eldritch invocation Thirsting
Blade doesn't give you additional attacks if you also have Extra Attack.

\hypertarget{unarmored-defense}{%
\paragraph{Unarmored Defense}\label{unarmored-defense}}

If you already have the Unarmored Defense feature, you can't gain it
again from another class.

\hypertarget{spellcasting}{%
\paragraph{Spellcasting}\label{spellcasting}}

Your capacity for spellcasting depends partly on your combined levels in
all your spellcasting classes and partly on your individual levels in
those classes. Once you have the Spellcasting feature from more than one
class, use the rules below. If you multiclass but have the Spellcasting
feature from only one class, you follow the rules as described in that
class.

\textbf{Spells Known and Prepared.} You determine what spells you know
and can prepare for each class individually, as if you were a single
classed member of that class. If you are a ranger 4/wizard 3, for
example, you know three 1st level ranger spells based on your levels in
the ranger class. As 3rd level wizard, you know three wizard cantrips,
and your spellbook contains ten wizard spells, two of which (the two you
gained when you reached 3rd level as a wizard) can be 2nd level spells.
If your Intelligence is 16, you can prepare six wizard spells from your
spellbook.

Each spell you know and prepare is associated with one of your classes,
and you use the spellcasting ability of that class when you cast the
spell. Similarly, a spellcasting focus, such as a holy symbol, can be
used only for the spells from the class associated with that focus.

\textbf{Spell Slots.} You determine your available spell slots by adding
together all your levels in the bard, cleric, druid, sorcerer, and
wizard classes, and half your levels (rounded down) in the paladin and
ranger classes. Use this total to determine your spell slots by
consulting the Multiclass Spellcaster table.

If you have more than one spellcasting class, this table might give you
spell slots of a level that is higher than the spells you know or can
prepare. You can use those slots, but only to cast your lower level
spells. If a lower level spell that you cast, like \emph{burning hands},
has an enhanced effect when cast using a higher level slot, you can use
the enhanced effect, even though you don't have any spells of that
higher level.

For example, if you are the aforementioned ranger 4/wizard 3, you count
as a 5th level character when determining your spell slots: you have
four 1st level slots, three 2nd level slots, and two 3rd level slots.
However, you don't know any 3rd level spells, nor do you know any 2nd
level ranger spells. You can use the spell slots of those levels to cast
the spells you do know---and potentially enhance their effects.

\textbf{Pact Magic.} If you have both the Spellcasting class feature and
the Pact Magic class feature from the warlock class, you can use the
spell slots you gain from the Pact Magic feature to cast spells you know
or have prepared from classes with the Spellcasting class feature, and
you can use the spell slots you gain from the Spellcasting class feature
to cast warlock spells you know.

\hypertarget{multiclass-spellcaster-spell-slots-per-spell-level}{%
\paragraph{Multiclass Spellcaster: Spell Slots per Spell
Level}\label{multiclass-spellcaster-spell-slots-per-spell-level}}

\begin{longtable}[]{@{}llllllllll@{}}
\toprule
Lvl. & 1st & 2nd & 3rd & 4th & 5th & 6th & 7th & 8th &
9th\tabularnewline
\midrule
\endhead
1st & 2 & --- & --- & --- & --- & --- & --- & --- & ---\tabularnewline
2nd & 3 & --- & --- & --- & --- & --- & --- & --- & ---\tabularnewline
3rd & 4 & 2 & --- & --- & --- & --- & --- & --- & ---\tabularnewline
4th & 4 & 3 & --- & --- & --- & --- & --- & --- & ---\tabularnewline
5th & 4 & 3 & 2 & --- & --- & --- & --- & --- & ---\tabularnewline
6th & 4 & 3 & 3 & --- & --- & --- & --- & --- & ---\tabularnewline
7th & 4 & 3 & 3 & 1 & --- & --- & --- & --- & ---\tabularnewline
8th & 4 & 3 & 3 & 2 & --- & --- & --- & --- & ---\tabularnewline
9th & 4 & 3 & 3 & 3 & 1 & --- & --- & --- & ---\tabularnewline
10th & 4 & 3 & 3 & 3 & 2 & --- & --- & --- & ---\tabularnewline
11th & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- & ---\tabularnewline
12th & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- & ---\tabularnewline
13th & 4 & 3 & 3 & 3 & 2 & 1 & 1 & --- & ---\tabularnewline
14th & 4 & 3 & 3 & 3 & 2 & 1 & 1 & --- & ---\tabularnewline
15th & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & ---\tabularnewline
16th & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & ---\tabularnewline
17th & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1\tabularnewline
18th & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 & 1\tabularnewline
19th & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 1 & 1\tabularnewline
20th & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 1\tabularnewline
\bottomrule
\end{longtable}

\end{document}
