% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{equipment}{%
\section{Equipment}\label{equipment}}

Common coins come in several different denominations based on the
relative worth of the metal from which they are made. The three most
common coins are the gold piece (gp), the silver piece (sp), and the
copper piece (cp).

With one gold piece, a character can buy a bedroll, 50 feet of good
rope, or a goat. A skilled (but not exceptional) artisan can earn one
gold piece a day. The gold piece is the standard unit of measure for
wealth, even if the coin itself is not commonly used. When merchants
discuss deals that involve goods or services worth hundreds or thousands
of gold pieces, the transactions don't usually involve the exchange of
individual coins. Rather, the gold piece is a standard measure of value,
and the actual exchange is in gold bars, letters of credit, or valuable
goods.

One gold piece is worth ten silver pieces, the most prevalent coin among
commoners. A silver piece buys a laborer's work for half a day, a flask
of lamp oil, or a night's rest in a poor inn.

One silver piece is worth ten copper pieces, which are common among
laborers and beggars. A single copper piece buys a candle, a torch, or a
piece of chalk.

In addition, unusual coins made of other precious metals sometimes
appear in treasure hoards. The electrum piece (ep) and the platinum
piece (pp) originate from fallen empires and lost kingdoms, and they
sometimes arouse suspicion and skepticism when used in transactions. An
electrum piece is worth five silver pieces, and a platinum piece is
worth ten gold pieces.

A standard coin weighs about a third of an ounce, so fifty coins weigh a
pound.

\hypertarget{standard-exchange-rates}{%
\paragraph{Standard Exchange Rates}\label{standard-exchange-rates}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
Coin & CP & SP & EP & GP & PP\tabularnewline
\midrule
\endhead
Copper (cp) & 1 & 1/10 & 1/50 & 1/100 & 1/1,000\tabularnewline
Silver (sp) & 10 & 1 & ⅕ & 1/10 & 1/100\tabularnewline
Electrum (ep) & 50 & 5 & 1 & ½ & 1/20\tabularnewline
Gold (gp) & 100 & 10 & 2 & 1 & 1/10\tabularnewline
Platinum (pp) & 1,000 & 100 & 20 & 10 & 1\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{selling-treasure}{%
\subsection{Selling Treasure}\label{selling-treasure}}

Opportunities abound to find treasure, equipment, weapons, armor, and
more in the dungeons you explore. Normally, you can sell your treasures
and trinkets when you return to a town or other settlement, provided
that you can find buyers and merchants interested in your loot.

\textbf{Arms, Armor, and Other Equipment.} As a general rule, undamaged
weapons, armor, and other equipment fetch half their cost when sold in a
market. Weapons and armor used by monsters are rarely in good enough
condition to sell.

\textbf{Magic Items.} Selling magic items is problematic. Finding
someone to buy a potion or a scroll isn't too hard, but other items are
out of the realm of most but the wealthiest nobles. Likewise, aside from
a few common magic items, you won't normally come across magic items or
spells to purchase. The value of magic is far beyond simple gold and
should always be treated as such.

\textbf{Gems, Jewelry, and Art Objects.} These items retain their full
value in the marketplace, and you can either trade them in for coin or
use them as currency for other transactions. For exceptionally valuable
treasures, the GM might require you to find a buyer in a large town or
larger community first.

\textbf{Trade Goods.} On the borderlands, many people conduct
transactions through barter. Like gems and art objects, trade
goods-\/-\/-bars of iron, bags of salt, livestock, and so
on-\/-\/-retain their full value in the market and can be used as
currency.

\hypertarget{armor}{%
\subsection{Armor}\label{armor}}

Fantasy gaming worlds are a vast tapestry made up of many different
cultures, each with its own technology level. For this reason,
adventurers have access to a variety of armor types, ranging from
leather armor to chain mail to costly plate armor, with several other
kinds of armor in between. The Armor table collects the most commonly
available types of armor found in the game and separates them into three
categories: light armor, medium armor, and heavy armor. Many warriors
supplement their armor with a shield.

The Armor table shows the cost, weight, and other properties of the
common types of armor worn in fantasy gaming worlds.

\textbf{Armor Proficiency.} Anyone can put on a suit of armor or strap a
shield to an arm. Only those proficient in the armor's use know how to
wear it effectively, however. Your class gives you proficiency with
certain types of armor. If you wear armor that you lack proficiency
with, you have disadvantage on any ability check, saving throw, or
attack roll that involves Strength or Dexterity, and you can't cast
spells.

\textbf{Armor Class (AC).} Armor protects its wearer from attacks. The
armor (and shield) you wear determines your base Armor Class.

\textbf{Heavy Armor.} Heavier armor interferes with the wearer's ability
to move quickly, stealthily, and freely. If the Armor table shows ``Str
13'' or ``Str 15'' in the Strength column for an armor type, the armor
reduces the wearer's speed by 10 feet unless the wearer has a Strength
score equal to or higher than the listed score.

\textbf{Stealth.} If the Armor table shows ``Disadvantage'' in the
Stealth column, the wearer has disadvantage on Dexterity (Stealth)
checks.

\textbf{Shields.} A shield is made from wood or metal and is carried in
one hand. Wielding a shield increases your Armor Class by 2. You can
benefit from only one shield at a time.

\hypertarget{light-armor}{%
\subsubsection{Light Armor}\label{light-armor}}

Made from supple and thin materials, light armor favors agile
adventurers since it offers some protection without sacrificing
mobility. If you wear light armor, you add your Dexterity modifier to
the base number from your armor type to determine your Armor Class.

\textbf{Padded.} Padded armor consists of quilted layers of cloth and
batting.

\textbf{Leather.} The breastplate and shoulder protectors of this armor
are made of leather that has been stiffened by being boiled in oil. The
rest of the armor is made of softer and more flexible materials.

\textbf{Studded Leather.} Made from tough but flexible leather, studded
leather is reinforced with close-set rivets or spikes.

\hypertarget{medium-armor}{%
\subsubsection{Medium Armor}\label{medium-armor}}

Medium armor offers more protection than light armor, but it also
impairs movement more. If you wear medium armor, you add your Dexterity
modifier, to a maximum of +2, to the base number from your armor type to
determine your Armor Class.

\textbf{Hide.} This crude armor consists of thick furs and pelts. It is
commonly worn by barbarian tribes, evil humanoids, and other folk who
lack access to the tools and materials needed to create better armor.

\textbf{Chain Shirt.} Made of interlocking metal rings, a chain shirt is
worn between layers of clothing or leather. This armor offers modest
protection to the wearer's upper body and allows the sound of the rings
rubbing against one another to be muffled by outer layers.

\textbf{Scale Mail.} This armor consists of a coat and leggings (and
perhaps a separate skirt) of leather covered with overlapping pieces of
metal, much like the scales of a fish. The suit includes gauntlets.

\textbf{Breastplate.} This armor consists of a fitted metal chest piece
worn with supple leather. Although it leaves the legs and arms
relatively unprotected, this armor provides good protection for the
wearer's vital organs while leaving the wearer relatively unencumbered.

\textbf{Half Plate.} Half plate consists of shaped metal plates that
cover most of the wearer's body. It does not include leg protection
beyond simple greaves that are attached with leather straps.

\hypertarget{heavy-armor}{%
\subsubsection{Heavy Armor}\label{heavy-armor}}

Of all the armor categories, heavy armor offers the best protection.
These suits of armor cover the entire body and are designed to stop a
wide range of attacks. Only proficient warriors can manage their weight
and bulk.

Heavy armor doesn't let you add your Dexterity modifier to your Armor
Class, but it also doesn't penalize you if your Dexterity modifier is
negative.

\textbf{Ring Mail.} This armor is leather armor with heavy rings sewn
into it. The rings help reinforce the armor against blows from swords
and axes. Ring mail is inferior to chain mail, and it's usually worn
only by those who can't afford better armor.

\textbf{Chain Mail.} Made of interlocking metal rings, chain mail
includes a layer of quilted fabric worn underneath the mail to prevent
chafing and to cushion the impact of blows. The suit includes gauntlets.

\textbf{Splint.} This armor is made of narrow vertical strips of metal
riveted to a backing of leather that is worn over cloth padding.
Flexible chain mail protects the joints.

\textbf{Plate.} Plate consists of shaped, interlocking metal plates to
cover the entire body. A suit of plate includes gauntlets, heavy leather
boots, a visored helmet, and thick layers of padding underneath the
armor. Buckles and straps distribute the weight over the body.

\hypertarget{armor-1}{%
\paragraph{Armor}\label{armor-1}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
Armor & Cost & Armor Class (AC) & Strength & Stealth &
Weight\tabularnewline
\midrule
\endhead
Light Armor & & & & &\tabularnewline
Padded & 5 gp & 11 + Dex modifier & --- & Disadvantage & 8
lb.\tabularnewline
Leather & 10 gp & 11 + Dex modifier & --- & --- & 10 lb.\tabularnewline
Studded leather & 45 gp & 12 + Dex modifier & --- & --- & 13
lb.\tabularnewline
Medium Armor & & & & &\tabularnewline
Hide & 10 gp & 12 + Dex modifier (max 2) & --- & --- & 12
lb.\tabularnewline
Chain shirt & 50 gp & 13 + Dex modifier (max 2) & --- & --- & 20
lb.\tabularnewline
Scale mail & 50 gp & 14 + Dex modifier (max 2) & --- & Disadvantage & 45
lb.\tabularnewline
Breastplate & 400 gp & 14 + Dex modifier (max 2) & --- & --- & 20
lb.\tabularnewline
Half plate & 750 gp & 15 + Dex modifier (max 2) & --- & Disadvantage &
40 lb.\tabularnewline
Heavy Armor & & & & &\tabularnewline
Ring mail & 30 gp & 14 & --- & Disadvantage & 40 lb.\tabularnewline
Chain mail & 75 gp & 16 & Str 13 & Disadvantage & 55 lb.\tabularnewline
Splint & 200 gp & 17 & Str 15 & Disadvantage & 60 lb.\tabularnewline
Plate & 1,500 gp & 18 & Str 15 & Disadvantage & 65 lb.\tabularnewline
Shield & & & & &\tabularnewline
Shield & 10 gp & +2 & --- & --- & 6 lb.\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{getting-into-and-out-of-armor}{%
\subsubsection{Getting Into and Out of
Armor}\label{getting-into-and-out-of-armor}}

The time it takes to don or doff armor depends on the armor's category.

\textbf{Don.} This is the time it takes to put on armor. You benefit
from the armor's AC only if you take the full time to don the suit of
armor.

\textbf{Doff.} This is the time it takes to take off armor. If you have
help, reduce this time by half.

\hypertarget{donning-and-doffing-armor}{%
\paragraph{Donning and Doffing Armor}\label{donning-and-doffing-armor}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Category & Don & Doff\tabularnewline
\midrule
\endhead
Light Armor & 1 minute & 1 minute\tabularnewline
Medium Armor & 5 minutes & 1 minute\tabularnewline
Heavy Armor & 10 minutes & 5 minutes\tabularnewline
Shield & 1 action & 1 action\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{weapons}{%
\subsection{Weapons}\label{weapons}}

Your class grants proficiency in certain weapons, reflecting both the
class's focus and the tools you are most likely to use. Whether you
favor a longsword or a longbow, your weapon and your ability to wield it
effectively can mean the difference between life and death while
adventuring.

The Weapons table shows the most common weapons used in the fantasy
gaming worlds, their price and weight, the damage they deal when they
hit, and any special properties they possess. Every weapon is classified
as either melee or ranged. A \textbf{melee weapon} is used to attack a
target within 5 feet of you, whereas a \textbf{ranged weapon} is used to
attack a target at a distance.

\hypertarget{weapon-proficiency}{%
\subsubsection{Weapon Proficiency}\label{weapon-proficiency}}

Your race, class, and feats can grant you proficiency with certain
weapons or categories of weapons. The two categories are simple and
martial. Most people can use simple weapons with proficiency. These
weapons include clubs, maces, and other weapons often found in the hands
of commoners. Martial weapons, including swords, axes, and polearms,
require more specialized training to use effectively. Most warriors use
martial weapons because these weapons put their fighting style and
training to best use.

Proficiency with a weapon allows you to add your proficiency bonus to
the attack roll for any attack you make with that weapon. If you make an
attack roll using a weapon with which you lack proficiency, you do not
add your proficiency bonus to the attack roll.

\hypertarget{weapon-properties}{%
\subsubsection{Weapon Properties}\label{weapon-properties}}

Many weapons have special properties related to their use, as shown in
the Weapons table.

\textbf{Ammunition.} You can use a weapon that has the ammunition
property to make a ranged attack only if you have ammunition to fire
from the weapon. Each time you attack with the weapon, you expend one
piece of ammunition. Drawing the ammunition from a quiver, case, or
other container is part of the attack (you need a free hand to load a
one-handed weapon). At the end of the battle, you can recover half your
expended ammunition by taking a minute to search the battlefield.

If you use a weapon that has the ammunition property to make a melee
attack, you treat the weapon as an improvised weapon (see "Improvised
Weapons" later in the section). A sling must be loaded to deal any
damage when used in this way.

\textbf{Finesse.} When making an attack with a finesse weapon, you use
your choice of your Strength or Dexterity modifier for the attack and
damage rolls. You must use the same modifier for both rolls.

\textbf{Heavy.} Small creatures have disadvantage on attack rolls with
heavy weapons. A heavy weapon's size and bulk make it too large for a
Small creature to use effectively.

\textbf{Light.} A light weapon is small and easy to handle, making it
ideal for use when fighting with two weapons.

\textbf{Loading.} Because of the time required to load this weapon, you
can fire only one piece of ammunition from it when you use an action,
bonus action, or reaction to fire it, regardless of the number of
attacks you can normally make.

\textbf{Range.} A weapon that can be used to make a ranged attack has a
range in parentheses after the ammunition or thrown property. The range
lists two numbers. The first is the weapon's normal range in feet, and
the second indicates the weapon's long range. When attacking a target
beyond normal range, you have disadvantage on the attack roll. You can't
attack a target beyond the weapon's long range.

\textbf{Reach.} This weapon adds 5 feet to your reach when you attack
with it, as well as when determining your reach for opportunity attacks
with it.

\textbf{Special.} A weapon with the special property has unusual rules
governing its use, explained in the weapon's description (see ``Special
Weapons'' later in this section).

\textbf{Thrown.} If a weapon has the thrown property, you can throw the
weapon to make a ranged attack. If the weapon is a melee weapon, you use
the same ability modifier for that attack roll and damage roll that you
would use for a melee attack with the weapon. For example, if you throw
a handaxe, you use your Strength, but if you throw a dagger, you can use
either your Strength or your Dexterity, since the dagger has the finesse
property. Two-Handed. This weapon requires two hands when you attack
with it.

\textbf{Versatile.} This weapon can be used with one or two hands. A
damage value in parentheses appears with the property---the damage when
the weapon is used with two hands to make a melee attack.

\hypertarget{improvised-weapons}{%
\paragraph{Improvised Weapons}\label{improvised-weapons}}

Sometimes characters don't have their weapons and have to attack with
whatever is at hand. An improvised weapon includes any object you can
wield in one or two hands, such as broken glass, a table leg, a frying
pan, a wagon wheel, or a dead goblin.

Often, an improvised weapon is similar to an actual weapon and can be
treated as such. For example, a table leg is akin to a club. At the GM's
option, a character proficient with a weapon can use a similar object as
if it were that weapon and use his or her proficiency bonus.

An object that bears no resemblance to a weapon deals 1d4 damage (the GM
assigns a damage type appropriate to the object). If a character uses a
ranged weapon to make a melee attack, or throws a melee weapon that does
not have the thrown property, it also deals 1d4 damage. An improvised
thrown weapon has a normal range of 20 feet and a long range of 60 feet.

\hypertarget{silvered-weapons}{%
\paragraph{Silvered Weapons}\label{silvered-weapons}}

Some monsters that have immunity or resistance to nonmagical weapons are
susceptible to silver weapons, so cautious adventurers invest extra coin
to plate their weapons with silver. You can silver a single weapon or
ten pieces of ammunition for 100 gp. This cost represents not only the
price of the silver, but the time and expertise needed to add silver to
the weapon without making it less effective.

\hypertarget{special-weapons}{%
\paragraph{Special Weapons}\label{special-weapons}}

Weapons with special rules are described here.

\textbf{Lance.} You have disadvantage when you use a lance to attack a
target within 5 feet of you. Also, a lance requires two hands to wield
when you aren't mounted.

\textbf{Net.} A Large or smaller creature hit by a net is restrained
until it is freed. A net has no effect on creatures that are formless,
or creatures that are Huge or larger. A creature can use its action to
make a DC 10 Strength check, freeing itself or another creature within
its reach on a success. Dealing 5 slashing damage to the net (AC 10)
also frees the creature without harming it, ending the effect and
destroying the net.

When you use an action, bonus action, or reaction to attack with a net,
you can make only one attack regardless of the number of attacks you can
normally make.

\hypertarget{weapons-1}{%
\paragraph{Weapons}\label{weapons-1}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Name & Cost & Damage & Weight & Properties\tabularnewline
\midrule
\endhead
Simple Melee Weapons & & & &\tabularnewline
Club & 1~sp & 1d4~bludgeoning & 2 ~lb. & Light\tabularnewline
Dagger & 2~gp & 1d4~piercing & 1~lb. & Finesse, light, thrown (range
20/60)\tabularnewline
Greatclub & 2~sp & 1d8~bludgeoning & 10~lb. & Two-handed\tabularnewline
Handaxe & 5~gp & 1d6~slashing & 2~lb. & Light, thrown (range
20/60)\tabularnewline
Javelin & 5~sp & 1d6~piercing & 2~lb. & Thrown (range
30/120)\tabularnewline
Light hammer & 2~gp & 1d4~bludgeoning & 2~lb. & Light, thrown (range
20/60)\tabularnewline
Mace & 5~gp & 1d6~bludgeoning & 4~lb. & ---\tabularnewline
Quarterstaff & 2~sp & 1d6~bludgeoning & 4~lb. & Versatile
(1d8)\tabularnewline
Sickle & 1~gp & 1d4~slashing & 2~lb. & Light\tabularnewline
Spear & 1~gp & 1d6~piercing & 3~lb. & Thrown (range 20/60), versatile
(1d8)\tabularnewline
Simple Ranged Weapons & & & &\tabularnewline
Crossbow, light & 25~gp & 1d8~piercing & 5~lb. & Ammunition (range
80/320), loading, two-handed\tabularnewline
Dart & 5~cp & 1d4~piercing & ¼~lb. & Finesse, thrown (range
20/60)\tabularnewline
Shortbow & 25~gp & 1d6~piercing & 2~lb. & Ammunition (range 80/320),
two-handed\tabularnewline
Sling & 1~sp & 1d4~bludgeoning & --- & Ammunition (range
30/120)\tabularnewline
Martial Melee Weapons & & & &\tabularnewline
Battleaxe & 10~gp & 1d8~slashing & 2~lb. & Versatile
(1d10)\tabularnewline
Flail & 10~gp & 1d8~bludgeoning & 2~lb. & ---\tabularnewline
Glaive & 20~gp & 1d10~slashing & 6~lb. & Heavy, reach,
two-handed\tabularnewline
Greataxe & 30~gp & 1d12~slashing & 7~lb. & Heavy,
two-handed\tabularnewline
Greatsword & 50~gp & 2d6~slashing & 6~lb. & Heavy,
two-handed\tabularnewline
Halberd & 20~gp & 1d10~slashing & 6~lb. & Heavy, reach,
two-handed\tabularnewline
Lance & 10~gp & 1d12~piercing & 6~lb. & Reach, special\tabularnewline
Longsword & 15~gp & 1d8~slashing & 3~lb. & Versatile
(1d10)\tabularnewline
Maul & 10~gp & 2d6~bludgeoning & 10~lb. & Heavy,
two-handed\tabularnewline
Morningstar & 15~gp & 1d8~piercing & 4~lb. & ---\tabularnewline
Pike & 5~gp & 1d10~piercing & 18~lb. & heavy, reach,
two-handed\tabularnewline
Rapier & 25~gp & 1d8~piercing & 2~lb. & Finesse\tabularnewline
Scimitar & 25~gp & 1d6~slashing & 3~lb. & Finesse, light\tabularnewline
Shortsword & 10~gp & 1d6~piercing & 2~lb. & Finesse,
light\tabularnewline
Trident & 5~gp & 1d6~piercing & 4~lb. & Thrown (range 20/60), versatile
(1d8)\tabularnewline
Martial Ranged Weapons & & & &\tabularnewline
Blowgun & 10~gp & 1~piercing & 1~lb. & Ammunition (range25/10),
loading\tabularnewline
Crossbow, hand & 75~gp & 1d6~piercing & 3~lb. & Ammunition (range
30/120), light, loading\tabularnewline
Crossbow, heavy & 50~gp & 1d10~piercing & 18~lb. & Ammunition (range
100/400), heavy, loading, two-handed\tabularnewline
Net & 1~gp & --- & 3~lb. & Special, thrown (range 5/15)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{adventuring-gear}{%
\subsection{Adventuring Gear}\label{adventuring-gear}}

This section describes items that have special rules or require further
explanation.

\textbf{Acid.} As an action, you can splash the contents of this vial
onto a creature within 5 feet of you or throw the vial up to 20 feet,
shattering it on impact. In either case, make a ranged attack against a
creature or object, treating the acid as an improvised weapon. On a hit,
the target takes 2d6 acid damage.

\textbf{Alchemist's Fire.} This sticky, adhesive fluid ignites when
exposed to air. As an action, you can throw this flask up to 20 feet,
shattering it on impact. Make a ranged attack against a creature or
object, treating the alchemist's fire as an improvised weapon. On a hit,
the target takes 1d4 fire damage at the start of each of its turns. A
creature can end this damage by using its action to make a DC 10
Dexterity check to extinguish the flames.

\textbf{Antitoxin.} A creature that drinks this vial of liquid gains
advantage on saving throws against poison for 1 hour. It confers no
benefit to undead or constructs.

\textbf{Arcane Focus.} An arcane focus is a special item-\/-\/-an orb, a
crystal, a rod, a specially constructed staff, a wand like length of
wood, or some similar item-\/-\/-designed to channel the power of arcane
spells. A sorcerer, warlock, or wizard can use such an item as a
spellcasting focus.

\textbf{Ball Bearings.} As an action, you can spill these tiny metal
balls from their pouch to cover a level, square area that is 10 feet on
a side. A creature moving across the covered area must succeed on a DC
10 Dexterity saving throw or fall prone. A creature moving through the
area at half speed doesn't need to make the save.

\textbf{Block and Tackle.} A set of pulleys with a cable threaded
through them and a hook to attach to objects, a block and tackle allows
you to hoist up to four times the weight you can normally lift.

\textbf{Book.} A book might contain poetry, historical accounts,
information pertaining to a particular field of lore, diagrams and notes
on gnomish contraptions, or just about anything else that can be
represented using text or pictures. A book of spells is a spellbook
(described later in this section).

\textbf{Caltrops.} As an action, you can spread a bag of caltrops to
cover a square area that is 5 feet on a side. Any creature that enters
the area must succeed on a DC 15 Dexterity saving throw or stop moving
this turn and take 1 piercing damage. Taking this damage reduces the
creature's walking speed by 10 feet until the creature regains at least
1 hit point. A creature moving through the area at half speed doesn't
need to make the save.

\textbf{Candle.} For 1 hour, a candle sheds bright light in a 5 foot
radius and dim light for an additional 5 feet.

\textbf{Case, Crossbow Bolt.} This wooden case can holdup to twenty
crossbow bolts.

\textbf{Case, Map or Scroll.} This cylindrical leather case can hold up
to ten rolled up sheets of paper or five rolled up sheets of parchment.

\textbf{Chain.} A chain has 10 hit points. It can be burst with a
successful DC 20 Strength check.

\textbf{Climber's Kit.} A climber's kit includes special pitons, boot
tips, gloves, and a harness. You can use the climber's kit as an action
to anchor yourself; when you do, you can't fall more than 25 feet from
the point where you anchored yourself, and you can't climb more than 25
feet away from that point without undoing the anchor.

\textbf{Component Pouch.} A component pouch is a small, watertight
leather belt pouch that has compartments to hold all the material
components and other special items you need to cast your spells, except
for those components that have a specific cost (as indicated in a
spell's description).

\textbf{Crowbar.} Using a crowbar grants advantage to Strength checks
where the crowbar's leverage can be applied.

\textbf{Druidic Focus.} A druidic focus might be a sprig of mistletoe or
holly, a wand or scepter made of yew or another special wood, a staff
drawn whole out of a living tree, or a totem object incorporating
feathers, fur, bones, and teeth from sacred animals. A druid can use
such an object as a spellcasting focus.

\textbf{Fishing Tackle.} This kit includes a wooden rod, silken line,
corkwood bobbers, steel hooks, lead sinkers, velvet lures, and narrow
netting.

\textbf{Healer's Kit.} This kit is a leather pouch containing bandages,
salves, and splints. The kit has ten uses. As an action, you can expend
one use of the kit to stabilize a creature that has 0 hit points,
without needing to make a Wisdom (Medicine) check.

\textbf{Holy Symbol.} A holy symbol is a representation of a god or
pantheon. It might be an amulet depicting a symbol representing a deity,
the same symbol carefully engraved or inlaid as an emblem on a shield,
or a tiny box holding a fragment of a sacred relic. Appendix PH B
"Fantasy Historical Pantheons" lists the symbols commonly associated
with many gods in the multiverse. A cleric or paladin can use a holy
symbol as a spellcasting focus. To use the symbol in this way, the
caster must hold it in hand, wear it visibly, or bear it on a shield.

\textbf{Holy Water.} As an action, you can splash the contents of this
flask onto a creature within 5 feet of you or throw it up to 20 feet,
shattering it on impact. In either case, make a ranged attack against a
target creature, treating the holy water as an improvised weapon. If the
target is a fiend or undead, it takes 2d6 radiant damage.

A cleric or paladin may create holy water by performing a special
ritual. The ritual takes 1 hour to perform, uses 25 gp worth of powdered
silver, and requires the caster to expend a 1st level spell slot.

\textbf{Hunting Trap.} When you use your action to set it, this trap
forms a saw toothed steel ring that snaps shut when a creature steps on
a pressure plate in the center. The trap is affixed by a heavy chain to
an immobile object, such as a tree or a spike driven into the ground. A
creature that steps on the plate must succeed on a DC 13 Dexterity
saving throw or take 1d4 piercing damage and stop moving. Thereafter,
until the creature breaks free of the trap, its movement is limited by
the length of the chain (typically 3 feet long). A creature can use its
action to make a DC 13 Strength check, freeing itself or another
creature within its reach on a success. Each failed check deals 1
piercing damage to the trapped creature.

\textbf{Lamp.} A lamp casts bright light in a 15 foot radius and dim
light for an additional 30 feet. Once lit, it burns for 6 hours on a
flask (1 pint) of oil.

\textbf{Lantern, Bullseye.} A bullseye lantern casts bright light in a
60 foot cone and dim light for an additional 60 feet. Once lit, it burns
for 6 hours on a flask (1 pint) of oil.

\textbf{Lantern, Hooded.} A hooded lantern casts bright light in a 30
foot radius and dim light for an additional 30 feet. Once lit, it burns
for 6 hours on a flask (1 pint) of oil. As an action, you can lower the
hood, reducing the light to dim light in a 5 foot radius.

\textbf{Lock.} A key is provided with the lock. Without the key, a
creature proficient with thieves' tools can pick this lock with a
successful DC 15 Dexterity check. Your GM may decide that better locks
are available for higher prices.

\textbf{Magnifying Glass.} This lens allows a closer look at small
objects. It is also useful as a substitute for flint and steel when
starting fires. Lighting a fire with a magnifying glass requires light
as bright as sunlight to focus, tinder to ignite, and about 5 minutes
for the fire to ignite. A magnifying glass grants advantage on any
ability check made to appraise or inspect an item that is small or
highly detailed.

\textbf{Manacles.} These metal restraints can bind a Small or Medium
creature. Escaping the manacles requires a successful DC 20 Dexterity
check. Breaking them requires a successful DC 20 Strength check. Each
set of manacles comes with one key. Without the key, a creature
proficient with thieves' tools can pick the manacles' lock with a
successful DC 15 Dexterity check. Manacles have 15 hit points.

\textbf{Mess Kit.} This tin box contains a cup and simple cutlery. The
box clamps together, and one side can be used as a cooking pan and the
other as a plate or shallow bowl.

\textbf{Oil.} Oil usually comes in a clay flask that holds 1 pint. As an
action, you can splash the oil in this flask onto a creature within 5
feet of you or throw it up to 20 feet, shattering it on impact. Make a
ranged attack against a target creature or object, treating the oil as
an improvised weapon. On a hit, the target is covered in oil. If the
target takes any fire damage before the oil dries (after 1 minute), the
target takes an additional 5 fire damage from the burning oil. You can
also pour a flask of oil on the ground to cover a 5 foot square area,
provided that the surface is level. If lit, the oil burns for 2 rounds
and deals 5 fire damage to any creature that enters the area or ends its
turn in the area. A creature can take this damage only once per turn.

\textbf{Poison, Basic.} You can use the poison in this vial to coat one
slashing or piercing weapon or up to three pieces of ammunition.
Applying the poison takes an action. A creature hit by the poisoned
weapon or ammunition must make a DC 10 Constitution saving throw or take
1d4 poison damage. Once applied, the poison retains potency for 1 minute
before drying.

\textbf{Potion of Healing.} A character who drinks the magical red fluid
in this vial regains 2d4 + 2 hit points. Drinking or administering a
potion takes an action.

\textbf{Pouch.} A cloth or leather pouch can hold up to 20 sling bullets
or 50 blowgun needles, among other things. A compartmentalized pouch for
holding spell components is called a component pouch (described earlier
in this section).

\textbf{Quiver.} A quiver can hold up to 20 arrows.

\textbf{Ram, Portable.} You can use a portable ram to break down doors.
When doing so, you gain a +4 bonus on the Strength check. One other
character can help you use the ram, giving you advantage on this check.

\textbf{Rations.} Rations consist of dry foods suitable for extended
travel, including jerky, dried fruit, hardtack, and nuts.

\textbf{Rope.} Rope, whether made of hemp or silk, has 2 hit points and
can be burst with a DC 17 Strength check.

\textbf{Scale, Merchant's.} A scale includes a small balance, pans, and
a suitable assortment of weights up to 2 pounds. With it, you can
measure the exact weight of small objects, such as raw precious metals
or trade goods, to help determine their worth.

\textbf{Spellbook.} Essential for wizards, a spellbook is a leather
bound tome with 100 blank vellum pages suitable for recording spells.

\textbf{Spyglass.} Objects viewed through a spyglass are magnified to
twice their size.

\textbf{Tent.} A simple and portable canvas shelter, a tent sleeps two.

\textbf{Tinderbox.} This small container holds flint, fire steel, and
tinder (usually dry cloth soaked in light oil) used to kindle a fire.
Using it to light a torch---or anything else with abundant, exposed
fuel---takes an action. Lighting any other fire takes 1 minute.

\textbf{Torch.} A torch burns for 1 hour, providing bright light in a 20
foot radius and dim light for an additional 20 feet. If you make a melee
attack with a burning torch and hit, it deals 1 fire damage.

\hypertarget{adventuring-gear-1}{%
\paragraph{Adventuring Gear}\label{adventuring-gear-1}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Item & Cost & Weight\tabularnewline
\midrule
\endhead
Abacus & 2 gp & 2 lb.\tabularnewline
Acid (vial) & 25 gp & 1 lb.\tabularnewline
Alchemist's fire (flask) & 50 gp & 1 lb.\tabularnewline
Ammunition & &\tabularnewline
Arrows (20) & 1 gp & 1 lb.\tabularnewline
Blowgun needles (50) & 1 gp & 1 lb.\tabularnewline
Crossbow bolts (20) & 1 gp & 1 ½ lb.\tabularnewline
Sling bullets (20) & 4 cp & 1 ½ lb.\tabularnewline
Antitoxin (vial) & 50 gp & ---\tabularnewline
Arcane Focus & &\tabularnewline
Crystal & 10 gp & 1 lb.\tabularnewline
Orb & 20 gp & 3 lb.\tabularnewline
Rod & 10 gp & 2 lb.\tabularnewline
Staff & 5 gp & 4 lb.\tabularnewline
Wand & 10 gp & 1 lb.\tabularnewline
Backpack & 2 gp & 5 lb.\tabularnewline
Ball bearings (bag of 1,000) & 1 gp & 2 lb.\tabularnewline
Barrel & 2 gp & 70 lb.\tabularnewline
Basket & 4 sp & 2 lb.\tabularnewline
Bedroll & 1 gp & 7 lb.\tabularnewline
Bell & 1 gp & ---\tabularnewline
Blanket & 5 sp & 3 lb.\tabularnewline
Block and tackle & 1 gp & 5 lb.\tabularnewline
Book & 25 gp & 5 lb.\tabularnewline
Bottle, glass & 2 gp & 2 lb.\tabularnewline
Bucket & 5 cp & 2 lb.\tabularnewline
Caltrops (bag of 20) & 1 gp & 2 lb.\tabularnewline
Candle & 1 cp & ---\tabularnewline
Case, crossbow bolt & 1 gp & 1 lb.\tabularnewline
Case, map or scroll & 1 gp & 1 lb.\tabularnewline
Chain (10 feet) & 5 gp & 10 lb.\tabularnewline
Chalk (1 piece) & 1 cp & ---\tabularnewline
Chest & 5 gp & 25 lb.\tabularnewline
Climber's kit & 25 gp & 12 lb.\tabularnewline
Clothes, common & 5 sp & 3 lb.\tabularnewline
Clothes, costume & 5 gp & 4 lb.\tabularnewline
Clothes, fine & 15 gp & 6 lb.\tabularnewline
Clothes, traveler's & 2 gp & 4 lb.\tabularnewline
Component pouch & 25 gp & 2 lb.\tabularnewline
Crowbar & 2 gp & 5 lb.\tabularnewline
Druidic Focus & &\tabularnewline
Sprig of mistletoe & 1 gp & ---\tabularnewline
Totem & 1 gp & ---\tabularnewline
Wooden staff & 5 gp & 4 lb.\tabularnewline
Yew wand & 10 gp & 1 lb.\tabularnewline
Fishing tackle & 1 gp & 4 lb.\tabularnewline
Flask or tankard & 2 cp & 1 lb.\tabularnewline
Grappling hook & 2 gp & 4 lb.\tabularnewline
Hammer & 1 gp & 3 lb.\tabularnewline
Hammer, sledge & 2 gp & 10 lb.\tabularnewline
Healer's kit & 5 gp & 3 lb.\tabularnewline
Holy Symbol & &\tabularnewline
Amulet & 5 gp & 1 lb.\tabularnewline
Emblem & 5 gp & ---\tabularnewline
Reliquary & 5 gp & 2 lb.\tabularnewline
Holy water (flask) & 25 gp & 1 lb.\tabularnewline
Hourglass & 25 gp & 1 lb.\tabularnewline
Hunting trap & 5 gp & 25 lb.\tabularnewline
Ink (1 ounce bottle) & 10 gp & ---\tabularnewline
Ink pen & 2 cp & ---\tabularnewline
Jug or pitcher & 2 cp & 4 lb.\tabularnewline
Ladder (10-foot) & 1 sp & 25 lb.\tabularnewline
Lamp & 5 sp & 1 lb.\tabularnewline
Lantern, bullseye & 10 gp & 2 lb.\tabularnewline
Lantern, hooded & 5 gp & 1 lb.\tabularnewline
Lock & 10 gp & 1 lb.\tabularnewline
Magnifying glass & 100 gp & ---\tabularnewline
Manacles & 2 gp & 6 lb.\tabularnewline
Mess kit & 2 sp & 1 lb.\tabularnewline
Mirror, steel & 5 gp & ½ lb.\tabularnewline
Oil (flask) & 1 sp & 1 lb.\tabularnewline
Paper (one sheet) & 2 sp & ---\tabularnewline
Parchment (one sheet) & 1 sp & ---\tabularnewline
Perfume (vial) & 5 gp & ---\tabularnewline
Pick, miner's & 2 gp & 10 lb.\tabularnewline
Piton & 5 cp & ¼ lb.\tabularnewline
poison, basic (vial) & 100 gp & ---\tabularnewline
Pole (10-foot) & 5 cp & 7 lb.\tabularnewline
Pot, iron & 2 gp & 10 lb.\tabularnewline
Potion of healing & 50 gp & ½ lb.\tabularnewline
Pouch & 5 sp & 1 lb.\tabularnewline
Quiver & 1 gp & 1 lb.\tabularnewline
Ram, portable & 4 gp & 35 lb.\tabularnewline
Rations (1 day) & 5 sp & 2 lb.\tabularnewline
Robes & 1 gp & 4 lb.\tabularnewline
Rope, hempen (50 feet) & 1 gp & 10 lb.\tabularnewline
Rope, silk (50 feet) & 10 gp & 5 lb.\tabularnewline
Sack & 1 cp & ½ lb.\tabularnewline
Scale, merchant's & 5 gp & 3 lb.\tabularnewline
Sealing wax & 5 sp & ---\tabularnewline
Shovel & 2 gp & 5 lb.\tabularnewline
Signal whistle & 5 cp & ---\tabularnewline
Signet ring & 5 gp & ---\tabularnewline
Soap & 2 cp & ---\tabularnewline
Spellbook & 50 gp & 3 lb.\tabularnewline
Spikes, iron (10) & 1 gp & 5 lb.\tabularnewline
Spyglass & 1,000 gp & 1 lb.\tabularnewline
Tent, two-person & 2 gp & 20 lb.\tabularnewline
Tinderbox & 5 sp & 1 lb.\tabularnewline
Torch & 1 cp & 1 lb.\tabularnewline
Vial & 1 gp & ---\tabularnewline
Waterskin & 2 sp & 5 lb. (full)\tabularnewline
Whetstone & 1 cp & 1 lb.\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{container-capacit}{%
\paragraph{Container Capacit}\label{container-capacit}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Container & Capacity\tabularnewline
\midrule
\endhead
Backpack* & 1 cubic foot/30 pounds of gear\tabularnewline
Barrel & 40 gallons liquid, 4 cubic feet solid\tabularnewline
Basket & 2 cubic feet/40 pounds of gear\tabularnewline
Bottle & 1½ pints liquid\tabularnewline
Bucket & 3 gallons liquid, ½ cubic foot solid\tabularnewline
Chest & 12 cubic feet/300 pounds of gear\tabularnewline
Flask or tankard & 1 pint liquid\tabularnewline
Jug or pitcher & 1 gallon liquid\tabularnewline
Pot, iron & 1 gallon liquid\tabularnewline
Pouch & ⅕ cubic foot/6 pounds of gear\tabularnewline
Sack & 1 cubic foot/30 pounds of gear\tabularnewline
Vial & 4 ounces liquid\tabularnewline
Waterskin & 4 pints liquid\tabularnewline
* You can also strap items, such as a bedroll or a coil of rope, to the
outside of a backpack. &\tabularnewline
\bottomrule
\end{longtable}

\begin{quote}
\hypertarget{equipment-packs}{%
\subsubsection{Equipment Packs}\label{equipment-packs}}

The starting equipment you get from your class includes a collection of
useful adventuring gear, put together in a pack. The contents of these
packs are listed here. If you are buying your starting equipment, you
can purchase a pack for the price shown, which might be cheaper than
buying the items individually.

\textbf{Burglar's Pack (16 gp).} Includes a backpack, a bag of 1,000
ball bearings, 10 feet of string, a bell, 5 candles, a crowbar, a
hammer, 10 pitons, a hooded lantern, 2 flasks of oil, 5 days rations, a
tinderbox, and a waterskin. The pack also has 50 feet of hempen rope
strapped to the side of it.

\textbf{Diplomat's Pack (39 gp).} Includes a chest, 2 cases for maps and
scrolls, a set of fine clothes, a bottle of ink, an ink pen, a lamp, 2
flasks of oil, 5 sheets of paper, a vial of perfume, sealing wax, and
soap.

\textbf{Dungeoneer's Pack (12 gp).} Includes a backpack, a crowbar, a
hammer, 10 pitons, 10 torches, a tinderbox, 10 days of rations, and a
waterskin. The pack also has 50 feet of hempen rope strapped to the side
of it.

\textbf{Entertainer's Pack (40 gp).} Includes a backpack, a bedroll, 2
costumes, 5 candles, 5 days of rations, a waterskin, and a disguise kit.

\textbf{Explorer's Pack (10 gp).} Includes a backpack, a bedroll, a mess
kit, a tinderbox, 10 torches, 10 days of rations, and a waterskin. The
pack also has 50 feet of hempen rope strapped to the side of it.

\textbf{Priest's Pack (19 gp).} Includes a backpack, a blanket, 10
candles, a tinderbox, an alms box, 2 blocks of incense, a censer,
vestments, 2 days of rations, and a waterskin.

\textbf{Scholar's Pack (40 gp).} Includes a backpack, a book of lore, a
bottle of ink, an ink pen, 10 sheets of parchment, a little bag of sand,
and a small knife.
\end{quote}

\hypertarget{tools}{%
\subsection{Tools}\label{tools}}

A tool helps you to do something you couldn't otherwise do, such as
craft or repair an item, forge a document, or pick a lock. Your race,
class, background, or feats give you proficiency with certain tools.
Proficiency with a tool allows you to add your proficiency bonus to any
ability check you make using that tool. Tool use is not tied to a single
ability, since proficiency with a tool represents broader knowledge of
its use. For example, the GM might ask you to make a Dexterity check to
carve a fine detail with your woodcarver's tools, or a Strength check to
make something out of particularly hard wood.

\hypertarget{tools-1}{%
\paragraph{Tools}\label{tools-1}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Item & Cost & Weight\tabularnewline
\midrule
\endhead
Artisan's tools & &\tabularnewline
Alchemist's supplies & 50 gp & 8 lb.\tabularnewline
Brewer's supplies & 20 gp & 9 lb.\tabularnewline
Calligrapher's supplies & 10 gp & 5 lb.\tabularnewline
Carpenter's tools & 8 gp & 6 lb.\tabularnewline
Cartographer's tools & 15 gp & 6 lb.\tabularnewline
Cobbler's tools & 5 gp & 5 lb.\tabularnewline
Cook's utensils & 1 gp & 8 lb.\tabularnewline
Glassblower's tools & 30 gp & 5 lb.\tabularnewline
Jeweler's tools & 25 gp & 2 lb.\tabularnewline
Leatherworker's tools & 5 gp & 5 lb.\tabularnewline
Mason's tools & 10 gp & 8 lb.\tabularnewline
Painter's supplies & 10 gp & 5 lb.\tabularnewline
Potter's tools & 10 gp & 3 lb.\tabularnewline
Smith's tools & 20 gp & 8lb.\tabularnewline
Tinker's tools & 50 gp & 10 lb.\tabularnewline
Weaver's tools & 1 gp & 5 lb.\tabularnewline
Woodcarver's tools & 1 gp & 5 lb.\tabularnewline
Disguise kit & 25 gp & 3 lb.\tabularnewline
Forgery kit & 15 gp & 5 lb.\tabularnewline
Gaming set & &\tabularnewline
Dice set & 1 sp & ---\tabularnewline
Playing card set & 5 sp & ---\tabularnewline
Herbalism kit & 5 gp & 3 lb.\tabularnewline
Musical instrument & &\tabularnewline
Bagpipes & 30 gp & 6 lb.\tabularnewline
Drum & 6 gp & 3 lb.\tabularnewline
Dulcimer & 25 gp & 10 lb.\tabularnewline
Flute & 2 gp & 1 lb.\tabularnewline
Lute & 35 gp & 2 lb.\tabularnewline
Lyre & 30 go & 2 lb.\tabularnewline
Horn & 3 gp & 2 lb.\tabularnewline
Pan flute & 12 gp & 2 lb.\tabularnewline
Shawm & 2 gp & 1 lb.\tabularnewline
Viol & 30 gp & 1 lb.\tabularnewline
Navigator's tools & 25 gp & 2 lb.\tabularnewline
Poisoner's kit & 50 gp & 2 lb.\tabularnewline
Thieves' tools & 25 gp & 1 lb.\tabularnewline
Vehicles (land or water) & * & *\tabularnewline
* See the ``Mounts and Vehicles'' section. & &\tabularnewline
\bottomrule
\end{longtable}

\textbf{Artisan's Tools.} These special tools include the items needed
to pursue a craft or trade. The table shows examples of the most common
types of tools, each providing items related to a single craft.
Proficiency with a set of artisan's tools lets you add your proficiency
bonus to any ability checks you make using the tools in your craft. Each
type of artisan's tools requires a separate proficiency.

\textbf{Disguise Kit.} This pouch of cosmetics, hair dye, and small
props lets you create disguises that change your physical appearance.
Proficiency with this kit lets you add your proficiency bonus to any
ability checks you make to create a visual disguise.

\textbf{Forgery Kit.} This small box contains a variety of papers and
parchments, pens and inks, seals and sealing wax, gold and silver leaf,
and other supplies necessary to create convincing forgeries of physical
documents. Proficiency with this kit lets you add your proficiency bonus
to any ability checks you make to create a physical forgery of a
document.

\textbf{Gaming Set.} This item encompasses a wide range of game pieces,
including dice and decks of cards (for games such as Three Dragon Ante).
A few common examples appear on the Tools table, but other kinds of
gaming sets exist. If you are proficient with a gaming set, you can add
your proficiency bonus to ability checks you make to play a game with
that set. Each type of gaming set requires a separate proficiency.

\textbf{Herbalism Kit.} This kit contains a variety of instruments such
as clippers, mortar and pestle, and pouches and vials used by herbalists
to create remedies and potions. Proficiency with this kit lets you add
your proficiency bonus to any ability checks you make to identify or
apply herbs. Also, proficiency with this kit is required to create
antitoxin and potions of healing.

\textbf{Musical Instrument.} Several of the most common types of musical
instruments are shown on the table as examples. If you have proficiency
with a given musical instrument, you can add your proficiency bonus to
any ability checks you make to play music with the instrument. A bard
can use a musical instrument as a spellcasting focus. Each type of
musical instrument requires a separate proficiency.

\textbf{Navigator's Tools.} This set of instruments is used for
navigation at sea. Proficiency with navigator's tools lets you chart a
ship's course and follow navigation charts. In addition, these tools
allow you to add your proficiency bonus to any ability check you make to
avoid getting lost at sea.

\textbf{Poisoner's Kit}. A poisoner's kit includes the vials, chemicals,
and other equipment necessary for the creation of poisons. Proficiency
with this kit lets you add your proficiency bonus to any ability checks
you make to craft or use poisons.

\textbf{Thieves' Tools.} This set of tools includes a small file, a set
of lock picks, a small mirror mounted on a metal handle, a set of narrow
bladed scissors, and a pair of pliers. Proficiency with these tools lets
you add your proficiency bonus to any ability checks you make to disarm
traps or open locks.

\hypertarget{mounts-and-vehicles}{%
\subsection{Mounts and Vehicles}\label{mounts-and-vehicles}}

A good mount can help you move more quickly through the wilderness, but
its primary purpose is to carry the gear that would otherwise slow you
down. The Mounts and Other Animals table shows each animal's speed and
base carrying capacity.

An animal pulling a carriage, cart, chariot, sled, or wagon can move
weight up to five times its base carrying capacity, including the weight
of the vehicle. If multiple animals pull the same vehicle, they can add
their carrying capacity together.

Mounts other than those listed here are available in fantasy gaming
worlds, but they are rare and not normally available for purchase. These
include flying mounts (pegasi, griffons, hippogriffs, and similar
animals) and even aquatic mounts (giant sea horses, for example).
Acquiring such a mount often means securing an egg and raising the
creature yourself, making a bargain with a powerful entity, or
negotiating with the mount itself.

\textbf{Barding.} Barding is armor designed to protect an animal's head,
neck, chest, and body. Any type of armor shown on the Armor table can be
purchased as barding. The cost is four times the equivalent armor made
for humanoids, and it weighs twice as much.

\textbf{Saddles.} A military saddle braces the rider, helping you keep
your seat on an active mount in battle. It gives you advantage on any
check you make to remain mounted. An exotic saddle is required for
riding any aquatic or flying mount.

\textbf{Vehicle Proficiency.} If you have proficiency with a certain
kind of vehicle (land or water), you can add your proficiency bonus to
any check you make to control that kind of vehicle in difficult
circumstances.

\textbf{Rowed Vessels.} Keelboats and rowboats are used on lakes and
rivers. If going downstream, add the speed of the current (typically 3
miles per hour) to the speed of the vehicle. These vehicles can't be
rowed against any significant current, but they can be pulled upstream
by draft animals on the shores. A rowboat weighs 100 pounds, in case
adventurers carry it over land.

\hypertarget{mounts-and-other-animals}{%
\paragraph{Mounts and Other Animals}\label{mounts-and-other-animals}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Item & Cost & Speed & Carrying Capacity\tabularnewline
\midrule
\endhead
Camel & 50 gp & 50 ft. & 480 lb.\tabularnewline
Donkey or mule & 8 gp & 40 ft. & 420 lb.\tabularnewline
Elephant & 200 gp & 40 ft. & 1,320 lb.\tabularnewline
Horse, draft & 50 gp & 40 ft. & 540 lb.\tabularnewline
Horse, riding & 75 gp & 60 ft. & 480 lb.\tabularnewline
Mastiff & 25 gp & 40 ft. & 195 lb.\tabularnewline
Pony & 30 gp & 40 ft. & 225 lb.\tabularnewline
Warhorse & 400 gp & 60 ft. & 540 lb.\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tack-harness-and-drawn-vehicles}{%
\paragraph{Tack, Harness, and Drawn
Vehicles}\label{tack-harness-and-drawn-vehicles}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Item & Cost & Weight\tabularnewline
\midrule
\endhead
Barding & x4 & x2\tabularnewline
Bit and bridle & 2 gp & 1 lb.\tabularnewline
Carriage & 100 gp & 600 lb.\tabularnewline
Cart & 15 gp & 200 lb.\tabularnewline
Chariot & 250 gp & 100 lb.\tabularnewline
Feed (per day) & 5 cp & 10 lb.\tabularnewline
Saddle & &\tabularnewline
Exotic & 60 gp & 40 lb.\tabularnewline
Military & 20 gp & 30 lb.\tabularnewline
Pack & 5 gp & 15 lb.\tabularnewline
Riding & 10 gp & 25 lb.\tabularnewline
Saddlebags & 4 gp & 8 lb.\tabularnewline
Sled & 20 gp & 300 lb.\tabularnewline
Stabling (per day) & 5 sp & ---\tabularnewline
Wagon & 35 gp & 400 lb.\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{waterborne-vehicles}{%
\paragraph{Waterborne Vehicles}\label{waterborne-vehicles}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Item & Cost & Speed\tabularnewline
\midrule
\endhead
Galley & 30,000 gp & 4 mph\tabularnewline
Keelboat & 3,000 gp & 1 mp\tabularnewline
Longship & 10,000 gp & 3 mph\tabularnewline
Rowboat & 50 gp & 1½ mph\tabularnewline
Sailing ship & 10,000 gp & 2 mph\tabularnewline
Warship & 25,000 gp & 2½ mph\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{trade-goods}{%
\subsection{Trade Goods}\label{trade-goods}}

Most wealth is not in coins. It is measured in livestock, grain, land,
rights to collect taxes, or rights to resources (such as a mine or a
forest).

Guilds, nobles, and royalty regulate trade. Chartered companies are
granted rights to conduct trade along certain routes, to send merchant
ships to various ports, or to buy or sell specific goods. Guilds set
prices for the goods or services that they control, and determine who
may or may not offer those goods and services. Merchants commonly
exchange trade goods without using currency. The Trade Goods table shows
the value of commonly exchanged goods.

\hypertarget{trade-goods-1}{%
\paragraph{Trade Goods}\label{trade-goods-1}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Cost & Goods\tabularnewline
\midrule
\endhead
1 cp & 1 lb. of wheat\tabularnewline
2 cp & 1 lb. of flour or one chicken\tabularnewline
5 cp & 1 lb. of salt\tabularnewline
1 sp & 1lb. of iron or 1sq. yd. ofcanvas\tabularnewline
5 sp & 1 lb. of copper or 1 sq. yd. of cotton cloth\tabularnewline
1 gp & 1 lb. of ginger or one goat\tabularnewline
2 gp & 1 lb. of cinnamon or pepper, or one sheep\tabularnewline
3 gp & 1 lb. of cloves or one pig\tabularnewline
5 gp & 1 lb. of silver or 1 sq. yd. of linen\tabularnewline
10 gp & 1sq. yd. of silk or one cow\tabularnewline
15 gp & 1 lb. of saffron or one ox\tabularnewline
50 gp & 1 lb. of gold\tabularnewline
500 gp & 1 lb. of platinum\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{trade-goods-2}{%
\paragraph{Trade Goods}\label{trade-goods-2}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Cost & Goods\tabularnewline
\midrule
\endhead
1 cp & 1 lb. of wheat\tabularnewline
2 cp & 1 lb. of flour or one chicken\tabularnewline
5 cp & 1 lb. of salt\tabularnewline
1 sp & 1lb. of iron or 1sq. yd. ofcanvas\tabularnewline
5 sp & 1 lb. of copper or 1 sq. yd. of cotton cloth\tabularnewline
1 gp & 1 lb. of ginger or one goat\tabularnewline
2 gp & 1 lb. of cinnamon or pepper, or one sheep\tabularnewline
3 gp & 1 lb. of cloves or one pig\tabularnewline
5 gp & 1 lb. of silver or 1 sq. yd. of linen\tabularnewline
10 gp & 1sq. yd. of silk or one cow\tabularnewline
15 gp & 1 lb. of saffron or one ox\tabularnewline
50 gp & 1 lb. of gold\tabularnewline
500 gp & 1 lb. of platinum\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{expenses}{%
\subsection{Expenses}\label{expenses}}

When not descending into the depths of the earth, exploring ruins for
lost treasures, or waging war against the encroaching darkness,
adventurers face more mundane realities. Even in a fantastical world,
people require basic necessities such as shelter, sustenance, and
clothing. These things cost money, although some lifestyles cost more
than others.

\hypertarget{lifestyle-expenses}{%
\subsubsection{Lifestyle Expenses}\label{lifestyle-expenses}}

Lifestyle expenses provide you with a simple way to account for the cost
of living in a fantasy world. They cover your accommodations, food and
drink, and all your other necessities. Furthermore, expenses cover the
cost of maintaining your equipment so you can be ready when adventure
next calls.

At the start of each week or month (your choice), choose a lifestyle
from the Expenses table and pay the price to sustain that lifestyle. The
prices listed are per day, so if you wish to calculate the cost of your
chosen lifestyle over a thirty-day period, multiply the listed price by
30.

Your lifestyle might change from one period to the next, based on the
funds you have at your disposal, or you might maintain the same
lifestyle throughout your character's career. Your lifestyle choice can
have consequences. Maintaining a wealthy lifestyle might help you make
contacts with the rich and powerful, though you run the risk of
attracting thieves. Likewise, living frugally might help you avoid
criminals, but you are unlikely to make powerful connections.

\hypertarget{lifestyle-expenses-1}{%
\paragraph{Lifestyle Expenses}\label{lifestyle-expenses-1}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Lifestyle & Price/Day\tabularnewline
\midrule
\endhead
Wretched & ---\tabularnewline
Squalid & 1~sp\tabularnewline
Poor & 2~sp\tabularnewline
Modest & 1~gp\tabularnewline
Comfortable & 2~gp\tabularnewline
Wealthy & 4~gp\tabularnewline
Aristocratic & 10~gp minimum\tabularnewline
\bottomrule
\end{longtable}

\textbf{Wretched.} You live in inhumane conditions. With no place to
call home, you shelter wherever you can, sneaking into barns, huddling
in old crates, and relying on the good graces of people better off than
you. A wretched lifestyle presents abundant dangers. Violence, disease,
and hunger follow you wherever you go. Other wretched people covet your
armor, weapons, and adventuring gear, which represent a fortune by their
standards. You are beneath the notice of most people.

\textbf{Squalid.} You live in a leaky stable, a mud-floored hut just
outside town, or a vermin-infested boarding house in the worst part of
town. You have shelter from the elements, but you live in a desperate
and often violent environment, in places rife with disease, hunger, and
misfortune. You are beneath the notice of most people, and you have few
legal protections. Most people at this lifestyle level have suffered
some terrible setback. They might be disturbed, marked as exiles, or
suffer from disease.

\textbf{Poor.} A poor lifestyle means going without the comforts
available in a stable community. Simple food and lodgings, threadbare
clothing, and unpredictable conditions result in a sufficient, though
probably unpleasant, experience. Your accommodations might be a room in
a flophouse or in the common room above a tavern. You benefit from some
legal protections, but you still have to contend with violence, crime,
and disease. People at this lifestyle level tend to be unskilled
laborers, costermongers, peddlers, thieves, mercenaries, and other
disreputable types.

\textbf{Modest.} A modest lifestyle keeps you out of the slums and
ensures that you can maintain your equipment. You live in an older part
of town, renting a room in a boarding house, inn, or temple. You don't
go hungry or thirsty, and your living conditions are clean, if simple.
Ordinary people living modest lifestyles include soldiers with families,
laborers, students, priests, hedge wizards, and the like.

\textbf{Comfortable.} Choosing a comfortable lifestyle means that you
can afford nicer clothing and can easily maintain your equipment. You
live in a small cottage in a middle-class neighborhood or in a private
room at a fine inn. You associate with merchants, skilled tradespeople,
and military officers.

\textbf{Wealthy.} Choosing a wealthy lifestyle means living a life of
luxury, though you might not have achieved the social status associated
with the old money of nobility or royalty. You live a lifestyle
comparable to that of a highly successful merchant, a favored servant of
the royalty, or the owner of a few small businesses. You have
respectable lodgings, usually a spacious home in a good part of town or
a comfortable suite at a fine inn. You likely have a small staff of
servants.

\textbf{Aristocratic.} You live a life of plenty and comfort. You move
in circles populated by the most powerful people in the community. You
have excellent lodgings, perhaps a townhouse in the nicest part of town
or rooms in the finest inn. You dine at the best restaurants, retain the
most skilled and fashionable tailor, and have servants attending to your
every need. You receive invitations to the social gatherings of the rich
and powerful, and spend evenings in the company of politicians, guild
leaders, high priests, and nobility. You must also contend with the
highest levels of deceit and treachery. The wealthier you are, the
greater the chance you will be drawn into political intrigue as a pawn
or participant.

\begin{quote}
\hypertarget{self-sufficiency}{%
\subsubsection{Self-Sufficiency}\label{self-sufficiency}}
\end{quote}

The expenses and lifestyles described here assume that you are spending
your time between adventures in town, availing yourself of whatever
services you can afford---paying for food and shelter, paying
townspeople to sharpen your sword and repair your armor, and so on. Some
characters, though, might prefer to spend their time away from
civilization, sustaining themselves in the wild by hunting, foraging,
and repairing their own gear.

\begin{quote}
Maintaining this kind of lifestyle doesn't require you to spend any
coin, but it is time-consuming. If you spend your time between
adventures practicing a profession, you can eke out the equivalent of a
poor lifestyle. Proficiency in the Survival skill lets you live at the
equivalent of a comfortable lifestyle.
\end{quote}

\hypertarget{food-drink-and-lodging}{%
\subsubsection{Food, Drink, and Lodging}\label{food-drink-and-lodging}}

The Food, Drink, and Lodging table gives prices for individual food
items and a single night's lodging. These prices are included in your
total lifestyle expenses.

\hypertarget{food-drink-and-lodging-1}{%
\paragraph{Food, Drink, and Lodging}\label{food-drink-and-lodging-1}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Item & Cost\tabularnewline
\midrule
\endhead
Ale &\tabularnewline
Gallon & 2~sp\tabularnewline
Mug & 4~cp\tabularnewline
Banquet (per person) & 10~gp\tabularnewline
Bread, loaf & 2~cp\tabularnewline
Cheese, hunk & 1~sp\tabularnewline
Inn stay (per day) &\tabularnewline
Squalid & 7~cp\tabularnewline
Poor & 1~sp\tabularnewline
Modest & 5~sp\tabularnewline
Comfortable & 8~sp\tabularnewline
Wealthy & 2~gp\tabularnewline
Aristocratic & 4~gp\tabularnewline
Meals (per day) &\tabularnewline
Squalid & 3~cp\tabularnewline
Poor & 6~cp\tabularnewline
Modest & 3~sp\tabularnewline
Comfortable & 5~sp\tabularnewline
Wealthy & 8~sp\tabularnewline
Aristocratic & 2~gp\tabularnewline
Meat, chunk & 3~sp\tabularnewline
Wine &\tabularnewline
Common (pitcher) & 2~sp\tabularnewline
Fine (bottle) & 10~gp\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{services}{%
\subsubsection{Services}\label{services}}

Adventurers can pay nonplayer characters to assist them or act on their
behalf in a variety of circumstances. Most such hirelings have fairly
ordinary skills, while others are masters of a craft or art, and a few
are experts with specialized adventuring skills.

Some of the most basic types of hirelings appear on the Services table.
Other common hirelings include any of the wide variety of people who
inhabit a typical town or city, when the adventurers pay them to perform
a specific task. For example, a wizard might pay a carpenter to
construct an elaborate chest (and its miniature replica) for use in the
\emph{secret chest} spell. A fighter might commission a blacksmith to
forge a special sword. A bard might pay a tailor to make exquisite
clothing for an upcoming performance in front of the duke.

Other hirelings provide more expert or dangerous services. Mercenary
soldiers paid to help the adventurers take on a hobgoblin army are
hirelings, as are sages hired to research ancient or esoteric lore. If a
high-level adventurer establishes a stronghold of some kind, he or she
might hire a whole staff of servants and agents to run the place, from a
castellan or steward to menial laborers to keep the stables clean. These
hirelings often enjoy a long-term contract that includes a place to live
within the stronghold as part of the offered compensation.

\hypertarget{services-1}{%
\paragraph{Services}\label{services-1}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Service & Pay\tabularnewline
\midrule
\endhead
Coach cab &\tabularnewline
Between towns & 3~cp per mile\tabularnewline
Within a city & 1~cp\tabularnewline
Hireling &\tabularnewline
Skilled & 2~gp per day\tabularnewline
Untrained & 2~sp per day\tabularnewline
Messenger & 2~cp per mile\tabularnewline
Road or gate toll & 1~cp\tabularnewline
Ship's passage & 1~sp per mile\tabularnewline
\bottomrule
\end{longtable}

Skilled hirelings include anyone hired to perform a service that
involves a proficiency (including weapon, tool, or skill): a mercenary,
artisan, scribe, and so on. The pay shown is a minimum; some expert
hirelings require more pay. Untrained hirelings are hired for menial
work that requires no particular skill and can include laborers,
porters, maids, and similar workers.

\hypertarget{spellcasting-services}{%
\subsubsection{Spellcasting Services}\label{spellcasting-services}}

People who are able to cast spells don't fall into the category of
ordinary hirelings. It might be possible to find someone willing to cast
a spell in exchange for coin or favors, but it is rarely easy and no
established pay rates exist. As a rule, the higher the level of the
desired spell, the harder it is to find someone who can cast it and the
more it costs.

Hiring someone to cast a relatively common spell of 1st or 2nd level,
such as \emph{cure wounds} or \emph{identify}, is easy enough in a city
or town, and might cost 10 to 50 gold pieces (plus the cost of any
expensive material components). Finding someone able and willing to cast
a higher-level spell might involve traveling to a large city, perhaps
one with a university or prominent temple. Once found, the spellcaster
might ask for a service instead of payment---the kind of service that
only adventurers can provide, such as retrieving a rare item from a
dangerous locale or traversing a monster-infested wilderness to deliver
something important to a distant settlement.

\end{document}
