% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{inspiration}{%
\section{Inspiration}\label{inspiration}}

Inspiration is a rule the game master can use to reward you for playing
your character in a way

that's true to his or her personality traits, ideal, bond, and flaw. By
using inspiration, you can draw on your personality trait of compassion
for the downtrodden to give you an edge in negotiating with the Beggar
Prince. Or inspiration can let you call on your bond to the defense of
your home village to push past the effect of a spell that has been laid
on you.

\hypertarget{gaining-inspiration}{%
\subsection{Gaining Inspiration}\label{gaining-inspiration}}

Your GM can choose to give you inspiration for a variety of reasons.
Typically, GMs award it when you play out your personality traits, give
in to the drawbacks presented by a flaw or bond, and otherwise portray
your character in a compelling way. Your GM will tell you how you can
earn inspiration in the game.

You either have inspiration or you don't---you can't stockpile multiple
``inspirations'' for later use.

\hypertarget{using-inspiration}{%
\subsection{Using Inspiration}\label{using-inspiration}}

If you have inspiration, you can expend it when you make an attack roll,
saving throw, or ability check. Spending your inspiration gives you
advantage on that roll.

Additionally, if you have inspiration, you can reward another player for
good roleplaying, clever thinking, or simply doing something exciting in
the game. When another player character does something that really
contributes to the story in a fun and interesting way, you can give up
your inspiration to give that character inspiration.

\end{document}
