% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-h}{%
\section{Monsters (H)}\label{monsters-h}}

\hypertarget{hags}{%
\subsubsection{Hags}\label{hags}}

\hypertarget{green-hag}{%
\subsubsection{Green Hag}\label{green-hag}}

\emph{Medium fey, neutral evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 82 (11d8 + 33)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 12 (+1) & 16 (+3) & 13 (+1) & 14 (+2) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Arcana +3, Deception +4, Perception +4, Stealth +3

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Common, Draconic, Sylvan

\textbf{Challenge} 3 (700 XP)

\textbf{Amphibious.} The hag can breathe air and water.

\textbf{Innate Spellcasting.} The hag's innate spellcasting ability is
Charisma (spell save DC 12). She can innately cast the following spells,
requiring no material components:

At will: \emph{dancing lights}, \emph{minor illusion}, \emph{vicious
mockery}

\textbf{Mimicry.} The hag can mimic animal sounds and humanoid voices. A
creature that hears the sounds can tell they are imitations with a
successful DC 14 Wisdom (Insight) check.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) slashing damage.

\textbf{Illusory Appearance.} The hag covers herself and anything she is
wearing or carrying with a magical illusion that makes her look like
another creature of her general size and humanoid shape. The illusion
ends if the hag takes a bonus action to end it or if she dies.

The changes wrought by this effect fail to hold up to physical
inspection. For example, the hag could appear to have smooth skin, but
someone touching her would feel her rough flesh. Otherwise, a creature
must take an action to visually inspect the illusion and succeed on a DC
20 Intelligence (Investigation) check to discern that the hag is
disguised.

\textbf{Invisible Passage.} The hag magically turns invisible until she
attacks or casts a spell, or until her concentration ends (as if
concentrating on a spell). While invisible, she leaves no physical
evidence of her passage, so she can be tracked only by magic. Any
equipment she wears or carries is invisible with her.

\hypertarget{night-hag}{%
\subsubsection{Night Hag}\label{night-hag}}

\emph{Medium fiend, neutral evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 112 (15d8 + 45)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 16 (+3) & 14 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +7, Insight +6, Perception +6, Stealth +6

\textbf{Damage Resistances} cold, fire; bludgeoning, piercing, and
slashing from nonmagical attacks not made with silvered weapons

\textbf{Condition Immunities} charmed

\textbf{Senses} darkvision 120 ft., passive Perception 16

\textbf{Languages} Abyssal, Common, Infernal, Primordial

\textbf{Challenge} 5 (1,800 XP)

\textbf{Innate Spellcasting.} The hag's innate spellcasting ability is
Charisma (spell save DC 14, +6 to hit with spell attacks). She can
innately cast the following spells, requiring no material components:

At will: \emph{detect magic}, \emph{magic missile}

2/day each: \emph{plane shift} (self only), \emph{ray of enfeeblement},
\emph{sleep}

\textbf{Magic Resistance.} The hag has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Claws (Hag Form Only).} \emph{Melee Weapon Attack:} +7 to hit,
reach 5 ft., one target. \emph{Hit:} 13 (2d8 + 4) slashing damage.

\textbf{Change Shape.} The hag magically polymorphs into a Small or
Medium female humanoid, or back into her true form. Her statistics are
the same in each form. Any equipment she is wearing or carrying isn't
transformed. She reverts to her true form if she dies.

\textbf{Etherealness.} The hag magically enters the Ethereal Plane from
the Material Plane, or vice versa. To do so, the hag must have a
\emph{heartstone} in her possession.

\textbf{Nightmare Haunting (1/Day).} While on the Ethereal Plane, the
hag magically touches a sleeping humanoid on the Material Plane. A
\emph{protection from evil and good} spell cast on the target prevents
this contact, as does a \emph{magic circle}. As long as the contact
persists, the target has dreadful visions. If these visions last for at
least 1 hour, the target gains no benefit from its rest, and its hit
point maximum is reduced by 5 (1d10). If this effect reduces the
target's hit point maximum to 0, the target dies, and if the target was
evil, its soul is trapped in the hag's \emph{soul bag}. The reduction to
the target's hit point maximum lasts until removed by the \emph{greater
restoration} spell or similar magic.

\hypertarget{sea-hag}{%
\subsubsection{Sea Hag}\label{sea-hag}}

\emph{Medium fey, chaotic evil}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 52 (7d8 + 21)

\textbf{Speed} 30 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 13 (+1) & 16 (+3) & 12 (+1) & 12 (+1) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} Aquan, Common, Giant

\textbf{Challenge} 2 (450 XP)

\textbf{Amphibious.} The hag can breathe air and water.

\textbf{Horrific Appearance.} Any humanoid that starts its turn within
30 feet of the hag and can see the hag's true form must make a DC 11
Wisdom saving throw. On a failed save, the creature is frightened for 1
minute. A creature can repeat the saving throw at the end of each of its
turns, with disadvantage if the hag is within line of sight, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
hag's Horrific Appearance for the next 24 hours.

Unless the target is surprised or the revelation of the hag's true form
is sudden, the target can avert its eyes and avoid making the initial
saving throw. Until the start of its next turn, a creature that averts
its eyes has disadvantage on attack rolls against the hag.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) slashing damage.

\textbf{Death Glare.} The hag targets one frightened creature she can
see within 30 feet of her. If the target can see the hag, it must
succeed on a DC 11 Wisdom saving throw against this magic or drop to 0
hit points.

\textbf{Illusory Appearance.} The hag covers herself and anything she is
wearing or carrying with a magical illusion that makes her look like an
ugly creature of her general size and humanoid shape. The effect ends if
the hag takes a bonus action to end it or if she dies.

The changes wrought by this effect fail to hold up to physical
inspection. For example, the hag could appear to have no claws, but
someone touching her hand might feel the claws. Otherwise, a creature
must take an action to visually inspect the illusion and succeed on a DC
16 Intelligence (Investigation) check to discern that the hag is
disguised.

\hypertarget{half-dragon-template}{%
\subsection{Half-Dragon Template}\label{half-dragon-template}}

A beast, humanoid, giant, or monstrosity can become a half-dragon. It
keeps its statistics, except as follows.

\textbf{Challenge}. To avoid recalculating the creature's challenge
rating, apply the template only to a creature that meets the optional
prerequisite in the Breath Weapon table below. Otherwise, recalculate
the rating after you apply the template.

\textbf{Senses}. The half-dragon gains blindsight with a radius of 10
feet and darkvision with a radius of 60 feet.

\textbf{Resistances.} The half-dragon gains resistance to a type of
damage based on its color.

\begin{longtable}[]{@{}ll@{}}
\toprule
\textbf{Color} & \textbf{Damage Resistance}\tabularnewline
\midrule
\endhead
Black or copper & Blue or bronze\tabularnewline
Acid & Lightning\tabularnewline
\bottomrule
\end{longtable}

\textbf{Languages}.\_ The half-dragon speaks Draconic in addition to any
other languages it knows.

\textbf{New Action: Breath Weapon.} The half-dragon has the breath
weapon of its dragon half. The half- dragon's size determines how this
action functions.

\begin{longtable}[]{@{}lll@{}}
\toprule
\textbf{Color} & \textbf{Damage Resistance} & Optional
Prerequisite\tabularnewline
\midrule
\endhead
Large or smaller & Huge & Gargantuan\tabularnewline
As a wyrmling & As a young dragon & As an adult dragon\tabularnewline
\textbf{Challenge} 2 or higher & \textbf{Challenge} 7 or higher &
\textbf{Challenge} 8 or higher\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{half-red-dragon-veteran}{%
\subsubsection{Half-­‐Red Dragon
Veteran}\label{half-red-dragon-veteran}}

\emph{Medium humanoid (human), any alignment}

\textbf{Armor Class} 18 (plate)

\textbf{Hit Points} 65 (10d8 + 20)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 13 (+1) & 14 (+2) & 10 (+0) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Athletics +5, Perception +2

\textbf{Damage Resistances} fire

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
12

\textbf{Languages} Common, Draconic

\textbf{Challenge} 5 (1,800 XP)

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The veteran makes two longsword attacks. If it has
a shortsword drawn, it can also make a shortsword attack.

\textbf{Longsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 7 (1d8 + 3) slashing damage, or 8 (1d10 + 3)
slashing damage if used with two hands.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) piercing damage.

\textbf{Heavy Crossbow.} \emph{Ranged Weapon Attack:} +3 to hit, range
100/400 ft., one target. \emph{Hit:} 6 (1d10 + 1) piercing damage.

\textbf{Fire Breath (Recharge 5--6).} The veteran exhales fire in a
15-­‐foot cone. Each creature in that area must make a DC 15 Dexterity
saving throw, taking 24 (7d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{harpy}{%
\subsubsection{Harpy}\label{harpy}}

\emph{Medium monstrosity, chaotic evil}

\textbf{Armor Class} 11

\textbf{Hit Points} 38 (7d8 + 7)

\textbf{Speed} 20 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
12 (+1) & 13 (+1) & 12 (+1) & 7 (−2) & 10 (+0) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} Common

\textbf{Challenge} 1 (200 XP)

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Multiattack.} The harpy makes two attacks: one with its claws
and one with its club.

\textbf{Claws.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 6 (2d4 + 1) slashing damage.

\textbf{Club.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 3 (1d4 + 1) bludgeoning damage.

\textbf{Luring Song.} The harpy sings a magical melody. Every humanoid
and giant within 300 feet of the harpy that can hear the song must
succeed on a DC 11 Wisdom saving throw or be charmed until the song
ends. The harpy must take a bonus action on its subsequent turns to
continue singing. It can stop singing at any time. The song ends if the
harpy is incapacitated.

While charmed by the harpy, a target is incapacitated and ignores the
songs of other harpies. If the charmed target is more than 5 feet away
from the harpy, the target must move on its turn toward the harpy by the
most direct route, trying to get within 5 feet. It doesn't avoid
opportunity attacks, but before moving into damaging terrain, such as
lava or a pit, and whenever it takes damage from a source other than the
harpy, the target can repeat the saving throw. A charmed target can also
repeat the saving throw at the end of each of its turns. If the saving
throw is successful, the effect ends on it.

A target that successfully saves is immune to this harpy's song for the
next 24 hours.

\hypertarget{hell-hound}{%
\subsubsection{Hell Hound}\label{hell-hound}}

\emph{Medium fiend, lawful evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 45 (7d8 + 14)

\textbf{Speed} 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 12 (+1) & 14 (+2) & 6 (−2) & 13 (+1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5

\textbf{Damage Immunities} fire

\textbf{Senses} darkvision 60 ft., passive Perception 15

\textbf{Languages} understands Infernal but can't speak it

\textbf{Challenge} 3 (700 XP)

\textbf{Keen Hearing and Smell.} The hound has advantage on Wisdom
(Perception) checks that rely on hearing or smell.

\textbf{Pack Tactics.} The hound has advantage on an attack roll against
a creature if at least one of the hound's allies is within 5 feet of the
creature and the ally isn't incapacitated.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d8 + 3) piercing damage plus 7 (2d6) fire
damage.

\textbf{Fire Breath (Recharge 5--6).} The hound exhales fire in a
15-­‐foot cone. Each creature in that area must make a DC 12 Dexterity
saving throw, taking 21 (6d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{hippogriff}{%
\subsubsection{Hippogriff}\label{hippogriff}}

\emph{Large monstrosity, unaligned}

\textbf{Armor Class} 11

\textbf{Hit Points} 19 (3d10 + 3)

\textbf{Speed} 40 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 13 (+1) & 13 (+1) & 2 (−4) & 12 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5

\textbf{Senses} passive Perception 15

\textbf{Languages} ---

\textbf{Challenge} 1 (200 XP)

\textbf{Keen Sight.} The hippogriff has advantage on Wisdom (Perception)
checks that rely on sight.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Multiattack.} The hippogriff makes two attacks: one with its
beak and one with its claws.

\textbf{Beak.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d10 + 3) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) slashing damage.

\hypertarget{hobgoblin}{%
\subsubsection{Hobgoblin}\label{hobgoblin}}

\emph{Medium humanoid (goblinoid), lawful evil}

\textbf{Armor Class} 18 (chain mail, shield)

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 12 (+1) & 12 (+1) & 10 (+0) & 10 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Common, Goblin

\textbf{Challenge} ½ (100 XP)

\textbf{Martial Advantage.} Once per turn, the hobgoblin can deal an
extra 7 (2d6) damage to a creature it hits with a weapon attack if that
creature is within 5 feet of an ally of the hobgoblin that isn't
incapacitated.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Longsword.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d8 + 1) slashing damage, or 6 (1d10 + 1)
slashing damage if used with two hands.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +3 to hit, range 150/600
ft., one target. \emph{Hit:} 5 (1d8 + 1) piercing damage.

\hypertarget{homunculus}{%
\subsubsection{Homunculus}\label{homunculus}}

\emph{Tiny construct, neutral}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 5 (2d4)

\textbf{Speed} 20 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
4 (−3) & 15 (+2) & 11 (+0) & 10 (+0) & 10 (+0) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} understands the languages of its creator but can't
speak

\textbf{Challenge} 0 (10 XP)

\textbf{Telepathic Bond.} While the homunculus is on the same plane of
existence as its master, it can magically convey what it \textbf{Senses}
to its master, and the two can communicate telepathically.

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 1 piercing damage, and the target must succeed on
a DC 10 Constitution saving throw or be poisoned for 1 minute. If the
saving throw fails by 5 or more, the target is instead poisoned for 5
(1d10) minutes and unconscious while poisoned in this way.

\hypertarget{hydra}{%
\subsubsection{Hydra}\label{hydra}}

\emph{Huge monstrosity, unaligned}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 172 (15d12 + 75)

\textbf{Speed} 30 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 12 (+1) & 20 (+5) & 2 (−4) & 10 (+0) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +6

\textbf{Senses} darkvision 60 ft., passive Perception 16

\textbf{Languages} ---

\textbf{Challenge} 8 (3,900 XP)

\textbf{Hold Breath.} The hydra can hold its breath for 1 hour.

\textbf{Multiple Heads.} The hydra has five heads. While it has more
than one head, the hydra has advantage on saving throws against being
blinded, charmed, deafened, frightened, stunned, and knocked
unconscious.

Whenever the hydra takes 25 or more damage in a single turn, one of its
heads dies. If all its heads die, the hydra dies.

At the end of its turn, it grows two heads for each of its heads that
died since its last turn, unless it has taken fire damage since its last
turn. The hydra regains 10 hit points for each head regrown in this way.

\textbf{Reactive Heads.} For each head the hydra has beyond one, it gets
an extra reaction that can be used only for opportunity attacks.

\textbf{Wakeful.} While the hydra sleeps, at least one of its heads is
awake.

\hypertarget{actions-9}{%
\paragraph{Actions}\label{actions-9}}

\textbf{Multiattack.} The hydra makes as many bite attacks as it has
heads.

\textbf{Bite.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 10 (1d10 + 5) piercing damage.

\end{document}
