% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-v}{%
\section{Monsters (V)}\label{monsters-v}}

\hypertarget{vampires}{%
\subsection{Vampires}\label{vampires}}

\hypertarget{vampire}{%
\subsubsection{Vampire}\label{vampire}}

\emph{Medium undead (shapechanger), lawful evil}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 144 (17d8 + 68)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 18 (+4) & 18 (+4) & 17 (+3) & 15 (+2) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +9, Wis +7, Cha +9

\textbf{Skills} Perception +7, Stealth +9

\textbf{Damage Resistances} necrotic; bludgeoning, piercing, and
slashing from nonmagical attacks

\textbf{Senses} darkvision 120 ft., passive Perception 17

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 13 (10,000 XP)

\textbf{Shapechanger.} If the vampire isn't in sunlight or running
water, it can use its action to polymorph into a Tiny bat or a Medium
cloud of mist, or back into its true form.

While in bat form, the vampire can't speak, its walking speed is 5 feet,
and it has a flying speed of 30 feet. Its statistics, other than its
size and speed, are unchanged. Anything it is wearing transforms with
it, but nothing it is carrying does. It reverts to its true form if it
dies.

While in mist form, the vampire can't take any actions, speak, or
manipulate objects. It is weightless, has a flying speed of 20 feet, can
hover, and can enter a hostile creature's space and stop there. In
addition, if air can pass through a space, the mist can do so without
squeezing, and it can't pass through water. It has advantage on
Strength, Dexterity, and Constitution saving throws, and it is immune to
all nonmagical damage, except the damage it takes from sunlight.

\textbf{Legendary Resistance (3/Day).} If the vampire fails a saving
throw, it can choose to succeed instead.

\textbf{Misty Escape.} When it drops to 0 hit points outside its resting
place, the vampire transforms into a cloud of mist (as in the
Shapechanger trait) instead of falling unconscious, provided that it
isn't in sunlight or running water. If it can't transform, it is
destroyed.

While it has 0 hit points in mist form, it can't revert to its vampire
form, and it must reach its resting place within 2 hours or be
destroyed. Once in its resting place, it reverts to its vampire form. It
is then paralyzed until it regains at least 1 hit point. After spending
1 hour in its resting place with 0 hit points, it regains 1 hit point.

\textbf{Regeneration.} The vampire regains 20 hit points at the start of
its turn if it has at least 1 hit point and isn't in sunlight or running
water. If the vampire takes radiant damage or damage from holy water,
this trait doesn't function at the start of the vampire's next turn.

\textbf{Spider Climb.} The vampire can climb difficult surfaces,
including upside down on ceilings, without needing to make an ability
check.

\textbf{Vampire Weaknesses.} The vampire has the following flaws:

\emph{Forbiddance.} The vampire can't enter a residence without an
invitation from one of the occupants.

\emph{Harmed by Running Water.} The vampire takes 20 acid damage if it
ends its turn in running water.

\emph{Stake to the Heart.} If a piercing weapon made of wood is driven
into the vampire's heart while the vampire is incapacitated in its
resting place, the vampire is paralyzed until the stake is removed.

\emph{Sunlight Hypersensitivity.} The vampire takes 20 radiant damage
when it starts its turn in sunlight. While in sunlight, it has
disadvantage on attack rolls and ability checks.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack (Vampire Form Only).} The vampire makes two attacks,
only one of which can be a bite attack.

\textbf{Unarmed Strike (Vampire Form Only).} \emph{Melee Weapon Attack:}
+9 to hit, reach 5 ft., one creature. \emph{Hit:} 8 (1d8 + 4)
bludgeoning damage. Instead of dealing damage, the vampire can grapple
the target (escape DC 18).

\textbf{Bite (Bat or Vampire Form Only).} \emph{Melee Weapon Attack:} +9
to hit, reach 5 ft., one willing creature, or a creature that is
grappled by the vampire, incapacitated, or restrained. \emph{Hit:} 7
(1d6 + 4) piercing damage plus 10 (3d6) necrotic damage. The target's
hit point maximum is reduced by an amount equal to the necrotic damage
taken, and the vampire regains hit points equal to that amount. The
reduction lasts until the target finishes a long rest. The target dies
if this effect reduces its hit point maximum to 0. A humanoid slain in
this way and then buried in the ground rises the following night as a
vampire spawn under the vampire's control.

\textbf{Charm.} The vampire targets one humanoid it can see within 30
feet of it. If the target can see the vampire, the target must succeed
on a DC 17 Wisdom saving throw against this magic or be charmed by the
vampire. The charmed target regards the vampire as a trusted friend to
be heeded and protected. Although the target isn't under the vampire's
control, it takes the vampire's requests or actions in the most
favorable way it can, and it is a willing target for the vampire's bite
attack.

Each time the vampire or the vampire's companions do anything harmful to
the target, it can repeat the saving throw, ending the effect on itself
on a success. Otherwise, the effect lasts 24 hours or until the vampire
is destroyed, is on a different plane of existence than the target, or
takes a bonus action to end the effect.

\textbf{Children of the Night (1/Day).} The vampire magically calls 2d4
swarms of bats or rats, provided that the sun isn't up. While outdoors,
the vampire can call 3d6 wolves instead. The called creatures arrive in
1d4 rounds, acting as allies of the vampire and obeying its spoken
commands. The beasts remain for 1 hour, until the vampire dies, or until
the vampire dismisses them as a bonus action.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The vampire can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The vampire regains spent
legendary actions at the start of its turn.

\textbf{Move.} The vampire moves up to its speed without provoking
opportunity attacks.

\textbf{Unarmed Strike.} The vampire makes one unarmed strike.

\textbf{Bite (Costs 2 Actions).} The vampire makes one bite attack.

\hypertarget{vampire-spawn}{%
\subsubsection{Vampire Spawn}\label{vampire-spawn}}

\emph{Medium undead, neutral evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 82 (11d8 + 33)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 16 (+3) & 16 (+3) & 11 (+0) & 10 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Wis +3

\textbf{Skills} Perception +3, Stealth +6

\textbf{Damage Resistances} necrotic; bludgeoning, piercing, and
slashing from nonmagical attacks

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 5 (1,800 XP)

\textbf{Regeneration.} The vampire regains 10 hit points at the start of
its turn if it has at least 1 hit point and isn't in sunlight or running
water. If the vampire takes radiant damage or damage from holy water,
this trait doesn't function at the start of the vampire's next turn.

\textbf{Spider Climb.} The vampire can climb difficult surfaces,
including upside down on ceilings, without needing to make an ability
check.

\textbf{Vampire Weaknesses.} The vampire has the following flaws:

\emph{Forbiddance.} The vampire can't enter a residence without an
invitation from one of the occupants.

\emph{Harmed by Running Water.} The vampire takes 20 acid damage when it
ends its turn in running water.

\emph{Stake to the Heart.} The vampire is destroyed if a piercing weapon
made of wood is driven into its heart while it is incapacitated in its
resting place.

\emph{Sunlight Hypersensitivity.} The vampire takes 20 radiant damage
when it starts its turn in sunlight. While in sunlight, it has
disadvantage on attack rolls and ability checks.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The vampire makes two attacks, only one of which
can be a bite attack.

\textbf{Claws.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
creature. \emph{Hit:} 8 (2d4 + 3) slashing damage. Instead of dealing
damage, the vampire can grapple the target (escape DC 13).

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
willing creature, or a creature that is grappled by the vampire,
incapacitated, or restrained. \emph{Hit:} 6 (1d6 + 3) piercing damage
plus 7 (2d6) necrotic damage. The target's hit point maximum is reduced
by an amount equal to the necrotic damage taken, and the vampire regains
hit points equal to that amount. The reduction lasts until the target
finishes a long rest. The target dies if this effect reduces its hit
point maximum to 0.

\end{document}
