% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-l}{%
\section{Monsters (L)}\label{monsters-l}}

\hypertarget{lamia}{%
\subsubsection{Lamia}\label{lamia}}

\emph{Large monstrosity, chaotic evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 97 (13d10 + 26)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 13 (+1) & 15 (+2) & 14 (+2) & 15 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +7, Insight +4, Stealth +3

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} Abyssal, Common

\textbf{Challenge} 4 (1,100 XP)

\textbf{Innate Spellcasting.} The lamia's innate spellcasting ability is
Charisma (spell save DC 13). It can innately cast the following spells,
requiring no material components.

At will: \emph{disguise self} (any humanoid form), \emph{major image}

3/day each: \emph{charm person}, \emph{mirror image}, \emph{scrying},
\emph{suggestion}

1/day: \emph{geas}

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The lamia makes two attacks: one with its claws
and one with its dagger or Intoxicating Touch.

\textbf{Claws.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d10 + 3) slashing damage.

\textbf{Dagger.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d4 + 3) piercing damage.

\textbf{Intoxicating Touch.} Melee Spell Attack: +5 to hit, reach 5 ft.,
one creature. \emph{Hit:} The target is magically cursed for 1 hour.
Until the curse ends, the target has disadvantage on Wisdom
\textbf{Saving Throws} and all ability checks.

\hypertarget{lich}{%
\subsubsection{Lich}\label{lich}}

\emph{Medium undead, any evil alignment}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 135 (18d8 + 54)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 16 (+3) & 16 (+3) & 20 (+5) & 14 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +10, Int +12, Wis +9

\textbf{Skills} Arcana +18, History +12, Insight +9, Perception +9

\textbf{Damage Resistances} cold, lightning, necrotic

\textbf{Damage Immunities} poison; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, poisoned

\textbf{Senses} truesight 120 ft., passive Perception 19

\textbf{Languages} Common plus up to five other languages

\textbf{Challenge} 21 (33,000 XP)

\textbf{Legendary Resistance (3/Day).} If the lich fails a saving throw,
it can choose to succeed instead.

\textbf{Rejuvenation.} If it has a phylactery, a destroyed lich gains a
new body in 1d10 days, regaining all its hit points and becoming active
again. The new body appears within 5 feet of the phylactery.

\textbf{Spellcasting.} The lich is an 18th-­‐level spellcaster. Its
spellcasting ability is Intelligence (spell save DC 20, +12 to hit with
spell attacks). The lich has the following wizard spells prepared:

Cantrips (at will): \emph{mage hand}, \emph{prestidigitation}, \emph{ray
of frost}

1st level (4 slots): \emph{detect magic}, \emph{magic missile},
\emph{shield}, \emph{thunderwave}

2nd level (3 slots): \emph{acid arrow}, \emph{detect thoughts},
\emph{invisibility}, \emph{mirror image}

3rd level (3 slots): \emph{animate dead},\emph{counterspell},
\emph{dispel magic}, \emph{fireball}

4th level (3 slots): \emph{blight}, \emph{dimension door}

5th level (3 slots): \emph{cloudkill}, \emph{scrying}

6th level (1 slot): \emph{disintegrate}, \emph{globe of invulnerability}

7th level (1 slot): \emph{finger of death}, \emph{plane shift}

8th level (1 slot): \emph{dominate monster}, \emph{power word stun}

9th level (1 slot): \emph{power word kill}

\textbf{Turn Resistance.} The lich has advantage on saving throws
against any effect that turns undead.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Paralyzing Touch.} Melee Spell Attack: +12 to hit, reach 5 ft.,
one creature. \emph{Hit:} 10 (3d6) cold damage. The target must succeed
on a DC 18 Constitution saving throw or be paralyzed for 1 minute. The
target can repeat the saving throw at the end of each of its turns,
ending the effect on itself on a success.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The lich can take 3 legendary actions, choosing from the options below.
Only one legendary action option can be used at a time and only at the
end of another creature's turn. The lich regains spent legendary actions
at the start of its turn.

\textbf{Cantrip.} The lich casts a \textbf{Cantrip.}

\textbf{Paralyzing Touch (Costs 2 Actions).} The lich uses its
Paralyzing Touch.

\textbf{Frightening Gaze (Costs 2 Actions).} The lich fixes its gaze on
one creature it can see within 10 feet of it. The target must succeed on
a DC 18 Wisdom saving throw against this magic or become frightened for
1 minute. The frightened target can repeat the saving throw at the end
of each of its turns, ending the effect on itself on a success. If a
target's saving throw is successful or the effect ends for it, the
target is immune to the lich's gaze for the next 24 hours.

\textbf{Disrupt Life (Costs 3 Actions).} Each living creature within 20
feet of the lich must make a DC 18 Constitution saving throw against
this magic, taking 21 (6d6) necrotic damage on a failed save, or half as
much damage on a successful one.

\hypertarget{lizardfolk}{%
\subsubsection{Lizardfolk}\label{lizardfolk}}

\emph{Medium humanoid (lizardfolk), neutral}

\textbf{Armor Class} 15 (natural armor, shield)

\textbf{Hit Points} 22 (4d8 + 4)

\textbf{Speed} 30 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 10 (+0) & 13 (+1) & 7 (−2) & 12 (+1) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +4, Survival +5

\textbf{Senses} passive Perception 13

\textbf{Languages} Draconic

\textbf{Challenge} ½ (100 XP)

\textbf{Hold Breath.} The lizardfolk can hold its breath for 15 minutes.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The lizardfolk makes two melee attacks, each one
with a different weapon.

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Heavy Club.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) bludgeoning damage.

\textbf{Javelin} \emph{Melee or Ranged Weapon Attack:} +4 to hit, reach
5 ft. or range 30/120 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing
damage.

\textbf{Spiked Shield.} \emph{Melee Weapon Attack:} +4 to hit, reach 5
ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\hypertarget{lycanthropes}{%
\subsection{Lycanthropes}\label{lycanthropes}}

\hypertarget{werebear}{%
\paragraph{Werebear}\label{werebear}}

\emph{Medium humanoid (human, shapechanger), neutral good}

\textbf{Armor Class} 10 in humanoid form, 11 (natural armor) in bear and
hybrid form

\textbf{Hit Points} 135 (18d8 + 54)

\textbf{Speed} 30 ft. (40 ft., climb 30 ft. in bear or hybrid form)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 10 (+0) & 17 (+3) & 11 (+0) & 12 (+1) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +7

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks not made with silvered weapons

\textbf{Senses} passive Perception 17

\textbf{Languages} Common (can't speak in bear form)

\textbf{Challenge} 5 (1,800 XP)

\textbf{Shapechanger.} The werebear can use its action to polymorph into
a Large bear-­‐humanoid hybrid or into a Large bear, or back into its
true form, which is humanoid. Its statistics, other than its size and
AC, are the same in each form. Any equipment it is wearing or carrying
isn't transformed. It reverts to its true form if it dies.

\textbf{Keen Smell.} The werebear has advantage on Wisdom (Perception)
checks that rely on smell.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} In bear form, the werebear makes two claw attacks.
In humanoid form, it makes two greataxe attacks. In hybrid form, it can
attack like a bear or a humanoid.

\textbf{Bite (Bear or Hybrid Form Only).} \emph{Melee Weapon Attack:} +7
to hit, reach 5 ft., one target. \emph{Hit:} 15 (2d10 + 4) piercing
damage. If the target is a humanoid, it must succeed on a DC 14
Constitution saving throw or be cursed with werebear lycanthropy.

\textbf{Claw (Bear or Hybrid Form Only).} \emph{Melee Weapon Attack:} +7
to hit, reach 5 ft., one target. \emph{Hit:} 13 (2d8 + 4) slashing
damage.

\textbf{Greataxe (Humanoid or Hybrid Form Only)} \emph{Melee Weapon
Attack:} +7 to hit, reach 5 ft., one target. \emph{Hit:} 10 (1d12 + 4)
slashing damage.

\hypertarget{wereboar}{%
\subsubsection{Wereboar}\label{wereboar}}

\emph{Medium humanoid (human, shapechanger), neutral evil}

\textbf{Armor Class} 10 in humanoid form, 11 (natural armor) in boar or
hybrid form

\textbf{Hit Points} 78 (12d8 + 24)

\textbf{Speed} 30 ft. (40 ft. in boar form)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 10 (+0) & 15 (+2) & 10 (+0) & 11 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks not made with silvered weapons

\textbf{Senses} passive Perception 12

\textbf{Languages} Common (can't speak in boar form)

\textbf{Challenge} 4 (1,100 XP)

\textbf{Shapechanger.} The wereboar can use its action to polymorph into
a boar-­‐humanoid hybrid or into a boar, or back into its true form,
which is humanoid. Its statistics, other than its AC, are the same in
each form. Any equipment it is wearing or carrying isn't transformed. It
reverts to its true form if it dies.

\textbf{Charge (Boar or Hybrid Form Only).} If the wereboar moves at
least 15 feet straight toward a target and then hits it with its tusks
on the same turn, the target takes an extra 7 (2d6) slashing damage. If
the target is a creature, it must succeed on a DC 13 Strength saving
throw or be knocked prone.

\textbf{Relentless (Recharges after a Short or Long Rest).} If the
wereboar takes 14 damage or less that would reduce it to 0 hit points,
it is reduced to 1 hit point instead.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Multiattack (Humanoid or Hybrid Form Only)} The wereboar makes
two attacks, only one of which can be with its tusks.

\textbf{Maul (Humanoid or Hybrid Form Only).} \emph{Melee Weapon
Attack:} +5 to hit, reach 5 ft., one target. \emph{Hit:} 10 (2d6 + 3)
bludgeoning damage.

\textbf{Tusks (Boar or Hybrid Form Only).} \emph{Melee Weapon Attack:}
+5 to hit, reach 5 ft., one target. \emph{Hit:} 10 (2d6 +3) slashing
damage. If the target is a humanoid, it must succeed on a DC 12
Constitution saving throw or be cursed with wereboar lycanthropy.

\hypertarget{wererat}{%
\subsubsection{Wererat}\label{wererat}}

\emph{Medium humanoid (human, shapechanger), lawful evil}

\textbf{Armor Class} 12

\textbf{Hit Points} 33 (6d8 + 6)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 15 (+2) & 12 (+1) & 11 (+0) & 10 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2, Stealth +4

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks not made with silvered weapons

\textbf{Senses} darkvision 60 ft. (rat form only), passive Perception 12

\textbf{Languages} Common (can't speak in rat form)

\textbf{Challenge} 2 (450 XP)

\textbf{Shapechanger.} The wererat can use its action to polymorph into
a rat-­‐humanoid hybrid or into a giant rat, or back into its true form,
which is humanoid. Its statistics, other than its size, are the same in
each form. Any equipment it is wearing or carrying isn't transformed. It
reverts to its true form if it dies.

\textbf{Keen Smell.} The wererat has advantage on Wisdom (Perception)
checks that rely on smell.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\_\emph{Multiattack (Humanoid or Hybrid Form Only)}* The wererat makes
two attacks, only one of which can be a \textbf{Bite.}

\textbf{Bite (Rat or Hybrid Form Only).} \emph{Melee Weapon Attack:} +4
to hit, reach 5 ft., one target. \emph{Hit:} 4 (1d4 + 2) piercing
damage. If the target is a humanoid, it must succeed on a DC 11
Constitution saving throw or be cursed with wererat lycanthropy.

\textbf{Shortsword (Humanoid or Hybrid Form Only).} \emph{Melee Weapon
Attack:} +4 to hit, reach 5 ft., one target. \emph{Hit:} 5 (1d6 + 2)
piercing damage.

\textbf{Hand Crossbow (Humanoid or Hybrid Form Only).} \emph{Ranged
Weapon Attack:} +4 to hit, range 30/120 ft., one target. \emph{Hit:} 5
(1d6 + 2) piercing damage.

\hypertarget{weretiger}{%
\subsubsection{Weretiger}\label{weretiger}}

\emph{Medium humanoid (human, shapechanger), neutral}

\textbf{Armor Class} 12

\textbf{Hit Points} 120 (16d8 + 48)

\textbf{Speed} 30 ft. (40 ft. in tiger form)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 15 (+2) & 16 (+3) & 10 (+0) & 13 (+1) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5, Stealth +4

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks not made with silvered weapons

\textbf{Senses} darkvision 60 ft., passive Perception 15

\textbf{Languages} Common (can't speak in tiger form)

\textbf{Challenge} 4 (1,100 XP)

\textbf{Shapechanger.} The weretiger can use its action to polymorph
into a tiger-­‐humanoid hybrid or into a tiger, or back into its true
form, which is humanoid. Its statistics, other than its size, are the
same in each form. Any equipment it is wearing or carrying isn't
transformed. It reverts to its true form if it dies.

\textbf{Keen Hearing and Smell.} The weretiger has advantage on Wisdom
(Perception) checks that rely on hearing or smell.

\textbf{Pounce (Tiger or Hybrid Form Only).} If the weretiger moves at
least 15 feet straight toward a creature and then hits it with a claw
attack on the same turn, that target must succeed on a DC 14 Strength
saving throw or be knocked prone. If the target is prone, the weretiger
can make one bite attack against it as a bonus action.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\_\emph{Multiattack (Humanoid or Hybrid Form Only).}* In humanoid form,
the weretiger makes two scimitar attacks or two longbow attacks. In
hybrid form, it can attack like a humanoid or make two claw attacks.

\textbf{Bite (Tiger or Hybrid Form Only).} \emph{Melee Weapon Attack:}
+5 to hit, reach 5 ft., one target. \emph{Hit:} 8 (1d10 + 3) piercing
damage. If the target is a humanoid, it must succeed on a DC 13
Constitution saving throw or be cursed with weretiger lycanthropy.

\textbf{Claw (Tiger or Hybrid Form Only).} \emph{Melee Weapon Attack:}
+5 to hit, reach 5 ft., one target. \emph{Hit:} 7 (1d8 + 3) slashing
damage.

\textbf{Scimitar (Humanoid or Hybrid Form Only).} \emph{Melee Weapon
Attack:} +5 to hit, reach 5 ft., one target. \emph{Hit:} 6 (1d6 + 3)
slashing damage.

\textbf{Longbow (Humanoid or Hybrid Form Only).} \emph{Ranged Weapon
Attack:} +4 to hit, range 150/600 ft., one target. \emph{Hit:} 6 (1d8 +
2) piercing damage.

\hypertarget{werewolf}{%
\subsubsection{Werewolf}\label{werewolf}}

\emph{Medium humanoid (human, shapechanger), chaotic evil}

\textbf{Armor Class} 11 in humanoid form, 12 (natural armor) in wolf or
hybrid form

\textbf{Hit Points} 58 (9d8 + 18)

\textbf{Speed} 30 ft. (40 ft. in wolf form)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 13 (+1) & 14 (+2) & 10 (+0) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4, Stealth +3

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks not made with silvered weapons

\textbf{Senses} passive Perception 14

\textbf{Languages} Common (can't speak in wolf form)

\textbf{Challenge} 3 (700 XP)

\textbf{Shapechanger.} The werewolf can use its action to polymorph into
a wolf-­‐humanoid hybrid or into a wolf, or back into its true form,
which is humanoid. Its statistics, other than its AC, are the same in
each form. Any equipment it is wearing or carrying isn't transformed. It
reverts to its true form if it dies.

\textbf{Keen Hearing and Smell.} The werewolf has advantage on Wisdom
(Perception) checks that rely on hearing or smell.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Multiattack (Humanoid or Hybrid Form Only)} The werewolf makes
two attacks: one with its bite and one with its claws or spear.

\textbf{Bite (Wolf or Hybrid Form Only).} \emph{Melee Weapon Attack:} +4
to hit, reach 5 ft., one target. \emph{Hit:} 6 (1d8 + 2) piercing
damage. If the target is a humanoid, it must succeed on a DC 12
Constitution saving throw or be cursed with werewolf lycanthropy.

\textbf{Claws (Hybrid Form Only).} \emph{Melee Weapon Attack:} +4 to
hit, reach 5 ft., one creature. \emph{Hit:} 7 (2d4 + 2) slashing damage.

\textbf{Spear (Humanoid Form Only).} \emph{Melee or Ranged Weapon
Attack:} +4 to hit, reach 5 ft. or range 20/60 ft., one creature.
\emph{Hit:} 5 (1d6 + 2) piercing damage, or 6 (1d8 + 2) piercing damage
if used with two hands to make a melee attack

\end{document}
