% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-x}{%
\section{Monsters (X)}\label{monsters-x}}

\hypertarget{xorn}{%
\subsubsection{Xorn}\label{xorn}}

\emph{Medium elemental, neutral}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 73 (7d8 + 42)

\textbf{Speed} 20 ft., burrow 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 10 (+0) & 22 (+6) & 11 (+0) & 10 (+0) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +6, Stealth +3

\textbf{Damage Resistances} piercing and slashing from nonmagical
attacks that aren't adamantine

\textbf{Senses} darkvision 60 ft., tremorsense 60 ft., passive
Perception 16

\textbf{Languages} Terran

\textbf{Challenge} 5 (1,800 XP)

\textbf{Earth Glide.} The xorn can burrow through nonmagical, unworked
earth and stone. While doing so, the xorn doesn't disturb the material
it moves through.

\textbf{Stone Camouflage.} The xorn has advantage on Dexterity (Stealth)
checks made to hide in rocky terrain.

\textbf{Treasure Sense.} The xorn can pinpoint, by scent, the location
of precious metals and stones, such as coins and gems, within 60 feet of
it.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The xorn makes three claw attacks and one bite
attack.

\textbf{Claw.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 6 (1d6 + 3) slashing damage.

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (3d6 + 3) piercing damage.

\end{document}
