% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-g}{%
\section{Monsters (G)}\label{monsters-g}}

\hypertarget{gargoyle}{%
\subsubsection{Gargoyle}\label{gargoyle}}

\emph{Medium elemental, chaotic evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 52 (7d8 + 21)

\textbf{Speed} 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 11 (+0) & 16 (+3) & 6 (−2) & 11 (+0) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks that aren't adamantine

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, petrified, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Terran

\textbf{Challenge} 2 (450 XP)

\textbf{False Appearance.} While the gargoyle remains motionless, it is
indistinguishable from an inanimate statue.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The gargoyle makes two attacks: one with its bite
and one with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d6 + 2) slashing damage.

\hypertarget{genies}{%
\subsection{Genies}\label{genies}}

\hypertarget{djinni}{%
\subsubsection{Djinni}\label{djinni}}

\emph{Large elemental, chaotic good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 161 (14d10 + 84)

\textbf{Speed} 30 ft., fly 90 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 15 (+2) & 22 (+6) & 15 (+2) & 16 (+3) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Wis +7, Cha +9

\textbf{Damage Immunities} lightning, thunder

\textbf{Senses} darkvision 120 ft., passive Perception 13

\textbf{Languages} Auran

\textbf{Challenge} 11 (7,200 XP)

\textbf{Elemental Demise.} If the djinni dies, its body disintegrates
into a warm breeze, leaving behind only equipment the djinni was wearing
or carrying.

\textbf{Innate Spellcasting.} The djinni's innate spellcasting ability
is Charisma (spell save DC 17, +9 to hit with spell attacks). It can
innately cast the following spells, requiring no material components:

At will: \emph{detect evil and good}, \emph{detect magic},
\emph{thunderwave}

3/day each: \emph{create food and water} (can create wine instead of
water), \emph{tongues}, \emph{wind walk}

1/day each: \emph{conjure elemental} (air elemental only),
\emph{creation}, \emph{gaseous form}, \emph{invisibility}, \emph{major
image}, \emph{plane shift}

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The djinni makes three scimitar attacks.

\textbf{Scimitar.} \emph{Melee Weapon Attack:} +9 to hit, reach 5 ft.,
one target. \emph{Hit:} 12 (2d6 + 5) slashing damage plus 3 (1d6)
lightning or thunder damage (djinni's choice).

\textbf{Create Whirlwind.} A 5-­‐foot-­‐radius, 30-­‐foot-­‐tall
cylinder of swirling air magically forms on a point the djinni can see
within 120 feet of it. The whirlwind lasts as long as the djinni
maintains concentration (as if concentrating on a spell). Any creature
but the djinni that enters the whirlwind must succeed on a DC 18
Strength saving throw or be restrained by it. The djinni can move the
whirlwind up to 60 feet as an action, and creatures restrained by the
whirlwind move with it. The whirlwind ends if the djinni loses sight of
it.

A creature can use its action to free a creature restrained by the
whirlwind, including itself, by succeeding on a DC 18 Strength check. If
the check succeeds, the creature is no longer restrained and moves to
the nearest space outside the whirlwind.

\hypertarget{efreeti}{%
\subsubsection{Efreeti}\label{efreeti}}

\emph{Large elemental, lawful evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 200 (16d10 + 112)

\textbf{Speed} 40 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 12 (+1) & 24 (+7) & 16 (+3) & 15 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Int +7, Wis +6, Cha +7

\textbf{Damage Immunities} fire

\textbf{Senses} darkvision 120 ft., passive Perception 12

\textbf{Languages} Ignan

\textbf{Challenge} 11 (7,200 XP)

\textbf{Elemental Demise.} If the efreeti dies, its body disintegrates
in a flash of fire and puff of smoke, leaving behind only equipment the
efreeti was wearing or carrying.

\textbf{Innate Spellcasting.} The efreeti's innate spellcasting ability
is Charisma (spell save DC 15, +7 to hit with spell attacks). It can
innately cast the following spells, requiring no material components:

At will: \emph{detect magic}

3/day: \emph{enlarge/reduce}, \emph{tongues}

1/day each: \emph{conjure elemental} (fire elemental only),
\emph{gaseous form}, \emph{invisibility}, \emph{major image},
\emph{plane shift}, \emph{wall of fire}

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The efreeti makes two scimitar attacks or uses its
Hurl Flame twice.

\textbf{Scimitar.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft.,
one target. \emph{Hit:} 13 (2d6 + 6) slashing damage plus 7 (2d6) fire
damage.

\textbf{Hurl Flame.} Ranged Spell Attack: +7 to hit, range 120 ft., one
target. \emph{Hit:} 17 (5d6) fire damage.

\hypertarget{ghost}{%
\subsubsection{Ghost}\label{ghost}}

\emph{Medium undead, any alignment}

\textbf{Armor Class} 11

\textbf{Hit Points} 45 (10d8)

\textbf{Speed} 0 ft., fly 40 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
7 (−2) & 13 (+1) & 10 (+0) & 10 (+0) & 12 (+1) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} acid, fire, lightning, thunder; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} cold, necrotic, poison

\textbf{Condition Immunities} charmed, exhaustion, frightened, grappled,
paralyzed, petrified, poisoned, prone, restrained

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} any languages it knew in life

\textbf{Challenge} 4 (1,100 XP)

\textbf{Ethereal Sight.} The ghost can see 60 feet into the Ethereal
Plane when it is on the Material Plane, and vice versa.

\textbf{Incorporeal Movement.} The ghost can move through other
creatures and objects as if they were difficult terrain. It takes 5
(1d10) force damage if it ends its turn inside an object.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Withering Touch.} \emph{Melee Weapon Attack:} +5 to hit, reach 5
ft., one target. \emph{Hit:} 17 (4d6 + 3) necrotic damage.

\textbf{Etherealness.} The ghost enters the Ethereal Plane from the
Material Plane, or vice versa. It is visible on the Material Plane while
it is in the Border Ethereal, and vice versa, yet it can't affect or be
affected by anything on the other plane.

\textbf{Horrifying Visage.} Each non-­‐undead creature within 60 feet of
the ghost that can see it must succeed on a DC 13 Wisdom saving throw or
be frightened for 1 minute. If the save fails by 5 or more, the target
also ages 1d4 × 10 years. A frightened target can repeat the saving
throw at the end of each of its turns, ending the frightened condition
on itself on a success. If a target's saving throw is successful or the
effect ends for it, the target is immune to this ghost's Horrifying
Visage for the next 24 hours. The aging effect can be reversed with a
\emph{greater restoration} spell, but only within 24 hours of it
occurring.

\textbf{Possession (Recharge 6).} One humanoid that the ghost can see
within 5 feet of it must succeed on a DC 13 Charisma saving throw or be
possessed by the ghost; the ghost then disappears, and the target is
incapacitated and loses control of its body. The ghost now controls the
body but doesn't deprive the target of awareness. The ghost can't be
targeted by any attack, spell, or other effect, except ones that turn
undead, and it retains its alignment, Intelligence, Wisdom, Charisma,
and immunity to being charmed and frightened. It otherwise uses the
possessed target's statistics, but doesn't gain access to the target's
knowledge, class features, or proficiencies.

The possession lasts until the body drops to 0 hit points, the ghost
ends it as a bonus action, or the ghost is turned or forced out by an
effect like the \emph{dispel evil and good} spell. When the possession
ends, the ghost reappears in an unoccupied space within 5 feet of the
body. The target is immune to this ghost's Possession for 24 hours after
succeeding on the saving throw or after the possession ends.

\hypertarget{ghouls}{%
\subsection{Ghouls}\label{ghouls}}

\hypertarget{ghast}{%
\subsubsection{Ghast}\label{ghast}}

\emph{Medium undead, chaotic evil}

\textbf{Armor Class} 13

\textbf{Hit Points} 36 (8d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 17 (+3) & 10 (+0) & 11 (+0) & 10 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} necrotic

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Common

\textbf{Challenge} 2 (450 XP)

\textbf{Stench.} Any creature that starts its turn within 5 feet of the
ghast must succeed on a DC 10 Constitution saving throw or be poisoned
until the start of its next turn. On a successful saving throw, the
creature is immune to the ghast's Stench for 24 hours.

\textbf{Turning Defiance.} The ghast and any ghouls within 30 feet of it
have advantage on saving throws against effects that turn undead.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
creature. \emph{Hit:} 12 (2d8 + 3) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) slashing damage. If the target is a
creature other than an undead, it must succeed on a DC 10 Constitution
saving throw or be paralyzed for 1 minute. The target can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\hypertarget{ghoul}{%
\subsubsection{Ghoul}\label{ghoul}}

\emph{Medium undead, chaotic evil}

\textbf{Armor Class} 12

\textbf{Hit Points} 22 (5d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 15 (+2) & 10 (+0) & 7 (−2) & 10 (+0) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Common

\textbf{Challenge} 1 (200 XP)

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
creature. \emph{Hit:} 9 (2d6 + 2) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (2d4 + 2) slashing damage. If the target is a
creature other than an elf or undead, it must succeed on a DC 10
Constitution saving throw or be paralyzed for 1 minute. The target can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\hypertarget{giants}{%
\subsection{Giants}\label{giants}}

\hypertarget{cloud-giant}{%
\subsubsection{Cloud Giant}\label{cloud-giant}}

\emph{Huge giant, neutral good (50\%) or neutral evil (50\%)}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 200 (16d12 + 96)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 10 (+0) & 22 (+6) & 12 (+1) & 16 (+3) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +10, Wis +7, Cha +7

\textbf{Skills} Insight +7, Perception +7

\textbf{Senses} passive Perception 17

\textbf{Languages} Common, Giant

\textbf{Challenge} 9 (5,000 XP)

\textbf{Keen Smell.} The giant has advantage on Wisdom (Perception)
checks that rely on smell.

\textbf{Innate Spellcasting.} The giant's innate spellcasting ability is
Charisma. It can innately cast the following spells, requiring no
material components:

At will: \emph{detect magic}, \emph{fog cloud}, \emph{light}

3/day each: \emph{feather fall}, \emph{fly}, \emph{misty step},
\emph{telekinesis}

1/day each: \emph{control weather}, \emph{gaseous form}

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Multiattack.} The giant makes two morningstar attacks.

\textbf{Morningstar.} \emph{Melee Weapon Attack:} +12 to hit, reach 10
ft., one target. \emph{Hit:} 21 (3d8 + 8) piercing damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +12 to hit, range 60/240
ft., one target. \emph{Hit:} 30 (4d10 + 8) bludgeoning damage.

\hypertarget{fire-giant}{%
\subsubsection{Fire Giant}\label{fire-giant}}

\emph{Huge giant, lawful evil}

\textbf{Armor Class} 18 (plate)

\textbf{Hit Points} 162 (13d12 + 78)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
25 (+7) & 9 (−1) & 23 (+6) & 10 (+0) & 14 (+2) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +10, Cha +5

\textbf{Skills} Athletics +11, Perception +6

\textbf{Damage Immunities} fire

\textbf{Senses} passive Perception 16

\textbf{Languages} Giant

\textbf{Challenge} 9 (5,000 XP)

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Multiattack.} The giant makes two greatsword attacks.

\textbf{Greatsword.} \emph{Melee Weapon Attack:} +11 to hit, reach 10
ft., one target. \emph{Hit:} 28 (6d6 + 7) slashing damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +11 to hit, range 60/240
ft., one target. \emph{Hit:} 29 (4d10 + 7) bludgeoning damage.

\hypertarget{frost-giant}{%
\subsubsection{Frost Giant}\label{frost-giant}}

\emph{Huge giant, neutral evil}

\textbf{Armor Class} 15 (patchwork armor)

\textbf{Hit Points} 138 (12d12 + 60)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 9 (−1) & 21 (+5) & 9 (−1) & 10 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +8, Wis +3, Cha +4

\textbf{Skills} Athletics +9, Perception +3

\textbf{Damage Immunities} cold

\textbf{Senses} passive Perception 13

\textbf{Languages} Giant

\textbf{Challenge} 8 (3,900 XP)

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Multiattack.} The giant makes two greataxe attacks.

\textbf{Greataxe.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft.,
one target. \emph{Hit:} 25 (3d12 + 6) slashing damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +9 to hit, range 60/240 ft.,
one target. \emph{Hit:} 28 (4d10 + 6) bludgeoning damage.

\hypertarget{hill-giant}{%
\subsubsection{Hill Giant}\label{hill-giant}}

\emph{Huge giant, chaotic evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 105 (10d12 + 40)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 8 (−1) & 19 (+4) & 5 (−3) & 9 (−1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2

\textbf{Senses} passive Perception 12

\textbf{Languages} Giant

\textbf{Challenge} 5 (1,800 XP)

\hypertarget{actions-9}{%
\paragraph{Actions}\label{actions-9}}

\textbf{Multiattack.} The giant makes two greatclub attacks.

\textbf{Greatclub.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft.,
one target. \emph{Hit:} 18 (3d8 + 5) bludgeoning damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +8 to hit, range 60/240 ft.,
one target. \emph{Hit:} 21 (3d10 + 5) bludgeoning damage.

\hypertarget{stone-giant}{%
\subsubsection{Stone Giant}\label{stone-giant}}

\emph{Huge giant, neutral}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 126 (11d12 + 55)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 15 (+2) & 20 (+5) & 10 (+0) & 12 (+1) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +8, Wis +4

\textbf{Skills} Athletics +12, Perception +4

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Giant

\textbf{Challenge} 7 (2,900 XP)

\textbf{Stone Camouflage.} The giant has advantage on Dexterity
(Stealth) checks made to hide in rocky terrain.

\hypertarget{actions-10}{%
\paragraph{Actions}\label{actions-10}}

\textbf{Multiattack.} The giant makes two greatclub attacks.

\textbf{Greatclub.} \emph{Melee Weapon Attack:} +9 to hit, reach 15 ft.,
one target. \emph{Hit:} 19 (3d8 + 6) bludgeoning damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +9 to hit, range 60/240 ft.,
one target. \emph{Hit:} 28 (4d10 + 6) bludgeoning damage. If the target
is a creature, it must succeed on a DC 17 Strength saving throw or be
knocked prone.

\hypertarget{reactions}{%
\paragraph{Reactions}\label{reactions}}

\textbf{Rock Catching.} If a rock or similar object is hurled at the
giant, the giant can, with a successful DC 10 Dexterity saving throw,
catch the missile and take no bludgeoning damage from it.

\hypertarget{storm-giant}{%
\subsubsection{Storm Giant}\label{storm-giant}}

\emph{Huge giant, chaotic good}

\textbf{Armor Class} 16 (scale mail)

\textbf{Hit Points} 230 (20d12 + 100)

\textbf{Speed} 50 ft., swim 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
29 (+9) & 14 (+2) & 20 (+5) & 16 (+3) & 18 (+4) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +14, Con +10, Wis +9, Cha +9

\textbf{Skills} Arcana +8, Athletics +14, History +8, Perception +9

\textbf{Damage Resistances} cold

\textbf{Damage Immunities} lightning, thunder

\textbf{Senses} passive Perception 19

\textbf{Languages} Common, Giant

\textbf{Challenge} 13 (10,000 XP)

\textbf{Amphibious.} The giant can breathe air and water.

\textbf{Innate Spellcasting.} The giant's innate spellcasting ability is
Charisma (spell save DC 17). It can innately cast the following spells,
requiring no material components:

At will: \emph{detect magic}, \emph{feather fall}, \emph{levitate},
\emph{light}

3/day each: \emph{control weather}, \emph{water breathing}

\hypertarget{actions-11}{%
\paragraph{Actions}\label{actions-11}}

\textbf{Multiattack.} The giant makes two greatsword attacks.

\textbf{Greatsword.} \emph{Melee Weapon Attack:} +14 to hit, reach 10
ft., one target. \emph{Hit:} 30 (6d6 + 9) slashing damage.

\textbf{Rock.} \emph{Ranged Weapon Attack:} +14 to hit, range 60/240
ft., one target. \emph{Hit:} 35 (4d12 + 9) bludgeoning damage.

\textbf{Lightning Strike (Recharge 5--6).} The giant hurls a magical
lightning bolt at a point it can see within 500 feet of it. Each
creature within 10 feet of that point must make a DC 17 Dexterity saving
throw, taking 54 (12d8) lightning damage on a failed save, or half as
much damage on a successful one.

\hypertarget{gibbering-mouther}{%
\subsubsection{Gibbering Mouther}\label{gibbering-mouther}}

\emph{Medium aberration, neutral}

\textbf{Armor Class} 9

\textbf{Hit Points} 67 (9d8 + 27)

\textbf{Speed} 10 ft., swim 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 8 (−1) & 16 (+3) & 3 (−4) & 10 (+0) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Condition Immunities} prone

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Aberrant Ground.} The ground in a 10-­‐foot radius around the
mouther is doughlike difficult terrain. Each creature that starts its
turn in that area must succeed on a DC 10 Strength saving throw or have
its speed reduced to 0 until the start of its next turn.

\textbf{Gibbering.} The mouther babbles incoherently while it can see
any creature and isn't incapacitated. Each creature that starts its turn
within 20 feet of the mouther and can hear the gibbering must succeed on
a DC 10 Wisdom saving throw. On a failure, the creature can't take
actions until the start of its next turn and rolls a d8 to determine
what it does during its turn. On a 1 to 4, the creature does nothing. On
a 5 or 6, the creature takes no action or bonus action and uses all its
movement to move in a randomly determined direction. On a 7 or 8, the
creature makes a melee attack against a randomly determined creature
within its reach or does nothing if it can't make such an attack.

\hypertarget{actions-12}{%
\paragraph{Actions}\label{actions-12}}

\textbf{Multiattack.} The gibbering mouther makes one bite attack and,
if it can, uses its Blinding Spittle.

\textbf{Bites.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
creature. \emph{Hit:} 17 (5d6) piercing damage. If the target is Medium
or smaller, it must succeed on a DC 10 Strength saving throw or be
knocked prone. If the target is killed by this damage, it is absorbed
into the mouther.

\textbf{Blinding Spittle (Recharge 5--6).} The mouther spits a chemical
glob at a point it can see within 15 feet of it. The glob explodes in a
blinding flash of light on impact. Each creature within 5 feet of the
flash must succeed on a DC 13 Dexterity saving throw or be blinded until
the end of the mouther's next turn.

\hypertarget{gnoll}{%
\subsubsection{Gnoll}\label{gnoll}}

\emph{Medium humanoid (gnoll), chaotic evil}

\textbf{Armor Class} 15 (hide armor, shield)

\textbf{Hit Points} 22 (5d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 12 (+1) & 11 (+0) & 6 (−2) & 10 (+0) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Gnoll

\textbf{Challenge} ½ (100 XP)

\textbf{Rampage.} When the gnoll reduces a creature to 0 hit poitns with
a melee attack on its turn, the gnoll can take a bonus action to move up
to half its speed and make a bite attack.

\hypertarget{actions-13}{%
\paragraph{Actions}\label{actions-13}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 4 (1d4 + 2) piercing damage.

\textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +4 to hit, reach 5
ft. or range 20/60 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing
damage, or 6 (1d8 + 2) piercing damage if used with two hands to make a
melee attack.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +3 to hit, range 150/600
ft., one target. \emph{Hit:} 5 (1d8 + 1) piercing damage.

\hypertarget{gnome-deep-svirfneblin}{%
\subsubsection{Gnome, Deep (Svirfneblin)}\label{gnome-deep-svirfneblin}}

\emph{Small humanoid (gnome), neutral good}

\textbf{Armor Class} 15 (chain shirt)

\textbf{Hit Points} 16 (3d6 + 6)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 14 (+2) & 14 (+2) & 12 (+1) & 10 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Investigation +3, Perception +2, Stealth +4

\textbf{Senses} darkvision 120 ft., passive Perception 12

\textbf{Languages} Gnomish, Terran, Undercommon

\textbf{Challenge} ½ (100 XP)

\textbf{Stone Camouflage.} The gnome has advantage on Dexterity
(Stealth) checks made to hide in rocky terrain.

\textbf{Gnome Cunning.} The gnome has advantage on Intelligence, Wisdom,
and Charisma saving throws against magic.

\textbf{Innate Spellcasting.} The gnome's innate spellcasting ability is
Intelligence (spell save DC 11). It can innately cast the following
spells, requiring no material components:

At will: \emph{nondetection} (self only)

1/day each: \emph{blindness/deafness}, \emph{blur}, \emph{disguise self}

\hypertarget{actions-14}{%
\paragraph{Actions}\label{actions-14}}

\textbf{War Pick.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d8 + 2) piercing damage.

\textbf{Poisoned Dart.} \emph{Ranged Weapon Attack:} +4 to hit, range
30/120 ft., one creature. \emph{Hit:} 4 (1d4 + 2) piercing damage, and
the target must succeed on a DC 12 Constitution saving throw or be
poisoned for 1 minute. The target can repeat the saving throw at the end
of each of its turns, ending the effect on itself on a success.

\hypertarget{goblin}{%
\subsubsection{Goblin}\label{goblin}}

\emph{Small humanoid (goblinoid), neutral evil}

\textbf{Armor Class} 15 (leather armor, shield)

\textbf{Hit Points} 7 (2d6)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
8 (−1) & 14 (+2) & 10 (+0) & 10 (+0) & 8 (−1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +6

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} Common, Goblin

\textbf{Challenge} ¼ (50 XP)

\textbf{Nimble Escape.} The goblin can take the Disengage or Hide action
as a bonus action on each of its turns.

\hypertarget{actions-15}{%
\paragraph{Actions}\label{actions-15}}

\textbf{Scimitar.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) slashing damage.

\textbf{Shortbow.} \emph{Ranged Weapon Attack:} +4 to hit, range 80/320
ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\hypertarget{golems}{%
\subsection{Golems}\label{golems}}

\hypertarget{clay-golem}{%
\subsubsection{Clay Golem}\label{clay-golem}}

\emph{Large construct, unaligned}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 133 (14d10 + 56)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 9 (−1) & 18 (+4) & 3 (−4) & 8 (−1) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} acid, poison, psychic; bludgeoning, piercing,
and slashing from nonmagical attacks that aren't adamantine

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} understands the languages of its creator but can't
speak

\textbf{Challenge} 9 (5,000 XP)

\textbf{Acid Absorption.} Whenever the golem is subjected to acid
damage, it takes no damage and instead regains a number of hit points
equal to the acid damage dealt.

\textbf{Berserk.} Whenever the golem starts its turn with 60 hit points
or fewer, roll a d6. On a 6, the golem goes \textbf{Berserk.} On each of
its turns while berserk, the golem attacks the nearest creature it can
see. If no creature is near enough to move to and attack, the golem
attacks an object, with preference for an object smaller than itself.
Once the golem goes berserk, it continues to do so until it is destroyed
or regains all its hit points.

\textbf{Immutable Form.} The golem is immune to any spell or effect that
would alter its form.

\textbf{Magic Resistance.} The golem has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The golem's weapon attacks are magical.

\hypertarget{actions-16}{%
\paragraph{Actions}\label{actions-16}}

\textbf{Multiattack.} The golem makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 16 (2d10 + 5) bludgeoning damage. If the target is a
creature, it must succeed on a DC 15 Constitution saving throw or have
its hit point maximum reduced by an amount equal to the damage taken.
The target dies if this attack reduces its hit point maximum to 0. The
reduction lasts until removed by the \emph{greater restoration} spell or
other magic.

\textbf{Haste (Recharge 5--6).} Until the end of its next turn, the
golem magically gains a +2 bonus to its AC, has advantage on Dexterity
\textbf{Saving Throws}, and can use its slam attack as a bonus action.

\hypertarget{flesh-golem}{%
\subsubsection{Flesh Golem}\label{flesh-golem}}

\emph{Medium construct, neutral}

\textbf{Armor Class} 9

\textbf{Hit Points} 93 (11d8 + 44)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 9 (−1) & 18 (+4) & 6 (−2) & 10 (+0) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} lightning, poison; bludgeoning, piercing, and
slashing from nonmagical attacks that aren't adamantine

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} understands the languages of its creator but can't
speak

\textbf{Challenge} 5 (1,800 XP)

\textbf{Berserk.} Whenever the golem starts its turn with 40 hit points
or fewer, roll a d6. On a 6, the golem goes berserk. On each of its
turns while berserk, the golem attacks the nearest creature it can see.
If no creature is near enough to move to and attack, the golem attacks
an object, with preference for an object smaller than itself. Once the
golem goes berserk, it continues to do so until it is destroyed or
regains all its hit points.

The golem's creator, if within 60 feet of the berserk golem, can try to
calm it by speaking firmly and persuasively. The golem must be able to
hear its creator, who must take an action to make a DC 15 Charisma
(Persuasion) check. If the check succeeds, the golem ceases being
berserk. If it takes damage while still at 40 hit points or fewer, the
golem might go berserk again.

\textbf{Aversion of Fire.} If the golem takes fire damage, it has
disadvantage on attack rolls and ability checks until the end of its
next turn.

\textbf{Immutable Form.} The golem is immune to any spell or effect that
would alter its form.

\textbf{Lightning Absorption.} Whenever the golem is subjected to
lightning damage, it takes no damage and instead regains a number of hit
points equal to the lightning damage dealt.

\textbf{Magic Resistance.} The golem has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The golem's weapon attacks are magical.

\hypertarget{actions-17}{%
\paragraph{Actions}\label{actions-17}}

\textbf{Multiattack.} The golem makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage.

\hypertarget{iron-golem}{%
\subsubsection{Iron Golem}\label{iron-golem}}

\emph{Large construct, unaligned}

\textbf{Armor Class} 20 (natural armor)

\textbf{Hit Points} 210 (20d10 + 100)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
24 (+7) & 9 (−1) & 20 (+5) & 3 (−4) & 11 (+0) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} fire, poison, psychic; bludgeoning, piercing,
and slashing from nonmagical attacks that aren't adamantine

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} understands the languages of its creator but can't
speak

\textbf{Challenge} 16 (15,000 XP)

\textbf{Fire Absorption.} Whenever the golem is subjected to fire
damage, it takes no damage and instead regains a number of hit points
equal to the fire damage dealt.

\textbf{Immutable Form.} The golem is immune to any spell or effect that
would alter its form.

\textbf{Magic Resistance.} The golem has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The golem's weapon attacks are magical.

\hypertarget{actions-18}{%
\paragraph{Actions}\label{actions-18}}

\textbf{Multiattack.} The golem makes two melee attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +13 to hit, reach 5 ft., one
target. \emph{Hit:} 20 (3d8 + 7) bludgeoning damage.

\textbf{Sword.} \emph{Melee Weapon Attack:} +13 to hit, reach 10 ft.,
one target. \emph{Hit:} 23 (3d10 + 7) slashing damage.

\textbf{Poison Breath (Recharge 6).} The golem exhales poisonous gas in
a 15-­‐foot cone. Each creature in that area must make a DC 19
Constitution saving throw, taking 45 (10d8) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{stone-golem}{%
\subsubsection{Stone Golem}\label{stone-golem}}

\emph{Large construct, unaligned}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 178 (17d10 + 85)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 9 (−1) & 20 (+5) & 3 (−4) & 11 (+0) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison, psychic; bludgeoning, piercing, and
slashing from nonmagical attacks that aren't adamantine

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} understands the languages of its creator but can't
speak

\textbf{Challenge} 10 (5,900 XP)

\textbf{Immutable Form.} The golem is immune to any spell or effect that
would alter its form.

\textbf{Magic Resistance.} The golem has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The golem's weapon attacks are magical.

\hypertarget{actions-19}{%
\paragraph{Actions}\label{actions-19}}

\textbf{Multiattack.} The golem makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 19 (3d8 + 6) bludgeoning damage.

\textbf{Slow (Recharge 5--6).} The golem targets one or more creatures
it can see within 10 feet of it. Each target must make a DC 17 Wisdom
saving throw against this magic. On a failed save, a target can't use
reactions, its speed is halved, and it can't make more than one attack
on its turn. In addition, the target can take either an action or a
bonus action on its turn, not both. These effects last for 1 minute. A
target can repeat the saving throw at the end of each of its turns,
ending the effect on itself on a success.

\hypertarget{gorgon}{%
\subsubsection{Gorgon}\label{gorgon}}

\emph{Large monstrosity, unaligned}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 114 (12d10 + 48)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 11 (+0) & 18 (+4) & 2 (−4) & 12 (+1) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4

\textbf{Condition Immunities} petrified

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} ---

\textbf{Challenge} 5 (1,800 XP)

\textbf{Trampling Charge} If the gorgon moves at least 20 feet straight
toward a creature and then hits it with a gore attack on the same turn,
that target must succeed on a DC 16 Strength saving throw or be knocked
prone. If the target is prone, the gorgon can make one attack with its
hooves against it as a bonus action.

\hypertarget{actions-20}{%
\paragraph{Actions}\label{actions-20}}

\textbf{Gore.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 18 (2d12 + 5) piercing damage.

\textbf{Hooves.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 16 (2d10 + 5) bludgeoning damage.

\textbf{Petrifying Breath (Recharge 5--6).} The gorgon exhales
petrifying gas in a 30-­‐foot cone. Each creature in that area must
succeed on a DC 13 Constitution saving throw. On a failed save, a target
begins to turn to stone and is restrained. The restrained target must
repeat the saving throw at the end of its next turn. On a success, the
effect ends on the target. On a failure, the target is petrified until
freed by the \emph{greater restoration} spell or other magic.

\hypertarget{grick}{%
\subsubsection{Grick}\label{grick}}

\emph{Medium monstrosity, neutral}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 27 (6d8)

\textbf{Speed} 30 ft., climb 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 14 (+2) & 11 (+0) & 3 (−4) & 14 (+2) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Stone Camouflage.} The grick has advantage on Dexterity
(Stealth) checks made to hide in rocky terrain.

\hypertarget{actions-21}{%
\paragraph{Actions}\label{actions-21}}

\textbf{Multiattack.} The grick makes one attack with its tentacles If
that attack hits, the grick can make one beak attack against the same
target.

\textbf{Tentacles.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 9 (2d6 + 2) slashing damage.

\textbf{Beak.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\hypertarget{griffon}{%
\subsubsection{Griffon}\label{griffon}}

\emph{Large monstrosity, unaligned}

\textbf{Armor Class} 12

\textbf{Hit Points} 59 (7d10 + 21)

\textbf{Speed} 30 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 2 (−4) & 13 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5

\textbf{Senses} darkvision 60 ft., passive Perception 15

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Keen Sight.} The griffon has advantage on Wisdom (Perception)
checks that rely on sight.

\hypertarget{actions-22}{%
\paragraph{Actions}\label{actions-22}}

\textbf{Multiattack.} The griffon makes two attacks: one with its beak
and one with its claws.

\textbf{Beak.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d8 + 4) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\hypertarget{grimlock}{%
\subsubsection{Grimlock}\label{grimlock}}

\emph{Medium humanoid (grimlock), neutral evil}

\textbf{Armor Class} 11

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 12 (+1) & 12 (+1) & 9 (−1) & 8 (−1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Athletics +5, Perception +3, Stealth +3

\textbf{Condition Immunities} blinded

\textbf{Senses} blindsight 30 ft. or 10 ft. while deafened (blind beyond
this radius), passive Perception 13

\textbf{Languages} Undercommon

\textbf{Challenge} ¼ (50 XP)

\textbf{Blind Senses.} The grimlock can't use its blindsight while
deafened and unable to smell.

\textbf{Keen Hearing and Smell.} The grimlock has advantage on Wisdom
(Perception) checks that rely on hearing or smell.

\textbf{Stone Camouflage.} The grimlock has advantage on Dexterity
(Stealth) checks made to hide in rocky terrain.

\hypertarget{actions-23}{%
\paragraph{Actions}\label{actions-23}}

\textbf{Spiked Bone Club.} \emph{Melee Weapon Attack:} +5 to hit, reach
5 ft., one target. \emph{Hit:} 5 (1d4 + 3) bludgeoning damage plus 2
(1d4) piercing damage.

\end{document}
