% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-f}{%
\section{Monsters (F)}\label{monsters-f}}

\hypertarget{fungi}{%
\subsubsection{Fungi}\label{fungi}}

\hypertarget{shrieker}{%
\subsubsection{Shrieker}\label{shrieker}}

\emph{Medium plant, unaligned}

\textbf{Armor Class} 5

\textbf{Hit Points} 13 (3d8)

\textbf{Speed} 0 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
1 (−5) & 1 (−5) & 10 (+0) & 1 (−5) & 3 (−4) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Condition Immunities} blinded, deafened, frightened

\textbf{Senses} blindsight 30 ft. (blind beyond this radius), passive
Perception 6

\textbf{Languages} ---

\textbf{Challenge} 0 (10 XP)

\textbf{False Appearance.} While the shrieker remains motionless, it is
indistinguishable from an ordinary fungus.

\hypertarget{reactions}{%
\paragraph{Reactions}\label{reactions}}

\textbf{Shriek.} When bright light or a creature is within 30 feet of
the shrieker, it emits a shriek audible within 300 feet of it. The
shrieker continues to shriek until the disturbance moves out of range
and for 1d4 of the shrieker's turns afterward.

\hypertarget{violet-fungus}{%
\subsubsection{Violet Fungus}\label{violet-fungus}}

\emph{Medium plant, unaligned}

\textbf{Armor Class} 5

\textbf{Hit Points} 18 (4d8)

\textbf{Speed} 5 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
3 (−4) & 1 (−5) & 10 (+0) & 1 (−5) & 3 (−4) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Condition Immunities} blinded, deafened, frightened

\textbf{Senses} blindsight 30 ft. (blind beyond this radius), passive
Perception 6

\textbf{Languages} ---

\textbf{Challenge} ¼ (50 XP)

\textbf{False Appearance.} While the violet fungus remains motionless,
it is indistinguishable from an ordinary fungus.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The fungus makes 1d4 Rotting Touch attacks.

\textbf{Rotting Touch.} \emph{Melee Weapon Attack:} +2 to hit, reach 10
ft., one creature. \emph{Hit:} 4 (1d8) necrotic damage.

\end{document}
