% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-p}{%
\section{Monsters (P)}\label{monsters-p}}

\hypertarget{pegasus}{%
\subsubsection{Pegasus}\label{pegasus}}

\emph{Large celestial, chaotic good}

\textbf{Armor Class} 12

\textbf{Hit Points} 59 (7d10 + 21)

\textbf{Speed} 60 ft., fly 90 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 10 (+0) & 15 (+2) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Wis +4, Cha +3

\textbf{Skills} Perception +6

\textbf{Senses} passive Perception 16

\textbf{Languages} understands Celestial, Common, Elvish, and Sylvan but
can't speak

\textbf{Challenge} 2 (450 XP)

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Hooves.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) bludgeoning damage.

\hypertarget{pseudodragon}{%
\subsubsection{Pseudodragon}\label{pseudodragon}}

\emph{Tiny dragon, neutral good}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 7 (2d4 + 2)

\textbf{Speed} 15 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
6 (−2) & 15 (+2) & 13 (+1) & 10 (+0) & 12 (+1) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +4

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
13

\textbf{Languages} understands Common and Draconic but can't speak

\textbf{Challenge} ¼ (50 XP)

\textbf{Keen Senses.} The pseudodragon has advantage on Wisdom
(Perception) checks that rely on sight, hearing, or smell.

\textbf{Magic Resistance.} The pseudodragon has advantage on saving
throws against spells and other magical effects.

\textbf{Limited Telepathy.} The pseudodragon can magically communicate
simple ideas, emotions, and images telepathically with any creature
within 100 feet of it that can understand a language.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 4 (1d4 + 2) piercing damage.

\textbf{Sting.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 4 (1d4 + 2) piercing damage, and the target must
succeed on a DC 11 Constitution saving throw or become poisoned for 1
hour. If the saving throw fails by 5 or more, the target falls
unconscious for the same duration, or until it takes damage or another
creature uses an action to shake it awake.

\hypertarget{purple-worm}{%
\subsubsection{Purple Worm}\label{purple-worm}}

\emph{Gargantuan monstrosity, unaligned}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 247 (15d20 + 90)

\textbf{Speed} 50 ft., burrow 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
28 (+9) & 7 (−2) & 22 (+6) & 1 (−5) & 8 (−1) & 4 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +11, Wis +4

\textbf{Senses} blindsight 30 ft., tremorsense 60 ft., passive
Perception 9

\textbf{Languages} ---

\textbf{Challenge} 15 (13,000 XP)

\textbf{Tunneler.} The worm can burrow through solid rock at half its
burrow \textbf{Speed} and leaves a 10-­‐foot-­‐diameter tunnel in its
wake.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The worm makes two attacks: one with its bite and
one with its stinger.

\textbf{Bite.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft., one
target. \emph{Hit:} 22 (3d8 + 9) piercing damage. If the target is a
Large or smaller creature, it must succeed on a DC 19 Dexterity saving
throw or be swallowed by the worm. A swallowed creature is blinded and
restrained, it has total cover against attacks and other effects outside
the worm, and it takes 21 (6d6) acid damage at the start of each of the
worm's turns.

If the worm takes 30 damage or more on a single turn from a creature
inside it, the worm must succeed on a DC 21 Constitution saving throw at
the end of that turn or regurgitate all swallowed creatures, which fall
prone in a space within 10 feet of the worm. If the worm dies, a
swallowed creature is no longer restrained by it and can escape from the
corpse by using 20 feet of movement, exiting prone.

\textbf{Tail Stinger.} \emph{Melee Weapon Attack:} +9 to hit, reach 10
ft., one creature. \emph{Hit:} 19 (3d6 + 9) piercing damage, and the
target must make a DC 19 Constitution saving throw, taking 42 (12d6)
poison damage on a failed save, or half as much damage on a successful
one.

\end{document}
