% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-w}{%
\section{Monsters (W)}\label{monsters-w}}

\hypertarget{wight}{%
\subsubsection{Wight}\label{wight}}

\emph{Medium undead, neutral evil}

\textbf{Armor Class} 14 (studded leather)

\textbf{Hit Points} 45 (6d8 + 18)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 14 (+2) & 16 (+3) & 10 (+0) & 13 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +4

\textbf{Damage Resistances} necrotic; bludgeoning, piercing, and
slashing from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 3 (700 XP)

\textbf{Sunlight Sensitivity.} While in sunlight, the wight has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The wight makes two longsword attacks or two
longbow attacks. It can use its Life Drain in place of one longsword
attack.

\textbf{Life Drain.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one creature. \emph{Hit:} 5 (1d6 + 2) necrotic damage. The target must
succeed on a DC 13 Constitution saving throw or its hit point maximum is
reduced by an amount equal to the damage taken. This reduction lasts
until the target finishes a long rest. The target dies if this effect
reduces its hit point maximum to 0.

A humanoid slain by this attack rises 24 hours later as a zombie under
the wight's control, unless the humanoid is restored to life or its body
is destroyed. The wight can have no more than twelve zombies under its
control at one time.

\textbf{Longsword.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d8 + 2) slashing damage, or 7 (1d10 + 2)
slashing damage if used with two hands.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +4 to hit, range 150/600
ft., one target. \emph{Hit:} 6 (1d8 + 2) piercing damage.

\hypertarget{will-o-wisp}{%
\subsubsection{Will-­‐o'-­‐Wisp}\label{will-o-wisp}}

\emph{Tiny undead, chaotic evil}

\textbf{Armor Class} 19

\textbf{Hit Points} 22 (9d4)

\textbf{Speed} 0 ft., fly 50 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
1 (−5) & 28 (+9) & 10 (+0) & 13 (+1) & 14 (+2) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} lightning, poison

\textbf{Damage Resistances} acid, cold, fire, necrotic, thunder;
bludgeoning, piercing, and slashing from nonmagical attacks

\textbf{Condition Immunities} exhaustion, grappled, paralyzed, poisoned,
prone, restrained, unconscious

\textbf{Senses} darkvision 120 ft., passive Perception 12

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 2 (450 XP)

\textbf{Consume Life.} As a bonus action, the will-­‐o'-­‐wisp can
target one creature it can see within 5 feet of it that has 0 hit points
and is still alive. The target must succeed on a DC 10 Constitution
saving throw against this magic or die. If the target dies, the
will-­‐o'-­‐wisp regains 10 (3d6) hit points.

\textbf{Ephemeral.} The will-­‐o'-­‐wisp can't wear or carry anything.

\textbf{Incorporeal Movement.} The will-­‐o'-­‐wisp can move through
other creatures and objects as if they were difficult terrain. It takes
5 (1d10) force damage if it ends its turn inside an object.

\textbf{Variable Illumination.} The will-­‐o'-­‐wisp sheds bright light
in a 5-­‐ to 20-­‐foot radius and dim light for an additional number of
feet equal to the chosen radius. The will-­‐o'-­‐wisp can alter the
radius as a bonus action.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Shock.} Melee Spell Attack: +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 9 (2d8) lightning damage.

\textbf{Invisibility.} The will-­‐o'-­‐wisp and its light magically
become invisible until it attacks or uses its Consume Life, or until its
concentration ends (as if concentrating on a spell).

\hypertarget{wraith}{%
\subsubsection{Wraith}\label{wraith}}

\emph{Medium undead, neutral evil}

\textbf{Armor Class} 13

\textbf{Hit Points} 67 (9d8 + 27)

\textbf{Speed} 0 ft., fly 60 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
6 (−2) & 16 (+3) & 16 (+3) & 12 (+1) & 14 (+2) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} acid, cold, fire, lightning, thunder;
bludgeoning, piercing, and slashing from nonmagical attacks that aren't
silvered

\textbf{Damage Immunities} necrotic, poison

\textbf{Condition Immunities} charmed, exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 5 (1,800 XP)

\textbf{Incorporeal Movement.} The wraith can move through other
creatures and objects as if they were difficult terrain. It takes 5
(1d10) force damage if it ends its turn inside an object.

\textbf{Sunlight Sensitivity.} While in sunlight, the wraith has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Life Drain.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one creature. \emph{Hit:} 21 (4d8 + 3) necrotic damage. The target must
succeed on a DC 14 Constitution saving throw or its hit point maximum is
reduced by an amount equal to the damage taken. This reduction lasts
until the target finishes a long rest. The target dies if this effect
reduces its hit point maximum to 0.

\textbf{Create Specter.} The wraith targets a humanoid within 10 feet of
it that has been dead for no longer than 1 minute and died violently.
The target's spirit rises as a specter in the space of its corpse or in
the nearest unoccupied space. The specter is under the wraith's control.
The wraith can have no more than seven specters under its control at one
time.

\hypertarget{wyvern}{%
\subsubsection{Wyvern}\label{wyvern}}

\emph{Large dragon, unaligned}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 110 (13d10 + 39)

\textbf{Speed} 20 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 10 (+0) & 16 (+3) & 5 (−3) & 12 (+1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} ---

\textbf{Challenge} 6 (2,300 XP)

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The wyvern makes two attacks: one with its bite
and one with its stinger. While flying, it can use its claws in place of
one other attack.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
creature. \emph{Hit:} 11 (2d6 + 4) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) slashing damage.

\textbf{Stinger.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft.,
one creature. \emph{Hit:} 11 (2d6 + 4) piercing damage. The target must
make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on
a failed save, or half as much damage on a successful one.

\end{document}
