% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-i}{%
\section{Monsters (I)}\label{monsters-i}}

\hypertarget{invisible-stalker}{%
\subsubsection{Invisible Stalker}\label{invisible-stalker}}

\emph{Medium elemental, neutral}

\textbf{Armor Class} 14

\textbf{Hit Points} 104 (16d8 + 32)

\textbf{Speed} 50 ft., fly 50 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 19 (+4) & 14 (+2) & 10 (+0) & 15 (+2) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +8, Stealth +10

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained, unconscious

\textbf{Senses} darkvision 60 ft., passive Perception 18

\textbf{Languages} Auran, understands Common but doesn't speak it

\textbf{Challenge} 6 (2,300 XP)

\textbf{Invisibility.} The stalker is invisible.

\textbf{Faultless Tracker.} The stalker is given a quarry by its
summoner. The stalker knows the direction and distance to its quarry as
long as the two of them are on the same plane of existence. The stalker
also knows the location of its summoner.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The stalker makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) bludgeoning damage.

\end{document}
