% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-e}{%
\section{Monsters (E)}\label{monsters-e}}

\hypertarget{elementals}{%
\subsection{Elementals}\label{elementals}}

\hypertarget{air-elemental}{%
\subsubsection{Air Elemental}\label{air-elemental}}

\emph{Large elemental, neutral}

\textbf{Armor Class} 15

\textbf{Hit Points} 90 (12d10 + 24)

\textbf{Speed} 0 ft., fly 90 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 20 (+5) & 14 (+2) & 6 (−2) & 10 (+0) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} lightning, thunder; bludgeoning, piercing,
and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained, unconscious

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Auran

\textbf{Challenge} 5 (1,800 XP)

\textbf{Air Form.} The elemental can enter a hostile creature's space
and stop there. It can move through a space as narrow as 1 inch wide
without squeezing.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The elemental makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d8 + 5) bludgeoning damage.

\textbf{Whirlwind (Recharge 4--6).} Each creature in the elemental's
space must make a DC 13 Strength saving throw. On a failure, a target
takes 15 (3d8 + 2) bludgeoning damage and is flung up 20 feet away from
the elemental in a random direction and knocked prone. If a thrown
target strikes an object, such as a wall or floor, the target takes 3
(1d6) bludgeoning damage for every 10 feet it was thrown. If the target
is thrown at another creature, that creature must succeed on a DC 13
Dexterity saving throw or take the same damage and be knocked prone. If
the saving throw is successful, the target takes half the bludgeoning
damage and isn't flung away or knocked prone.

\hypertarget{earth-elemental}{%
\subsubsection{Earth Elemental}\label{earth-elemental}}

\emph{Large elemental, neutral}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 126 (12d10 + 60)

\textbf{Speed} 30 ft., burrow 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 8 (−1) & 20 (+5) & 5 (−3) & 10 (+0) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Vulnerabilities} thunder

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, paralyzed, petrified,
poisoned, unconscious

\textbf{Senses} darkvision 60 ft., tremorsense 60 ft., passive
Perception 10

\textbf{Languages} Terran

\textbf{Challenge} 5 (1,800 XP)

\textbf{Earth Glide.} The elemental can burrow through nonmagical,
unworked earth and stone. While doing so, the elemental doesn't disturb
the material it moves through.

\textbf{Siege Monster.} The elemental deals double damage to objects and
structures.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The elemental makes two slam attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 14 (2d8 + 5) bludgeoning damage.

\hypertarget{fire-elemental}{%
\subsubsection{Fire Elemental}\label{fire-elemental}}

\emph{Large elemental, neutral}

\textbf{Armor Class} 13

\textbf{Hit Points} 102 (12d10 + 36)

\textbf{Speed} 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 17 (+3) & 16 (+3) & 6 (−2) & 10 (+0) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained, unconscious

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Ignan

\textbf{Challenge} 5 (1,800 XP)

\textbf{Fire Form.} The elemental can move through a space as narrow as
1 inch wide without squeezing. A creature that touches the elemental or
hits it with a melee attack while within 5 feet of it takes 5 (1d10)
fire damage. In addition, the elemental can enter a hostile creature's
space and stop there. The first time it enters a creature's space on a
turn, that creature takes 5 (1d10) fire damage and catches fire; until
someone takes an action to douse the fire, the creature takes 5 (1d10)
fire damage at the start of each of its turns.

\textbf{Illumination.} The elemental sheds bright light in a 30-­‐ foot
radius and dim light in an additional 30 feet.

\textbf{Water Susceptibility.} For every 5 feet the elemental moves in
water, or for every gallon of water splashed on it, it takes 1 cold
damage.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The elemental makes two touch attacks.

\textbf{Touch.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) fire damage. If the target is a
creature or a flammable object, it ignites. Until a creature takes an
action to douse the fire, the target takes 5 (1d10) fire damage at the
start of each of its turns.

\hypertarget{water-elemental}{%
\subsubsection{Water Elemental}\label{water-elemental}}

\emph{Large elemental, neutral}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 114 (12d10 + 48)

\textbf{Speed} 30 ft., swim 90 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 14 (+2) & 18 (+4) & 5 (−3) & 10 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} acid; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained, unconscious

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Aquan

\textbf{Challenge} 5 (1,800 XP)

\textbf{Water Form.} The elemental can enter a hostile creature's space
and stop there. It can move through a space as narrow as 1 inch wide
without squeezing.

\textbf{Freeze.} If the elemental takes cold damage, it partially
freezes; its speed is reduced by 20 feet until the end of its next turn.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The elemental makes two slam attacks.

\textbf{Slam.} Melee *Weapon Attack: *+7 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage.

\textbf{Whelm (Recharge 4--6).} Each creature in the elemental's space
must make a DC 15 Strength saving throw. On a failure, a target takes 13
(2d8 + 4) bludgeoning damage. If it is Large or smaller, it is also
grappled (escape DC 14). Until this grapple ends, the target is
restrained and unable to breathe unless it can breathe water. If the
saving throw is successful, the target is pushed out of the elemental's
space.

The elemental can grapple one Large creature or up to two Medium or
smaller creatures at one time. At the start of each of the elemental's
turns, each target grappled by it takes 13 (2d8 + 4) bludgeoning damage.
A creature within 5 feet of the elemental can pull a creature or object
out of it by taking an action to make a DC 14 Strength and succeeding.

\hypertarget{elf-drow}{%
\subsubsection{Elf, Drow}\label{elf-drow}}

\emph{Medium humanoid (elf), neutral evil}

\textbf{Armor Class} 15 (chain shirt)

\textbf{Hit Points} 13 (3d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 14 (+2) & 10 (+0) & 11 (+0) & 11 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2, Stealth +4

\textbf{Senses} darkvision 120 ft., passive Perception 12

\textbf{Languages} Elvish, Undercommon

\textbf{Challenge} ¼ (50 XP)

\textbf{Fey Ancestry.} The drow has advantage on saving throws against
being charmed, and magic can't put the drow to sleep.

\textbf{Innate Spellcasting.} The drow's spellcasting ability is
Charisma (spell save DC 11). It can innately cast the following spells,
requiring no material components:

At will: \emph{dancing lights}

1/day each: \emph{darkness}, \emph{faerie fire}

\textbf{Sunlight Sensitivity.} While in sunlight, the drow has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Hand Crossbow.} \emph{Ranged Weapon Attack:} +4 to hit, range
30/120 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing damage, and the
target must succeed on a DC 13 Constitution saving throw or be poisoned
for 1 hour. If the saving throw fails by 5 or more, the target is also
unconscious while poisoned in this way. The target wakes up if it takes
damage or if another creature takes an action to shake it awake.

\hypertarget{ettercap}{%
\subsubsection{Ettercap}\label{ettercap}}

\emph{Medium monstrosity, neutral evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 44 (8d8 + 8)

\textbf{Speed} 30 ft., climb 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 15 (+2) & 13 (+1) & 7 (−2) & 12 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +4, Survival +3

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Spider Climb.} The ettercap can climb difficult surfaces,
including upside down on ceilings, without needing to make an ability
check.

\textbf{Web Sense.} While in contact with a web, the ettercap knows the
exact location of any other creature in contact with the same web.

\textbf{Web Walker.} The ettercap ignores movement restrictions caused
by webbing.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Multiattack.} The ettercap makes two attacks: one with its bite
and one with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 6 (1d8 + 2) piercing damage plus 4 (1d8) poison
damage. The target must succeed on a DC 11 Constitution saving throw or
be poisoned for 1 minute. The creature can repeat the saving throw at
the end of each of its turns, ending the effect on itself on a success.

\textbf{Claws.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (2d4 + 2) slashing damage.

\textbf{Web (Recharge 5--6).} \emph{Ranged Weapon Attack:} +4 to hit,
range 30/60 ft., one Large or smaller creature. \emph{Hit:} The creature
is restrained by webbing. As an action, the restrained creature can make
a DC 11 Strength check, escaping from the webbing on a success. The
effect also ends if the webbing is destroyed. The webbing has AC 10, 5
hit points, vulnerability to fire damage, and immunity to bludgeoning,
poison, and psychic damage.

\hypertarget{ettin}{%
\subsubsection{Ettin}\label{ettin}}

\emph{Large giant, chaotic evil}

\textbf{Armor Class} 12 (natural armor)

\textbf{Hit Points} 85 (10d10 + 30)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 8 (−1) & 17 (+3) & 6 (−2) & 10 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Giant, Orc

\textbf{Challenge} 4 (1,100 XP)

\textbf{Two Heads.} The ettin has advantage on Wisdom (Perception)
checks and on saving throws against being blinded, charmed, deafened,
frightened, stunned, and knocked unconscious.

\textbf{Wakeful.} When one of the ettin's heads is asleep, its other
head is awake.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Multiattack.} The ettin makes two attacks: one with its
battleaxe and one with its morningstar.

\textbf{Battleaxe.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft.,
one target. \emph{Hit:} 14 (2d8 + 5) slashing damage.

\textbf{Morningstar.} \emph{Melee Weapon Attack:} +7 to hit, reach 5
ft., one target. \emph{Hit:} 14 (2d8 + 5) piercing damage.

\end{document}
