% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-z}{%
\section{Monsters (Z)}\label{monsters-z}}

\hypertarget{zombies}{%
\subsection{Zombies}\label{zombies}}

\hypertarget{zombie}{%
\subsubsection{Zombie}\label{zombie}}

\emph{Medium undead, neutral evil}

\textbf{Armor Class} 8

\textbf{Hit Points} 22 (3d8 + 9)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 6 (−2) & 16 (+3) & 3 (−4) & 6 (−2) & 5 (-3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Wis +0

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 8

\textbf{Languages} understands the languages it knew in life but can't
speak

\textbf{Challenge} ¼ (50 XP)

\textbf{Undead Fortitude.} If damage reduces the zombie to 0 hit points,
it must make a Constitution saving throw with a DC of 5 + the damage
taken, unless the damage is radiant or from a critical hit. On a
success, the zombie drops to 1 hit point instead.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Slam.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 4 (1d6 + 1) bludgeoning damage.

\hypertarget{ogre-zombie}{%
\subsubsection{Ogre Zombie}\label{ogre-zombie}}

\emph{Large undead, neutral evil}

\textbf{Armor Class} 8

\textbf{Hit Points} 85 (9d10 + 36)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 6 (−2) & 18 (+4) & 3 (−4) & 6 (−2) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Wis +0

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 8

\textbf{Languages} understands Common and Giant but can't speak

\textbf{Challenge} 2 (450 XP)

\textbf{Undead Fortitude.} If damage reduces the zombie to 0 hit points,
it must make a Constitution saving throw with a DC of 5 + the damage
taken, unless the damage is radiant or from a critical hit. On a
success, the zombie drops to 1 hit point instead.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Morningstar.} \emph{Melee Weapon Attack:} +6 to hit, reach 5
ft., one target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage.

\end{document}
