% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-m}{%
\section{Monsters (M)}\label{monsters-m}}

\hypertarget{magmin}{%
\subsubsection{Magmin}\label{magmin}}

\emph{Small elemental, chaotic neutral}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 9 (2d6 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
7 (−2) & 15 (+2) & 12 (+1) & 8 (−1) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} fire

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Ignan

\textbf{Challenge} ½ (100 XP)

\textbf{Death Burst.} When the magmin dies, it explodes in a burst of
fire and magma. Each creature within 10 feet of it must make a DC 11
Dexterity saving throw, taking 7 (2d6) fire damage on a failed save, or
half as much damage on a successful one. Flammable objects that aren't
being worn or carried in that area are ignited.

\textbf{Ignited Illumination.} As a bonus action, the magmin can set
itself ablaze or extinguish its flames. While ablaze, the magmin sheds
bright light in a 10-­‐foot radius and dim light for an additional 10
feet.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Touch.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (2d6) fire damage. If the target is a creature or
a flammable object, it ignites. Until a creature takes an action to
douse the fire, the target takes 3 (1d6) fire damage at the end of each
of its turns.

\hypertarget{manticore}{%
\subsubsection{Manticore}\label{manticore}}

\emph{Large monstrosity, lawful evil}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 68 (8d10 + 24)

\textbf{Speed} 30 ft., fly 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 16 (+3) & 17 (+3) & 7 (−2) & 12 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} Common

\textbf{Challenge} 3 (700 XP)

\textbf{Tail Spike Regrowth.} The manticore has twenty-­‐four tail
spikes. Used spikes regrow when the manticore finishes a long rest.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The manticore makes three attacks: one with its
bite and two with its claws or three with its tail spikes.

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d8 + 3) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 6 (1d6 + 3) slashing damage.

\textbf{Tail Spike.} \emph{Ranged Weapon Attack:} +5 to hit, range
100/200 ft., one target. \emph{Hit:} 7 (1d8 + 3) piercing damage.

\hypertarget{medusa}{%
\subsubsection{Medusa}\label{medusa}}

\emph{Medium monstrosity, lawful evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 127 (17d8 + 51)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 15 (+2) & 16 (+3) & 12 (+1) & 13 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +5, Insight +4, Perception +4, Stealth +5

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Common

\textbf{Challenge} 6 (2,300 XP)

\textbf{Petrifying Gaze.} When a creature that can see the medusa's eyes
starts its turn within 30 feet of the medusa, the medusa can force it to
make a DC 14 Constitution saving throw if the medusa isn't incapacitated
and can see the creature. If the saving throw fails by 5 or more, the
creature is instantly petrified. Otherwise, a creature that fails the
save begins to turn to stone and is restrained. The restrained creature
must repeat the saving throw at the end of its next turn, becoming
petrified on a failure or ending the effect on a success. The
petrification lasts until the creature is freed by the \emph{greater
restoration} spell or other magic.

Unless surprised, a creature can avert its eyes to avoid the saving
throw at the start of its turn. If the creature does so, it can't see
the medusa until the start of its next turn, when it can avert its eyes
again. If the creature looks at the medusa in the meantime, it must
immediately make the save.

If the medusa sees itself reflected on a polished surface within 30 feet
of it and in an area of bright light, the medusa is, due to its curse,
affected by its own gaze.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The medusa makes either three melee attacks---one
with its snake hair and two with its shortsword---or two ranged attacks
with its longbow.

\textbf{Snake Hair.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one creature. \emph{Hit:} 4 (1d4 + 2) piercing damage plus 14 (4d6)
poison damage.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +5 to hit, range 150/600
ft., one target. \emph{Hit:} 6 (1d8 + 2) piercing damage plus 7 (2d6)
poison damage.

\hypertarget{mephits}{%
\subsection{Mephits}\label{mephits}}

\hypertarget{dust-mephit}{%
\subsubsection{Dust Mephit}\label{dust-mephit}}

\emph{Small elemental, neutral evil}

\textbf{Armor Class} 12

\textbf{Hit Points} 17 (5d6)

\textbf{Speed} 30 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
5 (−3) & 14 (+2) & 10 (+0) & 9 (−1) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2, Stealth +4

\textbf{Damage Vulnerabilities} fire

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} Auran, Terran

\textbf{Challenge} ½ (100 XP)

\textbf{Death Burst.} When the mephit dies, it explodes in a burst of
dust. Each creature within 5 feet of it must then succeed on a DC 10
Constitution saving throw or be blinded for 1 minute. A blinded creature
can repeat the saving throw on each of its turns, ending the effect on
itself on a success.

\textbf{Innate Spellcasting (1/Day).} The mephit can innately cast
\emph{sleep}, requiring no material components. Its innate spellcasting
ability is Charisma.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 4 (1d4 + 2) slashing damage.

\textbf{Blinding Breath (Recharge 6).} The mephit exhales a 15-­‐ foot
cone of blinding dust. Each creature in that area must succeed on a DC
10 Dexterity saving throw or be blinded for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\hypertarget{ice-mephit}{%
\subsubsection{Ice Mephit}\label{ice-mephit}}

\emph{Small elemental, neutral evil}

\textbf{Armor Class} 11

\textbf{Hit Points} 21 (6d6)

\textbf{Speed} 30 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
7 (−2) & 13 (+1) & 10 (+0) & 9 (−1) & 11 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2, Stealth +3

\textbf{Damage Vulnerabilities} bludgeoning, fire

\textbf{Damage Immunities} cold, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} Aquan, Auran

\textbf{Challenge} ½ (100 XP)

\textbf{Death Burst.} When the mephit dies, it explodes in a burst of
jagged ice. Each creature within 5 feet of it must make a DC 10
Dexterity saving throw, taking 4 (1d8) slashing damage on a failed save,
or half as much damage on a successful one.

\textbf{False Appearance.} While the mephit remains motionless, it is
indistinguishable from an ordinary shard of ice.

\textbf{Innate Spellcasting (1/Day).} The mephit can innately cast
\emph{fog cloud}, requiring no material components. Its innate
spellcasting ability is Charisma.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
creature. \emph{Hit:} 3 (1d4 + 1) slashing damage plus 2 (1d4) cold
damage.

\textbf{Frost Breath (Recharge 6).} The mephit exhales a 15-­‐ foot cone
of cold air. Each creature in that area must succeed on a DC 10
Dexterity saving throw, taking 5 (2d4) cold damage on a failed save, or
half as much damage on a successful one.

\hypertarget{magma-mephit}{%
\subsubsection{Magma Mephit}\label{magma-mephit}}

\emph{Small elemental, neutral evil}

\textbf{Armor Class} 11

\textbf{Hit Points} 22 (5d6 + 5)

\textbf{Speed} 30 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
8 (−1) & 12 (+1) & 12 (+1) & 7 (−2) & 10 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +3

\textbf{Damage Vulnerabilities} cold

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Ignan, Terran

\textbf{Challenge} ½ (100 XP)

\textbf{Death Burst.} When the mephit dies, it explodes in a burst of
lava. Each creature within 5 feet of it must make a DC 11 Dexterity
saving throw, taking 7 (2d6) fire damage on a failed save, or half as
much damage on a successful one.

\textbf{False Appearance.} While the mephit remains motionless, it is
indistinguishable from an ordinary mound of magma.

\textbf{Innate Spellcasting (1/Day).} The mephit can innately cast
\emph{heat metal} (spell save DC 10), requiring no material components.
Its innate spellcasting ability is Charisma.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
creature. \emph{Hit:} 3 (1d4 + 1) slashing damage plus 2 (1d4) fire
damage.

\textbf{Fire Breath (Recharge 6).} The mephit exhales a 15-­‐foot cone
of fire. Each creature in that area must make a DC 11 Dexterity saving
throw, taking 7 (2d6) fire damage on a failed save, or half as much
damage on a successful one.

\hypertarget{steam-mephit}{%
\subsubsection{Steam Mephit}\label{steam-mephit}}

\emph{Small elemental, neutral evil}

\textbf{Armor Class} 10

\textbf{Hit Points} 21 (6d6)

\textbf{Speed} 30 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
5 (−3) & 11 (+0) & 10 (+0) & 11 (+0) & 10 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Aquan, Ignan

\textbf{Challenge} ¼ (50 XP)

\textbf{Death Burst.} When the mephit dies, it explodes in a cloud of
steam. Each creature within 5 feet of the mephit must succeed on a DC 10
Dexterity saving throw or take 4 (1d8) fire damage.

\textbf{Innate Spellcasting (1/Day).} The mephit can innately cast
\emph{blur}, requiring no material components. Its innate spellcasting
ability is Charisma.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Claws.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
creature. \emph{Hit:} 2 (1d4) slashing damage plus 2 (1d4) fire damage.

\textbf{Steam Breath (Recharge 6).} The mephit exhales a 15-­‐ foot cone
of scalding steam. Each creature in that area must succeed on a DC 10
Dexterity saving throw, taking 4 (1d8) fire damage on a failed save, or
half as much damage on a successful one.

\hypertarget{merfolk}{%
\subsubsection{Merfolk}\label{merfolk}}

\emph{Medium humanoid (merfolk), neutral}

\textbf{Armor Class} 11

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 10 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 13 (+1) & 12 (+1) & 11 (+0) & 11 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2

\textbf{Senses} passive Perception 12

\textbf{Languages} Aquan, Common

\textbf{Challenge} ⅛ (25 XP)

\textbf{Amphibious.} The merfolk can breathe air and water.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +2 to hit, reach 5
ft. or range 20/60 ft., one target. \emph{Hit:} 3 (1d6) piercing damage,
or 4 (1d8) piercing damage if used with two hands to make a melee
attack.

\hypertarget{merrow}{%
\subsubsection{Merrow}\label{merrow}}

\emph{Large monstrosity, chaotic evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 45 (6d10 + 12)

\textbf{Speed} 10 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 10 (+0) & 15 (+2) & 8 (−1) & 10 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Abyssal, Aquan

\textbf{Challenge} 2 (450 XP)

\textbf{Amphibious.} The merrow can breathe air and water.

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Multiattack.} The merrow makes two attacks: one with its bite
and one with its claws or harpoon.

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d8 + 4) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 9 (2d4 + 4) slashing damage.

\textbf{Harpoon.} \emph{Melee or Ranged Weapon Attack:} +6 to hit, reach
5 ft. or range 20/60 ft., one target. \emph{Hit:} 11 (2d6 + piercing
damage. If the target is a Huge or smaller creature, it must succeed on
a Strength contest against the merrow or be pulled up to 20 feet toward
the merrow.

\hypertarget{mimic}{%
\subsubsection{Mimic}\label{mimic}}

\emph{Medium monstrosity (shapechanger), neutral}

\textbf{Armor Class} 12 (natural armor)

\textbf{Hit Points} 58 (9d8 + 18)

\textbf{Speed} 15 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 12 (+1) & 15 (+2) & 5 (−3) & 13 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +5

\textbf{Damage Immunities} acid

\textbf{Condition Immunities} prone

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Shapechanger.} The mimic can use its action to polymorph into an
object or back into its true, amorphous form. Its statistics are the
same in each form. Any equipment it is wearing or carrying isn't
transformed. It reverts to its true form if it dies.

\textbf{Adhesive (Object Form Only).} The mimic adheres to anything that
touches it. A Huge or smaller creature adhered to the mimic is also
grappled by it (escape DC 13). Ability checks made to escape this
grapple have disadvantage.

\textbf{False Appearance (Object Form Only).} While the mimic remains
motionless, it is indistinguishable from an ordinary object.

\textbf{Grappler.} The mimic has advantage on attack rolls against any
creature grappled by it.

\hypertarget{actions-9}{%
\paragraph{Actions}\label{actions-9}}

\textbf{Pseudopod.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 7 (1d8 + 3) bludgeoning damage. If the mimic is
in object form, the target is subjected to its Adhesive trait.

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d8 + 3) piercing damage plus 4 (1d8) acid
damage.

\hypertarget{minotaur}{%
\subsubsection{Minotaur}\label{minotaur}}

\emph{Large monstrosity, chaotic evil}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 76 (9d10 + 27)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 11 (+0) & 16 (+3) & 6 (−2) & 16 (+3) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +7

\textbf{Senses} darkvision 60 ft., passive Perception 17

\textbf{Languages} Abyssal

\textbf{Challenge} 3 (700 XP)

\textbf{Charge} If the minotaur moves at least 10 feet straight toward a
target and then hits it with a gore attack on the same turn, the target
takes an extra 9 (2d8) piercing damage. If the target is a creature, it
must succeed on a DC 14 Strength saving throw or be pushed up to 10 feet
away and knocked prone.

\textbf{Labyrinthine Recall.} The minotaur can perfectly recall any path
it has traveled.

\textbf{Reckless.} At the start of its turn, the minotaur can gain
advantage on all melee weapon attack rolls it makes during that turn,
but attack rolls against it have advantage until the start of its next
turn.

\hypertarget{actions-10}{%
\paragraph{Actions}\label{actions-10}}

\textbf{Greataxe.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one target. \emph{Hit:} 17 (2d12 + 4) slashing damage.

\textbf{Gore.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) piercing damage.

\hypertarget{mummies}{%
\subsection{Mummies}\label{mummies}}

\hypertarget{mummy}{%
\subsubsection{Mummy}\label{mummy}}

\emph{Medium undead, lawful evil}

\textbf{Armor Class} 11 (natural armor)

\textbf{Hit Points} 58 (9d8 + 18)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 8 (−1) & 15 (+2) & 6 (−2) & 10 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Wis +2

\textbf{Damage Vulnerabilities} fire

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} necrotic, poison

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 3 (700 XP)

\hypertarget{actions-11}{%
\paragraph{Actions}\label{actions-11}}

\textbf{Multiattack.} The mummy can use its Dreadful Glare and makes one
attack with its rotting fist.

\textbf{Rotting Fist.} \emph{Melee Weapon Attack:} +5 to hit, reach 5
ft., one target. \emph{Hit:} 10 (2d6 + 3) bludgeoning damage plus 10
(3d6) necrotic damage. If the target is a creature, it must succeed on a
DC 12 Constitution saving throw or be cursed with mummy rot. The cursed
target can't regain hit points, and its hit point maximum decreases by
10 (3d6) for every 24 hours that elapse. If the curse reduces the
target's hit point maximum to 0, the target dies, and its body turns to
dust. The curse lasts until removed by the remove curse spell or other
magic.

\textbf{Dreadful Glare.} The mummy targets one creature it can see
within 60 feet of it. If the target can see the mummy, it must succeed
on a DC 11 Wisdom saving throw against this magic or become frightened
until the end of the mummy's next turn. If the target fails the saving
throw by 5 or more, it is also paralyzed for the same duration. A target
that succeeds on the saving throw is immune to the Dreadful Glare of all
mummies (but not mummy lords) for the next 24 hours.

\hypertarget{mummy-lord}{%
\subsubsection{Mummy Lord}\label{mummy-lord}}

\emph{Medium undead, lawful evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 97 (13d8 + 39)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 10 (+0) & 17 (+3) & 11 (+0) & 18 (+4) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +8, Int +5, Wis +9, Cha +8

\textbf{Skills} History +5, Religion +5

\textbf{Damage Vulnerabilities} fire

\textbf{Damage Immunities} necrotic, poison; bludgeoning, piercing, and
slashing from nonmagical attacks

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} the languages it knew in life

\textbf{Challenge} 15 (13,000 XP)

\textbf{Magic Resistance.} The mummy lord has advantage on saving throws
against spells and other magical effects.

\textbf{Rejuvenation.} A destroyed mummy lord gains a new body in 24
hours if its heart is intact, regaining all its hit points and becoming
active again. The new body appears within 5 feet of the mummy lord's
heart.

\textbf{Spellcasting.} The mummy lord is a 10th-­‐level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 17, +9 to hit with spell
attacks). The mummy lord has the following cleric spells prepared:

Cantrips (at will): \emph{sacred flame}, \emph{thaumaturgy}

1st level (4 slots): \emph{command}, \emph{guiding bolt}, \emph{shield
of faith}

2nd level (3 slots): \emph{hold person}, \emph{silence}, \emph{spiritual
weapon}

3rd level (3 slots): \emph{animate dead}, \emph{dispel magic}

4th level (3 slots): \emph{divination}, \emph{guardian of faith}

5th level (2 slots): \emph{contagion}, \emph{insect plague}

6th level (1 slot): \emph{harm}

\hypertarget{actions-12}{%
\paragraph{Actions}\label{actions-12}}

\textbf{Multiattack.} The mummy can use its Dreadful Glare and makes one
attack with its rotting fist.

\textbf{Rotting Fist.} \emph{Melee Weapon Attack:} +9 to hit, reach 5
ft., one target. \emph{Hit:} 14 (3d6 + 4) bludgeoning damage plus 21
(6d6) necrotic damage. If the target is a creature, it must succeed on a
DC 16 Constitution saving throw or be cursed with mummy rot. The cursed
target can't regain hit points, and its hit point maximum decreases by
10 (3d6) for every 24 hours that elapse. If the curse reduces the
target's hit point maximum to 0, the target dies, and its body turns to
dust. The curse lasts until removed by the remove curse spell or other
magic.

\textbf{Dreadful Glare.} The mummy lord targets one creature it can see
within 60 feet of it. If the target can see the mummy lord, it must
succeed on a DC 16 Wisdom saving throw against this magic or become
frightened until the end of the mummy's next turn. If the target fails
the saving throw by 5 or more, it is also paralyzed for the same
duration. A target that succeeds on the saving throw is immune to the
Dreadful Glare of all mummies and mummy lords for the next 24 hours.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The mummy lord can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The mummy lord regains spent
legendary actions at the start of its turn.

\textbf{Attack.} The mummy lord makes one attack with its rotting fist
or uses its \textbf{Dreadful Glare.}

\textbf{Blinding Dust.} Blinding dust and sand swirls magically around
the mummy lord. Each creature within 5 feet of the mummy lord must
succeed on a DC 16 Constitution saving throw or be blinded until the end
of the creature's next turn.

\textbf{Blasphemous Word (Costs 2 Actions).} The mummy lord utters a
blasphemous word. Each non-­‐undead creature within 10 feet of the mummy
lord that can hear the magical utterance must succeed on a DC 16
Constitution saving throw or be stunned until the end of the mummy
lord's next turn.

\textbf{Channel Negative Energy (Costs 2 Actions).} The mummy lord
magically unleashes negative energy. Creatures within 60 feet of the
mummy lord, including ones behind barriers and around corners, can't
regain hit points until the end of the mummy lord's next turn.

\textbf{Whirlwind of Sand (Costs 2 Actions).} The mummy lord magically
transforms into a whirlwind of sand, moves up to 60 feet, and reverts to
its normal form. While in whirlwind form, the mummy lord is immune to
all damage, and it can't be grappled, petrified, knocked prone,
restrained, or stunned. Equipment worn or carried by the mummy lord
remain in its possession.

\end{document}
