% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-u}{%
\section{Monsters (U)}\label{monsters-u}}

\hypertarget{unicorn}{%
\subsubsection{Unicorn}\label{unicorn}}

\emph{Large celestial, lawful good}

\textbf{Armor Class} 12

\textbf{Hit Points} 67 (9d10 + 18)

\textbf{Speed} 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 14 (+2) & 15 (+2) & 11 (+0) & 17 (+3) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, paralyzed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} Celestial, Elvish, Sylvan, telepathy 60 ft.

\textbf{Challenge} 5 (1,800 XP)

\textbf{Charge} If the unicorn moves at least 20 feet straight toward a
target and then hits it with a horn attack on the same turn, the target
takes an extra 9 (2d8) piercing damage. If the target is a creature, it
must succeed on a DC 15 Strength saving throw or be knocked prone.

\textbf{Innate Spellcasting.} The unicorn's innate spellcasting ability
is Charisma (spell save DC 14). The unicorn can innately cast the
following spells, requiring no components:

At will: \emph{detect evil and good}, \emph{druidcraft}, \emph{pass
without trace}

1/day each: \emph{calm emotions}, \emph{dispel evil and good},
\emph{entangle}

\textbf{Magic Resistance.} The unicorn has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The unicorn's weapon attacks are magical.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The unicorn makes two attacks: one with its hooves
and one with its horn.

\textbf{Hooves.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) bludgeoning damage.

\textbf{Horn.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d8 + 4) piercing damage.

\textbf{Healing Touch (3/Day).} The unicorn touches another creature
with its horn. The target magically regains 11 (2d8 + 2) hit points. In
addition, the touch removes all diseases and neutralizes all poisons
afflicting the target.

\textbf{Teleport (1/Day).} The unicorn magically teleports itself and up
to three willing creatures it can see within 5 feet of it, along with
any equipment they are wearing or carrying, to a location the unicorn is
familiar with, up to 1 mile away.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The unicorn can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The unicorn regains spent
legendary actions at the start of its turn.

\textbf{Hooves.} The unicorn makes one attack with its hooves.

\textbf{Shimmering Shield (Costs 2 Actions).} The unicorn creates a
shimmering, magical field around itself or another creature it can see
within 60 feet of it. The target gains a +2 bonus to AC until the end of
the unicorn's next turn.

\textbf{heal Self (Costs 3 Actions).} The unicorn magically regains 11
(2d8 + 2) hit points.

\end{document}
