% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-s}{%
\section{Monsters (S)}\label{monsters-s}}

\hypertarget{sahuagin}{%
\subsubsection{Sahuagin}\label{sahuagin}}

\emph{Medium humanoid (sahuagin), lawful evil}

\textbf{Armor Class} 12 (natural armor)

\textbf{Hit Points} 22 (4d8 + 4)

\textbf{Speed} 30 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 11 (+0) & 12 (+1) & 12 (+1) & 13 (+1) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5

\textbf{Senses} darkvision 120 ft., passive Perception 15

\textbf{Languages} Sahuagin

\textbf{Challenge} ½ (100 XP)

\textbf{Blood Frenzy.} The sahuagin has advantage on melee attack rolls
against any creature that doesn't have all its hit points.

\textbf{Limited Amphibiousness.} The sahuagin can breathe air and water,
but it needs to be submerged at least once every 4 hours to avoid
suffocating.

\textbf{Shark Telepathy.} The sahuagin can magically command any shark
within 120 feet of it, using a limited telepathy.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The sahuagin makes two melee attacks: one with its
bite and one with its claws or spear.

\textbf{Bite.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 3 (1d4 + 1) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 3 (1d4 + 1) slashing damage.

\textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +3 to hit, reach 5
ft. or range 20/60 ft., one target. \emph{Hit:} 4 (1d6 +1) piercing
damage, or 5 (1d8 + 1) piercing damage if used with two hands to make a
melee attack.

\hypertarget{salamander}{%
\subsubsection{Salamander}\label{salamander}}

\emph{Large elemental, neutral evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 90 (12d10 + 24)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 14 (+2) & 15 (+2) & 11 (+0) & 10 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Vulnerabilities} cold

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} fire

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Ignan

\textbf{Challenge} 5 (1,800 XP)

\textbf{Heated Body.} A creature that touches the salamander or hits it
with a melee attack while within 5 feet of it takes 7 (2d6) fire damage.

\textbf{Heated Weapons.} Any metal melee weapon the salamander wields
deals an extra 3 (1d6) fire damage on a hit (included in the attack).

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The salamander makes two attacks: one with its
spear and one with its tail.

\textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +7 to hit, reach 5
ft. or range 20 ft./60 ft., one target. \emph{Hit:} 11 (2d6 + 4)
piercing damage, or 13 (2d8 + 4) piercing damage if used with two hands
to make a melee attack, plus 3 (1d6) fire damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 11 (2d6 + 4) bludgeoning damage plus 7 (2d6) fire
damage, and the target is grappled (escape DC 14). Until this grapple
ends, the target is restrained, the salamander can automatically hit the
target with its tail, and the salamander can't make tail attacks against
other targets.

\hypertarget{satyr}{%
\subsubsection{Satyr}\label{satyr}}

\emph{Medium fey, chaotic neutral}

\textbf{Armor Class} 14 (leather armor)

\textbf{Hit Points} 31 (7d8)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
12 (+1) & 16 (+3) & 11 (+0) & 12 (+1) & 10 (+0) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2, Performance +6, Stealth +5

\textbf{Senses} passive Perception 12

\textbf{Languages} Common, Elvish, Sylvan

\textbf{Challenge} ½ (100 XP)

\textbf{Magic Resistance.} The satyr has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Ram.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 6 (2d4 + 1) bludgeoning damage.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) piercing damage.

\textbf{Shortbow.} \emph{Ranged Weapon Attack:} +5 to hit, range 80/320
ft., one target. \emph{Hit:} 6 (1d6 + 3) piercing damage.

\hypertarget{shadow}{%
\subsubsection{Shadow}\label{shadow}}

\emph{Medium undead, chaotic evil}

\textbf{Armor Class} 12

\textbf{Hit Points} 16 (3d8 + 3)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
6 (−2) & 14 (+2) & 13 (+1) & 6 (−2) & 10 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +4 (+6 in dim light or darkness)

\textbf{Damage Vulnerabilities} radiant

\textbf{Damage Resistances} acid, cold, fire, lightning, thunder;
bludgeoning, piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} necrotic, poison

\textbf{Condition Immunities} exhaustion, frightened, grappled,
paralyzed, petrified, poisoned, prone, restrained

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} ---

\textbf{Challenge} ½ (100 XP)

\textbf{Regeneration.} The shadow can move through a space as narrow as
1 inch wide without squeezing.

\textbf{Shadow Stealth.} While in dim light or darkness, the shadow can
take the Hide action as a bonus action.

\textbf{Sunlight Weakness.} While in sunlight, the shadow has
disadvantage on attack rolls, ability checks, and \textbf{Saving
Throws}.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Strength Drain.} \emph{Melee Weapon Attack:} +4 to hit, reach 5
ft., one creature. \emph{Hit:} 9 (2d6 + 2) necrotic damage, and the
target's Strength score is reduced by 1d4. The target dies if this
reduces its Strength to 0. Otherwise, the reduction lasts until the
target finishes a short or long rest.

If a non-­‐evil humanoid dies from this attack, a new shadow rises from
the corpse 1d4 hours later.

\hypertarget{shambling-mound}{%
\subsubsection{Shambling Mound}\label{shambling-mound}}

\emph{Large plant, unaligned}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 136 (16d10 + 48)

\textbf{Speed} 20 ft., swim 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 8 (−1) & 16 (+3) & 5 (−3) & 10 (+0) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +2

\textbf{Damage Resistances} cold, fire

\textbf{Damage Immunities} lightning

\textbf{Condition Immunities} blinded, deafened, exhaustion

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 10

\textbf{Languages} ---

\textbf{Challenge} 5 (1,800 XP)

\textbf{Lightning Absorption.} Whenever the shambling mound is subjected
to lightning damage, it takes no damage and regains a number of hit
points equal to the lightning damage dealt.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Multiattack.} The shambling mound makes two slam attacks. If
both attacks hit a Medium or smaller target, the target is grappled
(escape DC 14), and the shambling mound uses its Engulf on it.

\textbf{Slam.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage.

\textbf{Engulf.} The shambling mound engulfs a Medium or smaller
creature grappled by it. The engulfed target is blinded, restrained, and
unable to breathe, and it must succeed on a DC 14 Constitution saving
throw at the start of each of the mound's turns or take 13 (2d8 + 4)
bludgeoning damage. If the mound moves, the engulfed target moves with
it. The mound can have only one creature engulfed at a time.

\hypertarget{shield-guardian}{%
\subsubsection{Shield Guardian}\label{shield-guardian}}

\emph{Large construct, unaligned}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 142 (15d10 + 60)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 8 (−1) & 18 (+4) & 7 (−2) & 10 (+0) & 3 (−4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
10

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, exhaustion, frightened,
paralyzed, poisoned

\textbf{Languages} understands commands given in any language but can't
speak

\textbf{Challenge} 7 (2,900 XP)

\textbf{Bound.} The shield guardian is magically bound to an amulet. As
long as the guardian and its amulet are on the same plane of existence,
the amulet's wearer can telepathically call the guardian to travel to
it, and the guardian knows the distance and direction to the amulet. If
the guardian is within 60 feet of the amulet's wearer, half of any
damage the wearer takes (rounded up) is transferred to the guardian.

\textbf{Regeneration.} The shield guardian regains 10 hit points at the
start of its turn if it has at least 1 hit point.

\textbf{Spell Storing.} A spellcaster who wears the shield guardian's
amulet can cause the guardian to store one spell of 4th level or lower.
To do so, the wearer must cast the spell on the guardian. The spell has
no effect but is stored within the guardian. When commanded to do so by
the wearer or when a situation arises that was predefined by the
spellcaster, the guardian casts the stored spell with any parameters set
by the original caster, requiring no components. When the spell is cast
or a new spell is stored, any previously stored spell is lost.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Multiattack.} The guardian makes two fist attacks.

\textbf{Fist.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) bludgeoning damage.

\hypertarget{reactions}{%
\paragraph{Reactions}\label{reactions}}

\textbf{Shield.} When a creature makes an attack against the wearer of
the guardian's amulet, the guardian grants a +2 bonus to the wearer's AC
if the guardian is within 5 feet of the wearer.

\hypertarget{skeletons}{%
\subsection{Skeletons}\label{skeletons}}

\hypertarget{skeleton}{%
\subsubsection{Skeleton}\label{skeleton}}

\emph{Medium undead, lawful evil}

\textbf{Armor Class} 13 (armor scraps)

\textbf{Hit Points} 13 (2d8 + 4)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 14 (+2) & 15 (+2) & 6 (-2) & 8 (-1) & 5 (-3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Vulnerabilities} bludgeoning

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} understands Abyssal but can't speak

\textbf{Challenge} ¼ (50 XP)

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Shortbow.} \emph{Ranged Weapon Attack:} +4 to hit, range 80/320
ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\hypertarget{minotaur-skeleton}{%
\subsubsection{Minotaur Skeleton}\label{minotaur-skeleton}}

\emph{Large undead, lawful evil}

\textbf{Armor Class} 12 (natural armor)

\textbf{Hit Points} 67 (9d10 + 18)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 11 (+0) & 15 (+2) & 6 (-2) & 8 (-1) & 5 (-3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Vulnerabilities} bludgeoning

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} understands all languages it knew in life but can't
speak

\textbf{Challenge} 2 (450 XP)

\textbf{Charge} If the skeleton moves at least 10 feet straight toward a
target and then hits it with a gore attack on the same turn, the target
takes an extra 9 (2d8) piercing damage. If the target is a creature, it
must succeed on a DC 14 Strength saving throw or be pushed up to 10 feet
away and knocked prone.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Greataxe.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one target. \emph{Hit:} 17 (2d12 + 4) slashing damage.

\textbf{Gore.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) piercing damage.

\hypertarget{warhorse-skeleton}{%
\subsubsection{Warhorse Skeleton}\label{warhorse-skeleton}}

\emph{Large undead, lawful evil}

\textbf{Armor Class} 13 (barding scraps)

\textbf{Hit Points} 22 (3d10 + 6)

\textbf{Speed} 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 12 (+1) & 15 (+2) & 2 (−4) & 8 (−1) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Vulnerabilities} bludgeoning

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} exhaustion, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} ---

\textbf{Challenge} ½ (100 XP)

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Hooves.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) bludgeoning damage.

\hypertarget{specter}{%
\subsubsection{Specter}\label{specter}}

\emph{Medium undead, chaotic evil}

\textbf{Armor Class} 12

\textbf{Hit Points} 22 (5d8)

\textbf{Speed} 0 ft., fly 50 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
1 (−5) & 14 (+2) & 11 (+0) & 10 (+0) & 10 (+0) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} acid, cold, fire, lightning, thunder;
bludgeoning, piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} necrotic, poison

\textbf{Condition Immunities} charmed, exhaustion, grappled, paralyzed,
petrified, poisoned, prone, restrained, unconscious

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} understands all languages it knew in life but can't
speak

\textbf{Challenge} 1 (200 XP)

\textbf{Incorporeal Movement.} The specter can move through other
creatures and objects as if they were difficult terrain. It takes 5
(1d10) force damage if it ends its turn inside an object.

\textbf{Sunlight Sensitivity.} While in sunlight, the specter has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions-9}{%
\paragraph{Actions}\label{actions-9}}

\textbf{Life Drain.} Melee Spell Attack: +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 10 (3d6) necrotic damage. The target must succeed
on a DC 10 Constitution saving throw or its hit point maximum is reduced
by an amount equal to the damage taken. This reduction lasts until the
creature finishes a long rest. The target dies if this effect reduces
its hit point maximum to 0.

\hypertarget{sphinxes}{%
\subsection{Sphinxes}\label{sphinxes}}

\hypertarget{androsphinx}{%
\subsubsection{Androsphinx}\label{androsphinx}}

\emph{Large monstrosity, lawful neutral}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 199 (19d10 + 95)

\textbf{Speed} 40 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 10 (+0) & 20 (+5) & 16 (+3) & 18 (+4) & 23 (+6)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +11, Int +9, Wis +10

\textbf{Skills} Arcana +9, Perception +10, Religion +15

\textbf{Damage Immunities} psychic; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Condition Immunities} charmed, frightened

\textbf{Senses} truesight 120 ft., passive Perception 20

\textbf{Languages} Common, Sphinx

\textbf{Challenge} 17 (18,000 XP)

\textbf{Inscrutable.} The sphinx is immune to any effect that would
sense its emotions or read its thoughts, as well as any divination spell
that it refuses. Wisdom (Insight) checks made to ascertain the sphinx's
intentions or sincerity have disadvantage.

\textbf{Magic Weapons.} The sphinx's weapon attacks are magical.

\textbf{Spellcasting.} The sphinx is a 12th-­‐level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 18, +10 to hit with spell
attacks). It requires no material components to cast its spells. The
sphinx has the following cleric spells prepared:

Cantrips (at will): \emph{sacred flame}, \emph{spare the dying},
\emph{thaumaturgy}

1st level (4 slots): \emph{command}, \emph{detect evil and good},
\emph{detect magic}

2nd level (3 slots): \emph{lesser restoration}, \emph{zone of truth}

3rd level (3 slots): \emph{dispel magic}, \emph{tongues}

4th level (3 slots): \emph{banishment}, \emph{freedom of movement}

5th level (2 slots): \emph{flame strike}, \emph{greater restoration}

6th level (1 slot): \emph{heroes' feast}

\hypertarget{actions-10}{%
\paragraph{Actions}\label{actions-10}}

\textbf{Multiattack.} The sphinx makes two claw attacks.

\textbf{Claw.} \emph{Melee Weapon Attack:} +12 to hit, reach 5 ft., one
target. \emph{Hit:} 17 (2d10 + 6) slashing damage.

\textbf{Roar (3/Day).} The sphinx emits a magical roar. Each time it
roars before finishing a long rest, the roar is louder and the effect is
different, as detailed below. Each creature within 500 feet of the
sphinx and able to hear the roar must make a saving throw.

\textbf{First Roar.} Each creature that fails a DC 18 Wisdom saving
throw is frightened for 1 minute. A frightened creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\textbf{Second Roar.} Each creature that fails a DC 18 Wisdom saving
throw is deafened and frightened for 1 minute. A frightened creature is
paralyzed and can repeat the saving throw at the end of each of its
turns, ending the effect on itself on a success.

\textbf{Third Roar.} Each creature makes a DC 18 Constitution saving
throw. On a failed save, a creature takes 44 (8d10) thunder damage and
is knocked prone. On a successful save, the creature takes half as much
damage and isn't knocked prone.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The sphinx can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The sphinx regains spent
legendary actions at the start of its turn.

\textbf{Claw Attack.} The sphinx makes one claw attack.

\textbf{Teleport (Costs 2 Actions).} The sphinx magically teleports,
along with any equipment it is wearing or carrying, up to 120 feet to an
unoccupied space it can see.

\textbf{Cast a Spell (Costs 3 Actions).} The sphinx casts a spell from
its list of prepared spells, using a spell slot as normal.

\hypertarget{gynosphinx}{%
\subsubsection{Gynosphinx}\label{gynosphinx}}

\emph{Large monstrosity, lawful neutral}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 136 (16d10 + 48)

\textbf{Speed} 40 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 18 (+4) & 18 (+4) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Arcana +12, History +12, Perception +8, Religion +8

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Damage Immunities} psychic

\textbf{Condition Immunities} charmed, frightened

\textbf{Senses} truesight 120 ft., passive Perception 18

\textbf{Languages} Common, Sphinx

\textbf{Challenge} 11 (7,200 XP)

\textbf{Inscrutable.} The sphinx is immune to any effect that would
sense its emotions or read its thoughts, as well as any divination spell
that it refuses. Wisdom (Insight) checks made to ascertain the sphinx's
intentions or sincerity have disadvantage.

\textbf{Magic Weapons.} The sphinx's weapon attacks are magical.

\textbf{Spellcasting.} The sphinx is a 9th-­‐level spellcaster. Its
spellcasting ability is Intelligence (spell save DC 16, +8 to hit with
spell attacks). It requires no material components to cast its spells.
The sphinx has the following wizard spells prepared:

Cantrips (at will): \emph{mage hand}, \emph{minor illusion},
\emph{prestidigitation}

1st level (4 slots): \emph{detect magic}, \emph{identify}, \emph{shield}

2nd level (3 slots): \emph{darkness}, \emph{locate object},
\emph{suggestion}

3rd level (3 slots): \emph{dispel magic}, \emph{remove curse},
\emph{tongues}

4th level (3 slots): \emph{banishment}, \emph{greater invisibility}

5th level (1 slot): \emph{legend lore}

\hypertarget{actions-11}{%
\paragraph{Actions}\label{actions-11}}

\textbf{Multiattack.} The sphinx makes two claw attacks.

\textbf{Claw.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) slashing damage.

\hypertarget{legendary-actions-1}{%
\paragraph{Legendary Actions}\label{legendary-actions-1}}

The sphinx can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The sphinx regains spent
legendary actions at the start of its turn.

\textbf{Claw Attack.} The sphinx makes one claw attack.

\textbf{Teleport (Costs 2 Actions).} The sphinx magically teleports,
along with any equipment it is wearing or carrying, up to 120 feet to an
unoccupied space it can see.

\textbf{Cast a Spell (Costs 3 Actions).} The sphinx casts a spell from
its list of prepared spells, using a spell slot as normal.

\hypertarget{sprite}{%
\subsubsection{Sprite}\label{sprite}}

\emph{Tiny fey, neutral good}

\textbf{Armor Class} 15 (leather armor)

\textbf{Hit Points} 2 (1d4)

\textbf{Speed} 10 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
3 (−4) & 18 (+4) & 10 (+0) & 14 (+2) & 13 (+1) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +8

\textbf{Senses} passive Perception 13

\textbf{Languages} Common, Elvish, Sylvan

\textbf{Challenge} ¼ (50 XP)

\hypertarget{actions-12}{%
\paragraph{Actions}\label{actions-12}}

\textbf{Longsword.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft.,
one target. \emph{Hit:} 1 slashing damage.

\textbf{Shortbow.} \emph{Ranged Weapon Attack:} +6 to hit, range 40/160
ft., one target. \emph{Hit:} 1 piercing damage, and the target must
succeed on a DC 10 Constitution saving throw or become poisoned for 1
minute. If its saving throw result is 5 or lower, the poisoned target
falls unconscious for the same duration, or until it takes damage or
another creature takes an action to shake it awake.

\textbf{Heart Sight.} The sprite touches a creature and magically knows
the creature's current emotional state. If the target fails a DC 10
Charisma saving throw, the sprite also knows the creature's alignment.
Celestials, fiends, and undead automatically fail the saving throw.

\textbf{Invisibility.} The sprite magically turns invisible until it
attacks or casts a spell, or until its concentration ends (as if
concentrating on a spell). Any equipment the sprite wears or carries is
invisible with it.

\hypertarget{stirge}{%
\subsubsection{Stirge}\label{stirge}}

\emph{Tiny beast, unaligned}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 2 (1d4)

\textbf{Speed} 10 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
4 (−3) & 16 (+3) & 11 (+0) & 2 (−4) & 8 (−1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} ---

\textbf{Challenge} ⅛ (25 XP)

\hypertarget{actions-13}{%
\paragraph{Actions}\label{actions-13}}

\textbf{Blood Drain.} \emph{Melee Weapon Attack:} +5 to hit, reach 5
ft., one creature. \emph{Hit:} 5 (1d4 + 3) piercing damage, and the
stirge attaches to the target. While attached, the stirge doesn't
attack. Instead, at the start of each of the stirge's turns, the target
loses 5 (1d4 + 3) hit points due to blood loss.

The stirge can detach itself by spending 5 feet of its movement. It does
so after it drains 10 hit points of blood from the target or the target
dies. A creature, including the target, can use its action to detach the
stirge.

\hypertarget{succubusincubus}{%
\subsubsection{Succubus/Incubus}\label{succubusincubus}}

\emph{Medium fiend (shapechanger), neutral evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 66 (12d8 + 12)

\textbf{Speed} 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
8 (−1) & 17 (+3) & 13 (+1) & 15 (+2) & 12 (+1) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +9, Insight +5, Perception +5, Persuasion +9,
Stealth +7

\textbf{Damage Resistances} cold, fire, lightning, poison; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Senses} darkvision 60 ft., passive Perception 15

\textbf{Languages} Abyssal, Common, Infernal, telepathy 60 ft.

\textbf{Challenge} 4 (1,100 XP)

\textbf{Telepathic Bond.} The fiend ignores the range restriction on its
telepathy when communicating with a creature it has charmed. The two
don't even need to be on the same plane of existence.

\textbf{Shapechanger.} The fiend can use its action to polymorph into a
Small or Medium humanoid, or back into its true form. Without wings, the
fiend loses its flying speed. Other than its size and speed, its
statistics are the same in each form. Any equipment it is wearing or
carrying isn't transformed. It reverts to its true form if it dies.

\hypertarget{actions-14}{%
\paragraph{Actions}\label{actions-14}}

\textbf{Claw (Fiend Form Only).} \emph{Melee Weapon Attack:} +5 to hit,
reach 5 ft., one target. \emph{Hit:} 6 (1d6 + 3) slashing damage.

\textbf{Charm.} One humanoid the fiend can see within 30 feet of it must
succeed on a DC 15 Wisdom saving throw or be magically charmed for 1
day. The charmed target obeys the fiend's verbal or telepathic commands.
If the target suffers any harm or receives a suicidal command, it can
repeat the saving throw, ending the effect on a success. If the target
successfully saves against the effect, or if the effect on it ends, the
target is immune to this fiend's Charm for the next 24 hours.

The fiend can have only one target charmed at a time. If it charms
another, the effect on the previous target ends.

\textbf{Draining Kiss.} The fiend kisses a creature charmed by it or a
willing creature. The target must make a DC 15

Constitution saving throw against this magic, taking 32 (5d10 + 5)
psychic damage on a failed save, or half as much damage on a successful
one. The target's hit point maximum is reduced by an amount equal to the
damage taken. This reduction lasts until the target finishes a long
rest. The target dies if this effect reduces its hit point maximum to 0.

\textbf{Etherealness.} The fiend magically enters the Ethereal Plane
from the Material Plane, or vice versa.

\end{document}
