% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-d}{%
\section{Monsters (D)}\label{monsters-d}}

\hypertarget{darkmantle}{%
\subsubsection{Darkmantle}\label{darkmantle}}

\emph{Small monstrosity, unaligned}

\textbf{Armor Class} 11

\textbf{Hit Points} 22 (5d6 + 5)

\textbf{Speed} 10 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 12 (+1) & 13 (+1) & 2 (-4) & 10 (+5) & 5 (-3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +3

\textbf{Senses} blindsight 60 ft., passive Perception 10

\textbf{Languages} ---

\textbf{Challenge} ½ (100 XP)

\textbf{Echolocation.} The darkmantle can't use its blindsight while
deafened.

\textbf{False Appearance.} While the darkmantle remains motionless, it
is indistinguishable from a cave formation such as a stalactite or
stalagmite.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Crush.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
creature. \emph{Hit:} 6 (1d6 + 3) bludgeoning damage, and the darkmantle
attaches to the target. If the target is Medium or smaller and the
darkmantle has advantage on the attack roll, it attaches by engulfing
the target's head, and the target is also blinded and unable to breathe
while the darkmantle is attached in this way.

While attached to the target, the darkmantle can attack no other
creature except the target but has advantage on its attack rolls. The
darkmantle's speed also becomes 0, it can't benefit from any bonus to
its speed, and it moves with the target.

A creature can detach the darkmantle by making a successful DC 13
Strength check as an action. On its turn, the darkmantle can detach
itself from the target by using 5 feet of movement.

\textbf{Darkness Aura (1/Day).} A 15-­‐foot radius of magical darkness
extends out from the darkmantle, moves with it, and spreads around
corners. The darkness lasts as long as the darkmantle maintains
concentration, up to 10 minutes (as if concentrating on a spell).
Darkvision can't penetrate this darkness, and no natural light can
illuminate it. If any of the darkness overlaps with an area of light
created by a spell of 2nd level or lower, the spell creating the light
is dispelled.

\hypertarget{demons}{%
\subsection{Demons}\label{demons}}

\hypertarget{balor}{%
\subsubsection{Balor}\label{balor}}

\emph{Huge fiend (demon), chaotic evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 262 (21d12 + 126)

\textbf{Speed} 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
26 (+8) & 15 (+2) & 22 (+6) & 20 (+5) & 16 (+3) & 22 (+6)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +14, Con +12, Wis +9, Cha +12

\textbf{Damage Resistances} cold, lightning; bludgeoning, piercing, and
slashing from nonmagical attacks

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 13

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 19 (22,000 XP)

\textbf{Death Throes.} When the balor dies, it explodes, and each
creature within 30 feet of it must make a DC 20 Dexterity saving throw,
taking 70 (20d6) fire damage on a failed save, or half as much damage on
a successful one. The explosion ignites flammable objects in that area
that aren't being worn or carried, and it destroys the balor's weapons.

\textbf{Fire Aura.} At the start of each of the balor's turns, each
creature within 5 feet of it takes 10 (3d6) fire damage, and flammable
objects in the aura that aren't being worn or carried ignite. A creature
that touches the balor or hits it with a melee attack while within 5
feet of it takes 10 (3d6) fire damage.

\textbf{Magic Resistance.} The balor has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The balor's weapon attacks are magical.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The balor makes two attacks: one with its
longsword and one with its whip.

\textbf{Longsword.} \emph{Melee Weapon Attack:} +14 to hit, reach 10
ft., one target. \emph{Hit:} 21 (3d8 + 8) slashing damage plus 13 (3d8)
lightning damage. If the balor scores a critical hit, it rolls damage
dice three times, instead of twice.

\textbf{Whip.} \emph{Melee Weapon Attack:} +14 to hit, reach 30 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage plus 10 (3d6) fire
damage, and the target must succeed on a DC 20 Strength saving throw or
be pulled up to 25 feet toward the balor.

\textbf{Teleport.} The balor magically teleports, along with any
equipment it is wearing or carrying, up to 120 feet to an unoccupied
space it can see.

\hypertarget{dretch}{%
\subsubsection{Dretch}\label{dretch}}

\emph{Small fiend (demon), chaotic evil}

\textbf{Armor Class} 11 (natural armor)

\textbf{Hit Points} 18 (4d6 + 4)

\textbf{Speed} 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 11 (+0) & 12 (+1) & 5 (−3) & 8 (−1) & 3 (−4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} cold, fire, lightning

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 9

\textbf{Languages} Abyssal, telepathy 60 ft. (works only with creatures
that understand Abyssal)

\textbf{Challenge} ¼ (50 XP)

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The dretch makes two attacks: one with its bite
and one with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
target. \emph{Hit:} 3 (1d6) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (2d4) slashing damage.

\textbf{Fetid Cloud (1/Day).} A 10-­‐foot radius of disgusting green gas
extends out from the dretch. The gas spreads around corners, and its
area is lightly obscured. It lasts for 1 minute or until a strong wind
disperses it. Any creature that starts its turn in that area must
succeed on a DC 11 Constitution saving throw or be poisoned until the
start of its next turn. While poisoned in this way, the target can take
either an action or a bonus action on its turn, not both, and can't take
actions.

\hypertarget{glabrezu}{%
\subsubsection{Glabrezu}\label{glabrezu}}

\emph{Large fiend (demon), chaotic evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 157 (15d10 + 75)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 15 (+2) & 21 (+5) & 19 (+4) & 17 (+3) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +9, Con +9, Wis +7, Cha +7

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 13

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 9 (5,000 XP)

\textbf{Innate Spellcasting} The glabrezu's spellcasting ability is
Intelligence (spell save DC 16). The glabrezu can innately cast the
following spells, requiring no material components:

At will: \emph{darkness}, \emph{detect magic}, \emph{dispel magic}

1/day each: \emph{confusion}, \emph{fly}, \emph{power word stun}

\textbf{Magic Resistance.} The glabrezu has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The glabrezu makes four attacks: two with its
pincers and two with its fists. Alternatively, it makes two attacks with
its pincers and casts one spell.

\textbf{Pincer.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft.,
one target. \emph{Hit:} 16 (2d10 + 5) bludgeoning damage. If the target
is a Medium or smaller creature, it is grappled (escape DC 15). The
glabrezu has two pincers, each of which can grapple only one target.

\textbf{Fist.} \emph{Melee Weapon Attack:} +9 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (2d4 + 2) bludgeoning damage.

\hypertarget{hezrou}{%
\subsubsection{Hezrou}\label{hezrou}}

\emph{Large fiend (demon), chaotic evil}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 136 (13d10 + 65)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 17 (+3) & 20 (+5) & 5 (−3) & 12 (+1) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +7, Con +8, Wis +4

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 8 (3,900 XP)

\textbf{Magic Resistance.} The hezrou has advantage on saving throws
against spells and other magical effects.

\textbf{Stench.} Any creature that starts its turn within 10 feet of the
hezrou must succeed on a DC 14 Constitution saving throw or be poisoned
until the start of its next turn. On a successful saving throw, the
creature is immune to the hezrou's stench for 24 hours.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Multiattack.} The hezrou makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\hypertarget{marilith}{%
\subsubsection{Marilith}\label{marilith}}

\emph{Large fiend (demon), chaotic evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 189 (18d10 + 90)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 20 (+5) & 20 (+5) & 18 (+4) & 16 (+3) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +9, Con +10, Wis +8, Cha +10

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 13

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 16 (15,000 XP)

\textbf{Magic Resistance.} The marilith has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The marilith's weapon attacks are magical.

\textbf{Reactive.} The marilith can take one reaction on every turn in a
combat.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Multiattack.} The marilith makes seven attacks: six with its
longswords and one with its tail.

\emph{\textbf{Longsword.}} \emph{Melee Weapon Attack:} +9 to hit, reach
5 ft., one target. \emph{Hit:} 13 (2d8 + 4) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft., one
creature. \emph{Hit:} 15 (2d10 + 4) bludgeoning damage. If the target is
Medium or smaller, it is grappled (escape DC 19). Until this grapple
ends, the target is restrained, the marilith can automatically hit the
target with its tail, and the marilith can't make tail attacks against
other targets.

\textbf{Teleport.} The marilith magically teleports, along with any
equipment it is wearing or carrying, up to 120 feet to an unoccupied
space it can see.

\hypertarget{reactions}{%
\paragraph{Reactions}\label{reactions}}

\textbf{Parry.} The marilith adds 5 to its AC against one melee attack
that would hit it. To do so, the marilith must see the attacker and be
wielding a melee weapon.

\hypertarget{nalfeshnee}{%
\subsubsection{Nalfeshnee}\label{nalfeshnee}}

\emph{Large fiend (demon), chaotic evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 184 (16d10 + 96)

\textbf{Speed} 20 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 10 (+0) & 22 (+6) & 19 (+4) & 12 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +11, Int +9, Wis +6, Cha +7

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 11

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 13 (10,000 XP)

\textbf{Magic Resistance.} The nalfeshnee has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Multiattack.} The nalfeshnee uses Horror Nimbus if it can. It
then makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 32 (5d10 + 5) piercing damage.

\emph{\textbf{Claw.}} \emph{Melee Weapon Attack:} +10 to hit, reach 10
ft., one target. \emph{Hit:} 15 (3d6 + 5) slashing damage.

\textbf{Horror Nimbus (Recharge 5--6).} The nalfeshnee magically emits
scintillating, multicolored light. Each creature within 15 feet of the
nalfeshnee that can see the light must succeed on a DC 15 Wisdom saving
throw or be frightened for 1 minute. A creature can repeat the saving
throw at the end of each of its turns, ending the effect on itself on a
success. If a creature's saving throw is successful or the effect ends
for it, the creature is immune to the nalfeshnee's Horror Nimbus for the
next 24 hours.

\textbf{Teleport.} The nalfeshnee magically teleports, along with any
equipment it is wearing or carrying, up to 120 feet to an unoccupied
space it can see.

\hypertarget{quasit}{%
\subsubsection{Quasit}\label{quasit}}

\emph{Tiny fiend (demon, shapechanger), chaotic evil}

\textbf{Armor Class} 13

\textbf{Hit Points} 7 (3d4)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
5 (−3) & 17 (+3) & 10 (+0) & 7 (−2) & 10 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +5

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} Abyssal, Common

\textbf{Challenge} 1 (200 XP)

\textbf{Shapechanger.} The quasit can use its action to polymorph into a
beast form that resembles a bat (Speed 10 ft. fly 40 ft.), a centipede
(40 ft., climb 40 ft.), or a toad (40 ft., swim 40 ft.), or back into
its true form. Its statistics are the same in each form, except for the
Speed changes noted. Any equipment it is wearing or carrying isn't
transformed. It reverts to its true form if it dies.

\textbf{Magic Resistance.} The quasit has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Claws (Bite in Beast Form).} \emph{Melee Weapon Attack:} +4 to
hit, reach 5 ft., one target. \emph{Hit:} 5 (1d4 + 3) piercing damage,
and the target must succeed on a DC 10 Constitution saving throw or take
5 (2d4) poison damage and become poisoned for 1 minute. The target can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\textbf{Scare (1/Day).} One creature of the quasit's choice within 20
feet of it must succeed on a DC 10 Wisdom saving throw or be frightened
for 1 minute. The target can repeat the saving throw at the end of each
of its turns, with disadvantage if the quasit is within line of sight,
ending the effect on itself on a success.

\textbf{Invisibility.} The quasit magically turns invisible until it
attacks or uses Scare, or until its concentration ends (as if
concentrating on a spell). Any equipment the quasit wears or carries is
invisible with it.

\hypertarget{vrock}{%
\subsubsection{Vrock}\label{vrock}}

\emph{Large fiend (demon), chaotic evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 104 (11d10 + 44)

\textbf{Speed} 40 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 15 (+2) & 18 (+4) & 8 (−1) & 13 (+1) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Wis +4, Cha +2

\textbf{Damage Resistances} cold, fire, lightning; bludgeoning,
piercing, and slashing from nonmagical attacks

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Abyssal, telepathy 120 ft.

\textbf{Challenge} 6 (2,300 XP)

\textbf{Magic Resistance.} The vrock has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Multiattack.} The vrock makes two attacks: one with its beak and
one with its talons.

\textbf{Beak.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) piercing damage.

\textbf{Talons} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d10 + 3) slashing damage.

\textbf{Spores (Recharge 6).} A 15-­‐foot-­‐radius cloud of toxic spores
extends out from the vrock. The spores spread around corners. Each
creature in that area must succeed on a DC 14 Constitution saving throw
or become poisoned. While poisoned in this way, a target takes 5 (1d10)
poison damage at the start of each of its turns. A target can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success. Emptying a vial of holy water on the target also
ends the effect on it.

\textbf{Stunning Screech (1/Day).} The vrock emits a horrific screech.
Each creature within 20 feet of it that can hear it and that isn't a
demon must succeed on a DC 14 Constitution saving throw or be stunned
until the end of the vrock's next turn.

\hypertarget{devils}{%
\subsection{Devils}\label{devils}}

\hypertarget{barbed-devil}{%
\subsubsection{Barbed Devil}\label{barbed-devil}}

\emph{Medium fiend (devil), lawful evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 110 (13d8 + 52)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 17 (+3) & 18 (+4) & 12 (+1) & 14 (+2) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +6, Con +7, Wis +5, Cha +5

\textbf{Skills} Deception +5, Insight +5, Perception +8

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 18

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 5 (1,800 XP)

\textbf{Barbed Hide.} At the start of each of its turns, the barbed
devil deals 5 (1d10) piercing damage to any creature grappling it.

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-9}{%
\paragraph{Actions}\label{actions-9}}

\textbf{Multiattack.} The devil makes three melee attacks: one with its
tail and two with its claws. Alternatively, it can use Hurl Flame twice.

\textbf{Claw.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 6 (1d6 + 3) piercing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) piercing damage.

\textbf{Hurl Flame.} Ranged Spell Attack: +5 to hit, range 150 ft., one
target. \emph{Hit:} 10 (3d6) fire damage. If the target is a flammable
object that isn't being worn or carried, it also catches fire.

\hypertarget{bearded-devil}{%
\subsubsection{Bearded Devil}\label{bearded-devil}}

\emph{Medium fiend (devil), lawful evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 52 (8d8 + 16)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 15 (+2) & 15 (+2) & 9 (-1) & 11 (0) & 11 (0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +5, Con +4, Wis +2

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 3 (700 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\textbf{Steadfast.} The devil can't be frightened while it can see an
allied creature within 30 feet of it.

\hypertarget{actions-10}{%
\paragraph{Actions}\label{actions-10}}

\textbf{Multiattack.} The devil makes two attacks: one with its beard
and one with its glaive.

\textbf{Beard.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
creature. \emph{Hit:} 6 (1d8 + 2) piercing damage, and the target must
succeed on a DC 12 Constitution saving throw or be poisoned for 1
minute. While poisoned in this way, the target can't regain hit points.
The target can repeat the saving throw at the end of each of its turns,
ending the effect on itself on a success.

\textbf{Glaive.} \emph{Melee Weapon Attack:} +5 to hit, reach 10 ft.,
one target. \emph{Hit:} 8 (1d10 + 3) slashing damage. If the target is a
creature other than an undead or a construct, it must succeed on a DC 12
Constitution saving throw or lose 5 (1d10) hit points at the start of
each of its turns due to an infernal wound. Each time the devil hits the
wounded target with this attack, the damage dealt by the wound increases
by 5 (1d10). Any creature can take an action to stanch the wound with a
successful DC 12 Wisdom (Medicine) check. The wound also closes if the
target receives magical healing.

\hypertarget{bone-devil}{%
\subsubsection{Bone Devil}\label{bone-devil}}

\emph{Large fiend (devil), lawful evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 142 (15d10 + 60)

\textbf{Speed} 40 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 16 (+3) & 18 (+4) & 13 (+1) & 14 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Int +5, Wis +6, Cha +7

\textbf{Skills} Deception +7, Insight +6

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 12

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 9 (5,000 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-11}{%
\paragraph{Actions}\label{actions-11}}

\textbf{Multiattack.} The devil makes three attacks: two with its claws
and one with its sting.

\textbf{Claw.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 8 (1d8 + 4) slashing damage.

\textbf{Sting.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 13 (2d8 + 4) piercing damage plus 17 (5d6) poison
damage, and the target must succeed on a DC 14 Constitution saving throw
or become poisoned for 1 minute. The target can repeat the saving throw
at the end of each of its turns, ending the effect on itself on a
success.

\hypertarget{chain-devil}{%
\subsubsection{Chain Devil}\label{chain-devil}}

\emph{Medium fiend (devil), lawful evil}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 85 (10d8 + 40)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 18 (+4) & 11 (0) & 12 (+1) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +7, Wis +4, Cha +5

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 8 (3,900 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-12}{%
\paragraph{Actions}\label{actions-12}}

\textbf{Multiattack.} The devil makes two attacks with its chains.

\textbf{Chain.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage. The target is grappled
(escape DC 14) if the devil isn't already grappling a creature. Until
this grapple ends, the target is restrained and takes 7 (2d6) piercing
damage at the start of each of its turns.

\textbf{Animate Chains (Recharges after a Short or Long Rest).} Up to
four chains the devil can see within 60 feet of it magically sprout
razor-­‐edged barbs and animate under the devil's control, provided that
the chains aren't being worn or carried.

Each animated chain is an object with AC 20, 20 hit points, resistance
to piercing damage, and immunity to psychic and thunder damage. When the
devil uses Multiattack on its turn, it can use each animated chain to
make one additional chain attack. An animated chain can grapple one
creature of its own but can't make attacks while grappling. An animated
chain reverts to its inanimate state if reduced to 0 hit points or if
the devil is incapacitated or dies.

\hypertarget{reactions-1}{%
\paragraph{Reactions}\label{reactions-1}}

\textbf{Unnerving Mask.} When a creature the devil can see starts its
turn within 30 feet of the devil, the devil can create the illusion that
it looks like one of the creature's departed loved ones or bitter
enemies. If the creature can see the devil, it must succeed on a DC 14
Wisdom saving throw or be frightened until the end of its turn.

\hypertarget{erinyes}{%
\subsubsection{Erinyes}\label{erinyes}}

\emph{Medium fiend (devil), lawful evil}

\textbf{Armor Class} 18 (plate)

\textbf{Hit Points} 153 (18d8 + 72)

\textbf{Speed} 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 16 (+3) & 18 (+4) & 14 (+2) & 14 (+2) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +8, Wis +6, Cha +8

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 12

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 12 (8,400 XP)

\textbf{Hellish Weapons.} The erinyes's weapon attacks are magical and
deal an extra 13 (3d8) poison damage on a hit (included in the attacks).

\textbf{Magic Resistance.} The erinyes has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-13}{%
\paragraph{Actions}\label{actions-13}}

\textbf{Multiattack.} The erinyes makes three attacks.

\textbf{Longsword.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft.,
one target. \emph{Hit:} 8 (1d8 + 4) slashing damage, or 9 (1d10 + 4)
slashing damage if used with two hands, plus 13 (3d8) poison damage.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +7 to hit, range 150/600
ft., one target. \emph{Hit:} 7 (1d8 + 3) piercing damage plus 13 (3d8)
poison damage, and the target must succeed on a DC 14 Constitution
saving throw or be poisoned. The poison lasts until it is removed by the
\emph{lesser restoration} spell or similar magic.

\hypertarget{reactions-2}{%
\paragraph{Reactions}\label{reactions-2}}

\textbf{Parry.} The erinyes adds 4 to its AC against one melee attack
that would hit it. To do so, the erinyes must see the attacker and be
wielding a melee weapon.

\hypertarget{horned-devil}{%
\subsubsection{Horned Devil}\label{horned-devil}}

\emph{Large fiend (devil), lawful evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 178 (17d10 + 85)

\textbf{Speed} 20 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 17 (+3) & 21 (+5) & 12 (+1) & 16 (+3) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +10, Dex +7, Wis +7, Cha +7

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks not made with silvered weapons

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 13

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 11 (7,200 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-14}{%
\paragraph{Actions}\label{actions-14}}

\textbf{Multiattack.} The devil makes three melee attacks: two with its
fork and one with its tail. It can use Hurl Flame in place of any melee
attack.

\textbf{Fork.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d8 + 6) piercing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 10 (1d8 + 6) piercing damage. If the target is a
creature other than an undead or a construct, it must succeed on a DC 17
Constitution saving throw or lose 10 (3d6) hit points at the start of
each of its turns due to an infernal wound. Each time the devil hits the
wounded target with this attack, the damage dealt by the wound increases
by 10 (3d6). Any creature can take an action to stanch the wound with a
successful DC 12 Wisdom (Medicine) check. The wound also closes if the
target receives magical healing.

\textbf{Hurl Flame.} Ranged Spell Attack: +7 to hit, range 150 ft., one
target. \emph{Hit:} 14 (4d6) fire damage. If the target is a flammable
object that isn't being worn or carried, it also catches fire.

\hypertarget{ice-devil}{%
\subsubsection{Ice Devil}\label{ice-devil}}

\emph{Large fiend (devil), lawful evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 180 (19d10 + 76)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 14 (+2) & 18 (+4) & 18 (+4) & 15 (+2) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +9, Wis +7, Cha +9

\textbf{Damage Resistances} bludgeoning, piercing, and slashing from
nonmagical attacks that aren't silvered

\textbf{Damage Immunities} cold, fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 12

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 14 (11,500 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the devil's
darkvision.

\textbf{Magic Resistance.} The devil has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-15}{%
\paragraph{Actions}\label{actions-15}}

\textbf{Multiattack.} The devil makes three attacks: one with its bite,
one with its claws, and one with its tail.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 12 (2d6 + 5) piercing damage plus 10 (3d6) cold
damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d4 + 5) slashing damage plus 10 (3d6) cold
damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 12 (2d6 + 5) bludgeoning damage plus 10 (3d6) cold
damage.

\textbf{Wall of Ice (Recharge 6).} The devil magically forms an opaque
wall of ice on a solid surface it can see within 60 feet of it. The wall
is 1 foot thick and up to 30 feet long and 10 feet high, or it's a
hemispherical dome up to 20 feet in diameter.

When the wall appears, each creature in its space is pushed out of it by
the shortest route. The creature chooses which side of the wall to end
up on, unless the creature is incapacitated. The creature then makes a
DC 17 Dexterity saving throw, taking 35 (10d6) cold damage on a failed
save, or half as much damage on a successful one.

The wall lasts for 1 minute or until the devil is incapacitated or dies.
The wall can be damaged and breached; each 10-­‐foot section has AC 5,
30 hit points, vulnerability to fire damage, and immunity to acid, cold,
necrotic, poison, and psychic damage. If a section is destroyed, it
leaves behind a sheet of frigid air in the space the wall occupied.
Whenever a creature finishes moving through the frigid air on a turn,
willingly or otherwise, the creature must make a DC 17 Constitution
saving throw, taking 17 (5d6) cold damage on a failed save, or half as
much damage on a successful one. The frigid air dissipates when the rest
of the wall vanishes.

\hypertarget{imp}{%
\subsubsection{Imp}\label{imp}}

\emph{Tiny fiend (devil, shapechanger), lawful evil}

\textbf{Armor Class} 13

\textbf{Hit Points} 10 (3d4 + 3)

\textbf{Speed} 20 ft., fly 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
6 (-2) & 17 (+3) & 13 (+1) & 11 (0) & 12 (+1) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +4, Insight +3, Persuasion +4, Stealth +5

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Infernal, Common

\textbf{Challenge} 1 (200 XP)

\textbf{Shapechanger.} The imp can use its action to polymorph into a
beast form that resembles a rat (Speed 20 ft.), a raven (20 ft., fly 60
ft.), or a spider (20 ft., climb 20 ft.), or back into its true form.
Its statistics are the same in each form, except for the Speed changes
noted. Any equipment it is wearing or carrying isn't transformed. It
reverts to its true form if it dies.

\textbf{Devil's Sight.} Magical darkness doesn't impede the imp's
darkvision.

\textbf{Magic Resistance.} The imp has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-16}{%
\paragraph{Actions}\label{actions-16}}

\textbf{Sting (Bite in Beast Form).} \emph{Melee Weapon Attack:} +5 to
hit, reach 5 ft., one target. \emph{Hit:} 5 (1d4 + 3) piercing damage,
and the target must make on a DC 11 Constitution saving throw, taking 10
(3d6) poison damage on a failed save, or half as much damage on a
successful one.

\textbf{Invisibility.} The imp magically turns invisible until it
attacks or until its concentration ends (as if concentrating on a
spell). Any equipment the imp wears or carries is invisible with it.

\hypertarget{lemure}{%
\subsubsection{Lemure}\label{lemure}}

\emph{Medium fiend (devil), lawful evil}

\textbf{Armor Class} 7

\textbf{Hit Points} 13 (3d8)

\textbf{Speed} 15 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 5 (-3) & 11 (+0) & 1 (-5) & 11 (+0) & 3 (-4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} cold

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} charmed, frightened, poisoned

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} understands Infernal but can't speak

\textbf{Challenge} 0 (10 XP)

\textbf{Devil's Sight.} Magical darkness doesn't impede the lemure's
darkvision.

\textbf{Hellish Rejuvenation} A lemure that dies in the Nine Hells comes
back to life with all its hit points in 1d10 days unless it is killed by
a good-­‐aligned creature with a \emph{bless} spell cast on that
creature or its remains are sprinkled with holy water.

\hypertarget{actions-17}{%
\paragraph{Actions}\label{actions-17}}

\textbf{Fist.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 2 (1d4) bludgeoning damage.

\hypertarget{pit-fiend}{%
\subsubsection{Pit Fiend}\label{pit-fiend}}

\emph{Large fiend (devil), lawful evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 300 (24d10 + 168)

\textbf{Speed} 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
26 (+8) & 14 (+2) & 24 (+7) & 22 (+6) & 18 (+4) & 24 (+7)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +8, Con +13, Wis +10

\textbf{Damage Resistances} cold; bludgeoning, piercing, and slashing
from nonmagical attacks that aren't silvered

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} truesight 120 ft., passive Perception 14

\textbf{Languages} Infernal, telepathy 120 ft.

\textbf{Challenge} 20 (25,000 XP)

\textbf{Fear Aura.} Any creature hostile to the pit fiend that starts
its turn within 20 feet of the pit fiend must make a DC 21 Wisdom saving
throw, unless the pit fiend is incapacitated. On a failed save, the
creature is frightened until the start of its next turn. If a creature's
saving throw is successful, the creature is immune to the pit fiend's
Fear Aura for the next 24 hours.

\textbf{Magic Resistance.} The pit fiend has advantage on saving throws
against spells and other magical effects.

\textbf{Magic Weapons.} The pit fiend's weapon attacks are magical.

\textbf{Innate Spellcasting} The pit fiend's spellcasting ability is
Charisma (spell save DC 21). The pit fiend can innately cast the
following spells, requiring no material components:

At will: \emph{detect magic}, \emph{fireball}

3/day each: \emph{hold monster}, \emph{wall of fire}

\hypertarget{actions-18}{%
\paragraph{Actions}\label{actions-18}}

\textbf{Multiattack.} The pit fiend makes four attacks: one with its
bite, one with its claw, one with its mace, and one with its tail.

\textbf{Bite.} \emph{Melee Weapon Attack:} +14 to hit, reach 5 ft., one
target. \emph{Hit:} 22 (4d6 + 8) piercing damage. The target must
succeed on a DC 21 Constitution saving throw or become poisoned. While
poisoned in this way, the target can't regain hit points, and it takes
21 (6d6) poison damage at the start of each of its turns. The poisoned
target can repeat the saving throw at the end of each of its turns,
ending the effect on itself on a success.

\textbf{Claw.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d8 + 8) slashing damage.

\textbf{Mace.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d6 + 8) bludgeoning damage plus 21 (6d6) fire
damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 24 (3d10 + 8) bludgeoning damage.

\hypertarget{dinosaurs}{%
\subsection{Dinosaurs}\label{dinosaurs}}

\hypertarget{plesiosaurus}{%
\subsubsection{Plesiosaurus}\label{plesiosaurus}}

\emph{Large beast, unaligned}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 68 (8d10 + 24)

\textbf{Speed} 20 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 2 (−4) & 12 (+1) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3, Stealth +4

\textbf{Senses} passive Perception 13

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Hold Breath.} The plesiosaurus can hold its breath for 1 hour.

\hypertarget{actions-19}{%
\paragraph{Actions}\label{actions-19}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 10 ft., one
target. \emph{Hit:} 14 (3d6 + 4) piercing damage.

\hypertarget{triceratops}{%
\subsubsection{Triceratops}\label{triceratops}}

\emph{Huge beast, unaligned}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 95 (10d12 + 30)

\textbf{Speed} 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 9 (-1) & 17 (+3) & 2 (−4) & 11 (+0) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} ---

\textbf{Challenge} 5 (1,800 XP)

\textbf{Trampling Charge} If the triceratops moves at least 20 feet
straight toward a creature and then hits it with a gore attack on the
same turn, that target must succeed on a DC 13 Strength saving throw or
be knocked prone.

If the target is prone, the triceratops can make one stomp attack
against it as a bonus action.

\hypertarget{actions-20}{%
\paragraph{Actions}\label{actions-20}}

\textbf{Gore.} \emph{Melee Weapon Attack:} +9 to hit, reach 5 ft., one
target. \emph{Hit:} 24 (4d8 + 6) piercing damage.

\textbf{Stomp.} \emph{Melee Weapon Attack:} +9 to hit, reach 5 ft., one
prone creature. \emph{Hit:} 22 (3d10 + 6) bludgeoning damage.

\hypertarget{tyrannosaurus-rex}{%
\subsubsection{Tyrannosaurus Rex}\label{tyrannosaurus-rex}}

\emph{Huge beast, unaligned}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 136 (13d12 + 52)

\textbf{Speed} 50 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
25 (+7) & 10 (+0) & 19 (+4) & 2 (−4) & 12 (+1) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4

\textbf{Senses} passive Perception 14

\textbf{Languages} ---

\textbf{Challenge} 8 (3,900 XP)

\hypertarget{actions-21}{%
\paragraph{Actions}\label{actions-21}}

\textbf{Multiattack.} The tyrannosaurus makes two attacks: one with its
bite and one with its tail. It can't make both attacks against the same
target.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 33 (4d12 + 7) piercing damage. If the target is a
Medium or smaller creature, it is grappled (escape DC 17). Until this
grapple ends, the target is restrained, and the tyrannosaurus can't bite
another target.

\textbf{Tail.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 20 (3d8 + 7) bludgeoning damage.

\hypertarget{doppelganger}{%
\subsubsection{Doppelganger}\label{doppelganger}}

\emph{Medium monstrosity (shapechanger), neutral}

\textbf{Armor Class} 14

\textbf{Hit Points} 52 (8d8 + 16)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 18 (+4) & 14 (+2) & 11 (+0) & 12 (+1) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +6, Insight +3

\textbf{Condition Immunities} charmed

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} Common

\textbf{Challenge} 3 (700 XP)

\textbf{Shapechanger.} The doppelganger can use its action to polymorph
into a Small or Medium humanoid it has seen, or back into its true form.
Its statistics, other than its size, are the same in each form. Any
equipment it is wearing or carrying isn't transformed. It reverts to its
true form if it dies.

\textbf{Ambusher.} In the first round of a combat, the doppelganger has
advantage on attack rolls against any creature it has surprised.

\textbf{Surprise Attack.} If the doppelganger surprises a creature and
hits it with an attack during the first round of combat, the target
takes an extra 10 (3d6) damage from the attack.

\hypertarget{actions-22}{%
\paragraph{Actions}\label{actions-22}}

\textbf{Multiattack.} The doppelganger makes two melee attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d6 + 4) bludgeoning damage.

\textbf{Read Thoughts.} The doppelganger magically reads the surface
thoughts of one creature within 60 feet of it. The effect can penetrate
barriers, but 3 feet of wood or dirt, 2 feet of stone, 2 inches of
metal, or a thin sheet of lead blocks it. While the target is in range,
the doppelganger can continue reading its thoughts, as long as the
doppelganger's concentration isn't broken (as if concentrating on a
spell). While reading the target's mind, the doppelganger has advantage
on Wisdom (Insight) and Charisma (Deception, Intimidation, and
Persuasion) checks against the target.

\hypertarget{dragons-chromatic}{%
\subsection{Dragons, Chromatic}\label{dragons-chromatic}}

\hypertarget{black-dragon}{%
\subsubsection{Black Dragon}\label{black-dragon}}

\hypertarget{ancient-black-dragon}{%
\subsubsection{Ancient Black Dragon}\label{ancient-black-dragon}}

\emph{Gargantuan dragon, chaotic evil}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 367 (21d20 + 147)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 14 (+2) & 25 (+7) & 16 (+3) & 15 (+2) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +9, Con +14, Wis +9, Cha +11

\textbf{Skills} Perception +16, Stealth +9

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 26

\textbf{Languages} Common, Draconic

\textbf{Challenge} 21 (33,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-23}{%
\paragraph{Actions}\label{actions-23}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +15 to hit, reach 15 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage plus 9 (2d8) acid
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +15 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +15 to hit, reach 20 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 19
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Acid Breath (Recharge 5--6).} The dragon exhales acid in a
90-­‐foot line that is 10 feet wide. Each creature in that line must
make a DC 22 Dexterity saving throw, taking 67 (15d8) acid damage on a
failed save, or half as much damage on a successful one.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 23 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-black-dragon}{%
\subsubsection{Adult Black Dragon}\label{adult-black-dragon}}

\emph{Huge dragon, chaotic evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 195 (17d12 + 85)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 14 (+2) & 21 (+5) & 14 (+2) & 13 (+1) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +10, Wis +6, Cha +8

\textbf{Skills} Perception +11, Stealth +7

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 21

\textbf{Languages} Common, Draconic

\textbf{Challenge} 14 (11,500 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-24}{%
\paragraph{Actions}\label{actions-24}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage plus 4 (1d8) acid
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +11 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +11 to hit, reach 15 ft., one
target. \emph{Hit:} 15 (2d8 + 6) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 16
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Acid Breath (Recharge 5--6).} The dragon exhales acid in a
60-­‐foot line that is 5 feet wide. Each creature in that line must make
a DC 18 Dexterity saving throw, taking 54 (12d8) acid damage on a failed
save, or half as much damage on a successful one.

\hypertarget{legendary-actions-1}{%
\paragraph{Legendary Actions}\label{legendary-actions-1}}

\emph{The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.}

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 19 Dexterity
saving throw or take 13 (2d6 + 6) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-black-dragon}{%
\paragraph{Young Black Dragon}\label{young-black-dragon}}

\emph{Large dragon, chaotic evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 127 (15d10 + 45)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 14 (+2) & 17 (+3) & 12 (+1) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +6, Wis +3, Cha +5

\textbf{Skills} Perception +6, Stealth +5

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 16

\textbf{Languages} Common, Draconic

\textbf{Challenge} 7 (2,900 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-25}{%
\paragraph{Actions}\label{actions-25}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage plus 4 (1d8) acid
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\textbf{Acid Breath (Recharge 5--6).} The dragon exhales acid in a
30-­‐foot line that is 5 feet wide. Each creature in that line must make
a DC 14 Dexterity saving throw, taking 49 (11d8) acid damage on a failed
save, or half as much damage on a successful one.

\hypertarget{black-dragon-wyrmling}{%
\subsubsection{Black Dragon Wyrmling}\label{black-dragon-wyrmling}}

\emph{Medium dragon, chaotic evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 33 (6d8 + 6)

\textbf{Speed} 30 ft., fly 60 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 14 (+2) & 13 (+1) & 10 (+0) & 11 (+0) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +3, Wis +2, Cha +3

\textbf{Skills} Perception +4, Stealth +4

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 2 (450 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-26}{%
\paragraph{Actions}\label{actions-26}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d10 + 2) piercing damage plus 2 (1d4) acid
damage.

\textbf{Acid Breath (Recharge 5--6).} The dragon exhales acid in a
15-­‐foot line that is 5 feet wide. Each creature in that line must make
a DC 11 Dexterity saving throw, taking 22 (5d8) acid damage on a failed
save, or half as much damage on a successful one.

\hypertarget{blue-dragon}{%
\subsubsection{Blue Dragon}\label{blue-dragon}}

\hypertarget{ancient-blue-dragon}{%
\subsubsection{Ancient Blue Dragon}\label{ancient-blue-dragon}}

\emph{Gargantuan dragon, lawful evil}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 481 (26d20 + 208)

\textbf{Speed} 40 ft., burrow 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
29 (+9) & 10 (+0) & 27 (+8) & 18 (+4) & 17 (+3) & 21 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +15, Wis +10, Cha +12

\textbf{Skills} Perception +17, Stealth +7

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 27

\textbf{Languages} Common, Draconic

\textbf{Challenge} 23 (50,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-27}{%
\paragraph{Actions}\label{actions-27}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +16 to hit, reach 15 ft., one
target. \emph{Hit:} 20 (2d10 + 9) piercing damage plus 11 (2d10)
lightning damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +16 to hit, reach 10 ft., one
target. \emph{Hit:} 16 (2d6 + 9) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +16 to hit, reach 20 ft., one
target. \emph{Hit:} 18 (2d8 + 9) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 20
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Lightning Breath (Recharge 5--6).} The dragon exhales lightning
in a 120-­‐foot line that is 10 feet wide. Each creature in that line
must make a DC 23 Dexterity saving throw, taking 88 (16d10) lightning
damage on a failed save, or half as much damage on a successful one.

\hypertarget{legendary-actions-2}{%
\paragraph{Legendary Actions}\label{legendary-actions-2}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 24 Dexterity
saving throw or take 16 (2d6 + 9) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-blue-dragon}{%
\subsubsection{Adult Blue Dragon}\label{adult-blue-dragon}}

\emph{Huge dragon, lawful evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 225 (18d12 + 108)

\textbf{Speed} 40 ft., burrow 30 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
25 (+7) & 10 (+0) & 23 (+6) & 16 (+3) & 15 (+2) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +11, Wis +7, Cha +9

\textbf{Skills} Perception +12, Stealth +5

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 22

\textbf{Languages} Common, Draconic

\textbf{Challenge} 16 (15,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-28}{%
\paragraph{Actions}\label{actions-28}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +12 to hit, reach 10 ft., one
target. \emph{Hit:} 18 (2d10 + 7) piercing damage plus 5 (1d10)
lightning damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +12 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d6 + 7) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +12 to hit, reach 15 ft., one
target. \emph{Hit:} 16 (2d8 + 7) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 17
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Lightning Breath (Recharge 5--6).} The dragon exhales lightning
in a 90-­‐foot line that is 5 feet wide. Each creature in that line must
make a DC 19 Dexterity saving throw, taking 66 (12d10) lightning damage
on a failed save, or half as much damage on a successful one.

\hypertarget{legendary-actions-3}{%
\paragraph{Legendary Actions}\label{legendary-actions-3}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 20 Dexterity
saving throw or take 14 (2d6 + 7) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-blue-dragon}{%
\subsubsection{Young Blue Dragon}\label{young-blue-dragon}}

\emph{Large dragon, lawful evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 152 (16d10 + 64)

\textbf{Speed} 40 ft., burrow 20 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 10 (+0) & 19 (+4) & 14 (+2) & 13 (+1) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +8, Wis +5, Cha +7

\textbf{Skills} Perception +9, Stealth +4

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 19

\textbf{Languages} Common, Draconic

\textbf{Challenge} 9 (5,000 XP)

\hypertarget{actions-29}{%
\paragraph{Actions}\label{actions-29}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft., one
target. \emph{Hit:} 16 (2d10 + 5) piercing damage plus 5 (1d10)
lightning damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +9 to hit, reach 5 ft., one
target. \emph{Hit:} 12 (2d6 + 5) slashing damage.

\textbf{Lightning Breath (Recharge 5--6).} The dragon exhales lightning
in an 60-­‐foot line that is 5 feet wide. Each creature in that line
must make a DC 16 Dexterity saving throw, taking 55 (10d10) lightning
damage on a failed save, or half as much damage on a successful one.

\hypertarget{blue-dragon-wyrmling}{%
\subsubsection{Blue Dragon Wyrmling}\label{blue-dragon-wyrmling}}

\emph{Medium dragon, lawful evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 52 (8d8 + 16)

\textbf{Speed} 30 ft., burrow 15 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 10 (+0) & 15 (+2) & 12 (+1) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +2, Con +4, Wis +2, Cha +4

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 3 (700 XP)

\hypertarget{actions-30}{%
\paragraph{Actions}\label{actions-30}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d10 + 3) piercing damage plus 3 (1d6) lightning
damage.

\textbf{Lightning Breath (Recharge 5--6).} The dragon exhales lightning
in a 30-­‐foot line that is 5 feet wide. Each creature in that line must
make a DC 12 Dexterity saving throw, taking 22 (4d10) lightning damage
on a failed save, or half as much damage on a successful one.

\hypertarget{green-dragon}{%
\subsubsection{Green Dragon}\label{green-dragon}}

\hypertarget{ancient-green-dragon}{%
\subsubsection{Ancient Green Dragon}\label{ancient-green-dragon}}

\emph{Gargantuan dragon, lawful evil}

\textbf{Armor Class} 21 (natural armor)

\textbf{Hit Points} 385 (22d20 + 154)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 12 (+1) & 25 (+7) & 20 (+5) & 17 (+3) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +8, Con +14, Wis +10, Cha +11

\textbf{Skills} Deception +11, Insight +10, Perception +17, Persuasion
+11, Stealth +8

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 27

\textbf{Languages} Common, Draconic

\textbf{Challenge} 22 (41,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-31}{%
\paragraph{Actions}\label{actions-31}}

\textbf{Multiattack.} The dragon can use its Frightful Presence It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +15 to hit, reach 15 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage plus 10 (3d6) poison
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +15 to hit, reach 10 ft., one
target. \emph{Hit:} 22 (4d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +15 to hit, reach 20 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 19
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Poison Breath (Recharge 5--6).} The dragon exhales poisonous gas
in a 90-­‐foot cone. Each creature in that area must make a DC 22
Constitution saving throw, taking 77 (22d6) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{legendary-actions-4}{%
\paragraph{Legendary Actions}\label{legendary-actions-4}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 23 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-green-dragon}{%
\subsubsection{Adult Green Dragon}\label{adult-green-dragon}}

\emph{Huge dragon, lawful evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 207 (18d12 + 90)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 12 (+1) & 21 (+5) & 18 (+4) & 15 (+2) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +10, Wis +7, Cha +8

\textbf{Skills} Deception +8, Insight +7, Perception +12, Persuasion +8,
Stealth +6

\textbf{Damage Immunities} poison *

\emph{Condition Immunities}* poisoned

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 22

\textbf{Languages} Common, Draconic

\textbf{Challenge} 15 (13,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-32}{%
\paragraph{Actions}\label{actions-32}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage plus 7 (2d6) poison
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +11 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +11 to hit, reach 15 ft., one
target. \emph{Hit:} 15 (2d8 + 6) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 16
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Poison Breath (Recharge 5--6).} The dragon exhales poisonous gas
in a 60-­‐foot cone. Each creature in that area must make a DC 18
Constitution saving throw, taking 56 (16d6) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{legendary-actions-5}{%
\paragraph{Legendary Actions}\label{legendary-actions-5}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 19 Dexterity
saving throw or take 13 (2d6 + 6) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-green-dragon}{%
\subsubsection{Young Green Dragon}\label{young-green-dragon}}

\emph{Large dragon, lawful evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 136 (16d10 + 48)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 12 (+1) & 17 (+3) & 16 (+3) & 13 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +6, Wis +4, Cha +5

\textbf{Skills} Deception +5, Perception +7, Stealth +4

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 17

\textbf{Languages} Common, Draconic

\textbf{Challenge} 8 (3,900 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-33}{%
\paragraph{Actions}\label{actions-33}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage plus 7 (2d6) poison
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\textbf{Poison Breath (Recharge 5--6).} The dragon exhales poisonous gas
in a 30-­‐foot cone. Each creature in that area must make a DC 14
Constitution saving throw, taking 42 (12d6) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{green-dragon-wyrmling}{%
\subsubsection{Green Dragon Wyrmling}\label{green-dragon-wyrmling}}

\emph{Medium dragon, lawful evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 38 (7d8 + 7)

\textbf{Speed} 30 ft., fly 60 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 12 (+1) & 13 (+1) & 14 (+2) & 11 (+0) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +3, Wis +2, Cha +3

\textbf{Skills} Perception +4, Stealth +3

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 2 (450 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-34}{%
\paragraph{Actions}\label{actions-34}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d10 + 2) piercing damage plus 3 (1d6) poison
damage.

\textbf{Poison Breath (Recharge 5--6).} The dragon exhales poisonous gas
in a 15-­‐foot cone. Each creature in that area must make a DC 11
Constitution saving throw, taking 21 (6d6) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{red-dragon}{%
\subsubsection{Red Dragon}\label{red-dragon}}

\hypertarget{ancient-red-dragon}{%
\subsubsection{Ancient Red Dragon}\label{ancient-red-dragon}}

\emph{Gargantuan dragon, chaotic evil}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 546 (28d20 + 252)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
30 (+10) & 10 (+0) & 29 (+9) & 18 (+4) & 15 (+2) & 23
(+6)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +16, Wis +9, Cha +13

\textbf{Skills} Perception +16, Stealth +7

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 26

\textbf{Languages} Common, Draconic

\textbf{Challenge} 24 (62,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-35}{%
\paragraph{Actions}\label{actions-35}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +17 to hit, reach 15 ft., one
target. \emph{Hit:} 21 (2d10 + 10) piercing damage plus 14 (4d6) fire
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +17 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d6 + 10) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +17 to hit, reach 20 ft., one
target. \emph{Hit:} 19 (2d8 + 10) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 21
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Fire Breath (Recharge 5--6).} The dragon exhales fire in a
90-­‐foot cone. Each creature in that area must make a DC 24 Dexterity
saving throw, taking 91 (26d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{legendary-actions-6}{%
\paragraph{Legendary Actions}\label{legendary-actions-6}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 25 Dexterity
saving throw or take 17 (2d6 + 10) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-red-dragon}{%
\subsubsection{Adult Red Dragon}\label{adult-red-dragon}}

\emph{Huge dragon, chaotic evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 256 (19d12 + 133)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 10 (+0) & 25 (+7) & 16 (+3) & 13 (+1) & 21 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +13, Wis +7, Cha +11

\textbf{Skills} Perception +13, Stealth +6

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 23

\textbf{Languages} Common, Draconic

\textbf{Challenge} 17 (18,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-36}{%
\paragraph{Actions}\label{actions-36}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage plus 7 (2d6) fire
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +14 to hit, reach 5 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +14 to hit, reach 15 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 19
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Fire Breath (Recharge 5--6).} The dragon exhales fire in a
60-­‐foot cone. Each creature in that area must make a DC 21 Dexterity
saving throw, taking 63 (18d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{legendary-actions-7}{%
\paragraph{Legendary Actions}\label{legendary-actions-7}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 22 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-red-dragon}{%
\subsubsection{Young Red Dragon}\label{young-red-dragon}}

\emph{Large dragon, chaotic evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 178 (17d10 + 85)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 10 (+0) & 21 (+5) & 14 (+2) & 11 (+0) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +9, Wis +4, Cha +8

\textbf{Skills} Perception +8, Stealth +4

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 18

\textbf{Languages} Common, Draconic

\textbf{Challenge} 10 (5,900 XP)

\hypertarget{actions-37}{%
\paragraph{Actions}\label{actions-37}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage plus 3 (1d6) fire
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Fire Breath (Recharge 5--6).} The dragon exhales fire in a
30-­‐foot cone. Each creature in that area must make a DC 17 Dexterity
saving throw, taking 56 (16d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{red-dragon-wyrmling}{%
\subsubsection{Red Dragon Wyrmling}\label{red-dragon-wyrmling}}

\emph{Medium dragon, chaotic evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 75 (10d8 + 30)

\textbf{Speed} 30 ft., climb 30 ft., fly 60 ft.

\textbar{} STR \textbar{} DEX \textbar{} CON \textbar{} INT \textbar{}
WIS \textbar{} CHA \textbar{} \textbar{} -\/- -\/-\/-\/-\/-\/-\/-\/-\/-
\textbar{} -\/- -\/-\/-\/-\/-\/-\/-\/-\/- \textbar{} -\/-
-\/-\/-\/-\/-\/-\/-\/-\/- \textbar{} -\/- -\/-\/-\/-\/-\/-\/-\/-\/-
\textbar{} -\/- -\/-\/-\/-\/-\/-\/-\/-\/- \textbar{}
-\/-\/-\/-\/-\/-\/-\/-\/-\/-\/- \textbar{} \textbar{} 19 (+4) \textbar{}
10 (+0) \textbar{} 17 (+3) \textbar{} 12 (+1) \textbar{} 11 (+0)
\textbar{} 15 (+2) \textbar{}

\textbf{Saving Throws} Dex +2, Con +5, Wis +2, Cha +4

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 4 (1,100 XP)

\hypertarget{actions-38}{%
\paragraph{Actions}\label{actions-38}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 9 (1d10 + 4) piercing damage plus 3 (1d6) fire
damage.

\textbf{Fire Breath (Recharge 5--6).} The dragon exhales fire in a
15-­‐foot cone. Each creature in that area must make a DC 13 Dexterity
saving throw, taking 24 (7d6) fire damage on a failed save, or half as
much damage on a successful one.

\hypertarget{white-dragon}{%
\subsubsection{White Dragon}\label{white-dragon}}

\hypertarget{ancient-white-dragon}{%
\subsubsection{Ancient White Dragon}\label{ancient-white-dragon}}

\emph{Gargantuan dragon, chaotic evil}

\textbf{Armor Class} 20 (natural armor)

\textbf{Hit Points} 333 (18d20 + 144)

\textbf{Speed} 40 ft., burrow 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
26 (+8) & 10 (+0) & 26 (+8) & 10 (+0) & 13 (+1) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +14, Wis +7, Cha +8

\textbf{Skills} Perception +13, Stealth +6

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 23

\textbf{Languages} Common, Draconic

\textbf{Challenge} 20 (25,000 XP)

\textbf{Ice Walk.} The dragon can move across and climb icy surfaces
without needing to make an ability check. Additionally, difficult
terrain composed of ice or snow doesn't cost it extra moment.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-39}{%
\paragraph{Actions}\label{actions-39}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +14 to hit, reach 15 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage plus 9 (2d8) cold
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +14 to hit, reach 20 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 16
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Cold Breath (Recharge 5--6).} The dragon exhales an icy blast in
a 90-­‐foot cone. Each creature in that area must make a DC 22
Constitution saving throw, taking 72 (16d8) cold damage on a failed
save, or half as much damage on a successful one.

\hypertarget{legendary-actions-8}{%
\paragraph{Legendary Actions}\label{legendary-actions-8}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 22 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-white-dragon}{%
\subsubsection{Adult White Dragon}\label{adult-white-dragon}}

\emph{Huge dragon, chaotic evil}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 200 (16d12 + 96)

\textbf{Speed} 40 ft., burrow 30 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
22 (+6) & 10 (+0) & 22 (+6) & 8 (−1) & 12 (+1) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +11, Wis +6, Cha +6

\textbf{Skills} Perception +11, Stealth +5

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 21

\textbf{Languages} Common, Draconic

\textbf{Challenge} 13 (10,000 XP)

\textbf{Ice Walk.} The dragon can move across and climb icy surfaces
without needing to make an ability check. Additionally, difficult
terrain composed of ice or snow doesn't cost it extra moment.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-40}{%
\paragraph{Actions}\label{actions-40}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage plus 4 (1d8) cold
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +11 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +11 to hit, reach 15 ft., one
target. \emph{Hit:} 15 (2d8 + 6) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 14
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Cold Breath (Recharge 5--6).} The dragon exhales an icy blast in
a 60-­‐foot cone. Each creature in that area must make a DC 19
Constitution saving throw, taking 54 (12d8) cold damage on a failed
save, or half as much damage on a successful one.

\hypertarget{legendary-actions-9}{%
\paragraph{Legendary Actions}\label{legendary-actions-9}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 19 Dexterity
saving throw or take 13 (2d6 + 6) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-white-dragon}{%
\subsubsection{Young White Dragon}\label{young-white-dragon}}

\emph{Large dragon, chaotic evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 133 (14d10 + 56)

\textbf{Speed} 40 ft., burrow 20 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 10 (+0) & 18 (+4) & 6 (−2) & 11 (+0) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +7, Wis +3, Cha +4

\textbf{Skills} Perception +6, Stealth +3

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 16

\textbf{Languages} Common, Draconic

\textbf{Challenge} 6 (2,300 XP)

\textbf{Ice Walk.} The dragon can move across and climb icy surfaces
without needing to make an ability check. Additionally, difficult
terrain composed of ice or snow doesn't cost it extra moment.

\hypertarget{actions-41}{%
\paragraph{Actions}\label{actions-41}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage plus 4 (1d8) cold
damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\textbf{Cold Breath (Recharge 5--6).} The dragon exhales an icy blast in
a 30-­‐foot cone. Each creature in that area must make a DC 15
Constitution saving throw, taking 45 (10d8) cold damage on a failed
save, or half as much damage on a successful one.

\hypertarget{white-dragon-wyrmling}{%
\subsubsection{White Dragon Wyrmling}\label{white-dragon-wyrmling}}

\emph{Medium dragon, chaotic evil}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 32 (5d8 + 10)

\textbf{Speed} 30 ft., burrow 15 ft., fly 60 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 10 (+0) & 14 (+2) & 5 (−3) & 10 (+0) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +2, Con +4, Wis +2, Cha +2

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 2 (450 XP)

\hypertarget{actions-42}{%
\paragraph{Actions}\label{actions-42}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d10 + 2) piercing damage plus 2 (1d4) cold
damage.

\textbf{Cold Breath (Recharge 5--6).} The dragon exhales an icy blast of
hail in a 15-­‐foot cone. Each creature in that area must make a DC 12
Constitution saving throw, taking 22 (5d8) cold damage on a failed save,
or half as much damage on a successful one.

\hypertarget{dragons-metallic}{%
\subsection{Dragons, Metallic}\label{dragons-metallic}}

\hypertarget{brass-dragon}{%
\subsubsection{Brass Dragon}\label{brass-dragon}}

\hypertarget{ancient-brass-dragon}{%
\subsubsection{Ancient Brass Dragon}\label{ancient-brass-dragon}}

\emph{Gargantuan dragon, chaotic good}

\textbf{Armor Class} 20 (natural armor)

\textbf{Hit Points} 297 (17d20 + 119)

\textbf{Speed} 40 ft., burrow 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 10 (+0) & 25 (+7) & 16 (+3) & 15 (+2) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +13, Wis +8, Cha +10

\textbf{Skills} History +9, Perception +14, Persuasion +10, Stealth +6

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 24

\textbf{Languages} Common, Draconic

\textbf{Challenge} 20 (25,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-43}{%
\paragraph{Actions}\label{actions-43}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +14 to hit, reach 15 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +14 to hit, reach 20 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 18
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons:

\textbf{Fire Breath} The dragon exhales fire in an 90-­‐foot line that
is 10 feet wide. Each creature in that line must make a DC 21 Dexterity
saving throw, taking 56 (16d6) fire damage on a failed save, or half as
much damage on a successful one.

\textbf{Sleep Breath.} The dragon exhales sleep gas in a 90-­‐foot cone.
Each creature in that area must succeed on a DC 21 Constitution saving
throw or fall unconscious for 10 minutes. This effect ends for a
creature if the creature takes damage or someone uses an action to wake
it.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-10}{%
\paragraph{Legendary Actions}\label{legendary-actions-10}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 22 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-brass-dragon}{%
\subsubsection{Adult Brass Dragon}\label{adult-brass-dragon}}

\emph{Huge dragon, chaotic good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 172 (15d12 + 75)

\textbf{Speed} 40 ft., burrow 30 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 10 (+0) & 21 (+5) & 14 (+2) & 13 (+1) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +10, Wis +6, Cha +8

\textbf{Skills} History +7, Perception +11, Persuasion +8, Stealth +5

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 21

\textbf{Languages} Common, Draconic

\textbf{Challenge} 13 (10,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-44}{%
\paragraph{Actions}\label{actions-44}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +11 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +11 to hit, reach 15 ft., one
target. \emph{Hit:} 15 (2d8 + 6) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 16
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in an 60-­‐foot line that
is 5 feet wide. Each creature in that line must make a DC 18 Dexterity
saving throw, taking 45 (13d6) fire damage on a failed save, or half as
much damage on a successful one.

\textbf{Sleep Breath.} The dragon exhales sleep gas in a 60-­‐foot cone.
Each creature in that area must succeed on a DC 18 Constitution saving
throw or fall unconscious for 10 minutes. This effect ends for a
creature if the creature takes damage or someone uses an action to wake
it.

\hypertarget{legendary-actions-11}{%
\paragraph{Legendary Actions}\label{legendary-actions-11}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 19 Dexterity
saving throw or take 13 (2d6 + 6) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-brass-dragon}{%
\subsubsection{Young Brass Dragon}\label{young-brass-dragon}}

\emph{Large dragon, chaotic good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 110 (13d10 + 39)

\textbf{Speed} 40 ft., burrow 20 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 10 (+0) & 17 (+3) & 12 (+1) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +6, Wis +3, Cha +5

\textbf{Skills} Perception +6, Persuasion +5, Stealth +3

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 16

\textbf{Languages} Common, Draconic

\textbf{Challenge} 6 (2,300 XP)

\hypertarget{actions-45}{%
\paragraph{Actions}\label{actions-45}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in a 40-­‐foot line that is
5 feet wide. Each creature in that line must make a DC 14 Dexterity
saving throw, taking 42 (12d6) fire damage on a failed save, or half as
much damage on a successful one.

\textbf{Sleep Breath.} The dragon exhales sleep gas in a 30-­‐foot cone.
Each creature in that area must succeed on a DC 14 Constitution saving
throw or fall unconscious for 5 minutes. This effect ends for a creature
if the creature takes damage or someone uses an action to wake it.

\hypertarget{brass-dragon-wyrmling}{%
\subsubsection{Brass Dragon Wyrmling}\label{brass-dragon-wyrmling}}

\emph{Medium dragon, chaotic good}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 16 (3d8 + 3)

\textbf{Speed} 30 ft., burrow 15 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 10 (+0) & 13 (+1) & 10 (+0) & 11 (+0) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +2, Con +3, Wis +2, Cha +3

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 1 (200 XP)

\hypertarget{actions-46}{%
\paragraph{Actions}\label{actions-46}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d10 + 2) piercing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in an 20-­‐foot line that
is 5 feet wide. Each creature in that line must make a DC 11 Dexterity
saving throw, taking 14 (4d6) fire damage on a failed save, or half as
much damage on a successful one.

\textbf{Sleep Breath.} The dragon exhales sleep gas in a 15-­‐foot cone.
Each creature in that area must succeed on a DC 11 Constitution saving
throw or fall unconscious for 1 minute. This effect ends for a creature
if the creature takes damage or someone uses an action to wake it.

\hypertarget{bronze-dragon}{%
\subsubsection{Bronze Dragon}\label{bronze-dragon}}

\hypertarget{ancient-bronze-dragon}{%
\subsubsection{Ancient Bronze Dragon}\label{ancient-bronze-dragon}}

\emph{Gargantuan dragon, lawful good}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 444 (24d20 + 192)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
29 (+9) & 10 (+0) & 27 (+8) & 18 (+4) & 17 (+3) & 21 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +15, Wis +10, Cha +12

\textbf{Skills} Insight +10, Perception +17, Stealth +7

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 27

\textbf{Languages} Common, Draconic

\textbf{Challenge} 22 (41,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-47}{%
\paragraph{Actions}\label{actions-47}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +16 to hit, reach 15 ft., one
target. \emph{Hit:} 20 (2d10 + 9) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +16 to hit, reach 10 ft., one
target. \emph{Hit:} 16 (2d6 + 9) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +16 to hit, reach 20 ft., one
target. \emph{Hit:} 18 (2d8 + 9) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 20
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Lightning Breath.} The dragon exhales lightning in a 120-­‐foot
line that is 10 feet wide. Each creature in that line must make a DC 23
Dexterity saving throw, taking 88 (16d10) lightning damage on a failed
save, or half as much damage on a successful one.

\textbf{Repulsion Breath.} The dragon exhales repulsion energy in a
30-­‐foot cone. Each creature in that area must succeed on a DC 23
Strength saving throw. On a failed save, the creature is pushed 60 feet
away from the dragon.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-12}{%
\paragraph{Legendary Actions}\label{legendary-actions-12}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 24 Dexterity
saving throw or take 16 (2d6 + 9) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-bronze-dragon}{%
\subsubsection{Adult Bronze Dragon}\label{adult-bronze-dragon}}

\emph{Huge dragon, lawful good}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 212 (17d12 + 102)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
25 (+7) & 10 (+0) & 23 (+6) & 16 (+3) & 15 (+2) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +11, Wis +7, Cha +9

\textbf{Skills} Insight +7, Perception +12, Stealth +5

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 22

\textbf{Languages} Common, Draconic

\textbf{Challenge} 15 (13,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-48}{%
\paragraph{Actions}\label{actions-48}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +12 to hit, reach 10 ft., one
target. \emph{Hit:} 18 (2d10 + 7) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +12 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d6 + 7) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +12 to hit, reach 15 ft., one
target. \emph{Hit:} 16 (2d8 + 7) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 17
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Lightning Breath.} The dragon exhales lightning in a 90-­‐ foot
line that is 5 feet wide. Each creature in that line must make a DC 19
Dexterity saving throw, taking 66 (12d10) lightning damage on a failed
save, or half as much damage on a successful one.

\textbf{Repulsion Breath.} The dragon exhales repulsion energy in a
30-­‐foot cone. Each creature in that area must succeed on a DC 19
Strength saving throw. On a failed save, the creature is pushed 60 feet
away from the dragon.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-13}{%
\paragraph{Legendary Actions}\label{legendary-actions-13}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 20 Dexterity
saving throw or take 14 (2d6 + 7) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-bronze-dragon}{%
\subsubsection{Young Bronze Dragon}\label{young-bronze-dragon}}

\emph{Large dragon, lawful good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 142 (15d10 + 60)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 10 (+0) & 19 (+4) & 14 (+2) & 13 (+1) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +7, Wis +4, Cha +6

\textbf{Skills} Insight +4, Perception +7, Stealth +3

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 17

\textbf{Languages} Common, Draconic

\textbf{Challenge} 8 (3,900 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-49}{%
\paragraph{Actions}\label{actions-49}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
target. \emph{Hit:} 16 (2d10 + 5) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 12 (2d6 + 5) slashing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Lightning Breath.} The dragon exhales lightning in a 60-­‐ foot
line that is 5 feet wide. Each creature in that line must make a DC 15
Dexterity saving throw, taking 55 (10d10) lightning damage on a failed
save, or half as much damage on a successful one.

\textbf{Repulsion Breath.} The dragon exhales repulsion energy in a
30-­‐foot cone. Each creature in that area must succeed on a DC 15
Strength saving throw. On a failed save, the creature is pushed 40 feet
away from the dragon.

\hypertarget{bronze-dragon-wyrmling}{%
\subsubsection{Bronze Dragon Wyrmling}\label{bronze-dragon-wyrmling}}

\emph{Medium dragon, lawful good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 32 (5d8 + 10)

\textbf{Speed} 30 ft., fly 60 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 10 (+0) & 15 (+2) & 12 (+1) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +2, Con +4, Wis +2, Cha +4

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} lightning

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 2 (450 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-50}{%
\paragraph{Actions}\label{actions-50}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 8 (1d10 + 3) piercing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Lightning Breath.} The dragon exhales lightning in a 40-­‐ foot
line that is 5 feet wide. Each creature in that line must make a DC 12
Dexterity saving throw, taking 16 (3d10) lightning damage on a failed
save, or half as much damage on a successful one.

\textbf{Repulsion Breath.} The dragon exhales repulsion energy in a
30-­‐foot cone. Each creature in that area must succeed on a DC 12
Strength saving throw. On a failed save, the creature is pushed 30 feet
away from the dragon.

\hypertarget{copper-dragon}{%
\subsubsection{Copper Dragon}\label{copper-dragon}}

\hypertarget{ancient-copper-dragon}{%
\subsubsection{Ancient Copper Dragon}\label{ancient-copper-dragon}}

\emph{Gargantuan dragon, chaotic good}

\textbf{Armor Class} 21 (natural armor)

\textbf{Hit Points} 350 (20d20 + 140)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 12 (+1) & 25 (+7) & 20 (+5) & 17 (+3) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +8, Con +14, Wis +10, Cha +11

\textbf{Skills} Deception +11, Perception +17, Stealth +8

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 27

\textbf{Languages} Common, Draconic

\textbf{Challenge} 21 (33,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-51}{%
\paragraph{Actions}\label{actions-51}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +15 to hit, reach 15 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +15 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +15 to hit, reach 20 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 19
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Acid Breath.} The dragon exhales acid in an 90-­‐foot line that
is 10 feet wide. Each creature in that line must make a DC 22 Dexterity
saving throw, taking 63 (14d8) acid damage on a failed save, or half as
much damage on a successful one.

\textbf{Slowing Breath.} The dragon exhales gas in a 90-­‐foot cone.
Each creature in that area must succeed on a DC 22 Constitution saving
throw. On a failed save, the creature can't use reactions, its speed is
halved, and it can't make more than one attack on its turn. In addition,
the creature can use either an action or a bonus action on its turn, but
not both. These effects last for 1 minute. The creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself with a successful save.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-14}{%
\paragraph{Legendary Actions}\label{legendary-actions-14}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 23 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-copper-dragon}{%
\subsubsection{Adult Copper Dragon}\label{adult-copper-dragon}}

\emph{Huge dragon, chaotic good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 184 (16d12 + 80)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 12 (+1) & 21 (+5) & 18 (+4) & 15 (+2) & 17 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +10, Wis +7, Cha +8

\textbf{Skills} Deception +8, Perception +12, Stealth +6

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 22

\textbf{Languages} Common, Draconic

\textbf{Challenge} 14 (11,500 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-52}{%
\paragraph{Actions}\label{actions-52}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +11 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +11 to hit, reach 15 ft., one
target. \emph{Hit:} 15 (2d8 + 6) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 16
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Acid Breath.} The dragon exhales acid in an 60-­‐foot line that
is 5 feet wide. Each creature in that line must make a DC 18 Dexterity
saving throw, taking 54 (12d8) acid damage on a failed save, or half as
much damage on a successful one.

\textbf{Slowing Breath.} The dragon exhales gas in a 60-­‐foot cone.
Each creature in that area must succeed on a DC 18 Constitution saving
throw. On a failed save, the creature can't use reactions, its speed is
halved, and it can't make more than one attack on its turn. In addition,
the creature can use either an action or a bonus action on its turn, but
not both. These effects last for 1 minute. The creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself with a successful save.

\hypertarget{legendary-actions-15}{%
\paragraph{Legendary Actions}\label{legendary-actions-15}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 19 Dexterity
saving throw or take 13 (2d6 + 6) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-copper-dragon}{%
\subsubsection{Young Copper Dragon}\label{young-copper-dragon}}

\emph{Large dragon, chaotic good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 119 (14d10 + 42)

\textbf{Speed} 40 ft., climb 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 12 (+1) & 17 (+3) & 16 (+3) & 13 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +6, Wis +4, Cha +5

\textbf{Skills} Deception +5, Perception +7, Stealth +4

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 17

\textbf{Languages} Common, Draconic

\textbf{Challenge} 7 (2,900 XP)

\hypertarget{actions-53}{%
\paragraph{Actions}\label{actions-53}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
target. \emph{Hit:} 15 (2d10 + 4) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 11 (2d6 + 4) slashing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Acid Breath.} The dragon exhales acid in an 40-­‐foot line that
is 5 feet wide. Each creature in that line must make a DC 14 Dexterity
saving throw, taking 40 (9d8) acid damage on a failed save, or half as
much damage on a successful one.

\textbf{Slowing Breath.} The dragon exhales gas in a 30-­‐foot cone.
Each creature in that area must succeed on a DC 14 Constitution saving
throw. On a failed save, the creature can't use reactions, its speed is
halved, and it can't make more than one attack on its turn. In addition,
the creature can use either an action or a bonus action on its turn, but
not both. These effects last for 1 minute. The creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself with a successful save.

\hypertarget{copper-dragon-wyrmling}{%
\subsubsection{Copper Dragon Wyrmling}\label{copper-dragon-wyrmling}}

\emph{Medium dragon, chaotic good}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 22 (4d8 + 4)

\textbf{Speed} 30 ft., climb 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 12 (+1) & 13 (+1) & 14 (+2) & 11 (+0) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +3, Wis +2, Cha +3

\textbf{Skills} Perception +4, Stealth +3

\textbf{Damage Immunities} acid

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 1 (200 XP)

\hypertarget{actions-54}{%
\paragraph{Actions}\label{actions-54}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d10 + 2) piercing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Acid Breath.} The dragon exhales acid in an 20-­‐foot line that
is 5 feet wide. Each creature in that line must make a DC 11 Dexterity
saving throw, taking 18 (4d8) acid damage on a failed save, or half as
much damage on a successful one.

\textbf{Slowing Breath.} The dragon exhales gas in a 15-­‐foot cone.
Each creature in that area must succeed on a DC 11 Constitution saving
throw. On a failed save, the creature can't use reactions, its speed is
halved, and it can't make more than one attack on its turn. In addition,
the creature can use either an action or a bonus action on its turn, but
not both. These effects last for 1 minute. The creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself with a successful save.

\hypertarget{gold-dragon}{%
\subsubsection{Gold Dragon}\label{gold-dragon}}

\hypertarget{ancient-gold-dragon}{%
\subsubsection{Ancient Gold Dragon}\label{ancient-gold-dragon}}

\emph{Gargantuan dragon, lawful good}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 546 (28d20 + 252)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
30 (+10) & 14 (+2) & 29 (+9) & 18 (+4) & 17 (+3) & 28
(+9)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +9, Con +16, Wis +10, Cha +16

\textbf{Skills} Insight +10, Perception +17, Persuasion +16, Stealth +9

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 27

\textbf{Languages} Common, Draconic

\textbf{Challenge} 24 (62,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-55}{%
\paragraph{Actions}\label{actions-55}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +17 to hit, reach 15 ft., one
target. \emph{Hit:} 21 (2d10 + 10) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +17 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d6 + 10) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +17 to hit, reach 20 ft., one
target. \emph{Hit:} 19 (2d8 + 10) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 24
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in a 90-­‐foot cone. Each
creature in that area must make a DC 24 Dexterity saving throw, taking
71 (13d10) fire damage on a failed save, or half as much damage on a
successful one.

\textbf{Weakening Breath.} The dragon exhales gas in a 90-­‐foot cone.
Each creature in that area must succeed on a DC 24 Strength saving throw
or have disadvantage on Strength-­‐based attack rolls, Strength checks,
and Strength saving throws for 1 minute. A creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-16}{%
\paragraph{Legendary Actions}\label{legendary-actions-16}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 25 Dexterity
saving throw or take 17 (2d6 + 10) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-gold-dragon}{%
\subsubsection{Adult Gold Dragon}\label{adult-gold-dragon}}

\emph{Huge dragon, lawful good}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 256 (19d12 + 133)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 14 (+2) & 25 (+7) & 16 (+3) & 15 (+2) & 24 (+7)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +8, Con +13, Wis +8, Cha +13

\textbf{Skills} Insight +8, Perception +14, Persuasion +13, Stealth +8

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 24

\textbf{Languages} Common, Draconic

\textbf{Challenge} 17 (18,000 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-56}{%
\paragraph{Actions}\label{actions-56}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +14 to hit, reach 10 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +14 to hit, reach 5 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +14 to hit, reach 15 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 21
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in a 60-­‐foot cone. Each
creature in that area must make a DC 21 Dexterity saving throw, taking
66 (12d10) fire damage on a failed save, or half as much damage on a
successful one.

\textbf{Weakening Breath.} The dragon exhales gas in a 60-­‐foot cone.
Each creature in that area must succeed on a DC 21 Strength saving throw
or have disadvantage on Strength-­‐based attack rolls, Strength checks,
and Strength saving throws for 1 minute. A creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-17}{%
\paragraph{Legendary Actions}\label{legendary-actions-17}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 22 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-gold-dragon}{%
\subsubsection{Young Gold Dragon}\label{young-gold-dragon}}

\emph{Large dragon, lawful good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 178 (17d10 + 85)

\textbf{Speed} 40 ft., fly 80 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 14 (+2) & 21 (+5) & 16 (+3) & 13 (+1) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +9, Wis +5, Cha +9

\textbf{Skills} Insight +5, Perception +9, Persuasion +9, Stealth +6

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 19

\textbf{Languages} Common, Draconic

\textbf{Challenge} 10 (5,900 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-57}{%
\paragraph{Actions}\label{actions-57}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in a 30-­‐foot cone. Each
creature in that area must make a DC 17 Dexterity saving throw, taking
55 (10d10) fire damage on a failed save, or half as much damage on a
successful one.

\textbf{Weakening Breath.} The dragon exhales gas in a 30-­‐foot cone.
Each creature in that area must succeed on a DC 17 Strength saving throw
or have disadvantage on Strength-­‐based attack rolls, Strength checks,
and Strength saving throws for 1 minute. A creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\hypertarget{gold-dragon-wyrmling}{%
\subsubsection{Gold Dragon Wyrmling}\label{gold-dragon-wyrmling}}

\emph{Medium dragon, lawful good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 60 (8d8 + 24)

\textbf{Speed} 30 ft., fly 60 ft., swim 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 14 (+2) & 17 (+3) & 14 (+2) & 11 (+0) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +5, Wis +2, Cha +5

\textbf{Skills} Perception +4, Stealth +4

\textbf{Damage Immunities} fire

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 3 (700 XP)

\textbf{Amphibious.} The dragon can breathe air and water.

\hypertarget{actions-58}{%
\paragraph{Actions}\label{actions-58}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 9 (1d10 + 4) piercing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Fire Breath} The dragon exhales fire in a 15-­‐foot cone. Each
creature in that area must make a DC 13 Dexterity saving throw, taking
22 (4d10) fire damage on a failed save, or half as much damage on a
successful one.

\textbf{Weakening Breath.} The dragon exhales gas in a 15-­‐foot cone.
Each creature in that area must succeed on a DC 13 Strength saving throw
or have disadvantage on Strength-­‐based attack rolls, Strength checks,
and Strength saving throws for 1 minute. A creature can repeat the
saving throw at the end of each of its turns, ending the effect on
itself on a success.

\hypertarget{silver-dragon}{%
\subsubsection{Silver Dragon}\label{silver-dragon}}

\hypertarget{ancient-silver-dragon}{%
\subsubsection{Ancient Silver Dragon}\label{ancient-silver-dragon}}

\emph{Gargantuan dragon, lawful good}

\textbf{Armor Class} 22 (natural armor)

\textbf{Hit Points} 487 (25d20 + 225)

\textbf{Speed} 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
30 (+10) & 10 (+0) & 29 (+9) & 18 (+4) & 15 (+2) & 23
(+6)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +7, Con +16, Wis +9, Cha +13

\textbf{Skills} Arcana +11, History +11, Perception +16, Stealth +7

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 26

\textbf{Languages} Common, Draconic

\textbf{Challenge} 23 (50,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-59}{%
\paragraph{Actions}\label{actions-59}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +17 to hit, reach 15 ft., one
target. \emph{Hit:} 21 (2d10 + 10) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +17 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d6 + 10) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +17 to hit, reach 20 ft., one
target. \emph{Hit:} 19 (2d8 + 10) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 21
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Cold Breath.} The dragon exhales an icy blast in a 90-­‐ foot
cone. Each creature in that area must make a DC 24 Constitution saving
throw, taking 67 (15d8) cold damage on a failed save, or half as much
damage on a successful one.

\textbf{Paralyzing Breath.} The dragon exhales paralyzing gas in a
90-­‐foot cone. Each creature in that area must succeed on a DC 24
Constitution saving throw or be paralyzed for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-18}{%
\paragraph{Legendary Actions}\label{legendary-actions-18}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 15 feet of the dragon must succeed on a DC 25 Dexterity
saving throw or take 17 (2d6 + 10) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{adult-silver-dragon}{%
\subsubsection{Adult Silver Dragon}\label{adult-silver-dragon}}

\emph{Huge dragon, lawful good}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 243 (18d12 + 126)

\textbf{Speed} 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
27 (+8) & 10 (+0) & 25 (+7) & 16 (+3) & 13 (+1) & 21 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +5, Con +12, Wis +6, Cha +10

\textbf{Skills} Arcana +8, History +8, Perception +11, Stealth +5

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 60 ft., darkvision 120 ft., passive
Perception 21

\textbf{Languages} Common, Draconic

\textbf{Challenge} 16 (15,000 XP)

\textbf{Legendary Resistance (3/Day).} If the dragon fails a saving
throw, it can choose to succeed instead.

\hypertarget{actions-60}{%
\paragraph{Actions}\label{actions-60}}

\textbf{Multiattack.} The dragon can use its Frightful Presence. It then
makes three attacks: one with its bite and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +13 to hit, reach 10 ft., one
target. \emph{Hit:} 19 (2d10 + 8) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +13 to hit, reach 5 ft., one
target. \emph{Hit:} 15 (2d6 + 8) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +13 to hit, reach 15 ft., one
target. \emph{Hit:} 17 (2d8 + 8) bludgeoning damage.

\textbf{Frightful Presence.} Each creature of the dragon's choice that
is within 120 feet of the dragon and aware of it must succeed on a DC 18
Wisdom saving throw or become frightened for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success. If a creature's saving throw is
successful or the effect ends for it, the creature is immune to the
dragon's Frightful Presence for the next 24 hours.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Cold Breath.} The dragon exhales an icy blast in a 60-­‐ foot
cone. Each creature in that area must make a DC 20 Constitution saving
throw, taking 58 (13d8) cold damage on a failed save, or half as much
damage on a successful one.

\textbf{Paralyzing Breath.} The dragon exhales paralyzing gas in a
60-­‐foot cone. Each creature in that area must succeed on a DC 20
Constitution saving throw or be paralyzed for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\textbf{Change Shape.} The dragon magically polymorphs into a humanoid
or beast that has a challenge rating no higher than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the dragon's choice).

In a new form, the dragon retains its alignment, hit points, Hit Dice,
ability to speak, proficiencies, Legendary Resistance, Lair Actions, and
Intelligence, Wisdom, and Charisma scores, as well as this action. Its
statistics and capabilities are otherwise replaced by those of the new
form, except any class features or legendary actions of that form.

\hypertarget{legendary-actions-19}{%
\paragraph{Legendary Actions}\label{legendary-actions-19}}

The dragon can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The dragon regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The dragon makes a Wisdom (Perception) check.

\textbf{Tail Attack.} The dragon makes a tail attack

\textbf{Wing Attack (Costs 2 Actions).} The dragon beats its wings. Each
creature within 10 feet of the dragon must succeed on a DC 21 Dexterity
saving throw or take 15 (2d6 + 8) bludgeoning damage and be knocked
prone. The dragon can then fly up to half its flying speed.

\hypertarget{young-silver-dragon}{%
\subsubsection{Young Silver Dragon}\label{young-silver-dragon}}

\emph{Large dragon, lawful good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 168 (16d10 + 80)

\textbf{Speed} 40 ft., fly 80 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
23 (+6) & 10 (+0) & 21 (+5) & 14 (+2) & 11 (+0) & 19 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +9, Wis +4, Cha +8

\textbf{Skills} Arcana +6, History +6, Perception +8, Stealth +4

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 30 ft., darkvision 120 ft., passive
Perception 18

\textbf{Languages} Common, Draconic

\textbf{Challenge} 9 (5,000 XP)

\hypertarget{actions-61}{%
\paragraph{Actions}\label{actions-61}}

\textbf{Multiattack.} The dragon makes three attacks: one with its bite
and two with its claws.

\textbf{Bite.} \emph{Melee Weapon Attack:} +10 to hit, reach 10 ft., one
target. \emph{Hit:} 17 (2d10 + 6) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +10 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d6 + 6) slashing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Cold Breath.} The dragon exhales an icy blast in a 30-­‐ foot
cone. Each creature in that area must make a DC 17 Constitution saving
throw, taking 54 (12d8) cold damage on a failed save, or half as much
damage on a successful one.

\textbf{Paralyzing Breath.} The dragon exhales paralyzing gas in a
30-­‐foot cone. Each creature in that area must succeed on a DC 17
Constitution saving throw or be paralyzed for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\hypertarget{silver-dragon-wyrmling}{%
\subsubsection{Silver Dragon Wyrmling}\label{silver-dragon-wyrmling}}

\emph{Medium dragon, lawful good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 45 (6d8 + 18)

\textbf{Speed} 30 ft., fly 60 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 10 (+0) & 17 (+3) & 12 (+1) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +2, Con +5, Wis +2, Cha +4

\textbf{Skills} Perception +4, Stealth +2

\textbf{Damage Immunities} cold

\textbf{Senses} blindsight 10 ft., darkvision 60 ft., passive Perception
14

\textbf{Languages} Draconic

\textbf{Challenge} 2 (450 XP)

\hypertarget{actions-62}{%
\paragraph{Actions}\label{actions-62}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 9 (1d10 + 4) piercing damage.

\textbf{Breath Weapons (Recharge 5--6).} The dragon uses one of the
following breath weapons.

\textbf{Cold Breath.} The dragon exhales an icy blast in a 15-­‐ foot
cone. Each creature in that area must make a DC 13 Constitution saving
throw, taking 18 (4d8) cold damage on a failed save, or half as much
damage on a successful one.

\textbf{Paralyzing Breath.} The dragon exhales paralyzing gas in a
15-­‐foot cone. Each creature in that area must succeed on a DC 13
Constitution saving throw or be paralyzed for 1 minute. A creature can
repeat the saving throw at the end of each of its turns, ending the
effect on itself on a success.

\hypertarget{dragon-turtle}{%
\subsubsection{Dragon Turtle}\label{dragon-turtle}}

\emph{Gargantuan dragon, neutral}

\textbf{Armor Class} 20 (natural armor)

\textbf{Hit Points} 341 (22d20 + 110)

\textbf{Speed} 20 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
25 (+7) & 10 (+0) & 20 (+5) & 10 (+0) & 12 (+1) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +11, Wis +7

\textbf{Damage Resistances} fire

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Aquan, Draconic

\textbf{Challenge} 17 (18,000 XP)

\textbf{Amphibious.} The dragon turtle can breathe air and water.

\hypertarget{actions-63}{%
\paragraph{Actions}\label{actions-63}}

\textbf{Multiattack.} The dragon turtle makes three attacks: one with
its bite and two with its claws. It can make one tail attack in place of
its two claw attacks.

\textbf{Bite.} \emph{Melee Weapon Attack:} +13 to hit, reach 15 ft., one
target. \emph{Hit:} 26 (3d12 + 7) piercing damage.

\textbf{Claw.} \emph{Melee Weapon Attack:} +13 to hit, reach 10 ft., one
target. \emph{Hit:} 16 (2d8 + 7) slashing damage.

\textbf{Tail.} \emph{Melee Weapon Attack:} +13 to hit, reach 15 ft., one
target. \emph{Hit:} 26 (3d12 + 7) bludgeoning damage. If the target is a
creature, it must succeed on a DC 20 Strength saving throw or be pushed
up to 10 feet away from the dragon turtle and knocked prone.

\textbf{Steam Breath (Recharge 5--6).} The dragon turtle exhales
scalding steam in a 60-­‐foot cone. Each creature in that area must make
a DC 18 Constitution saving throw, taking 52 (15d6) fire damage on a
failed save, or half as much damage on a successful one. Being
underwater doesn't grant resistance against this damage.

\hypertarget{drider}{%
\subsubsection{Drider}\label{drider}}

\emph{Large monstrosity, chaotic evil}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 123 (13d10 + 52)

\textbf{Speed} 30 ft., climb 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 16 (+3) & 18 (+4) & 13 (+1) & 14 (+2) & 12 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +5, Stealth +9

\textbf{Senses} darkvision 120 ft., passive Perception 15

\textbf{Languages} Elvish, Undercommon

\textbf{Challenge} 6 (2,300 XP)

\textbf{Fey Ancestry.} The drider has advantage on saving throws against
being charmed, and magic can't put the drider to sleep.

\textbf{Innate Spellcasting.} The drider's innate spellcasting ability
is Wisdom (spell save DC 13). The drider can innately cast the following
spells, requiring no material components:

At will: \emph{dancing lights}

1/day each: \emph{darkness}, \emph{faerie fire}

\textbf{Spider Climb.} The drider can climb difficult surfaces,
including upside down on ceilings, without needing to make an ability
check.

\textbf{Sunlight Sensitivity.} While in sunlight, the drider has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\textbf{Web Walker.} The drider ignores movement restrictions caused by
webbing.

\hypertarget{actions-64}{%
\paragraph{Actions}\label{actions-64}}

\textbf{Multiattack.} The drider makes three attacks, either with its
longsword or its longbow. It can replace one of those attacks with a
bite attack.

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
creature. \emph{Hit:} 2 (1d4) piercing damage plus 9 (2d8) poison
damage.

\textbf{Longsword.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one target. \emph{Hit:} 7 (1d8 + 3) slashing damage, or 8 (1d10+ 3)
slashing damage if used with two hands.

\textbf{Longbow.} \emph{Ranged Weapon Attack:} +6 to hit, range 150/600
ft., one target. \emph{Hit:} 7 (1d8 + 3) piercing damage plus 4 (1d8)
poison damage.

\hypertarget{dryad}{%
\subsubsection{Dryad}\label{dryad}}

\emph{Medium fey, neutral}

\textbf{\textbf{Armor Class}} 11 (16 with \emph{barkskin})

\textbf{Hit Points} 22 (5d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 12 (+1) & 11 (+0) & 14 (+2) & 15 (+2) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +4, Stealth +5

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Elvish, Sylvan

\textbf{Challenge} 1 (200 XP)

\textbf{Innate Spellcasting.} The dryad's innate spellcasting ability is
Charisma (spell save DC 14). The dryad can innately cast the following
spells, requiring no material components:

At will: \emph{druidcraft}

3/day each: \emph{entangle}, \emph{goodberry}

1/day each: \emph{barkskin}, \emph{pass without trace},
\emph{shillelagh}

\textbf{Magic Resistance.} The dryad has advantage on saving throws
against spells and other magical effects.

\textbf{Speak with Beasts and Plants.} The dryad can communicate with
beasts and plants as if they shared a language.

\textbf{Tree Stride.} Once on her turn, the dryad can use 10 feet of her
movement to step magically into one living tree within her reach and
emerge from a second living tree within 60 feet of the first tree,
appearing in an unoccupied space within 5 feet of the second tree.

Both trees must be Large or bigger.

\hypertarget{actions-65}{%
\paragraph{Actions}\label{actions-65}}

\textbf{Club.} \emph{Melee Weapon Attack:} +2 to hit (+6 to hit with
shillelagh), reach 5 ft., one target. \emph{Hit:} 2 (1d4) bludgeoning
damage, or 8 (1d8 + 4) bludgeoning damage with shillelagh.

\textbf{Fey \textbf{Charm.}} The dryad targets one humanoid or beast
that she can see within 30 feet of her. If the target can see the dryad,
it must succeed on a DC 14 Wisdom saving throw or be magically charmed.
The charmed creature regards the dryad as a trusted friend to be heeded
and protected. Although the target isn't under the dryad's control, it
takes the dryad's requests or actions in the most favorable way it can.

Each time the dryad or its allies do anything harmful to the target, it
can repeat the saving throw, ending the effect on itself on a success.
Otherwise, the effect lasts 24 hours or until the dryad dies, is on a
different plane of existence from the target, or ends the effect as a
bonus action. If a target's saving throw is successful, the target is
immune to the dryad's Fey Charm for the next 24 hours.

The dryad can have no more than one humanoid and up to three beasts
charmed at a time.

\hypertarget{duergar}{%
\subsubsection{Duergar}\label{duergar}}

\emph{Medium humanoid (dwarf), lawful evil}

\textbf{Armor Class} 16 (scale mail, shield)

\textbf{Hit Points} 26 (4d8 + 8)

\textbf{Speed} 25 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 11 (+0) & 14 (+2) & 11 (+0) & 10 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} poison

\textbf{Senses} darkvision 120 ft., passive Perception 10

\textbf{Languages} Dwarvish, Undercommon

\textbf{Challenge} 1 (200 XP)

\textbf{Duergar Resilience.} The duergar has advantage on saving throws
against poison, spells, and illusions, as well as to resist being
charmed or paralyzed.

\textbf{Sunlight Sensitivity.} While in sunlight, the duergar has
disadvantage on attack rolls, as well as on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions-66}{%
\paragraph{Actions}\label{actions-66}}

\textbf{Enlarge (Recharges after a Short or Long Rest).} For 1 minute,
the duergar magically increases in size, along with anything it is
wearing or carrying. While enlarged, the duergar is Large, doubles its
damage dice on Strength-­‐based weapon attacks (included in the
attacks), and makes Strength checks and Strength saving throws with
advantage. If the duergar lacks the room to become Large, it attains the
maximum size possible in the space available.

\textbf{War Pick.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d8 + 2) piercing damage, or 11 (2d8+2)
piercing damage while enlarged.

\textbf{Javelin} \emph{Melee or Ranged Weapon Attack:} +4 to hit, reach
5 ft. or range 30/120 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing
damage, or 9 (2d6 + 2) piercing damage while enlarged.

\textbf{Invisibility (Recharges after a Short or Long Rest).} The
duergar magically turns invisible until it attacks, casts a spell, or
uses its Enlarge, or until its concentration is broken, up to 1 hour (as
if concentrating on a spell).

Any equipment the duergar wears or carries is invisible with it.

\end{document}
