% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-r}{%
\section{Monsters (R)}\label{monsters-r}}

\hypertarget{rakshasa}{%
\subsubsection{Rakshasa}\label{rakshasa}}

\emph{Medium fiend, lawful evil}

\textbf{Armor Class} 16 (natural armor)

\textbf{Hit Points} 110 (13d8 + 52)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 17 (+3) & 18 (+4) & 13 (+1) & 16 (+3) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +10, Insight +8

\textbf{Damage Vulnerabilities} piercing from magic weapons wielded by
good creatures

\textbf{Damage Immunities} bludgeoning, piercing, and slashing from
nonmagical attacks

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} Common, Infernal

\textbf{Challenge} 13 (10,000 XP)

\textbf{Limited Magic Immunity.} The rakshasa can't be affected or
detected by spells of 6th level or lower unless it wishes to be. It has
advantage on saving throws against all other spells and magical effects.

\textbf{Innate Spellcasting.} The rakshasa's innate spellcasting ability
is Charisma (spell save DC 18, +10 to hit with spell attacks). The
rakshasa can innately cast the following spells, requiring no material
components:

At will: \emph{detect thoughts}, \emph{diguise self}, \emph{mage hand},
\emph{minor illusion}

3/day each: \emph{charm person}, \emph{detect magic},
\emph{invisibility}, \emph{major image}, \emph{suggestion}

1/day each: \emph{dominate person}, \emph{fly}, \emph{plane shift},
\emph{true seeing}

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The rakshasa makes two claw attacks.

\textbf{Claw.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 9 (2d6 + 2) slashing damage, and the target is
cursed if it is a creature. The magical curse takes effect whenever the
target takes a short or long rest, filling the target's thoughts with
horrible images and dreams. The cursed target gains no benefit from
finishing a short or long rest. The curse lasts until it is lifted by a
remove curse spell or similar magic.

\hypertarget{remorhaz}{%
\subsubsection{Remorhaz}\label{remorhaz}}

\emph{Huge monstrosity, unaligned}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 195 (17d12 + 85)

\textbf{Speed} 30 ft., burrow 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
24 (+7) & 13 (+1) & 21 (+5) & 4 (−3) & 10 (+0) & 5 (−3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} cold, fire

\textbf{Senses} darkvision 60 ft., tremorsense 60 ft., passive
Perception 10

\textbf{Languages} ---

\textbf{Challenge} 11 (7,200 XP)

\textbf{Heated Body.} A creature that touches the remorhaz or hits it
with a melee attack while within 5 feet of it takes 10 (3d6) fire
damage.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +11 to hit, reach 10 ft., one
target. \emph{Hit:} 40 (6d10 + 7) piercing damage plus 10 (3d6) fire
damage. If the target is a creature, it is grappled (escape DC 17).
Until this grapple ends, the target is restrained, and the remorhaz
can't bite another target.

\textbf{Swallow.} The remorhaz makes one bite attack against a Medium or
smaller creature it is grappling. If the attack hits, that creature
takes the bite's damage and is swallowed, and the grapple ends. While
swallowed, the creature is blinded and restrained, it has total cover
against attacks and other effects outside the remorhaz, and it takes 21
(6d6) acid damage at the start of each of the remorhaz's turns.

If the remorhaz takes 30 damage or more on a single turn from a creature
inside it, the remorhaz must succeed on a DC 15 Constitution saving
throw at the end of that turn or regurgitate all swallowed creatures,
which fall prone in a space within 10 feet of the remorhaz. If the
remorhaz dies, a swallowed creature is no longer restrained by it and
can escape from the corpse using 15 feet of movement, exiting prone.

\hypertarget{roc}{%
\subsubsection{Roc}\label{roc}}

\emph{Gargantuan monstrosity, unaligned}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 248 (16d20 + 80)

\textbf{Speed} 20 ft., fly 120 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
28 (+9) & 10 (+0) & 20 (+5) & 3 (−4) & 10 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4, Con +9, Wis +4, Cha +3

\textbf{Skills} Perception +4

\textbf{Senses} passive Perception 14

\textbf{Languages} ---

\textbf{Challenge} 11 (7,200 XP)

\textbf{Keen Sight.} The roc has advantage on Wisdom (Perception) checks
that rely on sight.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The roc makes two attacks: one with its beak and
one with its talons.

\textbf{Beak.} \emph{Melee Weapon Attack:} +13 to hit, reach 10 ft., one
target. \emph{Hit:} 27 (4d8 + 9) piercing damage.

\textbf{Talons} \emph{Melee Weapon Attack:} +13 to hit, reach 5 ft., one
target. \emph{Hit:} 23 (4d6 + 9) slashing damage, and the target is
grappled (escape DC 19). Until this grapple ends, the target is
restrained, and the roc can't use its talons on another target.

\hypertarget{roper}{%
\subsubsection{Roper}\label{roper}}

\emph{Large monstrosity, neutral evil}

\textbf{Armor Class} 20 (natural armor)

\textbf{Hit Points} 93 (11d10 + 33)

\textbf{Speed} 10 ft., climb 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 8 (−1) & 17 (+3) & 7 (−2) & 16 (+3) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +6, Stealth +5

\textbf{Senses} darkvision 60 ft., passive Perception 16

\textbf{Languages} ---

\textbf{Challenge} 5 (1,800 XP)

\textbf{False Appearance.} While the roper remains motionless, it is
indistinguishable from a normal cave formation, such as a stalagmite.

\textbf{Grasping Tendrils.} The roper can have up to six tendrils at a
time. Each tendril can be attacked (AC 20; 10 hit points; immunity to
poison and psychic damage).

Destroying a tendril deals no damage to the roper, which can extrude a
replacement tendril on its next turn. A tendril can also be broken if a
creature takes an action and succeeds on a DC 15 Strength check against
it.

\textbf{Spider Climb.} The roper can climb difficult surfaces, including
upside down on ceilings, without needing to make an ability check.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The roper makes four attacks with its tendrils,
uses Reel, and makes one attack with its \textbf{Bite.}

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 22 (4d8 + 4) piercing damage.

\textbf{Tendril.} \emph{Melee Weapon Attack:} +7 to hit, reach 50 ft.,
one creature. \emph{Hit:} The target is grappled (escape DC 15). Until
the grapple ends, the target is restrained and has disadvantage on
Strength checks and Strength \textbf{Saving Throws}, and the roper can't
use the same tendril on another target.

\textbf{Reel.} The roper pulls each creature grappled by it up to 25
feet straight toward it.

\hypertarget{rust-monster}{%
\subsubsection{Rust Monster}\label{rust-monster}}

\emph{Medium monstrosity, unaligned}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 27 (5d8 + 5)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 12 (+1) & 13 (+1) & 2 (−4) & 13 (+1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 11

\textbf{Languages} ---

\textbf{Challenge} ½ (100 XP)

\textbf{Iron Scent.} The rust monster can pinpoint, by scent, the
location of ferrous metal within 30 feet of it.

\textbf{Rust Metal.} Any nonmagical weapon made of metal that hits the
rust monster corrodes. After dealing damage, the weapon takes a
permanent and cumulative −1 penalty to damage rolls. If its penalty
drops to −5, the weapon is destroyed. Nonmagical ammunition made of
metal that hits the rust monster is destroyed after dealing damage.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d8 + 1) piercing damage.

\textbf{Antennae.} The rust monster corrodes a nonmagical ferrous metal
object it can see within 5 feet of it. If the object isn't being worn or
carried, the touch destroys a 1-­‐foot cube of it. If the object is
being worn or carried by a creature, the creature can make a DC 11
Dexterity saving throw to avoid the rust monster's touch.

If the object touched is either metal armor or a metal shield being worn
or carried, its takes a permanent and cumulative −1 penalty to the AC it
offers. Armor reduced to an AC of 10 or a shield that drops to a +0
bonus is destroyed. If the object touched is a held metal weapon, it
rusts as described in the Rust Metal trait.

\end{document}
