% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-n}{%
\section{Monsters (N)}\label{monsters-n}}

\hypertarget{nagas}{%
\subsection{Nagas}\label{nagas}}

\hypertarget{guardian-naga}{%
\subsubsection{Guardian Naga}\label{guardian-naga}}

\emph{Large monstrosity, lawful good}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 127 (15d10 + 45)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 18 (+4) & 16 (+3) & 16 (+3) & 19 (+4) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +8, Con +7, Int +7, Wis +8, Cha +8

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Celestial, Common

\textbf{Challenge} 10 (5,900 XP)

\textbf{Rejuvenation.} If it dies, the naga returns to life in 1d6 days
and regains all its hit points. Only a \emph{wish} spell can prevent
this trait from functioning.

\textbf{Spellcasting.} The naga is an 11th-­‐level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 16, +8 to hit with spell
attacks), and it needs only verbal components to cast its spells. It has
the following cleric spells prepared:

Cantrips (at will): \emph{mending}, \emph{sacred flame},
\emph{thaumaturgy}

1st level (4 slots): \emph{command}, \emph{cure wounds}, \emph{shield of
faith}

2nd level (3 slots): \emph{calm emotions}, \emph{hold person}

3rd level (3 slots): \emph{bestow curse}, \emph{clairvoyance}

4th level (3 slots): \emph{banishment}, \emph{freedom of movement}

5th level (2 slots): \emph{flame strike}, \emph{geas}

6th level (1 slot): \emph{true seeing}

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +8 to hit, reach 10 ft., one
creature. \emph{Hit:} 8 (1d8 + 4) piercing damage, and the target must
make a DC 15 Constitution saving throw, taking 45 (10d8) poison damage
on a failed save, or half as much damage on a successful one.

\textbf{Spit Poison.} \emph{Ranged Weapon Attack:} +8 to hit, range
15/30 ft., one creature. \emph{Hit:} The target must make a DC 15
Constitution saving throw, taking 45 (10d8) poison damage on a failed
save, or half as much damage on a successful one.

\hypertarget{spirit-naga}{%
\subsubsection{Spirit Naga}\label{spirit-naga}}

\emph{Large monstrosity, chaotic evil}

\textbf{Armor Class} 15 (natural armor)

\textbf{Hit Points} 75 (10d10 + 20)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 17 (+3) & 14 (+2) & 16 (+3) & 15 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Con +5, Wis +5, Cha +6

\textbf{Damage Immunities} poison

\textbf{Condition Immunities} charmed, poisoned

\textbf{Senses} darkvision 60 ft., passive Perception 12

\textbf{Languages} Abyssal, Common

\textbf{Challenge} 8 (3,900 XP)

\textbf{Rejuvenation.} If it dies, the naga returns to life in 1d6 days
and regains all its hit points. Only a \emph{wish} spell can prevent
this trait from functioning.

\textbf{Spellcasting.} The naga is a 10th-­‐level spellcaster. Its
spellcasting ability is Intelligence (spell save DC 14, +6 to hit with
spell attacks), and it needs only verbal components to cast its spells.
It has the following wizard spells prepared:

Cantrips (at will): \emph{mage hand}, \emph{minor illusion}, \emph{ray
of frost}

1st level (4 slots): \emph{charm person}, \emph{detect magic},
\emph{sleep}

2nd level (3 slots): \emph{detect thoughts}, \emph{hold person}

3rd level (3 slots): \emph{lightning bolt}, \emph{water breathing}

4th level (3 slots): \emph{blight}, \emph{dimension door}

5th level (2 slots): \emph{dominate person}

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft., one
creature. \emph{Hit:} 7 (1d6 + 4) piercing damage, and the target must
make a DC 13 Constitution saving throw, taking 31 (7d8) poison damage on
a failed save, or half as much damage on a successful one.

\hypertarget{nightmare}{%
\subsubsection{Nightmare}\label{nightmare}}

\emph{Large fiend, neutral evil}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 68 (8d10 + 24)

\textbf{Speed} 60 ft., fly 90 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 10 (+0) & 13 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} fire

\textbf{Senses} passive Perception 11

\textbf{Languages} understands Abyssal, Common, and Infernal but can't
speak

\textbf{Challenge} 3 (700 XP)

\textbf{Confer Fire Resistance.} The nightmare can grant resistance to
fire damage to anyone riding it.

\textbf{Illumination.} The nightmare sheds bright light in a 10-­‐ foot
radius and dim light for an additional 10 feet.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Hooves.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage plus 7 (2d6) fire
damage.

\textbf{Ethereal Stride.} The nightmare and up to three willing
creatures within 5 feet of it magically enter the Ethereal Plane from
the Material Plane, or vice versa.

\end{document}
