% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-a}{%
\section{Monsters (A)}\label{monsters-a}}

\hypertarget{aboleth}{%
\subsubsection{Aboleth}\label{aboleth}}

\emph{Large aberration, lawful evil}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 135 (18d10 + 36)

\textbf{Speed} 10 ft., swim 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
21 (+5) & 9 (−1) & 15 (+2) & 18 (+4) & 15 (+2) & 18 (+4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +6, Int +8, Wis +6

\textbf{Skills} History +12, Perception +10

\textbf{Senses} darkvision 120 ft., passive Perception 20

\textbf{Languages} Deep Speech, telepathy 120 ft.

\textbf{Challenge} 10 (5,900 XP)

\textbf{Amphibious.} The aboleth can breathe air and water.

\textbf{Mucous Cloud.} While underwater, the aboleth is surrounded by
transformative mucus. A creature that touches the aboleth or that hits
it with a melee attack while within 5 feet of it must make a DC 14
Constitution saving throw. On a failure, the creature is diseased for
1d4 hours. The diseased creature can breathe only underwater.

\textbf{Probing Telepathy.} If a creature communicates telepathically
with the aboleth, the aboleth learns the creature's greatest desires if
the aboleth can see the creature.

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Multiattack.} The aboleth makes three tentacle attacks.

\textbf{Tentacle.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft.,
one target. \emph{Hit:} 12 (2d6 + 5) bludgeoning damage. If the target
is a creature, it must succeed on a DC 14 Constitution saving throw or
become diseased. The disease has no effect for 1 minute and can be
removed by any magic that cures disease. After 1 minute, the diseased
creature's skin becomes translucent and slimy, the creature can't regain
hit points unless it is underwater, and the disease can be removed only
by \emph{heal} or another disease-­‐curing spell of 6th level or higher.
When the creature is outside a body of water, it takes 6 (1d12) acid
damage every 10 minutes unless moisture is applied to the skin before 10
minutes have passed.

\textbf{Tail.} \emph{Melee Weapon Attack:} +9 to hit, reach 10 ft. one
target. \emph{Hit:} 15 (3d6 + 5) bludgeoning damage.

\textbf{Enslave (3/Day)}. The aboleth targets one creature it can see
within 30 feet of it. The target must succeed on a DC 14 Wisdom saving
throw or be magically charmed by the aboleth until the aboleth dies or
until it is on a different plane of existence from the target. The
charmed target is under the aboleth's control and can't take actions,
and the aboleth and the target can communicate telepathically with each
other over any distance.

Whenever the charmed target takes damage, the target can repeat the
saving throw. On a success, the effect ends. No more than once every 24
hours, the target can also repeat the saving throw when it is at least 1
mile away from the aboleth.

\hypertarget{legendary-actions}{%
\paragraph{Legendary Actions}\label{legendary-actions}}

The aboleth can take 3 legendary actions, choosing from the options
below. Only one legendary action option can be used at a time and only
at the end of another creature's turn. The aboleth regains spent
legendary actions at the start of its turn.

\textbf{Detect.} The aboleth makes a Wisdom (Perception) check.

\textbf{Tail Swipe.} The aboleth makes one \textbf{Tail Attack.}

\textbf{Psychic Drain (Costs 2 Actions).}. One creature charmed by the
aboleth takes 10 (3d6) psychic damage, and the aboleth regains hit
points equal to the damage the creature takes.

\hypertarget{angels}{%
\subsection{Angels}\label{angels}}

\hypertarget{deva}{%
\subsubsection{Deva}\label{deva}}

\emph{Medium celestial, lawful good}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 136 (16d8 + 64)

\textbf{Speed} 30 ft., fly 90 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 18 (+4) & 18 (+4) & 17 (+3) & 20 (+5) & 20 (+5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Wis +9, Cha +9

\textbf{Skills} Insight +9, Perception +9

\textbf{Damage Resistances} radiant; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Condition Immunities} charmed, exhaustion, frightened

\textbf{Senses} darkvision 120 ft., passive Perception 19

\textbf{Languages} all, telepathy 120 ft.

\textbf{Challenge} 10 (5,900 XP)

\textbf{Angelic Weapons.} The deva's weapon attacks are magical. When
the deva hits with any weapon, the weapon deals an extra 4d8 radiant
damage (included in the attack).

\textbf{Innate Spellcasting} The deva's spellcasting ability is Charisma
(spell save DC 17). The deva can innately cast the following spells,
requiring only verbal components:

At will: \emph{detect evil and good}

1/day each: \emph{commune}, \emph{raise dead}

\textbf{Magic Resistance.} The deva has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The deva makes two melee attacks.

\textbf{Mace.} \emph{Melee Weapon Attack:} +8 to hit, reach 5 ft., one
target. \emph{Hit:} 7 (1d6 + 4) bludgeoning damage plus 18 (4d8) radiant
damage.

\textbf{Healing Touch (3/Day).} The deva touches another creature. The
target magically regains 20 (4d8 + 2) hit points and is freed from any
curse, disease, poison, blindness, or deafness.

\textbf{Change Shape.} The deva magically polymorphs into a humanoid or
beast that has a challenge rating equal to or less than its own, or back
into its true form. It reverts to its true form if it dies. Any
equipment it is wearing or carrying is absorbed or borne by the new form
(the deva's choice).

In a new form, the deva retains its game statistics and ability to
speak, but its AC, movement modes, Strength, Dexterity, and special
senses are replaced by those of the new form, and it gains any
statistics and capabilities (except class features, legendary actions,
and lair actions) that the new form has but that it lacks.

\hypertarget{planetar}{%
\subsubsection{Planetar}\label{planetar}}

\emph{Large celestial, lawful good}

\textbf{Armor Class} 19 (natural armor)

\textbf{Hit Points} 200 (16d10 + 112)

\textbf{Speed} 40 ft., fly 120 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
24 (+7) & 20 (+5) & 24 (+7) & 19 (+4) & 22 (+6) & 25 (+7)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +12, Wis +11, Cha +12

\textbf{Skills} Perception +11

\textbf{Damage Resistances} radiant; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Condition Immunities} charmed, exhaustion, frightened

\textbf{Senses} truesight 120 ft., passive Perception 21

\textbf{Languages} all, telepathy 120 ft.

\textbf{Challenge} 16 (15,000 XP)

\textbf{Angelic Weapons.} The planetar's weapon attacks are magical.
When the planetar hits with any weapon, the weapon deals an extra 5d8
radiant damage (included in the attack).

\textbf{Divine Awareness.} The planetar knows if it hears a lie.

\textbf{Innate Spellcasting} The planetar's spellcasting ability is
Charisma (spell save DC 20). The planetar can innately cast the
following spells, requiring no material components:

At will: \emph{detect evil and good}, \emph{invisibility} (self only)

3/day each: \emph{blade barrier}, \emph{dispel evil and good},
\emph{flamestrike}, \emph{raise dead}

1/day each: \emph{commune}, \emph{control weather}, \emph{insect plague}

\textbf{Magic Resistance.} The planetar has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Multiattack.} The planetar makes two melee attacks.

\textbf{Greatsword.} \emph{Melee Weapon Attack:} +12 to hit, reach 5
ft., one target. \emph{Hit:} 21 (4d6 + 7) slashing damage plus 22 (5d8)
radiant damage.

\textbf{Healing Touch (4/Day).} The planetar touches another creature.
The target magically regains 30 (6d8 + 3) hit points and is freed from
any curse, disease, poison, blindness, or deafness.

\hypertarget{solar}{%
\subsubsection{Solar}\label{solar}}

\emph{Large celestial, lawful good}

\textbf{Armor Class} 21 (natural armor)

\textbf{Hit Points} 243 (18d10 + 144)

\textbf{Speed} 50 ft., fly 150 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
26 (+8) & 22 (+6) & 26 (+8) & 25 (+7) & 25 (+7) & 30
(+10)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Int +14, Wis +14, Cha +17

\textbf{Skills} Perception +14

\textbf{Damage Resistances} radiant; bludgeoning, piercing, and slashing
from nonmagical attacks

\textbf{Damage Immunities} necrotic, poison

\textbf{Condition Immunities} charmed, exhaustion, frightened, poisoned

\textbf{Senses} truesight 120 ft., passive Perception 24

\textbf{Languages} all, telepathy 120 ft.

\textbf{Challenge} 21 (33,000 XP)

\textbf{Angelic Weapons.} The solar's weapon attacks are magical. When
the solar hits with any weapon, the weapon deals an extra 6d8 radiant
damage (included in the attack).

\textbf{Divine Awareness.} The solar knows if it hears a lie.

\textbf{Innate Spellcasting} The solar's spellcasting ability is
Charisma (spell save DC 25). It can innately cast the following spells,
requiring no material components:

At will: \emph{detect evil and good}, \emph{invisibility} (self only)

3/day each: \emph{blade barrier}, \emph{dispel evil and good},
\emph{resurrection}

1/day each: \emph{commune}, \emph{control weather}

\textbf{Magic Resistance.} The solar has advantage on saving throws
against spells and other magical effects.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Multiattack.} The solar makes two greatsword attacks.

\textbf{Greatsword.} \emph{Melee Weapon Attack:} +15 to hit, reach 5
ft., one target. \emph{Hit:} 22 (4d6 + 8) slashing damage plus 27 (6d8)
radiant damage.

\textbf{Slaying Longbow.} Ranged \emph{Weapon Attack:} +13 to hit, range
150/600 ft., one target. \emph{Hit:} 15 (2d8 + 6) piercing damage plus
27 (6d8) radiant damage. If the target is a creature that has 100 hit
points or fewer, it must succeed on a DC 15 Constitution saving throw or
die.

\textbf{Flying Sword.} The solar releases its greatsword to hover
magically in an unoccupied space within 5 feet of it. If the solar can
see the sword, the solar can mentally command it as a bonus action to
fly up to 50 feet and either make one attack against a target or return
to the solar's hands. If the hovering sword is targeted by any effect,
the solar is considered to be holding it. The hovering sword falls if
the solar dies.

\textbf{Healing Touch (4/Day).} The solar touches another creature. The
target magically regains 40 (8d8 + 4) hit points and is freed from any
curse, disease, poison, blindness, or deafness.

\hypertarget{legendary-actions-1}{%
\paragraph{Legendary Actions}\label{legendary-actions-1}}

The solar can take 3 legendary actions, choosing from the options below.
Only one legendary action option can be used at a time and only at the
end of another creature's turn. The solar regains spent legendary
actions at the start of its turn.

\textbf{Teleport.} The solar magically teleports, along with any
equipment it is wearing or carrying, up to 120 feet to an unoccupied
space it can see.

\textbf{Searing Burst (Costs 2 Actions).} The solar emits magical,
divine energy. Each creature of its choice in a 10-­‐foot radius must
make a DC 23 Dexterity saving throw, taking 14 (4d6) fire damage plus 14
(4d6) radiant damage on a failed save, or half as much damage on a
successful one.

\textbf{Blinding Gaze (Costs 3 Actions).} The solar targets one creature
it can see within 30 feet of it. If the target can see it, the target
must succeed on a DC 15 Constitution saving throw or be blinded until
magic such as the \emph{lesser restoration} spell removes the blindness.

\hypertarget{animated-objects}{%
\subsection{Animated Objects}\label{animated-objects}}

\hypertarget{animated-armor}{%
\subsubsection{Animated Armor}\label{animated-armor}}

\emph{Medium construct, unaligned}

\textbf{Armor Class} 18 (natural armor)

\textbf{Hit Points} 33 (6d8 + 6)

\textbf{Speed} 25 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 11 (+0) & 13 (+1) & 1 (−5) & 3 (−4) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison, psychic

\textbf{Condition Immunities} blinded, charmed, deafened, exhaustion,
frightened, paralyzed, petrified, poisoned

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 6

\textbf{Languages} ---

\textbf{Challenge} 1 (200 XP)

\textbf{Antimagic Susceptibility.} The armor is incapacitated while in
the area of an \emph{antimagic field.} If targeted by \emph{dispel
magic}, the armor must succeed on a Constitution saving throw against
the caster's spell save DC or fall unconscious for 1 minute.

\textbf{False Appearance.} While the armor remains motionless, it is
indistinguishable from a normal suit of armor.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Multiattack.} The armor makes two melee attacks.

\textbf{Slam.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
target. \emph{Hit:} 5 (1d6 + 2) bludgeoning damage.

\hypertarget{flying-sword}{%
\subsubsection{Flying Sword}\label{flying-sword}}

\emph{Small construct, unaligned}

\textbf{Armor Class} 17 (natural armor)

\textbf{Hit Points} 17 (5d6)

\textbf{Speed} 0 ft., fly 50 ft. (hover)

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
12 (+1) & 15 (+2) & 11 (+0) & 1 (−5) & 5 (−3) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +4

\textbf{Damage Immunities} poison, psychic

\textbf{Condition Immunities} blinded, charmed, deafened, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 7

\textbf{Languages} ---

\textbf{Challenge} ¼ (50 XP)

\textbf{Antimagic Susceptibility.} The sword is incapacitated while in
the area of an \emph{antimagic field.} If targeted by \emph{dispel
magic}, the sword must succeed on a Constitution saving throw against
the caster's spell save DC or fall unconscious for 1 minute.

\textbf{False Appearance.} While the sword remains motionless and isn't
flying, it is indistinguishable from a normal sword.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Longsword.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d8 + 1) slashing damage.

\hypertarget{rug-of-smothering}{%
\subsubsection{Rug of Smothering}\label{rug-of-smothering}}

\emph{Large construct, unaligned}

\textbf{Armor Class} 12

\textbf{Hit Points} 33 (6d10)

\textbf{Speed} 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 14 (+2) & 10 (+0) & 1 (−5) & 3 (−4) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} poison, psychic

\textbf{Condition Immunities} blinded, charmed, deafened, frightened,
paralyzed, petrified, poisoned

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 6

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Antimagic Susceptibility.} The rug is incapacitated while in the
area of an \emph{antimagic field.} If targeted by \emph{dispel magic},
the rug must succeed on a Constitution saving throw against the caster's
spell save DC or fall unconscious for 1 minute.

\textbf{Damage Transfer.} While it is grappling a creature, the rug
takes only half the damage dealt to it, and the creature grappled by the
rug takes the other half.

\textbf{False Appearance.} While the rug remains motionless, it is
indistinguishable from a normal rug.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Smother.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one Medium or smaller creature. \emph{Hit:} The creature is grappled
(escape DC 13). Until this grapple ends, the target is restrained,
blinded, and at risk of suffocating, and the rug can't smother another
target. In addition, at the start of each of the target's turns, the
target takes 10 (2d6 + 3) bludgeoning damage.

\hypertarget{ankheg}{%
\subsubsection{Ankheg}\label{ankheg}}

\emph{Large monstrosity, unaligned}

\textbf{Armor Class} 14 (natural armor), 11 while prone

\textbf{Hit Points} 39 (6d10 + 6)

\textbf{Speed} 30 ft., burrow 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 11 (+0) & 13 (+1) & 1 (−5) & 13 (+1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., tremorsense 60 ft., passive
Perception 11

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Bite.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft., one
target. \emph{Hit:} 10 (2d6 + 3) slashing damage plus 3 (1d6) acid
damage. If the target is a Large or smaller creature, it is grappled
(escape DC 13). Until this grapple ends, the ankheg can bite only the
grappled creature and has advantage on attack rolls to do so.

\textbf{Acid Spray (Recharge 6).} The Ankheg spits acid in a line that
is 30 feet long and 5 feet wide, provided that it has no creature
grappled. Each creature in that line must make a DC 13 Dexterity saving
throw, taking 10 (3d6) acid damage on a failed save, or half as much
damage on a successful one.

\hypertarget{azer}{%
\subsubsection{Azer}\label{azer}}

\emph{Medium elemental, lawful neutral}

\textbf{Armor Class} 17 (natural armor, shield)

\textbf{Hit Points} 39 (6d8 + 12)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
17 (+3) & 12 (+1) & 15 (+2) & 12 (+1) & 13 (+1) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +4

\textbf{Damage Immunities} fire, poison

\textbf{Condition Immunities} poisoned

\textbf{Senses} passive Perception 11

\textbf{Languages} Ignan

\textbf{Challenge} 2 (450 XP)

\textbf{Heated Body.} A creature that touches the azer or hits it with a
melee attack while within 5 feet of it takes 5 (1d10) fire damage.

\textbf{Heated Weapons.} When the azer hits with a metal melee weapon,
it deals an extra 3 (1d6) fire damage (included in the attack).

\textbf{Illumination.} The azer sheds bright light in a 10-­‐foot radius
and dim light for an additional 10 feet.

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Warhammer.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 7 (1d8 + 3) bludgeoning damage, or 8 (1d10 + 3)
bludgeoning damage if used with two hands to make a melee attack, plus 3
(1d6) fire damage.

\end{document}
