% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monsters-o}{%
\section{Monsters (O)}\label{monsters-o}}

\hypertarget{ogre}{%
\subsubsection{Ogre}\label{ogre}}

\emph{Large giant, chaotic evil}

\textbf{Armor Class} 11 (hide armor)

\textbf{Hit Points} 59 (7d10 + 21)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 8 (−1) & 16 (+3) & 5 (−3) & 7 (−2) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} darkvision 60 ft., passive Perception 8

\textbf{Languages} Common, Giant

\textbf{Challenge} 2 (450 XP)

\hypertarget{actions}{%
\paragraph{Actions}\label{actions}}

\textbf{Greatclub.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one target. \emph{Hit:} 13 (2d8 + 4) bludgeoning damage.

\textbf{Javelin} \emph{Melee or Ranged Weapon Attack:} +6 to hit, reach
5 ft. or range 30/120 ft., one target. \emph{Hit:} 11 (2d6 + 4) piercing
damage.

\hypertarget{oni}{%
\subsubsection{Oni}\label{oni}}

\emph{Large giant, lawful evil}

\textbf{Armor Class} 16 (chain mail)

\textbf{Hit Points} 110 (13d10 + 39)

\textbf{Speed} 30 ft., fly 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
19 (+4) & 11 (+0) & 16 (+3) & 14 (+2) & 12 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +3, Con +6, Wis +4, Cha +5

\textbf{Skills} Arcana +5, Deception +8, Perception +4

\textbf{Senses} darkvision 60 ft., passive Perception 14

\textbf{Languages} Common, Giant

\textbf{Challenge} 7 (2,900 XP)

\textbf{Innate Spellcasting.} The oni's innate spellcasting ability is
Charisma (spell save DC 13). The oni can innately cast the following
spells, requiring no material components:

At will: \emph{darkness}, \emph{invisibility}

1/day each: \emph{charm person}, \emph{cone of cold}, \emph{gaseous
form}, \emph{sleep}

\textbf{Magic Weapons.} The oni's weapon attacks are magical.

\textbf{Regeneration.} The oni regains 10 hit points at the start of its
turn if it has at least 1 hit point.

\hypertarget{actions-1}{%
\paragraph{Actions}\label{actions-1}}

\textbf{Multiattack.} The oni makes two attacks, either with its claws
or its glaive.

\textbf{Claw (Oni Form Only).} \emph{Melee Weapon Attack:} +7 to hit,
reach 5 ft., one target. \emph{Hit:} 8 (1d8 + 4) slashing damage.

\textbf{Glaive.} \emph{Melee Weapon Attack:} +7 to hit, reach 10 ft.,
one target. \emph{Hit:} 15 (2d10 + 4) slashing damage, or 9 (1d10 + 4)
slashing damage in Small or Medium form.

\textbf{Change Shape.} The oni magically polymorphs into a Small or
Medium humanoid, into a Large giant, or back into its true form. Other
than its size, its statistics are the same in each form. The only
equipment that is transformed is its glaive, which shrinks so that it
can be wielded in humanoid form. If the oni dies, it reverts to its true
form, and its glaive reverts to its normal size.

\hypertarget{oozes}{%
\subsection{Oozes}\label{oozes}}

\hypertarget{black-pudding}{%
\subsubsection{Black Pudding}\label{black-pudding}}

\emph{Large ooze, unaligned}

\textbf{Armor Class} 7

\textbf{Hit Points} 85 (10d10 + 30)

\textbf{Speed} 20 ft., climb 20 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 5 (−3) & 16 (+3) & 1 (−5) & 6 (−2) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Immunities} acid, cold, lightning, slashing

\textbf{Condition Immunities} blinded, charmed, deafened, exhaustion,
frightened, prone

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 8

\textbf{Languages} ---

\textbf{Challenge} 4 (1,100 XP)

\textbf{Regeneration.} The pudding can move through a space as narrow as
1 inch wide without squeezing.

\textbf{Corrosive Form.} A creature that touches the pudding or hits it
with a melee attack while within 5 feet of it takes 4 (1d8) acid damage.
Any nonmagical weapon made of metal or wood that hits the pudding
corrodes. After dealing damage, the weapon takes a permanent and
cumulative −1 penalty to damage rolls. If its penalty drops to −5, the
weapon is destroyed. Nonmagical ammunition made of metal or wood that
hits the pudding is destroyed after dealing damage. The pudding can eat
through 2-­‐inch-­‐thick, nonmagical wood or metal in 1 round.

\textbf{Spider Climb.} The pudding can climb difficult surfaces,
including upside down on ceilings, without needing to make an ability
check.

\hypertarget{actions-2}{%
\paragraph{Actions}\label{actions-2}}

\textbf{Pseudopod.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) bludgeoning damage plus 18 (4d8)
acid damage. In addition, nonmagical armor worn by the target is partly
dissolved and takes a permanent and cumulative −1 penalty to the AC it
offers. The armor is destroyed if the penalty reduces its AC to 10.

\hypertarget{reactions}{%
\paragraph{Reactions}\label{reactions}}

\textbf{Split.} When a pudding that is Medium or larger is subjected to
lightning or slashing damage, it splits into two new puddings if it has
at least 10 hit points. Each new pudding has hit points equal to half
the original pudding's, rounded down. New puddings are one size smaller
than the original pudding.

\hypertarget{gelatinous-cube}{%
\subsubsection{Gelatinous Cube}\label{gelatinous-cube}}

\emph{Large ooze, unaligned}

\textbf{Armor Class} 6

\textbf{Hit Points} 84 (8d10 + 40)

\textbf{Speed} 15 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
14 (+2) & 3 (−4) & 20 (+5) & 1 (−5) & 6 (−2) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Condition Immunities} blinded, charmed, deafened, exhaustion,
frightened, prone

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 8

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Ooze Cube.} The cube takes up its entire space. Other creatures
can enter the space, but a creature that does so is subjected to the
cube's Engulf and has disadvantage on the saving throw.

Creatures inside the cube can be seen but have total cover.

A creature within 5 feet of the cube can take an action to pull a
creature or object out of the cube. Doing so requires a successful DC 12
Strength check, and the creature making the attempt takes 10 (3d6) acid
damage.

The cube can hold only one Large creature or up to four Medium or
smaller creatures inside it at a time.

\textbf{Transparent.} Even when the cube is in plain sight, it takes a
successful DC 15 Wisdom (Perception) check to spot a cube that has
neither moved nor attacked. A creature that tries to enter the cube's
space while unaware of the cube is surprised by the cube.

\hypertarget{actions-3}{%
\paragraph{Actions}\label{actions-3}}

\textbf{Pseudopod.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one creature. \emph{Hit:} 10 (3d6) acid damage.

\textbf{Engulf.} The cube moves up to its speed. While doing so, it can
enter Large or smaller creatures' spaces.

Whenever the cube enters a creature's space, the creature must make a DC
12 Dexterity saving throw.

On a successful save, the creature can choose to be pushed 5 feet back
or to the side of the cube. A creature that chooses not to be pushed
suffers the consequences of a failed saving throw.

On a failed save, the cube enters the creature's space, and the creature
takes 10 (3d6) acid damage and is engulfed. The engulfed creature can't
breathe, is restrained, and takes 21 (6d6) acid damage at the start of
each of the cube's turns. When the cube moves, the engulfed creature
moves with it.

An engulfed creature can try to escape by taking an action to make a DC
12 Strength check. On a success, the creature escapes and enters a space
of its choice within 5 feet of the cube.

\hypertarget{gray-ooze}{%
\subsubsection{Gray Ooze}\label{gray-ooze}}

\emph{Medium ooze, unaligned}

\textbf{Armor Class} 8

\textbf{Hit Points} 22 (3d8 + 9)

\textbf{Speed} 10 ft., climb 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
12 (+1) & 6 (−2) & 16 (+3) & 1 (−5) & 6 (−2) & 2 (−4)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Stealth +2

\textbf{Damage Resistances} acid, cold, fire

\textbf{Condition Immunities} blinded, charmed, deafened, exhaustion,
frightened, prone

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 8

\textbf{Languages} ---

\textbf{Challenge} ½ (100 XP)

\textbf{Regeneration.} The ooze can move through a space as narrow as 1
inch wide without squeezing.

\textbf{Corrode Metal.} Any nonmagical weapon made of metal that hits
the ooze corrodes. After dealing damage, the weapon takes a permanent
and cumulative −1 penalty to damage rolls. If its penalty drops to −5,
the weapon is destroyed. Nonmagical ammunition made of metal that hits
the ooze is destroyed after dealing damage.

The ooze can eat through 2-­‐inch-­‐thick, nonmagical metal in 1 round.

\textbf{False Appearance.} While the ooze remains motionless, it is
indistinguishable from an oily pool or wet rock.

\hypertarget{actions-4}{%
\paragraph{Actions}\label{actions-4}}

\textbf{Pseudopod.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft.,
one target. \emph{Hit:} 4 (1d6 + 1) bludgeoning damage plus 7 (2d6) acid
damage, and if the target is wearing nonmagical metal armor, its armor
is partly corroded and takes a permanent and cumulative −1 penalty to
the AC it offers. The armor is destroyed if the penalty reduces its AC
to 10.

\hypertarget{ochre-jelly}{%
\subsubsection{Ochre Jelly}\label{ochre-jelly}}

\emph{Large ooze, unaligned}

\textbf{Armor Class} 8

\textbf{Hit Points} 45 (6d10 + 12)

\textbf{Speed} 10 ft., climb 10 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 6 (−2) & 14 (+2) & 2 (−4) & 6 (−2) & 1 (−5)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Damage Resistances} acid

\textbf{Damage Immunities} lightning, slashing

\textbf{Condition Immunities} blinded, charmed, deafened, exhaustion,
frightened, prone

\textbf{Senses} blindsight 60 ft. (blind beyond this radius), passive
Perception 8

\textbf{Languages} ---

\textbf{Challenge} 2 (450 XP)

\textbf{Regeneration.} The jelly can move through a space as narrow as 1
inch wide without squeezing.

\textbf{Spider Climb.} The jelly can climb difficult surfaces, including
upside down on ceilings, without needing to make an ability check.

\hypertarget{actions-5}{%
\paragraph{Actions}\label{actions-5}}

\textbf{Pseudopod.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 9 (2d6 + 2) bludgeoning damage plus 3 (1d6) acid
damage.

\hypertarget{reactions-1}{%
\paragraph{Reactions}\label{reactions-1}}

\textbf{Split.} When a jelly that is Medium or larger is subjected to
lightning or slashing damage, it splits into two new jellies if it has
at least 10 hit points. Each new jelly has hit points equal to half the
original jelly's, rounded down. New jellies are one size smaller than
the original jelly.

\hypertarget{orc}{%
\subsubsection{Orc}\label{orc}}

\emph{Medium humanoid (orc), chaotic evil}

\textbf{Armor Class} 13 (hide armor)

\textbf{Hit Points} 15 (2d8 + 6)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 12 (+1) & 16 (+3) & 7 (−2) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Intimidation +2

\textbf{Senses} darkvision 60 ft., passive Perception 10

\textbf{Languages} Common, Orc

\textbf{Challenge} ½ (100 XP)

\textbf{Aggressive.} As a bonus action, the orc can move up to its speed
toward a hostile creature that it can see.

\hypertarget{actions-6}{%
\paragraph{Actions}\label{actions-6}}

\textbf{Greataxe.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 9 (1d12 + 3) slashing damage.

\textbf{Javelin} \emph{Melee or Ranged Weapon Attack:} +5 to hit, reach
5 ft. or range 30/120 ft., one target. \emph{Hit:} 6 (1d6 + 3) piercing
damage.

\hypertarget{otyugh}{%
\subsubsection{Otyugh}\label{otyugh}}

\emph{Large aberration, neutral}

\textbf{Armor Class} 14 (natural armor)

\textbf{Hit Points} 114 (12d10 + 48)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 11 (+0) & 19 (+4) & 6 (−2) & 13 (+1) & 6 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +7

\textbf{Senses} darkvision 120 ft., passive Perception 11

\textbf{Languages} Otyugh

\textbf{Challenge} 5 (1,800 XP)

\textbf{Limited Telepathy.} The otyugh can magically transmit simple
messages and images to any creature within 120 feet of it that can
understand a language. This form of telepathy doesn't allow the
receiving creature to telepathically respond.

\hypertarget{actions-7}{%
\paragraph{Actions}\label{actions-7}}

\textbf{Multiattack.} The otyugh makes three attacks: one with its bite
and two with its tentacles

\textbf{Bite.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft., one
target. \emph{Hit:} 12 (2d8 + 3) piercing damage. If the target is a
creature, it must succeed on a DC 15 Constitution saving throw against
disease or become poisoned until the disease is cured. Every 24 hours
that elapse, the target must repeat the saving throw, reducing its hit
point maximum by 5 (1d10) on a failure. The disease is cured on a
success. The target dies if the disease reduces its hit point maximum to
0. This reduction to the target's hit point maximum lasts until the
disease is cured.

\textbf{Tentacle.} \emph{Melee Weapon Attack:} +6 to hit, reach 10 ft.,
one target. \emph{Hit:} 7 (1d8 + 3) bludgeoning damage plus 4 (1d8)
piercing damage. If the target is Medium or smaller, it is grappled
(escape DC 13) and restrained until the grapple ends. The otyugh has two
tentacles, each of which can grapple one target.

\textbf{Tentacle Slam.} The otyugh slams creatures grappled by it into
each other or a solid surface. Each creature must succeed on a DC 14
Constitution saving throw or take 10 (2d6 + 3) bludgeoning damage and be
stunned until the end of the otyugh's next turn. On a successful save,
the target takes half the bludgeoning damage and isn't stunned.

\hypertarget{owlbear}{%
\subsubsection{Owlbear}\label{owlbear}}

\emph{Large monstrosity, unaligned}

\textbf{Armor Class} 13 (natural armor)

\textbf{Hit Points} 59 (7d10 + 21)

\textbf{Speed} 40 ft.

\begin{longtable}[]{@{}llllll@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
20 (+5) & 12 (+1) & 17 (+3) & 3 (−4) & 12 (+1) & 7 (−2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +3

\textbf{Senses} darkvision 60 ft., passive Perception 13

\textbf{Languages} ---

\textbf{Challenge} 3 (700 XP)

\textbf{Keen Sight and Smell.} The owlbear has advantage on Wisdom
(Perception) checks that rely on sight or smell.

\hypertarget{actions-8}{%
\paragraph{Actions}\label{actions-8}}

\textbf{Multiattack.} The owlbear makes two attacks: one with its beak
and one with its claws.

\textbf{Beak.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
creature. \emph{Hit:} 10 (1d10 + 5) piercing damage.

\textbf{Claws.} \emph{Melee Weapon Attack:} +7 to hit, reach 5 ft., one
target. \emph{Hit:} 14 (2d8 + 5) slashing damage.

\end{document}
