% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{appendix-mm-b-nonplayer-characters}{%
\section{Appendix MM-B: Nonplayer
Characters}\label{appendix-mm-b-nonplayer-characters}}

This appendix contains statistics for various humanoid nonplayer
characters (NPCs) that adventurers might encounter during a campaign,
including lowly commoners and mighty archmages. These stat blocks can be
used to represent both human and nonhuman NPCs.

\hypertarget{customizing-npcs}{%
\subsubsection{Customizing NPCs}\label{customizing-npcs}}

There are many easy ways to customize the NPCs in this appendix for your
home campaign.

\textbf{Racial Traits.} You can add racial traits to an NPC. For
example, a halfling druid might have a speed of 25 feet and the Lucky
trait. Adding racial traits to an NPC doesn't alter its challenge
rating. For more on racial traits, see the \emph{Player's Handbook}.

\textbf{Spell Swaps.} One way to customize an NPC spellcaster is to
replace one or more of its spells. You can substitute any spell on the
NPC's spell list with a different spell of the same level from the same
spell list. Swapping spells in this manner doesn't alter an NPC's
challenge rating.

\textbf{Armor and Weapon Swaps.} You can upgrade or downgrade an NPC's
armor, or add or switch weapons. Adjustments to Armor Class and damage
can change an NPC's challenge rating. Magic Items. The more powerful an
NPC, the more likely it has one or more magic items in its possession.
An archmage, for example, might have a magic staff or wand, as well as
one or more potions and scrolls. Giving an NPC a potent damage-dealing
magic item could alter its challenge rating.

\hypertarget{acolyte}{%
\paragraph{Acolyte}\label{acolyte}}

\emph{Medium humanoid (any race), any alignment}

\textbf{Armor Class} 10

\textbf{Hit Points} 9 (2d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 10 (+0) & 10 (+0) & 10 (+0) & 14 (+2) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Medicine +4, Religion +2

\textbf{Senses} passive Perception 12

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ¼ (50 XP)

\textbf{Spellcasting.} The acolyte is a 1st-level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 12, +4 to hit with spell
attacks). The acolyte has following cleric spells prepared:

Cantrips (at will): \emph{light}, \emph{sacred flame},
\emph{thaumaturgy}

1st level (3 slots): \emph{bless}, \emph{cure wounds}, \emph{sanctuary}

\textbf{Actions}

\textbf{Club.} \emph{Melee Weapon Attack:} +2 to hit, reach 5 ft., one
target. \emph{Hit:} 2 (1d4) bludgeoning damage.

\textbf{Acolytes} are junior members of a clergy, usually answerable to
a priest. They perform a variety of functions in a temple and are
granted minor spellcasting power by their deities.

\hypertarget{archmage}{%
\paragraph{Archmage}\label{archmage}}

\emph{Medium humanoid (any race), any alignment}

\textbf{Armor Class} 12 (15 with mage armor)

\textbf{Hit Points} 99 (18d8 + 18)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 14 (+2) & 12 (+1) & 20 (+5) & 15 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Int +9, Wis +6

\textbf{Skills} Arcana +13, History +13

\textbf{Damage Resistance} damage from spells; nonmagical bludgeoning,
piercing, and slashing (from stoneskin)

\textbf{Senses} passive Perception 12

\textbf{Languages} any six languages

\textbf{Challenge} 12 (8,400 XP)

\textbf{Magic Resistance.} The archmage has advantage on saving throws
against spells and other magical effects.

\textbf{Spellcasting.} The archmage is an 18th-level spellcaster. Its
spellcasting ability is Intelligence (spell save DC 17, +9 to hit with
spell attacks). The archmage can cast \emph{disguise self} and
\emph{invisibility} at will and has the following wizard spells
prepared:

Cantrips (at will): \emph{fire bolt}, \emph{light}, \emph{mage hand},
\emph{prestidigitation}, \emph{shocking grasp}

1st level (4 slots): \emph{detect magic}, \emph{identify}, \emph{mage
armor},* \emph{magic missile}

2nd level (3 slots): \emph{detect thoughts}, \emph{mirror image},
\emph{misty step}

3rd level (3 slots): \emph{counterspell}, \emph{fly}, \emph{lightning
bolt}

4th level (3 slots): \emph{banishment}, \emph{fire shield},
\emph{stoneskin}*

5th level (3 slots): \emph{cone of cold}, \emph{scrying}, \emph{wall of
force}

6th level (1 slot): \emph{globe of invulnerability}

7th level (1 slot): \emph{teleport}

8th level (1 slot): \emph{mind blank}*

9th level (1 slot): \emph{time stop}

*\emph{The archmage casts these spells on itself before combat.}

\textbf{Actions}

\textbf{Dagger.} \emph{Melee or Ranged Weapon Attack:} +6 to hit, reach
5 ft. or range 20/60 ft., one target. \emph{Hit:} 4 (1d4 + 2) piercing
damage.

\textbf{Archmages} are powerful (and usually quite old) spellcasters
dedicated to the study of the arcane arts. Benevolent ones counsel kings
and queens, while evil ones rule as tyrants and pursue lichdom. Those
who are neither good nor evil sequester themselves in remote towers to
practice their magic without interruption.

An archmage typically has one or more apprentice mages, and an
archmage's abode has numerous magical wards and guardians to discourage
interlopers.

\hypertarget{assassin}{%
\paragraph{Assassin}\label{assassin}}

\emph{Medium humanoid (any race), any non-good alignment}

\textbf{Armor Class} 15 (studded leather)

\textbf{Hit Points} 78 (12d8 + 24)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 16 (+3) & 14 (+2) & 13 (+1) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Dex +6, Int +4

\textbf{Skills} Acrobatics +6, Deception +3, Perception +3, Stealth +9

\textbf{Damage Resistances} poison

\textbf{Senses} passive Perception 13

\textbf{Languages} Thieves' cant plus any two languages

\textbf{Challenge} 8 (3,900 XP)

\textbf{Assassinate.} During its first turn, the assassin has advantage
on attack rolls against any creature that hasn't taken a turn. Any hit
the assassin scores against a surprised creature is a critical hit.

\textbf{Evasion.} If the assassin is subjected to an effect that allows
it to make a Dexterity saving throw to take only half damage, the
assassin instead takes no damage if it succeeds on the saving throw, and
only half damage if it fails.

\textbf{Sneak Attack.} Once per turn, the assassin deals an extra 14
(4d6) damage when it hits a target with a weapon attack and has
advantage on the attack roll, or when the target is within 5 feet of an
ally of the assassin that isn't incapacitated and the assassin doesn't
have disadvantage on the attack roll.

\textbf{Actions}

\textbf{Multiattack.} The assassin makes two shortsword attacks.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +6 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) piercing damage, and the target must
make a DC 15 Constitution saving throw, taking 24 (7d6) poison damage on
a failed save, or half as much damage on a successful one.

\textbf{Light Crossbow.} \emph{Ranged Weapon Attack:} +6 to hit, range
80/320 ft., one target. \emph{Hit:} 7 (1d8 + 3) piercing damage, and the
target must make a DC 15 Constitution saving throw, taking 24 (7d6)
poison damage on a failed save, or half as much damage on a successful
one.

Trained in the use of poison, \textbf{assassins} are remorseless killers
who work for nobles, guildmasters, sovereigns, and anyone else who can
afford them.

\hypertarget{bandit}{%
\paragraph{Bandit}\label{bandit}}

\emph{Medium humanoid (any race), any non-lawful alignment}

\textbf{Armor Class} 12 (leather armor)

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 12 (+1) & 12 (+1) & 10 (+0) & 10 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ⅛ (25 XP)

\textbf{Actions}

\textbf{Scimitar.} \emph{Melee Weapon Attack:} +3 to hit, reach 5 ft.,
one target. \emph{Hit:} 4 (1d6 + 1) slashing damage.

\textbf{Light Crossbow.} \emph{Ranged Weapon Attack:} +3 to hit, range
80 ft./320 ft., one target. \emph{Hit:} 5 (1d8 + 1) piercing damage.

\textbf{Bandits} rove in gangs and are sometimes led by thugs, veterans,
or spellcasters. Not all bandits are evil. Oppression, drought, disease,
or famine can often drive otherwise honest folk to a life of banditry.

\textbf{Pirates} are bandits of the high seas. They might be freebooters
interested only in treasure and murder, or they might be privateers
sanctioned by the crown to attack and plunder an enemy nation's vessels.

\hypertarget{bandit-captain}{%
\paragraph{Bandit Captain}\label{bandit-captain}}

\emph{Medium humanoid (any race), any non-lawful alignment}

\textbf{Armor Class} 15 (studded leather)

\textbf{Hit Points} 65 (10d8 + 20)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 16 (+3) & 14 (+2) & 14 (+2) & 11 (+0) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +4, Dex +5, Wis +2

\textbf{Skills} Athletics +4, Deception +4

\textbf{Senses} passive Perception 10

\textbf{Languages} any two languages

\textbf{Challenge} 2 (450 XP)

\textbf{Actions}

\textbf{Multiattack.} The captain makes three melee attacks: two with
its scimitar and one with its dagger. Or the captain makes two ranged
attacks with its daggers.

\textbf{Scimitar.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) slashing damage.

\textbf{Dagger.} \emph{Melee or Ranged Weapon Attack:} +5 to hit, reach
5 ft. or range 20/60 ft., one target. \emph{Hit:} 5 (1d4 + 3) piercing
damage.

\textbf{Reactions}

\textbf{Parry.} The captain adds 2 to its AC against one melee attack
that would hit it. To do so, the captain must see the attacker and be
wielding a melee weapon.

It takes a strong personality, ruthless cunning, and a silver tongue to
keep a gang of bandits in line. The \textbf{bandit captain} has these
qualities in spades.

In addition to managing a crew of selfish malcontents, the
\textbf{pirate captain} is a variation of the bandit captain, with a
ship to protect and command. To keep the crew in line, the captain must
mete out rewards and punishment on a regular basis.

More than treasure, a bandit captain or pirate captain craves infamy. A
prisoner who appeals to the captain's vanity or ego is more likely to be
treated fairly than a prisoner who does not or claims not to know
anything of the captain's colorful reputation.

\hypertarget{berserker}{%
\paragraph{Berserker}\label{berserker}}

\emph{Medium humanoid (any race), any chaotic alignment}

\textbf{Armor Class} 13 (hide armor)

\textbf{Hit Points} 67 (9d8 + 27)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 12 (+1) & 17 (+3) & 9 (−1) & 11 (+0) & 9 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common) \textbf{Challenge}
2 (450 XP)

\textbf{Reckless.} At the start of its turn, the berserker can gain
advantage on all melee weapon attack rolls during that turn, but attack
rolls against it have advantage until the start of its next turn.

\textbf{Actions}

\textbf{Greataxe.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 9 (1d12 + 3) slashing damage.

Hailing from uncivilized lands, unpredictable \textbf{berserkers} come
together in war parties and seek conflict wherever they can find it.

\hypertarget{commonermedium-humanoid-any-race-any-alignmentarmor-class-10}{%
\paragraph{\texorpdfstring{Commoner\emph{Medium humanoid (any race), any
alignment}\textbf{Armor Class}
10}{CommonerMedium humanoid (any race), any alignmentArmor Class 10}}\label{commonermedium-humanoid-any-race-any-alignmentarmor-class-10}}

\textbf{Hit Points} 4 (1d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 10 (+0) & 10 (+0) & 10 (+0) & 10 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} 0 (10 XP)\textbf{Actions} \textbf{Club.} \emph{Melee
Weapon Attack:} +2 to hit, reach 5 ft., one target. \emph{Hit:} 2 (1d4)
bludgeoning damage.\textbf{Commoners} include peasants, serfs, slaves,
servants, pilgrims, merchants, artisans, and hermits.\#\#\#\#
Cultist\emph{Medium humanoid (any race), any non-good alignment}
\textbf{Armor Class} 12 (leather armor)

\textbf{Hit Points} 9 (2d8) \textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 12 (+1) & 10 (+0) & 10 (+0) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +2, Religion +2

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ⅛ (25 XP)

\textbf{Dark Devotion.} The cultist has advantage on saving throws
against being charmed or frightened. \textbf{Actions} \textbf{Scimitar.}
\emph{Melee Weapon Attack:} +3 to hit, reach 5 ft., one creature.
\emph{Hit:} 4 (1d6 + 1) slashing damage.\textbf{Cultists} swear
allegiance to dark powers such as elemental princes, demon lords, or
archdevils. Most conceal their loyalties to avoid being ostracized,
imprisoned, or executed for their beliefs. Unlike evil acolytes,
cultists often show signs of insanity in their beliefs and practices.

\hypertarget{cult-fanaticmedium-humanoid-any-race-any-non-good-alignmentarmor-class-13-leather-armor}{%
\paragraph{\texorpdfstring{Cult Fanatic\emph{Medium humanoid (any race),
any non-good alignment}\textbf{Armor Class} 13 (leather
armor)}{Cult FanaticMedium humanoid (any race), any non-good alignmentArmor Class 13 (leather armor)}}\label{cult-fanaticmedium-humanoid-any-race-any-non-good-alignmentarmor-class-13-leather-armor}}

\textbf{Hit Points} 33 (6d8 + 6)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 14 (+2) & 12 (+1) & 10 (+0) & 13 (+1) & 14 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +4, Persuasion +4, Religion +2

\textbf{Senses} passive Perception 11

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} 2 (450 XP)\textbf{Dark Devotion.} The fanatic has
advantage on saving throws against being charmed or frightened.
\textbf{Spellcasting.} The fanatic is a 4th-level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 11, +3 to hit with spell
attacks). The fanatic has the following cleric spells prepared: Cantrips
(at will): \emph{light}, \emph{sacred flame}, \emph{thaumaturgy}

1st level (4 slots): \emph{command}, \emph{inflict wounds}, \emph{shield
of faith}

2nd level (3 slots): \emph{hold person}, \emph{spiritual weapon}

\textbf{Actions} \textbf{Multiattack.} The fanatic makes two melee
attacks. \textbf{Dagger.} \emph{Melee or Ranged Weapon Attack:} +4 to
hit, reach 5 ft. or range 20/60 ft., one creature. \emph{Hit:} 4 (1d4 +
2) piercing damage.

\textbf{Fanatics} are often part of a cult's leadership, using their
charisma and dogma to influence and prey on those of weak will. Most are
interested in personal power above all else.

\hypertarget{druidmedium-humanoid-any-race-any-alignmentarmor-class-11-16-with-barkskin}{%
\paragraph{\texorpdfstring{Druid\emph{Medium humanoid (any race), any
alignment}\textbf{Armor Class} 11 (16 with
barkskin)}{DruidMedium humanoid (any race), any alignmentArmor Class 11 (16 with barkskin)}}\label{druidmedium-humanoid-any-race-any-alignmentarmor-class-11-16-with-barkskin}}

\textbf{Hit Points} 27 (5d8 + 5) \textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 12 (+1) & 13 (+1) & 12 (+1) & 15 (+2) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Medicine +4, Nature +3, Perception +4 \textbf{Senses}
passive Perception 14

\textbf{Languages} Druidic plus any two languages

\textbf{Challenge} 2 (450 XP)

\textbf{Spellcasting.} The druid is a 4th-level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 12, +4 to hit with spell
attacks). It has the following druid spells prepared: Cantrips (at
will): \emph{druidcraft}, \emph{produce flame}, \emph{shillelagh}

1st level (4 slots): \emph{entangle}, \emph{longstrider}, \emph{speak
with animals}, \emph{thunderwave}

2nd level (3 slots): \emph{animal messenger}, \emph{barkskin}

\textbf{Actions}

\textbf{Quarterstaff.} \emph{Melee Weapon Attack:} +2 to hit (+4 to hit
with shillelagh), reach 5 ft., one target. \emph{Hit:} 3 (1d6)
bludgeoning damage, 4 (1d8) bludgeoning damage if wielded with two
hands, or 6 (1d8 + 2) bludgeoning damage with shillelagh.\textbf{Druids}
dwell in forests and other secluded wilderness locations, where they
protect the natural world from monsters and the encroachment of
civilization. Some are tribal shamans who heal the sick, pray to animal
spirits, and provide spiritual guidance.

\hypertarget{gladiatormedium-humanoid-any-race-any-alignmentarmor-class-16-studded-leather-shield}{%
\paragraph{\texorpdfstring{Gladiator\emph{Medium humanoid (any race),
any alignment}\textbf{Armor Class} 16 (studded leather,
shield)}{GladiatorMedium humanoid (any race), any alignmentArmor Class 16 (studded leather, shield)}}\label{gladiatormedium-humanoid-any-race-any-alignmentarmor-class-16-studded-leather-shield}}

\textbf{Hit Points} 112 (15d8 + 45)\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
18 (+4) & 15 (+2) & 16 (+3) & 10 (+0) & 12 (+1) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Str +7, Dex +5, Con +6

\textbf{Skills} Athletics +10, Intimidation +5

\textbf{Senses} passive Perception 11

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} 5 (1,800 XP)

\textbf{Brave.} The gladiator has advantage on saving throws against
being frightened.\textbf{Brute.} A melee weapon deals one extra die of
its damage when the gladiator hits with it (included in the attack).

\textbf{Actions}

\textbf{Multiattack.} The gladiator makes three melee attacks or two
ranged attacks. \textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +7
to hit, reach 5 ft. and range 20/60 ft., one target. \emph{Hit:} 11 (2d6
+ 4) piercing damage, or 13 (2d8 + 4) piercing damage if used with two
hands to make a melee attack. \textbf{Shield Bash.} \emph{Melee Weapon
Attack:} +7 to hit, reach 5 ft., one creature. \emph{Hit:} 9 (2d4 + 4)
bludgeoning damage. If the target is a Medium or smaller creature, it
must succeed on a DC 15 Strength saving throw or be knocked prone.

\textbf{Reactions}

\textbf{Parry.} The gladiator adds 3 to its AC against one melee attack
that would hit it. To do so, the gladiator must see the attacker and be
wielding a melee weapon.

\textbf{Gladiators} battle for the entertainment of raucous crowds. Some
gladiators are brutal pit fighters who treat each match as a
life\textbackslash or\textbackslash death struggle, while others are
professional duelists who command huge fees but rarely fight to the
death.

\hypertarget{guard}{%
\paragraph{Guard}\label{guard}}

\emph{Medium humanoid (any race), any alignment} \textbf{Armor Class} 16
(chain shirt, shield)

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 12 (+1) & 12 (+1) & 10 (+0) & 11 (+0) & 10 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Perception +2

\textbf{Senses} passive Perception 12

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ⅛ (25 XP)\textbf{Actions} \textbf{Spear.} \emph{Melee
or Ranged Weapon Attack:} +3 to hit, reach 5 ft. or range 20/60 ft., one
target. \emph{Hit:} 4 (1d6 + 1) piercing damage, or 5 (1d8 + 1) piercing
damage if used with two hands to make a melee attack.

\textbf{Guards} include members of a city watch, sentries in a citadel
or fortified town, and the bodyguards of merchants and nobles.

\hypertarget{knightmedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Knight\emph{Medium humanoid (any race), any
alignment}}{KnightMedium humanoid (any race), any alignment}}\label{knightmedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 18 (plate)

\textbf{Hit Points} 52 (8d8 + 16)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 11 (+0) & 14 (+2) & 11 (+0) & 11 (+0) & 15 (+2)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Con +4, Wis +2

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} 3 (700 XP)

\textbf{Brave.} The knight has advantage on saving throws against being
frightened.

\textbf{Actions}

\textbf{Multiattack.} The knight makes two melee attacks.

\textbf{Greatsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 10 (2d6 + 3) slashing damage. \textbf{Heavy
Crossbow.} \emph{Ranged Weapon Attack:} +2 to hit, range 100/400 ft.,
one target. \emph{Hit:} 5 (1d10) piercing damage. \textbf{Leadership
(Recharges after a Short or Long Rest).} For 1 minute, the knight can
utter a special command or warning whenever a nonhostile creature that
it can see within 30 feet of it makes an attack roll or a saving throw.
The creature can add a d4 to its roll provided it can hear and
understand the knight. A creature can benefit from only one Leadership
die at a time. This effect ends if the knight is incapacitated.

\textbf{Reactions}

\textbf{Parry.} The knight adds 2 to its AC against one melee attack
that would hit it. To do so, the knight must see the attacker and be
wielding a melee weapon.\textbf{Knights} are warriors who pledge service
to rulers, religious orders, and noble causes. A knight's alignment
determines the extent to which a pledge is honored. Whether undertaking
a quest or patrolling a realm, a knight often travels with an entourage
that includes squires and hirelings who are commoners.

\hypertarget{mage}{%
\paragraph{Mage}\label{mage}}

\emph{Medium humanoid (any race), any alignment} \textbf{Armor Class} 12
(15 with mage armor)

\textbf{Hit Points} 40 (9d8)\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
9 (−1) & 14 (+2) & 11 (+0) & 17 (+3) & 12 (+1) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Saving Throws} Int +6, Wis +4

\textbf{Skills} Arcana +6, History +6

\textbf{Senses} passive Perception 11

\textbf{Languages} any four languages

\textbf{Challenge} 6 (2,300 XP)

Spellcasting. The mage is a 9th-level spellcaster. Its spellcasting
ability is Intelligence (spell save DC 14, +6 to hit with spell
attacks). The mage has the following wizard spells prepared: Cantrips
(at will): \emph{fire bolt}, \emph{light}, \emph{mage hand},
\emph{prestidigitation} 1st level (4 slots): \emph{detect magic},
\emph{mage armor}, \emph{magic missile}, \emph{shield} 2nd level (3
slots): \emph{misty step}, \emph{suggestion}

3rd level (3 slots): \emph{counterspell}, \emph{fireball}, \emph{fly}

4th level (3 slots): \emph{greater invisibility}, \emph{ice storm}

5th level (1 slot): \emph{cone of cold}

\textbf{Actions}

\textbf{Dagger.} \emph{Melee or Ranged Weapon Attack:} +5 to hit, reach
5 ft. or range 20/60 ft., one target. \emph{Hit:} 4 (1d4 + 2) piercing
damage.\textbf{Mages} spend their lives in the study and practice of
magic. Good\textbackslash aligned mages offer counsel to nobles and
others in power, while evil mages dwell in isolated sites to perform
unspeakable experiments without interference.

\hypertarget{noblemedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Noble\emph{Medium humanoid (any race), any
alignment}}{NobleMedium humanoid (any race), any alignment}}\label{noblemedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 15 (breastplate)

\textbf{Hit Points} 9 (2d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 12 (+1) & 11 (+0) & 12 (+1) & 14 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +5, Insight +4, Persuasion +5

\textbf{Senses} passive Perception 12

\textbf{Languages} any two languages

\textbf{Challenge} ⅛ (25 XP)

\textbf{Actions} \textbf{Rapier.} \emph{Melee Weapon Attack:} +3 to hit,
reach 5 ft., one target. \emph{Hit:} 5 (1d8 + 1) piercing damage.
\textbf{Reactions} \textbf{Parry.} The noble adds 2 to its AC against
one melee attack that would hit it. To do so, the noble must see the
attacker and be wielding a melee weapon.\textbf{Nobles} wield great
authority and influence as members of the upper class, possessing wealth
and connections that can make them as powerful as monarchs and generals.
A noble often travels in the company of guards, as well as servants who
are commoners.The noble's statistics can also be used to represent
\textbf{courtiers} who aren't of noble birth.

\hypertarget{priestmedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Priest\emph{Medium humanoid (any race), any
alignment}}{PriestMedium humanoid (any race), any alignment}}\label{priestmedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 13 (chain shirt)

\textbf{Hit Points} 27 (5d8 + 5)

\textbf{Speed} 25 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 10 (+0) & 12 (+1) & 13 (+1) & 16 (+3) & 13 (+1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Medicine +7, Persuasion +3, Religion +4

\textbf{Senses} passive Perception 13

\textbf{Languages} any two languages

\textbf{Challenge} 2 (450 XP)

\textbf{Divine Eminence.} As a bonus action, the priest can expend a
spell slot to cause its melee weapon attacks to magically deal an extra
10 (3d6) radiant damage to a target on a hit. This benefit lasts until
the end of the turn. If the priest expends a spell slot of 2nd level or
higher, the extra damage increases by 1d6 for each level above
1st.\textbf{Spellcasting.} The priest is a 5th-level spellcaster. Its
spellcasting ability is Wisdom (spell save DC 13, +5 to hit with spell
attacks). The priest has the following cleric spells prepared: Cantrips
(at will): \emph{light}, \emph{sacred flame}, \emph{thaumaturgy}

1st level (4 slots): \emph{cure wounds}, \emph{guiding bolt},
\emph{sanctuary}

2nd level (3 slots): \emph{lesser restoration}, \emph{spiritual weapon}

3rd level (2 slots): \emph{dispel magic}, \emph{spirit guardians}
\textbf{Actions} \textbf{Mace.} \emph{Melee Weapon Attack:} +2 to hit,
reach 5 ft., one target. \emph{Hit:} 3 (1d6) bludgeoning
damage.\textbf{Priests} bring the teachings of their gods to the common
folk. They are the spiritual leaders of temples and shrines and often
hold positions of influence in their communities. Evil priests might
work openly under a tyrant, or they might be the leaders of religious
sects hidden in the shadows of good society, overseeing depraved rites.A
priest typically has one or more acolytes to help with religious
ceremonies and other sacred duties.

\hypertarget{scoutmedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Scout\emph{Medium humanoid (any race), any
alignment}}{ScoutMedium humanoid (any race), any alignment}}\label{scoutmedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 13 (leather armor)

\textbf{Hit Points} 16 (3d8 + 3)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
11 (+0) & 14 (+2) & 12 (+1) & 11 (+0) & 13 (+1) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Nature +4, Perception +5, Stealth +6, Survival +5

\textbf{Senses} passive Perception 15

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ½ (100 XP)

\textbf{Keen Hearing and Sight.} The scout has advantage on Wisdom
(Perception) checks that rely on hearing or sight.

\textbf{Actions} \textbf{Multiattack.} The scout makes two melee attacks
or two ranged attacks. \textbf{Shortsword.} \emph{Melee Weapon Attack:}
+4 to hit, reach 5 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing
damage. \textbf{Longbow.} Ranged Weapon Attack: +4 to hit, ranged
150/600 ft., one target. \emph{Hit:} 6 (1d8 + 2) piercing damage.
\textbf{Scouts} are skilled hunters and trackers who offer their
services for a fee. Most hunt wild game, but a few work as bounty
hunters, serve as guides, or provide military reconnaissance.

\hypertarget{spymedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Spy\emph{Medium humanoid (any race), any
alignment}}{SpyMedium humanoid (any race), any alignment}}\label{spymedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 12

\textbf{Hit Points} 27 (6d8)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
10 (+0) & 15 (+2) & 10 (+0) & 12 (+1) & 14 (+2) & 16 (+3)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Deception +5, Insight +4, Investigation +5, Perception
+6, Persuasion +5, Sleight of Hand +4, Stealth +4 \textbf{Senses}
passive Perception 16

\textbf{Languages} any two languages

\textbf{Challenge} 1 (200 XP)

\textbf{Cunning Action.} On each of its turns, the spy can use a bonus
action to take the Dash, Disengage, or Hide action. \textbf{Sneak Attack
(1/Turn).} The spy deals an extra 7 (2d6) damage when it hits a target
with a weapon attack and has advantage on the attack roll, or when the
target is within 5 feet of an ally of the spy that isn't incapacitated
and the spy doesn't have disadvantage on the attack roll.

\textbf{Actions} \textbf{Multiattack.} The spy makes two melee attacks.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft.,
one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.

\textbf{Hand Crossbow.} \emph{Ranged Weapon Attack:} +4 to hit, range
30/120 ft., one target. \emph{Hit:} 5 (1d6 + 2) piercing damage.Rulers,
nobles, merchants, guildmasters, and other wealthy individuals use
\textbf{spies} to gain the upper hand in a world of cutthroat politics.
A spy is trained to secretly gather information. Loyal spies would
rather die than divulge information that could compromise them or their
employers.

\hypertarget{thugmedium-humanoid-any-race-any-nontgood-alignment}{%
\paragraph{\texorpdfstring{Thug\emph{Medium humanoid (any race), any
nonTgood
alignment}}{ThugMedium humanoid (any race), any nonTgood alignment}}\label{thugmedium-humanoid-any-race-any-nontgood-alignment}}

\textbf{Armor Class} 11 (leather armor)

\textbf{Hit Points} 32 (5d8 + 10)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
15 (+2) & 11 (+0) & 14 (+2) & 10 (+0) & 10 (+0) & 11 (+0)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Skills} Intimidation +2 \textbf{Senses} passive Perception 10

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} ½ (100 XP)

\textbf{Pack Tactics.} The thug has advantage on an attack roll against
a creature if at least one of the thug's allies is within 5 feet of the
creature and the ally isn't incapacitated.

\textbf{Actions} \textbf{Multiattack.} The thug makes two melee attacks.

\textbf{Mace.} \emph{Melee Weapon Attack:} +4 to hit, reach 5 ft., one
creature. \emph{Hit:} 5 (1d6 + 2) bludgeoning damage.

\textbf{Heavy Crossbow.} \emph{Ranged Weapon Attack:} +2 to hit, range
100/400 ft., one target. \emph{Hit:} 5 (1d10) piercing
damage.\textbf{Thugs} are ruthless enforcers skilled at intimidation and
violence. They work for money and have few scruples.\#\#\#\# Tribal
Warrior\emph{Medium humanoid (any race), any alignment}\textbf{Armor
Class} 12 (hide armor)

\textbf{Hit Points} 11 (2d8 + 2)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
13 (+1) & 11 (+0) & 12 (+1) & 8 (−1) & 11 (+0) & 8 (−1)\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 10

\textbf{Languages} any one language

\textbf{Challenge} ⅛ (25 XP)

\textbf{Pack Tactics.} The warrior has advantage on an attack roll
against a creature if at least one of the warrior's allies is within 5
feet of the creature and the ally isn't incapacitated.\textbf{Actions}

\textbf{Spear.} \emph{Melee or Ranged Weapon Attack:} +3 to hit, reach 5
ft. or range 20/60 ft., one target. \emph{Hit:} 4 (1d6 + 1) piercing
damage, or 5 (1d8 + 1) piercing damage if used with two hands to make a
melee attack.

\textbf{Tribal warriors} live beyond civilization, most often subsisting
on fishing and hunting. Each tribe acts in accordance with the wishes of
its chief, who is the greatest or oldest warrior of the tribe or a tribe
member blessed by the gods.

\hypertarget{veteranmedium-humanoid-any-race-any-alignment}{%
\paragraph{\texorpdfstring{Veteran\emph{Medium humanoid (any race), any
alignment}}{VeteranMedium humanoid (any race), any alignment}}\label{veteranmedium-humanoid-any-race-any-alignment}}

\textbf{Armor Class} 17 (splint)

\textbf{Hit Points} 58 (9d8 + 18)

\textbf{Speed} 30 ft.

\begin{longtable}[]{@{}cccccc@{}}
\toprule
STR & DEX & CON & INT & WIS & CHA\tabularnewline
\midrule
\endhead
16 (+3) & 13 (+1) & 14 (+2) & 10 (+0) & 11 (+0) & 10 (+0)\tabularnewline
\textbf{Skills} Athletics +5, Perception +2 & & & & &\tabularnewline
\bottomrule
\end{longtable}

\textbf{Senses} passive Perception 12

\textbf{Languages} any one language (usually Common)

\textbf{Challenge} 3 (700 XP)

\textbf{Actions} \textbf{Multiattack.} The veteran makes two longsword
attacks. If it has a shortsword drawn, it can also make a shortsword
attack. \textbf{Longsword.} \emph{Melee Weapon Attack:} +5 to hit, reach
5 ft., one target. \emph{Hit:} 7 (1d8 + 3) slashing damage, or 8 (1d10 +
3) slashing damage if used with two hands.

\textbf{Shortsword.} \emph{Melee Weapon Attack:} +5 to hit, reach 5 ft.,
one target. \emph{Hit:} 6 (1d6 + 3) piercing damage.

\textbf{Heavy Crossbow.} \emph{Ranged Weapon Attack:} +3 to hit, range
100/400 ft., one target. \emph{Hit:} 6 (1d10 + 1) piercing damage.

\textbf{Veterans} are professional fighters that take up arms for pay or
to protect something they believe in or value. Their ranks include
soldiers retired from long service and warriors who never served anyone
but themselves.

\end{document}
