% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{barbarian}{%
\section{Barbarian}\label{barbarian}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a barbarian, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d12 per barbarian level

\textbf{Hit Points at 1st Level:} 12 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d12 (or 7) + your Constitution
modifier per barbarian level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor, medium armor, shields Weapons: Simple
weapons, martial weapons Tools: None

\textbf{Saving Throws:} Strength, Constitution

\textbf{Skills:} Choose two from Animal Handling, Athletics,
Intimidation, Nature, Perception, and Survival

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a greataxe or (\emph{b}) any martial melee weapon
\item
  (\emph{a}) two handaxes or (\emph{b}) any simple weapon
\item
  An explorer's pack and four javelins
\end{itemize}

\hypertarget{the-barbarian}{%
\paragraph{The Barbarian}\label{the-barbarian}}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Level & Proficiency Bonus & Features & Rages & Rage
Damage\tabularnewline
\midrule
\endhead
1st & +2 & Rage, Unarmored Defense & 2 & +2\tabularnewline
2nd & +2 & Reckless Attack, Danger Sense & 2 & +2\tabularnewline
3rd & +2 & Primal Path & 3 & +2\tabularnewline
4th & +2 & Ability Score Improvement & 3 & +2\tabularnewline
5th & +3 & Extra Attack, Fast Movement & 3 & +2\tabularnewline
6th & +3 & Path feature & 4 & +2\tabularnewline
7th & +3 & Feral Instinct & 4 & +2\tabularnewline
8th & +3 & Ability Score Improvement & 4 & +2\tabularnewline
9th & +4 & Brutal Critical (1die) & 4 & +3\tabularnewline
10th & +4 & Path feature & 4 & +3\tabularnewline
11th & +4 & Relentless Rage & 4 & +3\tabularnewline
12th & +4 & Ability Score Improvement & 5 & +3\tabularnewline
13th & +5 & Brutal Critical (2 dice) & 5 & +3\tabularnewline
14th & +5 & Path Feature & 5 & +3\tabularnewline
15th & +5 & Persistant Rage & 5 & +3\tabularnewline
16th & +5 & Ability Score Improvement & 5 & +4\tabularnewline
17th & +6 & Brutal Critical (3 dice) & 6 & +4\tabularnewline
18th & +6 & Indomitable Might & 6 & +4\tabularnewline
19th & +6 & Ability Score Improvement & 6 & +4\tabularnewline
20th & +6 & Primal Champion & Unlimited & +4\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{rage}{%
\subsubsection{Rage}\label{rage}}

In battle, you fight with primal ferocity. On your turn, you can enter a
rage as a bonus action.

While raging, you gain the following benefits if you aren't wearing
heavy armor:

\begin{itemize}
\tightlist
\item
  You have advantage on Strength checks and Strength saving throws.
\item
  When you make a melee weapon attack using Strength, you gain a bonus
  to the damage roll that increases as you gain levels as a barbarian,
  as shown in the Rage Damage column of the Barbarian table.
\item
  You have resistance to bludgeoning, piercing, and slashing damage.
\end{itemize}

If you are able to cast spells, you can't cast them or concentrate on
them while raging. Your rage lasts for 1 minute. It ends early if you
are knocked unconscious or if your turn ends and you haven't attacked a
hostile creature since your last turn or taken damage since then. You
can also end your rage on your turn as a bonus action.

Once you have raged the number of times shown for your barbarian level
in the Rages column of the Barbarian table, you must finish a long rest
before you can rage again.

\hypertarget{unarmored-defense}{%
\subsubsection{Unarmored Defense}\label{unarmored-defense}}

While you are not wearing any armor, your Armor Class equals 10 + your
Dexterity modifier + your Constitution modifier. You can use a shield
and still gain this benefit.

\hypertarget{reckless-attack}{%
\subsubsection{Reckless Attack}\label{reckless-attack}}

Starting at 2nd level, you can throw aside all concern for defense to
attack with fierce desperation. When you make your first attack on your
turn, you can decide to attack recklessly. Doing so gives you advantage
on melee weapon attack rolls using Strength during this turn, but attack
rolls against you have advantage until your next turn.

\hypertarget{danger-sense}{%
\subsubsection{Danger Sense}\label{danger-sense}}

At 2nd level, you gain an uncanny sense of when things nearby aren't as
they should be, giving you an edge when you dodge away from danger.

You have advantage on Dexterity saving throws against effects that you
can see, such as traps and spells. To gain this benefit, you can't be
blinded, deafened, or incapacitated.

\hypertarget{primal-path}{%
\subsubsection{Primal Path}\label{primal-path}}

At 3rd level, you choose a path that shapes the nature of your rage.
Choose the Path of the Berserker or the Path of the Totem Warrior, both
detailed at the end of the class description. Your choice grants you
features at 3rd level and again at 6th, 10th, and 14th levels.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{extra-attack}{%
\subsubsection{Extra Attack}\label{extra-attack}}

Beginning at 5th level, you can attack twice, instead of once, whenever
you take the Attack action on your turn.

\hypertarget{fast-movement}{%
\subsubsection{Fast Movement}\label{fast-movement}}

Starting at 5th level, your speed increases by 10 feet while you aren't
wearing heavy armor.

\hypertarget{feral-instinct}{%
\subsubsection{Feral Instinct}\label{feral-instinct}}

By 7th level, your instincts are so honed that you have advantage on
initiative rolls. Additionally, if you are surprised at the beginning of
combat and aren't incapacitated, you can act normally on your first
turn, but only if you enter your rage before doing anything else on that
turn.

\hypertarget{brutal-critical}{%
\subsubsection{Brutal Critical}\label{brutal-critical}}

Beginning at 9th level, you can roll one additional weapon damage die
when determining the extra damage for a critical hit with a melee
attack.

This increases to two additional dice at 13th level and three additional
dice at 17th level.

\hypertarget{relentless-rage}{%
\subsubsection{Relentless Rage}\label{relentless-rage}}

Starting at 11th level, your rage can keep you fighting despite grievous
wounds. If you drop to 0 hit points while you're raging and don't die
outright, you can make a DC 10 Constitution saving throw. If you
succeed, you drop to 1 hit point instead.

Each time you use this feature after the first, the DC increases by 5.
When you finish a short or long rest, the DC resets to 10.

\hypertarget{persistent-rage}{%
\subsubsection{Persistent Rage}\label{persistent-rage}}

Beginning at 15th level, your rage is so fierce that it ends early only
if you fall unconscious or if you choose to end it.

\hypertarget{indomitable-might}{%
\subsubsection{Indomitable Might}\label{indomitable-might}}

Beginning at 18th level, if your total for a Strength check is less than
your Strength score, you can use that score in place of the total.

\hypertarget{primal-champion}{%
\subsubsection{Primal Champion}\label{primal-champion}}

At 20th level, you embody the power of the wilds. Your Strength and
Constitution scores increase by 4. Your maximum for those scores is now
24.

\hypertarget{path-of-the-berserker}{%
\subsubsection{Path of the Berserker}\label{path-of-the-berserker}}

For some barbarians, rage is a means to an end--- that end being
violence. The Path of the Berserker is a path of untrammeled fury, slick
with blood. As you enter the berserker's rage, you thrill in the chaos
of battle, heedless of your own health or well being.

\hypertarget{frenzy}{%
\paragraph{Frenzy}\label{frenzy}}

Starting when you choose this path at 3rd level, you can go into a
frenzy when you rage. If you do so, for the duration of your rage you
can make a single melee weapon attack as a bonus action on each of your
turns after this one. When your rage ends, you suffer one level of
exhaustion (as described in appendix PH-A).

\hypertarget{mindless-rage}{%
\paragraph{Mindless Rage}\label{mindless-rage}}

Beginning at 6th level, you can't be charmed or frightened while raging.
If you are charmed or frightened when you enter your rage, the effect is
suspended for the duration of the rage.

\hypertarget{intimidating-presence}{%
\paragraph{Intimidating Presence}\label{intimidating-presence}}

Beginning at 10th level, you can use your action to frighten someone
with your menacing presence. When you do so, choose one creature that
you can see within 30 feet of you. If the creature can see or hear you,
it must succeed on a Wisdom saving throw (DC equal to 8 + your
proficiency bonus + your Charisma modifier) or be frightened of you
until the end of your next turn. On subsequent turns, you can use your
action to extend the duration of this effect on the frightened creature
until the end of your next turn. This effect ends if the creature ends
its turn out of line of sight or more than 60 feet away from you.

If the creature succeeds on its saving throw, you can't use this feature
on that creature again for 24 hours.

\hypertarget{retaliation}{%
\paragraph{Retaliation}\label{retaliation}}

Starting at 14th level, when you take damage from a creature that is
within 5 feet of you, you can use your reaction to make a melee weapon
attack against that creature.

\end{document}
