% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{bard}{%
\section{Bard}\label{bard}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a bard, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per bard level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per bard level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor

\textbf{Weapons:} Simple weapons, hand crossbows, longswords, rapiers,
shortswords

\textbf{Tools:} Three musical instruments of your choice

\textbf{Saving Throws:} Dexterity, Charisma

\textbf{Skills:} Choose any three

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a rapier, (\emph{b}) a longsword, or (\emph{c}) any simple
  weapon
\item
  (\emph{a}) a diplomat's pack or (\emph{b}) an entertainer's pack
\item
  (\emph{a}) a lute or (\emph{b}) any other musical instrument
\item
  Leather armor and a dagger
\end{itemize}

\hypertarget{the-bard}{%
\paragraph{The Bard}\label{the-bard}}

\begin{longtable}[]{@{}llllllllllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Cantrips Known & Spells Known &
1st & 2nd & 3rd & 4th & 5th & 6th & 7th & 8th & 9th\tabularnewline
\midrule
\endhead
1st & +2 & Spellcasting, Bardic Inspiration (d6) & 2 & 4 & 2 & --- & ---
& --- & --- & --- & --- & --- & ---\tabularnewline
2nd & +2 & Jack of All Trades, Song of Rest (d6) & 2 & 5 & 3 & --- & ---
& --- & --- & --- & --- & --- & ---\tabularnewline
3rd & +2 & Bard College, Expertise & 2 & 6 & 4 & 2 & --- & --- & --- &
--- & --- & --- & ---\tabularnewline
4th & +2 & Ability Score Improvement & 3 & 7 & 4 & 3 & --- & --- & --- &
--- & --- & --- & ---\tabularnewline
5th & +3 & Bardic Inspiration (d8), Font of Inspiration & 3 & 8 & 4 & 3
& 2 & --- & --- & --- & --- & --- & ---\tabularnewline
6th & +3 & Countercharm, Bard College feature & 3 & 9 & 4 & 3 & 3 & ---
& --- & --- & --- & --- & ---\tabularnewline
7th & +3 & --- & 3 & 10 & 4 & 3 & 3 & 1 & --- & --- & --- & --- &
---\tabularnewline
8th & +3 & Ability Score Improvement & 3 & 11 & 4 & 3 & 3 & 2 & --- &
--- & --- & --- & ---\tabularnewline
9th & +4 & Song of Rest (d8) & 3 & 12 & 4 & 3 & 3 & 3 & 1 & --- & --- &
--- & ---\tabularnewline
10th & +4 & Bardic Inspiration (d10), Expertise, Magical Secrets & 4 &
14 & 4 & 3 & 3 & 3 & 2 & --- & --- & --- & ---\tabularnewline
11th & +4 & --- & 4 & 15 & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- &
---\tabularnewline
12th & +4 & Ability Score Improvement & 4 & 15 & 4 & 3 & 3 & 3 & 2 & 1 &
--- & --- & ---\tabularnewline
13th & +5 & Song of Rest (d10) & 4 & 16 & 4 & 3 & 3 & 3 & 2 & 1 & 1 &
--- & ---\tabularnewline
14th & +5 & Magical Secrets, Bard College feature & 4 & 18 & 4 & 3 & 3 &
3 & 2 & 1 & 1 & --- & ---\tabularnewline
15th & +5 & Bardic Inspiration (d12) & 4 & 19 & 4 & 3 & 3 & 3 & 2 & 1 &
1 & 1 & ---\tabularnewline
16th & +5 & Ability Score Improvement & 4 & 19 & 4 & 3 & 3 & 3 & 2 & 1 &
1 & 1 & ---\tabularnewline
17th & +6 & Song of Rest (d12) & 4 & 20 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1
& 1\tabularnewline
18th & +6 & Magical Secrets & 4 & 22 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 &
1\tabularnewline
19th & +6 & Ability Score Improvement & 4 & 22 & 4 & 3 & 3 & 3 & 3 & 2 &
1 & 1 & 1\tabularnewline
20th & +6 & Superior Inspiration & 22 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 &
1 &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

You have learned to untangle and reshape the fabric of reality in
harmony with your wishes and music. Your spells are part of your vast
repertoire, magic that you can tune to different situations.

\hypertarget{cantrips}{%
\paragraph{Cantrips}\label{cantrips}}

You know two cantrips of your choice from the bard spell list. You learn
additional bard cantrips of your choice at higher levels, as shown in
the Cantrips Known column of the Bard table.

\hypertarget{spell-slots}{%
\paragraph{Spell Slots}\label{spell-slots}}

The Bard table shows how many spell slots you have to cast your spells
of 1st level and higher. To cast one of these spells, you must expend a
slot of the spell's level or higher. You regain all expended spell slots
when you finish a long rest.

For example, if you know the 1st level spell \emph{cure wounds} and have
a 1st level and a 2nd level spell slot available, you can cast cure
wounds using either slot.

\hypertarget{spells-known-of-1st-level-and-higher}{%
\paragraph{Spells Known of 1st Level and
Higher}\label{spells-known-of-1st-level-and-higher}}

You know four 1st level spells of your choice from the bard spell list.

The Spells Known column of the Bard table shows when you learn more bard
spells of your choice. Each of these spells must be of a level for which
you have spell slots, as shown on the table. For instance, when you
reach 3rd level in this class, you can learn one new spell of 1st or 2nd
level.

Additionally, when you gain a level in this class, you can choose one of
the bard spells you know and replace it with another spell from the bard
spell list, which also must be of a level for which you have spell
slots.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Charisma is your spellcasting ability for your bard spells. Your magic
comes from the heart and soul you pour into the performance of your
music or oration. You use your Charisma whenever a spell refers to your
spellcasting ability. In addition, you use your Charisma modifier when
setting the saving throw DC for a bard spell you cast and when making an
attack roll with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Charisma
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your Charisma
modifier

\hypertarget{ritual-casting}{%
\paragraph{Ritual Casting}\label{ritual-casting}}

You can cast any bard spell you know as a ritual if that spell has the
ritual tag.

\hypertarget{spellcasting-focus}{%
\paragraph{Spellcasting Focus}\label{spellcasting-focus}}

You can use a musical instrument (see ``Equipment'') as a spellcasting
focus for your bard spells.

\hypertarget{bardic-inspiration}{%
\subsubsection{Bardic Inspiration}\label{bardic-inspiration}}

You can inspire others through stirring words or music. To do so, you
use a bonus action on your turn to choose one creature other than
yourself within 60 feet of you who can hear you. That creature gains one
Bardic Inspiration die, a d6.

Once within the next 10 minutes, the creature can roll the die and add
the number rolled to one ability check, attack roll, or saving throw it
makes. The creature can wait until after it rolls the d20 before
deciding to use the Bardic Inspiration die, but must decide before the
GM says whether the roll succeeds or fails. Once the Bardic Inspiration
die is rolled, it is lost. A creature can have only one Bardic
Inspiration die at a time.

You can use this feature a number of times equal to your Charisma
modifier (a minimum of once). You regain any expended uses when you
finish a long rest.

Your Bardic Inspiration die changes when you reach certain levels in
this class. The die becomes a d8 at 5th level, a d10 at 10th level, and
a d12 at 15th level.

\hypertarget{jack-of-all-trades}{%
\subsubsection{Jack of All Trades}\label{jack-of-all-trades}}

Starting at 2nd level, you can add half your proficiency bonus, rounded
down, to any ability check you make that doesn't already include your
proficiency bonus.

\hypertarget{song-of-rest}{%
\subsubsection{Song of Rest}\label{song-of-rest}}

Beginning at 2nd level, you can use soothing music or oration to help
revitalize your wounded allies during a short rest. If you or any
friendly creatures who can hear your performance regain hit points at
the end of the short rest by spending one or more Hit Dice, each of
those creatures regains an extra 1d6 hit points.

The extra hit points increase when you reach certain levels in this
class: to 1d8 at 9th level, to 1d10 at 13th level, and to 1d12 at 17th
level.

\hypertarget{bard-college}{%
\subsubsection{Bard College}\label{bard-college}}

At 3rd level, you delve into the advanced techniques of a bard college
of your choice, such as the College of Lore. Your choice grants you
features at 3rd level and again at 6th and 14th level.

\hypertarget{expertise}{%
\subsubsection{Expertise}\label{expertise}}

At 3rd level, choose two of your skill proficiencies. Your proficiency
bonus is doubled for any ability check you make that uses either of the
chosen proficiencies.

At 10th level, you can choose another two skill proficiencies to gain
this benefit.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{font-of-inspiration}{%
\subsubsection{Font of Inspiration}\label{font-of-inspiration}}

Beginning when you reach 5th level, you regain all of your expended uses
of Bardic Inspiration when you finish a short or long rest.

\hypertarget{countercharm}{%
\subsubsection{Countercharm}\label{countercharm}}

At 6th level, you gain the ability to use musical notes or words of
power to disrupt mind influencing effects. As an action, you can start a
performance that lasts until the end of your next turn. During that
time, you and any friendly creatures within 30 feet of you have
advantage on saving throws against being frightened or charmed. A
creature must be able to hear you to gain this benefit. The performance
ends early if you are incapacitated or silenced or if you voluntarily
end it (no action required).

\hypertarget{magical-secrets}{%
\subsubsection{Magical Secrets}\label{magical-secrets}}

By 10th level, you have plundered magical knowledge from a wide spectrum
of disciplines. Choose two spells from any class, including this one. A
spell you choose must be of a level you can cast, as shown on the Bard
table, or a cantrip.

The chosen spells count as bard spells for you and are included in the
number in the Spells Known column of the Bard table.

You learn two additional spells from any class at 14th level and again
at 18th level.

\hypertarget{superior-inspiration}{%
\subsubsection{Superior Inspiration}\label{superior-inspiration}}

At 20th level, when you roll initiative and have no uses of Bardic
Inspiration left, you regain one use.

\hypertarget{college-of-lore}{%
\subsubsection{College of Lore}\label{college-of-lore}}

Bards of the College of Lore know something about most things,
collecting bits of knowledge from sources as diverse as scholarly tomes
and peasant tales. Whether singing folk ballads in taverns or elaborate
compositions in royal courts, these bards use their gifts to hold
audiences spellbound. When the applause dies down, the audience members
might find themselves questioning everything they held to be true, from
their faith in the priesthood of the local temple to their loyalty to
the king.

The loyalty of these bards lies in the pursuit of beauty and truth, not
in fealty to a monarch or following the tenets of a deity. A noble who
keeps such a bard as a herald or advisor knows that the bard would
rather be honest than politic.

The college's members gather in libraries and sometimes in actual
colleges, complete with classrooms and dormitories, to share their lore
with one another. They also meet at festivals or affairs of state, where
they can expose corruption, unravel lies, and poke fun at self important
figures of authority.

\hypertarget{bonus-proficiencies}{%
\paragraph{Bonus Proficiencies}\label{bonus-proficiencies}}

When you join the College of Lore at 3rd level, you gain proficiency
with three skills of your choice.

\hypertarget{cutting-words}{%
\paragraph{Cutting Words}\label{cutting-words}}

Also at 3rd level, you learn how to use your wit to distract, confuse,
and otherwise sap the confidence and competence of others. When a
creature that you can see within 60 feet of you makes an attack roll, an
ability check, or a damage roll, you can use your reaction to expend one
of your uses of Bardic Inspiration, rolling a Bardic Inspiration die and
subtracting the number rolled from the creature's roll. You can choose
to use this feature after the creature makes its roll, but before the GM
determines whether the attack roll or ability check succeeds or fails,
or before the creature deals its damage. The creature is immune if it
can't hear you or if it's immune to being charmed.

\hypertarget{additional-magical-secrets}{%
\paragraph{Additional Magical
Secrets}\label{additional-magical-secrets}}

At 6th level, you learn two spells of your choice from any class. A
spell you choose must be of a level you can cast, as shown on the Bard
table, or a cantrip. The chosen spells count as bard spells for you but
don't count against the number of bard spells you know.

\hypertarget{peerless-skill}{%
\paragraph{Peerless Skill}\label{peerless-skill}}

Starting at 14th level, when you make an ability check, you can expend
one use of Bardic Inspiration. Roll a Bardic Inspiration die and add the
number rolled to your ability check. You can choose to do so after you
roll the die for the ability check, but before the GM tells you whether
you succeed or fail.

\end{document}
