% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{cleric}{%
\section{Cleric}\label{cleric}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a cleric, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per cleric level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per cleric level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor, medium armor, shields

\textbf{Weapons:} Simple weapons

\textbf{Tools:} None

\textbf{Saving Throws:} Wisdom, Charisma

\textbf{Skills:} Choose two from History, Insight, Medicine, Persuasion,
and Religion

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a mace or (\emph{b}) a warhammer (if proficient)
\item
  (\emph{a}) scale mail, (\emph{b}) leather armor, or (\emph{c}) chain
  mail (if proficient)
\item
  (\emph{a}) a light crossbow and 20 bolts or (\emph{b}) any simple
  weapon
\item
  (\emph{a}) a priest's pack or (\emph{b}) an explorer's pack
\item
  A shield and a holy symbol
\end{itemize}

\hypertarget{the-cleric}{%
\paragraph{The Cleric}\label{the-cleric}}

\begin{longtable}[]{@{}lllllllllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Cantrips Known & 1st & 2nd & 3rd
& 4th & 5th & 6th & 7th & 8th & 9th\tabularnewline
\midrule
\endhead
1st & +2 & Spellcasting, Divine Domain & 3 & 2 & --- & --- & --- & --- &
--- & --- & --- & ---\tabularnewline
2nd & +2 & Channel Divinity (1/rest), Divine Domain feature & 3 & 3 &
--- & --- & --- & --- & --- & --- & --- & ---\tabularnewline
3rd & +2 & --- & 3 & 4 & 2 & --- & --- & --- & --- & --- & --- &
---\tabularnewline
4th & +2 & Ability Score Improvement & 4 & 4 & 3 & --- & --- & --- & ---
& --- & --- & ---\tabularnewline
5th & +3 & Destroy Undead (CR 1/2) & 4 & 4 & 3 & 2 & --- & --- & --- &
--- & --- & ---\tabularnewline
6th & +3 & Channel Divinity (2/rest), Divine Domain feature & 4 & 4 & 3
& 3 & --- & --- & --- & --- & --- & ---\tabularnewline
7th & +3 & --- & 4 & 4 & 3 & 3 & 1 & --- & --- & --- & --- &
---\tabularnewline
8th & +3 & Ability Score Improvement, Destroy Undead (CR 1), Divine
Domain feature & 4 & 4 & 3 & 3 & 2 & --- & --- & --- & --- &
---\tabularnewline
9th & +4 & --- & 4 & 4 & 3 & 3 & 3 & 1 & --- & --- & --- &
---\tabularnewline
10th & +1 & Divine Intervention & 5 & 4 & 3 & 3 & 3 & 2 & --- & --- &
--- & ---\tabularnewline
11th & +4 & Destroy Undead (CR 2) & 5 & 4 & 3 & 3 & 3 & 2 & 1 & --- &
--- & ---\tabularnewline
12th & +4 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 2 & 1 & ---
& --- & ---\tabularnewline
13th & +5 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & --- &
---\tabularnewline
14th & +5 & Destroy Undead (CR 3) & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & ---
& ---\tabularnewline
15th & +5 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & ---\tabularnewline
16th & +5 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 &
1 & ---\tabularnewline
17th & +6 & Destroy Undead (CR 4), Divine Domain feature & 5 & 4 & 3 & 3
& 3 & 2 & 1 & 1 & 1 & 1\tabularnewline
18th & +6 & Channel Divinity (3/rest) & 5 & 4 & 3 & 3 & 3 & 3 & 1 & 1 &
1 & 1\tabularnewline
19th & +6 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 3 & 2 & 1 &
1 & 1\tabularnewline
20th & +6 & Divine Intervention improvement & 5 & 4 & 3 & 3 & 3 & 3 & 2
& 2 & 1 & 1\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

As a conduit for divine power, you can cast cleric spells.

\hypertarget{cantrips}{%
\paragraph{Cantrips}\label{cantrips}}

At 1st level, you know three cantrips of your choice from the cleric
spell list. You learn additional cleric cantrips of your choice at
higher levels, as shown in the Cantrips Known column of the Cleric
table.

\hypertarget{preparing-and-casting-spells}{%
\paragraph{Preparing and Casting
Spells}\label{preparing-and-casting-spells}}

The Cleric table shows how many spell slots you have to cast your spells
of 1st level and higher. To cast one of these spells, you must expend a
slot of the spell's level or higher. You regain all expended spell slots
when you finish a long rest.

You prepare the list of cleric spells that are available for you to
cast, choosing from the cleric spell list. When you do so, choose a
number of cleric spells equal to your Wisdom modifier + your cleric
level (minimum of one spell). The spells must be of a level for which
you have spell slots.

For example, if you are a 3rd level cleric, you have four 1st level and
two 2nd level spell slots. With a Wisdom of 16, your list of prepared
spells can include six spells of 1st or 2nd level, in any combination.
If you prepare the 1st level spell \emph{cure wounds}, you can cast it
using a 1st level or 2nd level slot. Casting the spell doesn't remove it
from your list of prepared spells.

You can change your list of prepared spells when you finish a long rest.
Preparing a new list of cleric spells requires time spent in prayer and
meditation: at least 1 minute per spell level for each spell on your
list.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Wisdom is your spellcasting ability for your cleric spells. The power of
your spells comes from your devotion to your deity. You use your Wisdom
whenever a cleric spell refers to your spellcasting ability. In
addition, you use your Wisdom modifier when setting the saving throw DC
for a cleric spell you cast and when making an attack roll with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Wisdom
modifier \textbf{Spell attack modifier} = your proficiency bonus + your
Wisdom modifier

\hypertarget{ritual-casting}{%
\paragraph{Ritual Casting}\label{ritual-casting}}

You can cast a cleric spell as a ritual if that spell has the ritual tag
and you have the spell prepared.

\hypertarget{spellcasting-focus}{%
\paragraph{Spellcasting Focus}\label{spellcasting-focus}}

You can use a holy symbol (see ``Equipment'') as a spellcasting focus
for your cleric spells.

\hypertarget{divine-domain}{%
\subsubsection{Divine Domain}\label{divine-domain}}

Choose one domain related to your deity, such as Life. Each domain is
detailed at the end of the class description, and each one provides
examples of gods associated with it. Your choice grants you domain
spells and other features when you choose it at 1st level. It also
grants you additional ways to use Channel Divinity when you gain that
feature at 2nd level, and additional benefits at 6th, 8th, and 17th
levels.

\hypertarget{domain-spells}{%
\paragraph{Domain Spells}\label{domain-spells}}

Each domain has a list of spells---its domain spells---that you gain at
the cleric levels noted in the domain description. Once you gain a
domain spell, you always have it prepared, and it doesn't count against
the number of spells you can prepare each day.

If you have a domain spell that doesn't appear on the cleric spell list,
the spell is nonetheless a cleric spell for you.

\hypertarget{channel-divinity}{%
\subsubsection{Channel Divinity}\label{channel-divinity}}

At 2nd level, you gain the ability to channel divine energy directly
from your deity, using that energy to fuel magical effects. You start
with two such effects: Turn Undead and an effect determined by your
domain. Some domains grant you additional effects as you advance in
levels, as noted in the domain description.

When you use your Channel Divinity, you choose which effect to create.
You must then finish a short or long rest to use your Channel Divinity
again.

Some Channel Divinity effects require saving throws. When you use such
an effect from this class, the DC equals your cleric spell save DC.

Beginning at 6th level, you can use your Channel Divinity twice between
rests, and beginning at 18th level, you can use it three times between
rests. When you finish a short or long rest, you regain your expended
uses.

\hypertarget{channel-divinity-turn-undead}{%
\paragraph{Channel Divinity: Turn
Undead}\label{channel-divinity-turn-undead}}

As an action, you present your holy symbol and speak a prayer censuring
the undead. Each undead that can see or hear you within 30 feet of you
must make a Wisdom saving throw. If the creature fails its saving throw,
it is turned for 1 minute or until it takes any damage.

A turned creature must spend its turns trying to move as far away from
you as it can, and it can't willingly move to a space within 30 feet of
you. It also can't take reactions. For its action, it can use only the
Dash action or try to escape from an effect that prevents it from
moving. If there's nowhere to move, the creature can use the Dodge
action.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{destroy-undead}{%
\subsubsection{Destroy Undead}\label{destroy-undead}}

Starting at 5th level, when an undead fails its saving throw against
your Turn Undead feature, the creature is instantly destroyed if its
challenge rating is at or below a certain threshold, as shown in the
Destroy Undead table.

\hypertarget{destroy-undead-1}{%
\paragraph{Destroy Undead}\label{destroy-undead-1}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Cleric Level & Destroys Undead of CR \ldots{}\tabularnewline
\midrule
\endhead
5th & ½ or lower\tabularnewline
8th & 1 or lower\tabularnewline
11th & 2 or lower\tabularnewline
14th & 3 or lower\tabularnewline
17th & 4 or lower\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{divine-intervention}{%
\subsubsection{Divine Intervention}\label{divine-intervention}}

Beginning at 10th level, you can call on your deity to intervene on your
behalf when your need is great.

Imploring your deity's aid requires you to use your action. Describe the
assistance you seek, and roll percentile dice. If you roll a number
equal to or lower than your cleric level, your deity intervenes. The GM
chooses the nature of the intervention; the effect of any cleric spell
or cleric domain spell would be appropriate.

If your deity intervenes, you can't use this feature again for 7 days.
Otherwise, you can use it again after you finish a long rest.

At 20th level, your call for intervention succeeds automatically, no
roll required.

\hypertarget{life-domain}{%
\subsubsection{Life Domain}\label{life-domain}}

The Life domain focuses on the vibrant positive energy---one of the
fundamental forces of the universe---that sustains all life. The gods of
life promote vitality and health through healing the sick and wounded,
caring for those in need, and driving away the forces of death and
undeath. Almost any non evil deity can claim influence over this domain,
particularly agricultural deities (such as Chauntea, Arawai, and
Demeter), sun gods (such as Lathander, Pelor, and Re Horakhty), gods of
healing or endurance (such as Ilmater, Mishakal, Apollo, and Diancecht),
and gods of home and community (such as Hestia, Hathor, and Boldrei).

\hypertarget{life-domain-spells}{%
\paragraph{Life Domain Spells}\label{life-domain-spells}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Cleric Level & Spells\tabularnewline
\midrule
\endhead
1st & \emph{bless, cure wounds}\tabularnewline
3rd & \emph{lesser restoration, spiritual weapon}\tabularnewline
5th & \emph{beacon of hope, revivify}\tabularnewline
7th & \emph{death ward, guardian of faith}\tabularnewline
9th & \emph{mass cure wounds, raise dead}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{bonus-proficiency}{%
\paragraph{Bonus Proficiency}\label{bonus-proficiency}}

When you choose this domain at 1st level, you gain proficiency with
heavy armor.

\hypertarget{disciple-of-life}{%
\paragraph{Disciple of Life}\label{disciple-of-life}}

Also starting at 1st level, your healing spells are more effective.
Whenever you use a spell of 1st level or higher to restore hit points to
a creature, the creature regains additional hit points equal to 2 + the
spell's level.

\hypertarget{channel-divinity-preserve-life}{%
\paragraph{Channel Divinity: Preserve
Life}\label{channel-divinity-preserve-life}}

Starting at 2nd level, you can use your Channel Divinity to heal the
badly injured.

As an action, you present your holy symbol and evoke healing energy that
can restore a number of hit points equal to five times your cleric
level. Choose any creatures within 30 feet of you, and divide those hit
points among them. This feature can restore a creature to no more than
half of its hit point maximum. You can't use this feature on an undead
or a construct.

\hypertarget{blessed-healer}{%
\paragraph{Blessed Healer}\label{blessed-healer}}

Beginning at 6th level, the healing spells you cast on others heal you
as well. When you cast a spell of 1st level or higher that restores hit
points to a creature other than you, you regain hit points equal to 2 +
the spell's level.

\hypertarget{divine-strike}{%
\paragraph{Divine Strike}\label{divine-strike}}

At 8th level, you gain the ability to infuse your weapon strikes with
divine energy. Once on each of your turns when you hit a creature with a
weapon attack, you can cause the attack to deal an extra 1d8 radiant
damage to the target. When you reach 14th level, the extra damage
increases to 2d8.

\hypertarget{supreme-healing}{%
\paragraph{Supreme Healing}\label{supreme-healing}}

Starting at 17th level, when you would normally roll one or more dice to
restore hit points with a spell, you instead use the highest number
possible for each die. For example, instead of restoring 2d6 hit points
to a creature, you restore 12.

\end{document}
