% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{druid}{%
\section{Druid}\label{druid}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a druid, you gain the following class features

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per druid level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per druid level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor, medium armor, shields (druids will not wear
armor or use shields made of metal)

\textbf{Weapons:} Clubs, daggers, darts, javelins, maces, quarterstaffs,
scimitars, sickles, slings, spears

\textbf{Tools:} Herbalism kit

\textbf{Saving Throws:} Intelligence, Wisdom

\textbf{Skills:} Choose two from Arcana, Animal Handling, Insight,
Medicine, Nature, Perception, Religion, and Survival

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a wooden shield or (\emph{b}) any simple weapon
\item
  (\emph{a}) a scimitar or (\emph{b}) any simple melee weapon
\item
  Leather armor, an explorer's pack, and a druidic focus
\end{itemize}

\hypertarget{the-druid}{%
\paragraph{The Druid}\label{the-druid}}

\begin{longtable}[]{@{}lllllllllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Cantrips Known & 1st & 2nd & 3rd
& 4th & 5th & 6th & 7th & 8th & 9th\tabularnewline
\midrule
\endhead
1st & +2 & Druidic, Spellcasting & 2 & 2 & --- & --- & --- & --- & --- &
--- & --- & ---\tabularnewline
2nd & +2 & Wild Shape, Druid Circle & 2 & 3 & --- & --- & --- & --- &
--- & --- & --- & ---\tabularnewline
3rd & +2 & --- & 2 & 4 & 2 & --- & --- & --- & --- & --- & --- &
---\tabularnewline
4th & +2 & Wild Shape improvement, Ability Score Improvement & 3 & 4 & 3
& --- & --- & --- & --- & --- & --- & ---\tabularnewline
5th & +3 & --- & 3 & 4 & 3 & 2 & --- & --- & --- & --- & --- &
---\tabularnewline
6th & +3 & Druid Circle feature & 3 & 4 & 3 & 3 & --- & --- & --- & ---
& --- & ---\tabularnewline
7th & +3 & --- & 3 & 4 & 3 & 3 & 1 & --- & --- & --- & --- &
---\tabularnewline
8th & +3 & Wild Shape improvement, Ability Score Improvement & 3 & 4 & 3
& 3 & 2 & --- & --- & --- & --- & ---\tabularnewline
9th & +4 & --- & 3 & 4 & 3 & 3 & 2 & --- & --- & --- & --- &
---\tabularnewline
10th & +4 & Druid Circle feature & 4 & 4 & 3 & 3 & 3 & 2 & --- & --- &
--- & ---\tabularnewline
11th & +4 & --- & 4 & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- &
---\tabularnewline
12th & +4 & Ability Score Improvement & 4 & 4 & 3 & 3 & 3 & 2 & 1 & ---
& --- & ---\tabularnewline
13th & +5 & --- & 4 & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- &
---\tabularnewline
14th & +5 & Druid Circle feature & 4 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & --- &
---\tabularnewline
15th & +5 & --- & 4 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & ---\tabularnewline
16th & +5 & Ability Score Improvement & 4 & 4 & 3 & 3 & 3 & 2 & 1 & 1 &
1 & ---\tabularnewline
17th & +6 & --- & 4 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1\tabularnewline
18th & +6 & Timeless Body, Beast Spells & 4 & 4 & 3 & 3 & 3 & 3 & 1 & 1
& 1 & 1\tabularnewline
19th & +6 & Ability Score Improvement & 4 & 4 & 3 & 3 & 3 & 3 & 2 & 1 &
1 & 1\tabularnewline
20th & +6 & Archdruid & 4 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 &
1\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{druidic}{%
\subsubsection{Druidic}\label{druidic}}

You know Druidic, the secret language of druids. You can speak the
language and use it to leave hidden messages. You and others who know
this language automatically spot such a message. Others spot the
message's presence with a successful DC 15 Wisdom (Perception) check but
can't decipher it without magic.

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

Drawing on the divine essence of nature itself, you can cast spells to
shape that essence to your will.

\hypertarget{cantrips}{%
\paragraph{Cantrips}\label{cantrips}}

At 1st level, you know two cantrips of your choice from the druid spell
list. You learn additional druid cantrips of your choice at higher
levels, as shown in the Cantrips Known column of the Druid table.

\hypertarget{preparing-and-casting-spells}{%
\paragraph{Preparing and Casting
Spells}\label{preparing-and-casting-spells}}

The Druid table shows how many spell slots you have to cast your spells
of 1st level and higher. To cast one of these druid spells, you must
expend a slot of the spell's level or higher. You regain all expended
spell slots when you finish a long rest.

You prepare the list of druid spells that are available for you to cast,
choosing from the druid spell list. When you do so, choose a number of
druid spells equal to your Wisdom modifier + your druid level (minimum
of one spell). The spells must be of a level for which you have spell
slots.

For example, if you are a 3rd level druid, you have four 1st level and
two 2nd level spell slots. With a Wisdom of 16, your list of prepared
spells can include six spells of 1st or 2nd level, in any combination.
If you prepare the 1st level spell \emph{cure wounds}, you can cast it
using a 1st level or 2nd level slot. Casting the spell doesn't remove it
from your list of prepared spells.

You can also change your list of prepared spells when you finish a long
rest. Preparing a new list of druid spells requires time spent in prayer
and meditation: at least 1 minute per spell level for each spell on your
list.

Spellcasting Ability Wisdom is your spellcasting ability for your druid
spells, since your magic draws upon your devotion and attunement to
nature. You use your Wisdom whenever a spell refers to your spellcasting
ability. In addition, you use your Wisdom modifier when setting the
saving throw DC for a druid spell you cast and when making an attack
roll with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Wisdom
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your Wisdom
modifier

\hypertarget{ritual-casting}{%
\paragraph{Ritual Casting}\label{ritual-casting}}

You can cast a druid spell as a ritual if that spell has the ritual tag
and you have the spell prepared.

\hypertarget{spellcasting-focus}{%
\paragraph{Spellcasting Focus}\label{spellcasting-focus}}

You can use a druidic focus (see ``Equipment'') as a spellcasting focus
for your druid spells.

\hypertarget{wild-shape}{%
\subsubsection{Wild Shape}\label{wild-shape}}

Starting at 2nd level, you can use your action to magically assume the
shape of a beast that you have seen before. You can use this feature
twice. You regain expended uses when you finish a short or long rest.

Your druid level determines the beasts you can transform into, as shown
in the Beast Shapes table. At 2nd level, for example, you can transform
into any beast that has a challenge rating of ¼ or lower that doesn't
have a flying or swimming speed.

\hypertarget{beast-shapes}{%
\paragraph{Beast Shapes}\label{beast-shapes}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Level & Max. CR & Limitations & Example\tabularnewline
\midrule
\endhead
2nd & ¼ & No flying or swimming speed & Wolf\tabularnewline
4th & ½ & No flying speed & Crocodile\tabularnewline
8th & 1 & --- & Giant eagle\tabularnewline
\bottomrule
\end{longtable}

You can stay in a beast shape for a number of hours equal to half your
druid level (rounded down). You then revert to your normal form unless
you expend another use of this feature. You can revert to your normal
form earlier by using a bonus action on your turn. You automatically
revert if you fall unconscious, drop to 0 hit points, or die.

While you are transformed, the following rules apply:

\begin{itemize}
\tightlist
\item
  Your game statistics are replaced by the statistics of the beast, but
  you retain your alignment, personality, and Intelligence, Wisdom, and
  Charisma scores. You also retain all of your skill and saving throw
  proficiencies, in addition to gaining those of the creature. If the
  creature has the same proficiency as you and the bonus in its stat
  block is higher than yours, use the creature's bonus instead of yours.
  If the creature has any legendary or lair actions, you can't use them.
\item
  When you transform, you assume the beast's hit points and Hit Dice.
  When you revert to your normal form, you return to the number of hit
  points you had before you transformed. However, if you revert as a
  result of dropping to 0 hit points, any excess damage carries over to
  your normal form. For example, if you take 10 damage in animal form
  and have only 1 hit point left, you revert and take 9 damage. As long
  as the excess damage doesn't reduce your normal form to 0 hit points,
  you aren't knocked unconscious.
\item
  You can't cast spells, and your ability to speak or take any action
  that requires hands is limited to the capabilities of your beast form.
  Transforming doesn't break your concentration on a spell you've
  already cast, however, or prevent you from taking actions that are
  part of a spell, such as call lightning, that you've already cast.
\item
  You retain the benefit of any features from your class, race, or other
  source and can use them if the new form is physically capable of doing
  so. However, you can't use any of your special senses, such as
  darkvision, unless your new form also has that sense.
\item
  You choose whether your equipment falls to the ground in your space,
  merges into your new form, or is worn by it. Worn equipment functions
  as normal, but the GM decides whether it is practical for the new form
  to wear a piece of equipment, based on the creature's shape and size.
  Your equipment doesn't change size or shape to match the new form, and
  any equipment that the new form can't wear must either fall to the
  ground or merge with it. Equipment that merges with the form has no
  effect until you leave the form.
\end{itemize}

\hypertarget{druid-circle}{%
\subsubsection{Druid Circle}\label{druid-circle}}

At 2nd level, you choose to identify with a circle of druids, such as
the Circle of the Land. Your choice grants you features at 2nd level and
again at 6th, 10th, and 14th level.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{timeless-body}{%
\subsubsection{Timeless Body}\label{timeless-body}}

Starting at 18th level, the primal magic that you wield causes you to
age more slowly. For every 10 years that pass, your body ages only 1
year.

\hypertarget{beast-spells}{%
\subsubsection{Beast Spells}\label{beast-spells}}

Beginning at 18th level, you can cast many of your druid spells in any
shape you assume using Wild Shape. You can perform the somatic and
verbal components of a druid spell while in a beast shape, but you
aren't able to provide material components.

\hypertarget{archdruid}{%
\subsubsection{Archdruid}\label{archdruid}}

At 20th level, you can use your Wild Shape an unlimited number of times.
Additionally, you can ignore the verbal and somatic components of your
druid spells, as well as any material components that lack a cost and
aren't consumed by a spell. You gain this benefit in both your normal
shape and your beast shape from Wild Shape.

\hypertarget{circle-of-the-land}{%
\subsubsection{Circle of the Land}\label{circle-of-the-land}}

The Circle of the Land is made up of mystics and sages who safeguard
ancient knowledge and rites through a vast oral tradition. These druids
meet within sacred circles of trees or standing stones to whisper primal
secrets in Druidic. The circle's wisest members preside as the chief
priests of communities that hold to the Old Faith and serve as advisors
to the rulers of those folk. As a member of this circle, your magic is
influenced by the land where you were initiated into the circle's
mysterious rites.

\hypertarget{bonus-cantrip}{%
\paragraph{Bonus Cantrip}\label{bonus-cantrip}}

When you choose this circle at 2nd level, you learn one additional druid
cantrip of your choice.

\hypertarget{natural-recovery}{%
\paragraph{Natural Recovery}\label{natural-recovery}}

Starting at 2nd level, you can regain some of your magical energy by
sitting in meditation and communing with nature. During a short rest,
you choose expended spell slots to recover. The spell slots can have a
combined level that is equal to or less than half your druid level
(rounded up), and none of the slots can be 6th level or higher. You
can't use this feature again until you finish a long rest.

For example, when you are a 4th level druid, you can recover up to two
levels worth of spell slots. You can recover either a 2nd level slot or
two 1st level slots.

\hypertarget{circle-spells}{%
\paragraph{Circle Spells}\label{circle-spells}}

Your mystical connection to the land infuses you with the ability to
cast certain spells. At 3rd, 5th, 7th, and 9th level you gain access to
circle spells connected to the land where you became a druid. Choose
that land---arctic, coast, desert, forest, grassland, mountain, or
swamp---and consult the associated list of spells.

Once you gain access to a circle spell, you always have it prepared, and
it doesn't count against the number of spells you can prepare each day.
If you gain access to a spell that doesn't appear on the druid spell
list, the spell is nonetheless a druid spell for you.

\hypertarget{arctic}{%
\paragraph{Arctic}\label{arctic}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{hold person}, \emph{spike growth}\tabularnewline
5th & \emph{sleet storm}, \emph{slow}\tabularnewline
7th & \emph{freedom of movement}, \emph{ice storm}\tabularnewline
9th & \emph{commune with nature}, \emph{cone of cold}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{coast}{%
\paragraph{Coast}\label{coast}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{mirror image,} \emph{misty step}\tabularnewline
5th & \emph{water breathing}, \emph{water walk}\tabularnewline
7th & \emph{control water}, \emph{freedom of movement}\tabularnewline
9th & \emph{conjure elemental}, \emph{scrying}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{desert}{%
\paragraph{Desert}\label{desert}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{blur}, \emph{silence}\tabularnewline
5th & \emph{create food and water}, \emph{protection from
energy}\tabularnewline
7th & \emph{blight}, \emph{hallucinatory terrain}\tabularnewline
9th & \emph{insect plague}, \emph{wall of stone}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{forest}{%
\paragraph{Forest}\label{forest}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{barkskin}, \emph{spider climb}\tabularnewline
5th & \emph{call lightning}, \emph{plant growth}\tabularnewline
7th & \emph{divination}, \emph{freedom of movement}\tabularnewline
9th & \emph{commune with nature}, \emph{tree stride}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{grassland}{%
\paragraph{Grassland}\label{grassland}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{invisibility}, \emph{pass without trace}\tabularnewline
5th & \emph{daylight}, \emph{haste}\tabularnewline
7th & \emph{divination}, \emph{freedom of movement}\tabularnewline
9th & \emph{dream}, \emph{insect plague}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{mountain}{%
\paragraph{Mountain}\label{mountain}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{spider climb,} \emph{spike growth}\tabularnewline
5th & \emph{lightning bolt}, \emph{meld into stone}\tabularnewline
7th & \emph{stone shape}, \emph{stoneskin}\tabularnewline
9th & \emph{passwall}, \emph{wall of stone}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{swamp}{%
\paragraph{Swamp}\label{swamp}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Druid Level & Circle Spells\tabularnewline
\midrule
\endhead
3rd & \emph{acid arrow}, \emph{darkness}\tabularnewline
5th & \emph{water walk}, \emph{stinking cloud}\tabularnewline
7th & \emph{freedom of movement}, \emph{locate creature}\tabularnewline
9th & \emph{insect plague}, \emph{scrying}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{lands-stride}{%
\paragraph{Land's Stride}\label{lands-stride}}

Starting at 6th level, moving through nonmagical difficult terrain costs
you no extra movement. You can also pass through nonmagical plants
without being slowed by them and without taking damage from them if they
have thorns, spines, or a similar hazard.

In addition, you have advantage on saving throws against plants that are
magically created or manipulated to impede movement, such those created
by the \emph{entangle} spell.

\hypertarget{natures-ward}{%
\paragraph{Nature's Ward}\label{natures-ward}}

When you reach 10th level, you can't be charmed or frightened by
elementals or fey, and you are immune to poison and disease.

\hypertarget{natures-sanctuary}{%
\paragraph{Nature's Sanctuary}\label{natures-sanctuary}}

When you reach 14th level, creatures of the natural world sense your
connection to nature and become hesitant to attack you. When a beast or
plant creature attacks you, that creature must make a Wisdom saving
throw against your druid spell save DC. On a failed save, the creature
must choose a different target, or the attack automatically misses. On a
successful save, the creature is immune to this effect for 24 hours.

The creature is aware of this effect before it makes its attack against
you.

\begin{quote}
\mbox{}%
\hypertarget{sacred-plants-and-wood}{%
\paragraph{Sacred Plants and Wood}\label{sacred-plants-and-wood}}
\end{quote}

A druid holds certain plants to be sacred, particularly alder, ash,
birch, elder, hazel, holly, juniper, mistletoe, oak, rowan, willow, and
yew. Druids often use such plants as part of a spellcasting focus,
incorporating lengths of oak or yew or sprigs of mistletoe.

\begin{quote}
Similarly, a druid uses such woods to make other objects, such as
weapons and shields. Yew is associated with death and rebirth, so weapon
handles for scimitars or sickles might be fashioned from it. Ash is
associated with life and oak with strength. These woods make excellent
hafts or whole weapons, such as clubs or quarterstaffs, as well as
shields. Alder is associated with air, and it might be used for thrown
weapons, such as darts or javelins.

Druids from regions that lack the plants described here have chosen
other plants to take on similar uses. For instance, a druid of a desert
region might value the yucca tree and cactus plants.

\mbox{}%
\hypertarget{druids-and-the-gods}{%
\paragraph{Druids and the Gods}\label{druids-and-the-gods}}
\end{quote}

Some druids venerate the forces of nature themselves, but most druids
are devoted to one of the many nature deities worshiped in the
multiverse (the lists of gods in appendix PH-B include many such
deities). The worship of these deities is often considered a more
ancient tradition than the faiths of clerics and urbanized peoples.

\end{document}
