% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{fighter}{%
\section{Fighter}\label{fighter}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a fighter, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d10 per fighter level

\textbf{Hit Points at 1st Level:} 10 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d10 (or 6) + your Constitution
modifier per fighter level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} All armor, shields

\textbf{Weapons:} Simple weapons, martial weapons

\textbf{Tools:} None

\textbf{Saving Throws:} Strength, Constitution

\textbf{Skills:} Choose two skills from Acrobatics, Animal Handling,
Athletics, History, Insight, Intimidation, Perception, and Survival

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) chain mail or (\emph{b}) leather armor, longbow, and 20
  arrows
\item
  (\emph{a}) a martial weapon and a shield or (\emph{b}) two martial
  weapons
\item
  (\emph{a}) a light crossbow and 20 bolts or (\emph{b}) two handaxes
\item
  (\emph{a}) a dungeoneer's pack or (\emph{b}) an explorer's pack
\end{itemize}

\hypertarget{the-fighter}{%
\paragraph{The Fighter}\label{the-fighter}}

\begin{longtable}[]{@{}lll@{}}
\toprule
Level & Proficiency Bonus & Features\tabularnewline
\midrule
\endhead
1st & +2 & Fighting Style, Second Wind\tabularnewline
2nd & +2 & Action Surge (one use)\tabularnewline
3rd & +2 & Martial Archetype\tabularnewline
4th & +2 & Ability Score Improvement\tabularnewline
5th & +3 & Extra Attack\tabularnewline
6th & +3 & Ability Score Improvement\tabularnewline
7th & +3 & Martial Archetype feature\tabularnewline
8th & +3 & Ability Score Improvement\tabularnewline
9th & +4 & Indomitable (one use)\tabularnewline
10th & +4 & Martial Archetype feature\tabularnewline
11th & +4 & Extra Attack (2)\tabularnewline
12th & +4 & Ability Score Improvement\tabularnewline
13th & +5 & Indomitable (two uses)\tabularnewline
14th & +5 & Ability Score Improvement\tabularnewline
15th & +5 & Martial Archetype feature\tabularnewline
16th & +5 & Ability Score Improvement\tabularnewline
17th & +6 & Action Surge (two uses), Indomitable (three
uses)\tabularnewline
18th & +6 & Martial Archetype feature\tabularnewline
19th & +6 & Ability Score Improvement\tabularnewline
20th & +3 & Extra Attack (3)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{fighting-style}{%
\subsubsection{Fighting Style}\label{fighting-style}}

You adopt a particular style of fighting as your specialty. Choose one
of the following options. You can't take a Fighting Style option more
than once, even if you later get to choose again.

\hypertarget{archery}{%
\paragraph{Archery}\label{archery}}

You gain a +2 bonus to attack rolls you make with ranged weapons.

\hypertarget{defense}{%
\paragraph{Defense}\label{defense}}

While you are wearing armor, you gain a +1 bonus to AC.

\hypertarget{dueling}{%
\paragraph{Dueling}\label{dueling}}

When you are wielding a melee weapon in one hand and no other weapons,
you gain a +2 bonus to damage rolls with that weapon.

\hypertarget{great-weapon-fighting}{%
\paragraph{Great Weapon Fighting}\label{great-weapon-fighting}}

When you roll a 1 or 2 on a damage die for an attack you make with a
melee weapon that you are wielding with two hands, you can reroll the
die and must use the new roll, even if the new roll is a 1 or a 2. The
weapon must have the two handed or versatile property for you to gain
this benefit.

\hypertarget{protection}{%
\paragraph{Protection}\label{protection}}

When a creature you can see attacks a target other than you that is
within 5 feet of you, you can use your reaction to impose disadvantage
on the attack roll. You must be wielding a shield.

\hypertarget{two-weapon-fighting}{%
\paragraph{Two-Weapon Fighting}\label{two-weapon-fighting}}

When you engage in two weapon fighting, you can add your ability
modifier to the damage of the second attack.

\hypertarget{second-wind}{%
\subsubsection{Second Wind}\label{second-wind}}

You have a limited well of stamina that you can draw on to protect
yourself from harm. On your turn, you can use a bonus action to regain
hit points equal to 1d10 + your fighter level. Once you use this
feature, you must finish a short or long rest before you can use it
again.

\hypertarget{action-surge}{%
\subsubsection{Action Surge}\label{action-surge}}

Starting at 2nd level, you can push yourself beyond your normal limits
for a moment. On your turn, you can take one additional action on top of
your regular action and a possible bonus action.

Once you use this feature, you must finish a short or long rest before
you can use it again. Starting at 17th level, you can use it twice
before a rest, but only once on the same turn.

\hypertarget{martial-archetype}{%
\subsubsection{Martial Archetype}\label{martial-archetype}}

At 3rd level, you choose an archetype that you strive to emulate in your
combat styles and techniques, such as Champion. The archetype you choose
grants you features at 3rd level and again at 7th, 10th, 15th, and 18th
level.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 6th, 8th, 12th, 14th, 16th, and
19th level, you can increase one ability score of your choice by 2, or
you can increase two ability scores of your choice by 1. As normal, you
can't increase an ability score above 20 using this feature.

\hypertarget{extra-attack}{%
\subsubsection{Extra Attack}\label{extra-attack}}

Beginning at 5th level, you can attack twice, instead of once, whenever
you take the Attack action on your turn.

The number of attacks increases to three when you reach 11th level in
this class and to four when you reach 20th level in this class.

\hypertarget{indomitable}{%
\subsubsection{Indomitable}\label{indomitable}}

Beginning at 9th level, you can reroll a saving throw that you fail. If
you do so, you must use the new roll, and you can't use this feature
again until you finish a long rest.

You can use this feature twice between long rests starting at 13th level
and three times between long rests starting at 17th level.

\hypertarget{martial-archetypes}{%
\subsection{Martial Archetypes}\label{martial-archetypes}}

Different fighters choose different approaches to perfecting their
fighting prowess. The martial archetype you choose to emulate reflects
your approach.

\hypertarget{champion}{%
\subsubsection{Champion}\label{champion}}

The archetypal Champion focuses on the development of raw physical power
honed to deadly perfection. Those who model themselves on this archetype
combine rigorous training with physical excellence to deal devastating
blows.

\hypertarget{improved-critical}{%
\paragraph{Improved Critical}\label{improved-critical}}

Beginning when you choose this archetype at 3rd level, your weapon
attacks score a critical hit on a roll of 19 or 20.

\hypertarget{remarkable-athlete}{%
\paragraph{Remarkable Athlete}\label{remarkable-athlete}}

Starting at 7th level, you can add half your proficiency bonus (round
up) to any Strength, Dexterity, or Constitution check you make that
doesn't already use your proficiency bonus.

In addition, when you make a running long jump, the distance you can
cover increases by a number of feet equal to your Strength modifier.

\hypertarget{additional-fighting-style}{%
\paragraph{Additional Fighting Style}\label{additional-fighting-style}}

At 10th level, you can choose a second option from the Fighting Style
class feature.

\hypertarget{superior-critical}{%
\paragraph{Superior Critical}\label{superior-critical}}

Starting at 15th level, your weapon attacks score a critical hit on a
roll of 18--20.

\hypertarget{survivor}{%
\paragraph{Survivor}\label{survivor}}

At 18th level, you attain the pinnacle of resilience in battle. At the
start of each of your turns, you regain hit points equal to 5 + your
Constitution modifier if you have no more than half of your hit points
left. You don't gain this benefit if you have 0 hit points

\end{document}
