% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{monk}{%
\section{Monk}\label{monk}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a monk, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per monk level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per monk level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} None

\textbf{Weapons:} Simple weapons, shortswords

\textbf{Tools:} Choose one type of artisan's tools or one musical
instrument

\textbf{Saving Throws:} Strength, Dexterity

\textbf{Skills:} Choose two from Acrobatics, Athletics, History,
Insight, Religion, and Stealth

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a shortsword or (\emph{b}) any simple weapon
\item
  (\emph{a}) a dungeoneer's pack or (\emph{b}) an explorer's pack
\item
  10 darts
\end{itemize}

\hypertarget{the-monk}{%
\paragraph{The Monk}\label{the-monk}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
Level & Proficiency Bonus & Martial Arts & Ki Points & Unarmored
Movement & Features\tabularnewline
\midrule
\endhead
1st & +2 & 1d4 & --- & --- & Unarmored Defense, Martial
Arts\tabularnewline
2nd & +2 & 1d4 & 2 & +10 ft. & Ki, Unarmored Movement\tabularnewline
3rd & +2 & 1d4 & 3 & +10 ft. & Monastic Tradition, Deflect
Missiles\tabularnewline
4th & +2 & 1d4 & 4 & +10 ft. & Ability Score Improvement, Slow
Fall\tabularnewline
5th & +3 & 1d6 & 5 & +10 ft. & Extra Attack, Stunning
Strike\tabularnewline
6th & +3 & 1d6 & 6 & +15 ft. & Ki-Empowered Strikes, Monastic Tradition
feature\tabularnewline
7th & +3 & 1d6 & 7 & +15 ft. & Evasion, Stillness of Mind\tabularnewline
8th & +3 & 1d6 & 8 & +15 ft. & Ability Score Improvement\tabularnewline
9th & +4 & 1d6 & 9 & +15 ft. & Unarmored Movement
improvement\tabularnewline
10th & +4 & 1d6 & 10 & +20 ft. & Purity of Body\tabularnewline
11th & +4 & 1d8 & 11 & +20 ft. & Monastic Tradition
feature\tabularnewline
12th & +4 & 1d8 & 12 & +20 ft. & Ability Score
Improvement\tabularnewline
13th & +5 & 1d8 & 13 & +20 ft. & Tongue of the Sun and
Moon\tabularnewline
14th & +5 & 1d8 & 14 & +25 ft. & Diamond Soul\tabularnewline
15th & +5 & 1d8 & 15 & +25 ft. & Timeless Body\tabularnewline
16th & +5 & 1d8 & 16 & +25 ft. & Ability Score
Improvement\tabularnewline
17th & +6 & 1d10 & 17 & +25 ft. & Monastic Tradition
feature\tabularnewline
18th & +6 & 1d10 & 18 & +30 ft. & Empty Body\tabularnewline
19th & +6 & 1d10 & 19 & +30 ft. & Ability Score
Improvement\tabularnewline
20th & +6 & 1d10 & 20 & +30 ft. & Perfect Self\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{unarmored-defense}{%
\subsubsection{Unarmored Defense}\label{unarmored-defense}}

Beginning at 1st level, while you are wearing no armor and not wielding
a shield, your AC equals 10 + your Dexterity modifier + your Wisdom
modifier.

\hypertarget{martial-arts}{%
\subsubsection{Martial Arts}\label{martial-arts}}

At 1st level, your practice of martial arts gives you mastery of combat
styles that use unarmed strikes and monk weapons, which are shortswords
and any simple melee weapons that don't have the twohanded or heavy
property.

You gain the following benefits while you are unarmed or wielding only
monk weapons and you aren't wearing armor or wielding a shield:

\begin{itemize}
\tightlist
\item
  You can use Dexterity instead of Strength for the attack and damage
  rolls of your unarmed strikes and monk weapons.
\item
  You can roll a d4 in place of the normal damage of your unarmed strike
  or monk weapon. This die changes as you gain monk levels, as shown in
  the Martial Arts column of the Monk table.
\item
  When you use the Attack action with an unarmed strike or a monk weapon
  on your turn, you can make one unarmed strike as a bonus action. For
  example, if you take the Attack action and attack with a quarterstaff,
  you can also make an unarmed strike as a bonus action, assuming you
  haven't already taken a bonus action this turn.
\end{itemize}

\hypertarget{ki}{%
\subsubsection{Ki}\label{ki}}

Starting at 2nd level, your training allows you to harness the mystic
energy of ki. Your access to this energy is represented by a number of
ki points. Your monk level determines the number of points you have, as
shown in the Ki Points column of the Monk table. You can spend these
points to fuel various ki features. You start knowing three such
features: Flurry of Blows, Patient Defense, and Step of the Wind. You
learn more ki features as you gain levels in this class.

When you spend a ki point, it is unavailable until you finish a short or
long rest, at the end of which you draw all of your expended ki back
into yourself. You must spend at least 30 minutes of the rest meditating
to regain your ki points.

Some of your ki features require your target to make a saving throw to
resist the feature's effects. The saving throw DC is calculated as
follows:

\textbf{Ki save DC} = 8 + your proficiency bonus + your Wisdom modifier

\hypertarget{flurry-of-blows}{%
\paragraph{Flurry of Blows}\label{flurry-of-blows}}

Immediately after you take the Attack action on your turn, you can spend
1 ki point to make two unarmed strikes as a bonus action.

\hypertarget{patient-defense}{%
\paragraph{Patient Defense}\label{patient-defense}}

You can spend 1 ki point to take the Dodge action as a bonus action on
your turn.

\hypertarget{step-of-the-wind}{%
\paragraph{Step of the Wind}\label{step-of-the-wind}}

You can spend 1 ki point to take the Disengage or Dash action as a bonus
action on your turn, and your jump distance is doubled for the turn.

\hypertarget{unarmored-movement}{%
\subsubsection{Unarmored Movement}\label{unarmored-movement}}

Starting at 2nd level, your speed increases by 10 feet while you are not
wearing armor or wielding a shield. This bonus increases when you reach
certain monk levels, as shown in the Monk table.

At 9th level, you gain the ability to move along vertical surfaces and
across liquids on your turn without falling during the move.

\hypertarget{monastic-tradition}{%
\subsubsection{Monastic Tradition}\label{monastic-tradition}}

When you reach 3rd level, you commit yourself to a monastic tradition,
such as the Way of the Open Hand. Your tradition grants you features at
3rd level and again at 6th, 11th, and 17th level.

\hypertarget{deflect-missiles}{%
\subsubsection{Deflect Missiles}\label{deflect-missiles}}

Starting at 3rd level, you can use your reaction to deflect or catch the
missile when you are hit by a ranged weapon attack. When you do so, the
damage you take from the attack is reduced by 1d10 + your Dexterity
modifier + your monk level.

If you reduce the damage to 0, you can catch the missile if it is small
enough for you to hold in one hand and you have at least one hand free.
If you catch a missile in this way, you can spend 1 ki point to make a
ranged attack with the weapon or piece of ammunition you just caught, as
part of the same reaction. You make this attack with proficiency,
regardless of your weapon proficiencies, and the missile counts as a
monk weapon for the attack, which has a normal range of 20 feet and a
long range of 60 feet.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{slow-fall}{%
\subsubsection{Slow Fall}\label{slow-fall}}

Beginning at 4th level, you can use your reaction when you fall to
reduce any falling damage you take by an amount equal to five times your
monk level.

\#\#\#Extra Attack

Beginning at 5th level, you can attack twice, instead of once, whenever
you take the Attack action on your turn.

\hypertarget{stunning-strike}{%
\subsubsection{Stunning Strike}\label{stunning-strike}}

Starting at 5th level, you can interfere with the flow of ki in an
opponent's body. When you hit another creature with a melee weapon
attack, you can spend 1 ki point to attempt a stunning strike. The
target must succeed on a Constitution saving throw or be stunned until
the end of your next turn.

\hypertarget{ki-empowered-strikes}{%
\subsubsection{Ki-Empowered Strikes}\label{ki-empowered-strikes}}

Starting at 6th level, your unarmed strikes count as magical for the
purpose of overcoming resistance and immunity to nonmagical attacks and
damage.

\hypertarget{evasion}{%
\subsubsection{Evasion}\label{evasion}}

At 7th level, your instinctive agility lets you dodge out of the way of
certain area effects, such as a blue dragon's lightning breath or a
\emph{fireball} spell. When you are subjected to an effect that allows
you to make a Dexterity saving throw to take only half damage, you
instead take no damage if you succeed on the saving throw, and only half
damage if you fail.

\hypertarget{stillness-of-mind}{%
\subsubsection{Stillness of Mind}\label{stillness-of-mind}}

Starting at 7th level, you can use your action to end one effect on
yourself that is causing you to be charmed or frightened.

\hypertarget{purity-of-body}{%
\subsubsection{Purity of Body}\label{purity-of-body}}

At 10th level, your mastery of the ki flowing through you makes you
immune to disease and poison.

\hypertarget{tongue-of-the-sun-and-moon}{%
\subsubsection{Tongue of the Sun and
Moon}\label{tongue-of-the-sun-and-moon}}

Starting at 13th level, you learn to touch the ki of other minds so that
you understand all spoken languages. Moreover, any creature that can
understand a language can understand what you say.

\hypertarget{diamond-soul}{%
\subsubsection{Diamond Soul}\label{diamond-soul}}

Beginning at 14th level, your mastery of ki grants you proficiency in
all saving throws. Additionally, whenever you make a saving throw and
fail, you can spend 1 ki point to reroll it and take the second result.

\hypertarget{timeless-body}{%
\subsubsection{Timeless Body}\label{timeless-body}}

At 15th level, your ki sustains you so that you suffer none of the
frailty of old age, and you can't be aged magically. You can still die
of old age, however. In addition, you no longer need food or water.

\hypertarget{empty-body}{%
\subsubsection{Empty Body}\label{empty-body}}

Beginning at 18th level, you can use your action to spend 4 ki points to
become invisible for 1 minute. During that time, you also have
resistance to all damage but force damage. Additionally, you can spend 8
ki points to cast the \emph{astral projection} spell, without needing
material components. When you do so, you can't take any other creatures
with you.

\hypertarget{perfect-self}{%
\subsubsection{Perfect Self}\label{perfect-self}}

At 20th level, when you roll for initiative and have no ki points
remaining, you regain 4 ki points.

\hypertarget{monastic-traditions}{%
\subsection{Monastic Traditions}\label{monastic-traditions}}

Three traditions of monastic pursuit are common in the monasteries
scattered across the multiverse. Most monasteries practice one tradition
exclusively, but a few honor the three traditions and instruct each monk
according to his or her aptitude and interest. All three traditions rely
on the same basic techniques, diverging as the student grows more adept.
Thus, a monk need choose a tradition only upon reaching 3rd level.

\#\#\#Way of the Open Hand

Monks of the Way of the Open Hand are the ultimate masters of martial
arts combat, whether armed or unarmed. They learn techniques to push and
trip their opponents, manipulate ki to heal damage to their bodies, and
practice advanced meditation that can protect them from harm.

\hypertarget{open-hand-technique}{%
\paragraph{Open Hand Technique}\label{open-hand-technique}}

Starting when you choose this tradition at 3rd level, you can manipulate
your enemy's ki when you harness your own. Whenever you hit a creature
with one of the attacks granted by your Flurry of Blows, you can impose
one of the following effects on that target:

\begin{itemize}
\tightlist
\item
  It must succeed on a Dexterity saving throw or be knocked prone.
\item
  It must make a Strength saving throw. If it fails, you can push it up
  to 15 feet away from you.
\item
  It can't take reactions until the end of your next turn.
\end{itemize}

\hypertarget{wholeness-of-body}{%
\paragraph{Wholeness of Body}\label{wholeness-of-body}}

At 6th level, you gain the ability to heal yourself. As an action, you
can regain hit points equal to three times your monk level. You must
finish a long rest before you can use this feature again.

\hypertarget{tranquility}{%
\paragraph{Tranquility}\label{tranquility}}

Beginning at 11th level, you can enter a special meditation that
surrounds you with an aura of peace. At the end of a long rest, you gain
the effect of a sanctuary spell that lasts until the start of your next
long rest (the spell can end early as normal). The saving throw DC for
the spell equals 8 + your Wisdom modifier + your proficiency bonus.

\hypertarget{quivering-palm}{%
\paragraph{Quivering Palm}\label{quivering-palm}}

At 17th level, you gain the ability to set up lethal vibrations in
someone's body. When you hit a creature with an unarmed strike, you can
spend 3 ki points to start these imperceptible vibrations, which last
for a number of days equal to your monk level. The vibrations are
harmless unless you use your action to end them. To do so, you and the
target must be on the same plane of existence. When you use this action,
the creature must make a Constitution saving throw. If it fails, it is
reduced to 0 hit points. If it succeeds, it takes 10d10 necrotic damage.

You can have only one creature under the effect of this feature at a
time. You can choose to end the vibrations harmlessly without using an
action.

\end{document}
