% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{paladin}{%
\section{Paladin}\label{paladin}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a paladin, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d10 per paladin level

\textbf{Hit Points at 1st Level:} 10 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d10 (or 6) + your Constitution
modifier per paladin level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} All armor, shields

\textbf{Weapons:} Simple weapons, martial weapons

\textbf{Tools:} None

\textbf{Saving Throws:} Wisdom, Charisma

\textbf{Skills:} Choose two from Athletics, Insight, Intimidation,
Medicine, Persuasion, and Religion

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a martial weapon and a shield or (\emph{b}) two martial
  weapons
\item
  (\emph{a}) five javelins or (b) any simple melee weapon
\item
  (\emph{a}) a priest's pack or (\emph{b}) an explorer's pack
\item
  Chain mail and a holy symbol
\end{itemize}

\hypertarget{the-paladin}{%
\paragraph{The Paladin}\label{the-paladin}}

\begin{longtable}[]{@{}llllllll@{}}
\toprule
Level & Proficiency Bonus & Features & 1st & 2nd & 3rd & 4th &
5th\tabularnewline
\midrule
\endhead
1st & +2 & Divine Sense, Lay on Hands & --- & --- & --- & --- &
---\tabularnewline
2nd & +2 & Fighting Style, Spellcasting, Divine Smite & 2 & --- & --- &
--- & ---\tabularnewline
3rd & +2 & Divine Health, Sacred Oath & 3 & --- & --- & --- &
---\tabularnewline
4th & +2 & Ability Score Improvement & 3 & --- & --- & --- &
---\tabularnewline
5th & +3 & Extra Attack & 4 & 2 & --- & --- & ---\tabularnewline
6th & +3 & Aura of Protection & 4 & 2 & --- & --- & ---\tabularnewline
7th & +3 & Sacred Oath feature & 4 & 3 & --- & --- & ---\tabularnewline
8th & +3 & Ability Score Improvement & 4 & 3 & --- & --- &
---\tabularnewline
9th & +4 & --- & 4 & 3 & 2 & --- & ---\tabularnewline
10th & +4 & Aura of Courage & 4 & 3 & 2 & --- & ---\tabularnewline
11th & +4 & Improved Divine Smite & 4 & 3 & 3 & --- & ---\tabularnewline
12th & +4 & Ability Score Improvement & 4 & 3 & 3 & --- &
---\tabularnewline
13th & +5 & --- & 4 & 3 & 3 & 1 & ---\tabularnewline
14th & +5 & Cleansing Touch & 4 & 3 & 3 & 1 & ---\tabularnewline
15th & +5 & Sacred Oath feature & 4 & 3 & 3 & 2 & ---\tabularnewline
16th & +5 & Ability Score Improvement & 4 & 3 & 3 & 2 &
---\tabularnewline
17th & +6 & --- & 4 & 3 & 3 & 3 & 1\tabularnewline
18th & +6 & Aura improvements & 4 & 3 & 3 & 3 & 1\tabularnewline
19th & +6 & Ability Score Improvement & 4 & 3 & 3 & 3 & 2\tabularnewline
20th & +6 & Sacred Oath feature & 4 & 3 & 3 & 3 & 2\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{divine-sense}{%
\subsubsection{Divine Sense}\label{divine-sense}}

The presence of strong evil registers on your senses like a noxious
odor, and powerful good rings like heavenly music in your ears. As an
action, you can open your awareness to detect such forces. Until the end
of your next turn, you know the location of any celestial, fiend, or
undead within 60 feet of you that is not behind total cover. You know
the type (celestial, fiend, or undead) of any being whose presence you
sense, but not its identity (the vampire Count Strahd von Zarovich, for
instance). Within the same radius, you also detect the presence of any
place or object that has been consecrated or desecrated, as with the
\emph{hallow} spell.

You can use this feature a number of times equal to 1 + your Charisma
modifier. When you finish a long rest, you regain all expended uses.

\hypertarget{lay-on-hands}{%
\subsubsection{Lay on Hands}\label{lay-on-hands}}

Your blessed touch can heal wounds. You have a pool of healing power
that replenishes when you take a long rest. With that pool, you can
restore a total number of hit points equal to your paladin level × 5.

As an action, you can touch a creature and draw power from the pool to
restore a number of hit points to that creature, up to the maximum
amount remaining in your pool.

Alternatively, you can expend 5 hit points from your pool of healing to
cure the target of one disease or neutralize one poison affecting it.
You can cure multiple diseases and neutralize multiple poisons with a
single use of Lay on Hands, expending hit points separately for each
one.

This feature has no effect on undead and constructs.

\hypertarget{fighting-style}{%
\subsubsection{Fighting Style}\label{fighting-style}}

At 2nd level, you adopt a style of fighting as your specialty. Choose
one of the following options. You can't take a Fighting Style option
more than once, even if you later get to choose again.

\hypertarget{defense}{%
\paragraph{Defense}\label{defense}}

While you are wearing armor, you gain a +1 bonus to AC.

\hypertarget{dueling}{%
\paragraph{Dueling}\label{dueling}}

When you are wielding a melee weapon in one hand and no other weapons,
you gain a +2 bonus to damage rolls with that weapon.

\hypertarget{great-weapon-fighting}{%
\paragraph{Great Weapon Fighting}\label{great-weapon-fighting}}

When you roll a 1 or 2 on a damage die for an attack you make with a
melee weapon that you are wielding with two hands, you can reroll the
die and must use the new roll. The weapon must have the two handed or
versatile property for you to gain this benefit.

\hypertarget{protection}{%
\paragraph{Protection}\label{protection}}

When a creature you can see attacks a target other than you that is
within 5 feet of you, you can use your reaction to impose disadvantage
on the attack roll. You must be wielding a shield.

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

By 2nd level, you have learned to draw on divine magic through
meditation and prayer to cast spells as a cleric does.

\hypertarget{preparing-and-casting-spells}{%
\paragraph{Preparing and Casting
Spells}\label{preparing-and-casting-spells}}

The Paladin table shows how many spell slots you have to cast your
spells. To cast one of your paladin spells of 1st level or higher, you
must expend a slot of the spell's level or higher. You regain all
expended spell slots when you finish a long rest.

You prepare the list of paladin spells that are available for you to
cast, choosing from the paladin spell list. When you do so, choose a
number of paladin spells equal to your Charisma modifier + half your
paladin level, rounded down (minimum of one spell). The spells must be
of a level for which you have spell slots.

For example, if you are a 5th level paladin, you have four 1st level and
two 2nd level spell slots. With a Charisma of 14, your list of prepared
spells can include four spells of 1st or 2nd level, in any combination.
If you prepare the 1st level spell \emph{cure wounds}, you can cast it
using a 1st level or a 2ndlevel slot. Casting the spell doesn't remove
it from your list of prepared spells.

You can change your list of prepared spells when you finish a long rest.
Preparing a new list of paladin spells requires time spent in prayer and
meditation: at least 1 minute per spell level for each spell on your
list.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Charisma is your spellcasting ability for your paladin spells, since
their power derives from the strength of your convictions. You use your
Charisma whenever a spell refers to your spellcasting ability. In
addition, you use your Charisma modifier when setting the saving throw
DC for a paladin spell you cast and when making an attack roll with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Charisma
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your Charisma
modifier

\#\#\#\#Spellcasting Focus

You can use a holy symbol as a spellcasting focus for your paladin
spells.

\#\#\#Divine Smite

Starting at 2nd level, when you hit a creature with a melee weapon
attack, you can expend one spell slot to deal radiant damage to the
target, in addition to the weapon's damage. The extra damage is 2d8 for
a 1st level spell slot, plus 1d8 for each spell level higher than 1st,
to a maximum of 5d8. The damage increases by 1d8 if the target is an
undead or a fiend.

\hypertarget{divine-health}{%
\subsubsection{Divine Health}\label{divine-health}}

By 3rd level, the divine magic flowing through you makes you immune to
disease.

\hypertarget{sacred-oath}{%
\subsubsection{Sacred Oath}\label{sacred-oath}}

When you reach 3rd level, you swear the oath that binds you as a paladin
forever. Up to this time you have been in a preparatory stage, committed
to the path but not yet sworn to it. Now you choose an oath, such as the
Oath of Devotion.

Your choice grants you features at 3rd level and again at 7th, 15th, and
20th level. Those features include oath spells and the Channel Divinity
feature.

\hypertarget{oath-spells}{%
\paragraph{Oath Spells}\label{oath-spells}}

Each oath has a list of associated spells. You gain access to these
spells at the levels specified in the oath description. Once you gain
access to an oath spell, you always have it prepared. Oath spells don't
count against the number of spells you can prepare each day. If you gain
an oath spell that doesn't appear on the paladin spell list, the spell
is nonetheless a paladin spell for you.

\hypertarget{channel-divinity}{%
\paragraph{Channel Divinity}\label{channel-divinity}}

Your oath allows you to channel divine energy to fuel magical effects.
Each Channel Divinity option provided by your oath explains how to use
it.

When you use your Channel Divinity, you choose which option to use. You
must then finish a short or long rest to use your Channel Divinity
again.

Some Channel Divinity effects require saving throws. When you use such
an effect from this class, the DC equals your paladin spell save DC.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{extra-attack}{%
\subsubsection{Extra Attack}\label{extra-attack}}

Beginning at 5th level, you can attack twice, instead of once, whenever
you take the Attack action on your turn.

\hypertarget{aura-of-protection}{%
\subsubsection{Aura of Protection}\label{aura-of-protection}}

Starting at 6th level, whenever you or a friendly creature within 10
feet of you must make a saving throw, the creature gains a bonus to the
saving throw equal to your Charisma modifier (with a minimum bonus of
+1). You must be conscious to grant this bonus. At 18th level, the range
of this aura increases to 30 feet.

\hypertarget{aura-of-courage}{%
\subsubsection{Aura of Courage}\label{aura-of-courage}}

Starting at 10th level, you and friendly creatures within 10 feet of you
can't be frightened while you are conscious.

At 18th level, the range of this aura increases to 30 feet.

\hypertarget{improved-divine-smite}{%
\subsubsection{Improved Divine Smite}\label{improved-divine-smite}}

By 11th level, you are so suffused with righteous might that all your
melee weapon strikes carry divine power with them. Whenever you hit a
creature with a melee weapon, the creature takes an extra 1d8 radiant
damage. If you also use your Divine Smite with an attack, you add this
damage to the extra damage of your Divine Smite.

\hypertarget{cleansing-touch}{%
\subsubsection{Cleansing Touch}\label{cleansing-touch}}

Beginning at 14th level, you can use your action to end one spell on
yourself or on one willing creature that you touch.

You can use this feature a number of times equal to your Charisma
modifier (a minimum of once). You regain expended uses when you finish a
long rest.

\hypertarget{sacred-oaths}{%
\subsection{Sacred Oaths}\label{sacred-oaths}}

Becoming a paladin involves taking vows that commit the paladin to the
cause of righteousness, an active path of fighting wickedness. The final
oath, taken when he or she reaches 3rd level, is the culmination of all
the paladin's training. Some characters with this class don't consider
themselves true paladins until they have reached 3rd level and made this
oath. For others, the actual swearing of the oath is a formality, an
official stamp on what has always been true in the paladin's heart.

\hypertarget{oath-of-devotion}{%
\subsubsection{Oath of Devotion}\label{oath-of-devotion}}

The Oath of Devotion binds a paladin to the loftiest ideals of justice,
virtue, and order. Sometimes called cavaliers, white knights, or holy
warriors, these paladins meet the ideal of the knight in shining armor,
acting with honor in pursuit of justice and the greater good. They hold
themselves to the highest standards of conduct, and some, for better or
worse, hold the rest of the world to the same standards. Many who swear
this oath are devoted to gods of law and good and use their gods' tenets
as the measure of their devotion. They hold angels---the perfect
servants of good---as their ideals, and incorporate images of angelic
wings into their helmets or coats of arms.

\hypertarget{tenets-of-devotion}{%
\paragraph{Tenets of Devotion}\label{tenets-of-devotion}}

Though the exact words and strictures of the Oath of Devotion vary,
paladins of this oath share these tenets.

\textbf{Honesty.} Don't lie or cheat. Let your word be your promise.

\textbf{Courage.} Never fear to act, though caution is wise.

\textbf{Compassion.} Aid others, protect the weak, and punish those who
threaten them. Show mercy to your foes, but temper it with wisdom.

\textbf{Honor.} Treat others with fairness, and let your honorable deeds
be an example to them. Do as much good as possible while causing the
least amount of harm.

\textbf{Duty.} Be responsible for your actions and their consequences,
protect those entrusted to your care, and obey those who have just
authority over you.

\hypertarget{oath-spells-1}{%
\paragraph{Oath Spells}\label{oath-spells-1}}

You gain oath spells at the paladin levels listed.

\hypertarget{oath-of-devotion-spells}{%
\paragraph{Oath of Devotion Spells}\label{oath-of-devotion-spells}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Paladin Level & Spells\tabularnewline
\midrule
\endhead
3rd & \emph{protection from evil and good},
\emph{sanctuary}\tabularnewline
5th & \emph{lesser restoration}, \emph{zone of truth}\tabularnewline
9th & \emph{beacon of hope}, \emph{dispel magic}\tabularnewline
13th & \emph{freedom of movement}, \emph{guardian of
faith}\tabularnewline
17th & \emph{commune}, \emph{flame strike}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{channel-divinity-1}{%
\paragraph{Channel Divinity}\label{channel-divinity-1}}

When you take this oath at 3rd level, you gain the following two Channel
Divinity options.

\textbf{Sacred Weapon.} As an action, you can imbue one weapon that you
are holding with positive energy, using your Channel Divinity. For 1
minute, you add your Charisma modifier to attack rolls made with that
weapon (with a minimum bonus of +1). The weapon also emits bright light
in a 20 foot radius and dim light 20 feet beyond that. If the weapon is
not already magical, it becomes magical for the duration.

You can end this effect on your turn as part of any other action. If you
are no longer holding or carrying this weapon, or if you fall
unconscious, this effect ends.

\textbf{Turn the Unholy.} As an action, you present your holy symbol and
speak a prayer censuring fiends and undead, using your Channel Divinity.
Each fiend or undead that can see or hear you within 30 feet of you must
make a Wisdom saving throw. If the creature fails its saving throw, it
is turned for 1 minute or until it takes damage.

A turned creature must spend its turns trying to move as far away from
you as it can, and it can't willingly move to a space within 30 feet of
you. It also can't take reactions. For its action, it can use only the
Dash action or try to escape from an effect that prevents it from
moving. If there's nowhere to move, the creature can use the Dodge
action.

\hypertarget{aura-of-devotion}{%
\paragraph{Aura of Devotion}\label{aura-of-devotion}}

Starting at 7th level, you and friendly creatures within 10 feet of you
can't be charmed while you are conscious.

At 18th level, the range of this aura increases to 30 feet.

\hypertarget{purity-of-spirit}{%
\paragraph{Purity of Spirit}\label{purity-of-spirit}}

Beginning at 15th level, you are always under the effects of a
\emph{protection from evil and good} spell.

\hypertarget{holy-nimbus}{%
\paragraph{Holy Nimbus}\label{holy-nimbus}}

At 20th level, as an action, you can emanate an aura of sunlight. For 1
minute, bright light shines from you in a 30 foot radius, and dim light
shines 30 feet beyond that. Whenever an enemy creature starts its turn
in the bright light, the creature takes 10 radiant damage.

In addition, for the duration, you have advantage on saving throws
against spells cast by fiends or undead.

Once you use this feature, you can't use it again until you finish a
long rest.

\begin{quote}
\mbox{}%
\hypertarget{breaking-your-oath}{%
\paragraph{Breaking Your Oath}\label{breaking-your-oath}}
\end{quote}

A paladin tries to hold to the highest standards of conduct, but even
the most virtuous paladin is fallible. Sometimes the right path proves
too demanding, sometimes a situation calls for the lesser of two evils,
and sometimes the heat of emotion causes a paladin to transgress his or
her oath.

\begin{quote}
A paladin who has broken a vow typically seeks absolution from a cleric
who shares his or her faith or from another paladin of the same order.
The paladin might spend an all- night vigil in prayer as a sign of
penitence, or undertake a fast or similar act of self-denial. After a
rite of confession and forgiveness, the paladin starts fresh.

If a paladin willfully violates his or her oath and shows no sign of
repentance, the consequences can be more serious. At the GM's
discretion, an impenitent paladin might be forced to abandon this class
and adopt another.
\end{quote}

\end{document}
