% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{ranger}{%
\section{Ranger}\label{ranger}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a ranger, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d10 per ranger level

\textbf{Hit Points at 1st Level:} 10 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d10 (or 6) + your Constitution
modifier per ranger level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor, medium armor, shields

\textbf{Weapons:} Simple weapons, martial weapons

\textbf{Tools:} None

\textbf{Saving Throws:} Strength, Dexterity

\textbf{Skills:} Choose three from Animal Handling, Athletics, Insight,
Investigation, Nature, Perception, Stealth, and Survival

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) scale mail or (\emph{b}) leather armor
\item
  (\emph{a}) two shortswords or (\emph{b}) two simple melee weapons
\item
  (\emph{a}) a dungeoneer's pack or (\emph{b}) an explorer's pack
\item
  A longbow and a quiver of 20 arrows
\end{itemize}

\hypertarget{the-ranger}{%
\paragraph{The Ranger}\label{the-ranger}}

\begin{longtable}[]{@{}lllllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Spells Known & 1st & 2nd & 3rd &
4th & 5th\tabularnewline
\midrule
\endhead
1st & +2 & Favored Enemy, Natural Explorer & --- & --- & --- & --- & ---
& ---\tabularnewline
2nd & +2 & Fighting Style, Spellcasting & 2 & 2 & --- & --- & --- &
---\tabularnewline
3rd & +2 & Ranger Archetype, Primeval Awareness & 3 & 3 & --- & --- &
--- & ---\tabularnewline
4th & +2 & Ability Score Improvement & 3 & 3 & --- & --- & --- &
---\tabularnewline
5th & +3 & Extra Attack & 4 & 4 & 2 & --- & --- & ---\tabularnewline
6th & +3 & Favored Enemy and Natural Explorer improvements & 4 & 4 & 2 &
--- & --- & ---\tabularnewline
7th & +3 & Ranger Archetype feature & 5 & 4 & 3 & --- & --- &
---\tabularnewline
8th & +3 & Ability Score Improvement, Land's Stride & 5 & 4 & 3 & --- &
--- & ---\tabularnewline
9th & +4 & --- & 6 & 4 & 3 & 2 & --- & ---\tabularnewline
10th & +4 & Natural Explorer improvement, Hide in Plain Sight & 6 & 4 &
3 & 2 & --- & ---\tabularnewline
11th & +4 & Ranger Archetype feature & 7 & 4 & 3 & 3 & --- &
---\tabularnewline
12th & +4 & Ability Score Improvement & 7 & 4 & 3 & 3 & --- &
---\tabularnewline
13th & +5 & --- & 8 & 4 & 3 & 3 & 1 & ---\tabularnewline
14th & +5 & Favored Enemy improvement, Vanish & 8 & 4 & 3 & 3 & 1 &
---\tabularnewline
15th & +5 & Ranger Archetype feature & 9 & 4 & 3 & 3 & 2 &
---\tabularnewline
16th & +5 & Ability Score Improvement & 9 & 4 & 3 & 3 & 2 &
---\tabularnewline
17th & +6 & --- & 10 & 4 & 3 & 3 & 3 & 1\tabularnewline
18th & +6 & Feral Senses & 10 & 4 & 3 & 3 & 3 & 1\tabularnewline
19th & +6 & Ability Score Improvement & 11 & 4 & 3 & 3 & 3 &
2\tabularnewline
20th & +6 & Foe Slayer & 11 & 4 & 3 & 3 & 3 & 2\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{favored-enemy}{%
\subsubsection{Favored Enemy}\label{favored-enemy}}

Beginning at 1st level, you have significant experience studying,
tracking, hunting, and even talking to a certain type of enemy.

Choose a type of favored enemy: aberrations, beasts, celestials,
constructs, dragons, elementals, fey, fiends, giants, monstrosities,
oozes, plants, or undead. Alternatively, you can select two races of
humanoid (such as gnolls and orcs) as favored enemies.

You have advantage on Wisdom (Survival) checks to track your favored
enemies, as well as on Intelligence checks to recall information about
them.

When you gain this feature, you also learn one language of your choice
that is spoken by your favored enemies, if they speak one at all. You
choose one additional favored enemy, as well as an associated language,
at 6th and 14th level. As you gain levels, your choices should reflect
the types of monsters you have encountered on your adventures.

\hypertarget{natural-explorer}{%
\subsubsection{Natural Explorer}\label{natural-explorer}}

You are particularly familiar with one type of natural environment and
are adept at traveling and surviving in such regions. Choose one type of
favored terrain: arctic, coast, desert, forest, grassland, mountain, or
swamp. When you make an Intelligence or Wisdom check related to your
favored terrain, your proficiency bonus is doubled if you are using a
skill that you're proficient in. While traveling for an hour or more in
your favored terrain, you gain the following benefits:

\begin{itemize}
\tightlist
\item
  Difficult terrain doesn't slow your group's travel.
\item
  Your group can't become lost except by magical means.
\item
  Even when you are engaged in another activity while traveling (such as
  foraging, navigating, or tracking), you remain alert to danger.
\item
  If you are traveling alone, you can move stealthily at a normal pace.
\item
  When you forage, you find twice as much food as you normally would.
\item
  While tracking other creatures, you also learn their exact number,
  their sizes, and how long ago they passed through the area.
\end{itemize}

You choose additional favored terrain types at 6th and 10th level.

\hypertarget{fighting-style}{%
\subsubsection{Fighting Style}\label{fighting-style}}

At 2nd level, you adopt a particular style of fighting as your
specialty. Choose one of the following options. You can't take a
Fighting Style option more than once, even if you later get to choose
again.

\hypertarget{archery}{%
\paragraph{Archery}\label{archery}}

You gain a +2 bonus to attack rolls you make with ranged weapons.

\hypertarget{defense}{%
\paragraph{Defense}\label{defense}}

While you are wearing armor, you gain a +1 bonus to AC.

\#\#\#\#Dueling

When you are wielding a melee weapon in one hand and no other weapons,
you gain a +2 bonus to damage rolls with that weapon.

\hypertarget{two-weapon-fighting}{%
\paragraph{Two-Weapon Fighting}\label{two-weapon-fighting}}

When you engage in two weapon fighting, you can add your ability
modifier to the damage of the second attack.

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

By the time you reach 2nd level, you have learned to use the magical
essence of nature to cast spells, much as a druid does.

\hypertarget{spell-slots}{%
\paragraph{Spell Slots}\label{spell-slots}}

The Ranger table shows how many spell slots you have to cast your spells
of 1st level and higher. To cast one of these spells, you must expend a
slot of the spell's level or higher. You regain all expended spell slots
when you finish a long rest.

For example, if you know the 1st level spell \emph{animal friendship}
and have a 1st-level and a 2nd-level spell slot available, you can cast
\emph{animal friendship} using either slot.

\hypertarget{spells-known-of-1st-level-and-higher}{%
\paragraph{Spells Known of 1st Level and
Higher}\label{spells-known-of-1st-level-and-higher}}

You know two 1st level spells of your choice from the ranger spell list.

The Spells Known column of the Ranger table shows when you learn more
ranger spells of your choice. Each of these spells must be of a level
for which you have spell slots. For instance, when you reach 5th level
in this class, you can learn one new spell of 1st or 2nd level.

Additionally, when you gain a level in this class, you can choose one of
the ranger spells you know and replace it with another spell from the
ranger spell list, which also must be of a level for which you have
spell slots.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Wisdom is your spellcasting ability for your ranger spells, since your
magic draws on your attunement to nature. You use your Wisdom whenever a
spell refers to your spellcasting ability. In addition, you use your
Wisdom modifier when setting the saving throw DC for a ranger spell you
cast and when making an attack roll with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Wisdom
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your Wisdom
modifier

\hypertarget{ranger-archetype}{%
\subsubsection{Ranger Archetype}\label{ranger-archetype}}

At 3rd level, you choose an archetype that you strive to emulate, such
as the Hunter. Your choice grants you features at 3rd level and again at
7th, 11th, and 15th level.

\hypertarget{primeval-awareness}{%
\subsubsection{Primeval Awareness}\label{primeval-awareness}}

Beginning at 3rd level, you can use your action and expend one ranger
spell slot to focus your awareness on the region around you. For 1
minute per level of the spell slot you expend, you can sense whether the
following types of creatures are present within 1 mile of you (or within
up to 6 miles if you are in your favored terrain): aberrations,
celestials, dragons, elementals, fey, fiends, and undead. This feature
doesn't reveal the creatures' location or number.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{extra-attack}{%
\subsubsection{Extra Attack}\label{extra-attack}}

Beginning at 5th level, you can attack twice, instead of once, whenever
you take the Attack action on your turn.

\hypertarget{lands-stride}{%
\subsubsection{Land's Stride}\label{lands-stride}}

Starting at 8th level, moving through nonmagical difficult terrain costs
you no extra movement. You can also pass through nonmagical plants
without being slowed by them and without taking damage from them if they
have thorns, spines, or a similar hazard. In addition, you have
advantage on saving throws against plants that are magically created or
manipulated to impede movement, such those created by the entangle
spell.

\hypertarget{hide-in-plain-sight}{%
\subsubsection{Hide in Plain Sight}\label{hide-in-plain-sight}}

Starting at 10th level, you can spend 1 minute creating camouflage for
yourself. You must have access to fresh mud, dirt, plants, soot, and
other naturally occurring materials with which to create your
camouflage.

Once you are camouflaged in this way, you can try to hide by pressing
yourself up against a solid surface, such as a tree or wall, that is at
least as tall and wide as you are. You gain a +10 bonus to Dexterity
(Stealth) checks as long as you remain there without moving or taking
actions. Once you move or take an action or a reaction, you must
camouflage yourself again to gain this benefit.

\hypertarget{vanish}{%
\subsubsection{Vanish}\label{vanish}}

Starting at 14th level, you can use the Hide action as a bonus action on
your turn. Also, you can't be tracked by nonmagical means, unless you
choose to leave a trail.

\hypertarget{feral-senses}{%
\subsubsection{Feral Senses}\label{feral-senses}}

At 18th level, you gain preternatural senses that help you fight
creatures you can't see. When you attack a creature you can't see, your
inability to see it doesn't impose disadvantage on your attack rolls
against it. You are also aware of the location of any invisible creature
within 30 feet of you, provided that the creature isn't hidden from you
and you aren't blinded or deafened.

\hypertarget{foe-slayer}{%
\subsubsection{Foe Slayer}\label{foe-slayer}}

At 20th level, you become an unparalleled hunter of your enemies. Once
on each of your turns, you can add your Wisdom modifier to the attack
roll or the damage roll of an attack you make against one of your
favored enemies. You can choose to use this feature before or after the
roll, but before any effects of the roll are applied.

\hypertarget{ranger-archetypes}{%
\subsection{Ranger Archetypes}\label{ranger-archetypes}}

A classic expression of the ranger ideal is the Hunter.

\hypertarget{hunter}{%
\subsubsection{Hunter}\label{hunter}}

Emulating the Hunter archetype means accepting your place as a bulwark
between civilization and the terrors of the wilderness. As you walk the
Hunter's path, you learn specialized techniques for fighting the threats
you face, from rampaging ogres and hordes of orcs to towering giants and
terrifying dragons.

\hypertarget{hunters-prey}{%
\paragraph{Hunter's Prey}\label{hunters-prey}}

At 3rd level, you gain one of the following features of your choice.

\textbf{Colossus Slayer.} Your tenacity can wear down the most potent
foes. When you hit a creature with a weapon attack, the creature takes
an extra 1d8 damage if it's below its hit point maximum. You can deal
this extra damage only once per turn.

\textbf{Giant Killer.} When a Large or larger creature within 5 feet of
you hits or misses you with an attack, you can use your reaction to
attack that creature immediately after its attack, provided that you can
see the creature.

\textbf{Horde Breaker.} Once on each of your turns when you make a
weapon attack, you can make another attack with the same weapon against
a different creature that is within 5 feet of the original target and
within range of your weapon.

\hypertarget{defensive-tactics}{%
\paragraph{Defensive Tactics}\label{defensive-tactics}}

At 7th level, you gain one of the following features of your choice.

\textbf{Escape the Horde.} Opportunity attacks against you are made with
disadvantage. \textbf{Multiattack Defense.} When a creature hits you
with an attack, you gain a +4 bonus to AC against all subsequent attacks
made by that creature for the rest of the turn. \textbf{Steel Will.} You
have advantage on saving throws against being frightened.

\hypertarget{multiattack}{%
\paragraph{Multiattack}\label{multiattack}}

At 11th level, you gain one of the following features of your choice.
\textbf{Volley.} You can use your action to make a ranged attack against
any number of creatures within 10 feet of a point you can see within
your weapon's range. You must have ammunition for each target, as
normal, and you make a separate attack roll for each target.

\textbf{Whirlwind Attack.} You can use your action to make a melee
attack against any number of creatures within 5 feet of you, with a
separate attack roll for each target.

\hypertarget{superior-hunters-defense}{%
\paragraph{Superior Hunter's Defense}\label{superior-hunters-defense}}

At 15th level, you gain one of the following features of your choice.

\textbf{Evasion.} When you are subjected to an effect, such as a red
dragon's fiery breath or a lightning bolt spell, that allows you to make
a Dexterity saving throw to take only half damage, you instead take no
damage if you succeed on the saving throw, and only half damage if you
fail.

\textbf{Stand Against the Tide.} When a hostile creature misses you with
a melee attack, you can use your reaction to force that creature to
repeat the same attack against another creature (other than itself) of
your choice. \textbf{Uncanny Dodge.} When an attacker that you can see
hits you with an attack, you can use your reaction to halve the attack's
damage against you.

\end{document}
