% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{rogue}{%
\section{Rogue}\label{rogue}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a rogue, you have the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per rogue level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per rogue level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor

\textbf{Weapons:} Simple weapons, hand crossbows, longswords, rapiers,
shortswords

\textbf{Tools:} Thieves' tools

\textbf{Saving Throws:} Dexterity, Intelligence

\textbf{Skills:} Choose four from Acrobatics, Athletics, Deception,
Insight, Intimidation, Investigation, Perception, Performance,
Persuasion, Sleight of Hand, and Stealth

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a rapier or (\emph{b}) a shortsword
\item
  (\emph{a}) a shortbow and quiver of 20 arrows or (\emph{b}) a
  shortsword
\item
  (\emph{a}) a burglar's pack, (\emph{b}) a dungeoneer's pack, or
  (\emph{c}) an explorer's pack
\item
  (\emph{a}) Leather armor, two daggers, and thieves' tools
\end{itemize}

\hypertarget{the-rogue}{%
\paragraph{The Rogue}\label{the-rogue}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Level & Proficiency Bonus & Sneak Attack & Features\tabularnewline
\midrule
\endhead
1st & +2 & 1d6 & Expertise, Sneak Attack, Thieves' Cant\tabularnewline
2nd & +2 & 1d6 & Cunning Action\tabularnewline
3rd & +2 & 2d6 & Roguish Archetype\tabularnewline
4th & +2 & 2d6 & Ability Score Improvement\tabularnewline
5th & +3 & 3d6 & Uncanny Dodge\tabularnewline
6th & +3 & 3d6 & Expertise\tabularnewline
7th & +3 & 4d6 & Evasion\tabularnewline
8th & +3 & 4d6 & Ability Score Improvement\tabularnewline
9th & +4 & 5d6 & Roguish Archetype feature\tabularnewline
10th & +4 & 5d6 & Ability Score Improvement\tabularnewline
11th & +4 & 6d6 & Reliable Talent\tabularnewline
12th & +4 & 6d6 & Ability Score Improvement\tabularnewline
13th & +5 & 7d6 & Roguish Archetype feature\tabularnewline
14th & +5 & 7d6 & Blindsense\tabularnewline
15th & +5 & 8d6 & Slippery Mind\tabularnewline
16th & +5 & 8d6 & Ability Score Improvement\tabularnewline
17th & +6 & 9d6 & Roguish Archetype feature\tabularnewline
18th & +6 & 9d6 & Elusive\tabularnewline
19th & +6 & 10d6 & Ability Score Improvement\tabularnewline
20th & +6 & 10d6 & Stroke of Luck\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{expertise}{%
\subsubsection{Expertise}\label{expertise}}

At 1st level, choose two of your skill proficiencies, or one of your
skill proficiencies and your proficiency with thieves' tools. Your
proficiency bonus is doubled for any ability check you make that uses
either of the chosen proficiencies.

At 6th level, you can choose two more of your proficiencies (in skills
or with thieves' tools) to gain this benefit.

\hypertarget{sneak-attack}{%
\subsubsection{Sneak Attack}\label{sneak-attack}}

Beginning at 1st level, you know how to strike subtly and exploit a
foe's distraction. Once per turn, you can deal an extra 1d6 damage to
one creature you hit with an attack if you have advantage on the attack
roll. The attack must use a finesse or a ranged weapon.

You don't need advantage on the attack roll if another enemy of the
target is within 5 feet of it, that enemy isn't incapacitated, and you
don't have disadvantage on the attack roll.

The amount of the extra damage increases as you gain levels in this
class, as shown in the Sneak Attack column of the Rogue table.

\hypertarget{thieves-cant}{%
\subsubsection{Thieves' Cant}\label{thieves-cant}}

During your rogue training you learned thieves' cant, a secret mix of
dialect, jargon, and code that allows you to hide messages in seemingly
normal conversation. Only another creature that knows thieves' cant
understands such messages. It takes four times longer to convey such a
message than it does to speak the same idea plainly.

In addition, you understand a set of secret signs and symbols used to
convey short, simple messages, such as whether an area is dangerous or
the territory of a thieves' guild, whether loot is nearby, or whether
the people in an area are easy marks or will provide a safe house for
thieves on the run.

\hypertarget{cunning-action}{%
\subsubsection{Cunning Action}\label{cunning-action}}

Starting at 2nd level, your quick thinking and agility allow you to move
and act quickly. You can take a bonus action on each of your turns in
combat. This action can be used only to take the Dash, Disengage, or
Hide action.

\hypertarget{roguish-archetype}{%
\subsubsection{Roguish Archetype}\label{roguish-archetype}}

At 3rd level, you choose an archetype that you emulate in the exercise
of your rogue abilities, such as Thief. Your archetype choice grants you
features at 3rd level and then again at 9th, 13th, and 17th level.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 10th, 12th, 16th, and 19th
level, you can increase one ability score of your choice by 2, or you
can increase two ability scores of your choice by 1. As normal, you
can't increase an ability score above 20 using this feature.

\hypertarget{uncanny-dodge}{%
\subsubsection{Uncanny Dodge}\label{uncanny-dodge}}

Starting at 5th level, when an attacker that you can see hits you with
an attack, you can use your reaction to halve the attack's damage
against you.

\hypertarget{evasion}{%
\subsubsection{Evasion}\label{evasion}}

Beginning at 7th level, you can nimbly dodge out of the way of certain
area effects, such as a red dragon's fiery breath or an ice storm spell.
When you are subjected to an effect that allows you to make a Dexterity
saving throw to take only half damage, you instead take no damage if you
succeed on the saving throw, and only half damage if you fail.

\hypertarget{reliable-talent}{%
\subsubsection{Reliable Talent}\label{reliable-talent}}

By 11th level, you have refined your chosen skills until they approach
perfection. Whenever you make an ability check that lets you add your
proficiency bonus, you can treat a d20 roll of 9 or lower as a 10.

\hypertarget{blindsense}{%
\subsubsection{Blindsense}\label{blindsense}}

Starting at 14th level, if you are able to hear, you are aware of the
location of any hidden or invisible creature within 10 feet of you.

\hypertarget{slippery-mind}{%
\subsubsection{Slippery Mind}\label{slippery-mind}}

By 15th level, you have acquired greater mental strength. You gain
proficiency in Wisdom saving throws.

\hypertarget{elusive}{%
\subsubsection{Elusive}\label{elusive}}

Beginning at 18th level, you are so evasive that attackers rarely gain
the upper hand against you. No attack roll has advantage against you
while you aren't incapacitated.

\hypertarget{stroke-of-luck}{%
\subsubsection{Stroke of Luck}\label{stroke-of-luck}}

At 20th level, you have an uncanny knack for succeeding when you need
to. If your attack misses a target within range, you can turn the miss
into a hit. Alternatively, if you fail an ability check, you can treat
the d20 roll as a 20. Once you use this feature, you can't use it again
until you finish a short or long rest.

\hypertarget{roguish-archetypes}{%
\subsection{Roguish Archetypes}\label{roguish-archetypes}}

Rogues have many features in common, including their emphasis on
perfecting their skills, their precise and deadly approach to combat,
and their increasingly quick reflexes. But different rogues steer those
talents in varying directions, embodied by the rogue archetypes. Your
choice of archetype is a reflection of your focus---not necessarily an
indication of your chosen profession, but a description of your
preferred techniques.

\hypertarget{thief}{%
\subsubsection{Thief}\label{thief}}

You hone your skills in the larcenous arts. Burglars, bandits,
cutpurses, and other criminals typically follow this archetype, but so
do rogues who prefer to think of themselves as professional treasure
seekers, explorers, delvers, and investigators. In addition to improving
your agility and stealth, you learn skills useful for delving into
ancient ruins, reading unfamiliar languages, and using magic items you
normally couldn't employ.

\hypertarget{fast-hands}{%
\paragraph{Fast Hands}\label{fast-hands}}

Starting at 3rd level, you can use the bonus action granted by your
Cunning Action to make a Dexterity (Sleight of Hand) check, use your
thieves' tools to disarm a trap or open a lock, or take the Use an
Object action.

\hypertarget{second-story-work}{%
\paragraph{Second-Story Work}\label{second-story-work}}

When you choose this archetype at 3rd level, you gain the ability to
climb faster than normal; climbing no longer costs you extra movement.

In addition, when you make a running jump, the distance you cover
increases by a number of feet equal to your Dexterity modifier.

\hypertarget{supreme-sneak}{%
\paragraph{Supreme Sneak}\label{supreme-sneak}}

Starting at 9th level, you have advantage on a Dexterity (Stealth) check
if you move no more than half your speed on the same turn.

\hypertarget{use-magic-device}{%
\paragraph{Use Magic Device}\label{use-magic-device}}

By 13th level, you have learned enough about the workings of magic that
you can improvise the use of items even when they are not intended for
you. You ignore all class, race, and level requirements on the use of
magic items.

\hypertarget{thiefs-reflexes}{%
\paragraph{Thief's Reflexes}\label{thiefs-reflexes}}

When you reach 17th level, you have become adept at laying ambushes and
quickly escaping danger. You can take two turns during the first round
of any combat. You take your first turn at your normal initiative and
your second turn at your initiative minus 10. You can't use this feature
when you are surprised.

\end{document}
