% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{warlock}{%
\section{Warlock}\label{warlock}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a warlock, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d8 per warlock level

\textbf{Hit Points at 1st Level:} 8 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d8 (or 5) + your Constitution
modifier per warlock level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} Light armor

\textbf{Weapons:} Simple weapons

\textbf{Tools:} None

\textbf{Saving Throws:} Wisdom, Charisma

\textbf{Skills:} Choose two skills from Arcana, Deception, History,
Intimidation, Investigation, Nature, and Religion

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a light crossbow and 20 bolts or (\emph{b}) any simple
  weapon
\item
  (\emph{a}) a component pouch or (\emph{b}) an arcane focus
\item
  (\emph{a}) a scholar's pack or (\emph{b}) a dungeoneer's pack
\item
  Leather armor, any simple weapon, and two daggers
\end{itemize}

\hypertarget{the-warlock}{%
\paragraph{The Warlock}\label{the-warlock}}

\begin{longtable}[]{@{}llllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Cantrips Known & Spells Known &
Spell Slots & Slot Level & Invocations Known\tabularnewline
\midrule
\endhead
1st & +2 & Otherworldly Patron, Pact Magic & 2 & 2 & 1 & 1st &
---\tabularnewline
2nd & +2 & Eldritch Invocations & 2 & 3 & 2 & 1st & 2\tabularnewline
3rd & +2 & Pact Boon & 2 & 4 & 2 & 2nd & 2\tabularnewline
4th & +2 & Ability Score Improvement & 3 & 5 & 2 & 2nd &
2\tabularnewline
5th & +3 & --- & 3 & 6 & 2 & 3rd & 3\tabularnewline
6th & +3 & Otherworldly Patron feature & 3 & 7 & 2 & 3rd &
3\tabularnewline
7th & +3 & --- & 3 & 8 & 2 & 4th & 4\tabularnewline
8th & +3 & Ability Score Improvement & 3 & 9 & 2 & 4th &
4\tabularnewline
9th & +4 & --- & 3 & 10 & 2 & 5th & 5\tabularnewline
10th & +4 & Otherworldly Patron feature & 4 & 10 & 2 & 5th &
5\tabularnewline
11th & +4 & Mystic Arcanum (6th level) & 4 & 11 & 3 & 5th &
5\tabularnewline
12th & +4 & Ability Score Improvement & 4 & 11 & 3 & 5th &
6\tabularnewline
13th & +5 & Mystic Arcanum (7th level) & 4 & 12 & 3 & 5th &
6\tabularnewline
14th & +5 & Otherworldly Patron feature & 4 & 12 & 3 & 5th &
6\tabularnewline
15th & +5 & Mystic Arcanum (8th level) & 4 & 13 & 3 & 5th &
7\tabularnewline
16th & +5 & Ability Score Improvement & 4 & 13 & 3 & 5th &
7\tabularnewline
17th & +6 & Mystic Arcanum (9th level) & 4 & 14 & 4 & 5th &
7\tabularnewline
18th & +6 & --- & 4 & 14 & 4 & 5th & 8\tabularnewline
19th & +6 & Ability Score Improvement & 4 & 15 & 4 & 5th &
8\tabularnewline
20th & +6 & Eldritch Master & 4 & 15 & 4 & 5th & 8\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{otherworldly-patron}{%
\subsubsection{Otherworldly Patron}\label{otherworldly-patron}}

At 1st level, you have struck a bargain with an otherworldly being of
your choice: the Archfey, the Fiend, or the Great Old One, each of which
is detailed at the end of the class description. Your choice grants you
features at 1st level and again at 6th, 10th, and 14th level.

\hypertarget{pact-magic}{%
\subsubsection{Pact Magic}\label{pact-magic}}

Your arcane research and the magic bestowed on you by your patron have
given you facility with spells.

\hypertarget{cantrips}{%
\paragraph{Cantrips}\label{cantrips}}

You know two cantrips of your choice from the warlock spell list. You
learn additional warlock cantrips of your choice at higher levels, as
shown in the Cantrips Known column of the Warlock table.

\hypertarget{spell-slots}{%
\paragraph{Spell Slots}\label{spell-slots}}

The Warlock table shows how many spell slots you have. The table also
shows what the level of those slots is; all of your spell slots are the
same level. To cast one of your warlock spells of 1st level or higher,
you must expend a spell slot. You regain all expended spell slots when
you finish a short or long rest.

For example, when you are 5th level, you have two 3rd level spell slots.
To cast the 1st level spell \emph{thunderwave}, you must spend one of
those slots, and you cast it as a 3rd level spell.

\hypertarget{spells-known-of-1st-level-and-higher}{%
\paragraph{Spells Known of 1st Level and
Higher}\label{spells-known-of-1st-level-and-higher}}

At 1st level, you know two 1st level spells of your choice from the
warlock spell list. The Spells Known column of the Warlock table shows
when you learn more warlock spells of your choice of 1st level and
higher. A spell you choose must be of a level no higher than what's
shown in the table's Slot Level column for your level. When you reach
6th level, for example, you learn a new warlock spell, which can be 1st,
2nd, or 3rd level.

Additionally, when you gain a level in this class, you can choose one of
the warlock spells you know and replace it with another spell from the
warlock spell list, which also must be of a level for which you have
spell slots.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Charisma is your spellcasting ability for your warlock spells, so you
use your Charisma whenever a spell refers to your spellcasting ability.
In addition, you use your Charisma modifier when setting the saving
throw DC for a warlock spell you cast and when making an attack roll
with one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Charisma
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your Charisma
modifier

\hypertarget{spellcasting-focus}{%
\paragraph{Spellcasting Focus}\label{spellcasting-focus}}

You can use an arcane focus as a spellcasting focus for your warlock
spells.

\hypertarget{eldritch-invocations}{%
\subsubsection{Eldritch Invocations}\label{eldritch-invocations}}

In your study of occult lore, you have unearthed eldritch invocations,
fragments of forbidden knowledge that imbue you with an abiding magical
ability.

At 2nd level, you gain two eldritch invocations of your choice. Your
invocation options are detailed at the end of the class description.
When you gain certain warlock levels, you gain additional invocations of
your choice, as shown in the Invocations Known column of the Warlock
table. Additionally, when you gain a level in this class, you can choose
one of the invocations you know and replace it with another invocation
that you could learn at that level.

\hypertarget{pact-boon}{%
\subsubsection{Pact Boon}\label{pact-boon}}

At 3rd level, your otherworldly patron bestows a gift upon you for your
loyal service. You gain one of the following features of your choice.

\hypertarget{pact-of-the-chain}{%
\paragraph{Pact of the Chain}\label{pact-of-the-chain}}

You learn the \emph{find familiar} spell and can cast it as a ritual.
The spell doesn't count against your number of spells known.

When you cast the spell, you can choose one of the normal forms for your
familiar or one of the following special forms: imp, pseudodragon,
quasit, or sprite.

Additionally, when you take the Attack action, you can forgo one of your
own attacks to allow your familiar to make one attack of its own with
its reaction.

\hypertarget{pact-of-the-blade}{%
\paragraph{Pact of the Blade}\label{pact-of-the-blade}}

You can use your action to create a pact weapon in your empty hand. You
can choose the form that this melee weapon takes each time you create
it. You are proficient with it while you wield it. This weapon counts as
magical for the purpose of overcoming resistance and immunity to
nonmagical attacks and damage. Your pact weapon disappears if it is more
than 5 feet away from you for 1 minute or more. It also disappears if
you use this feature again, if you dismiss the weapon (no action
required), or if you die.

You can transform one magic weapon into your pact weapon by performing a
special ritual while you hold the weapon. You perform the ritual over
the course of 1 hour, which can be done during a short rest. You can
then dismiss the weapon, shunting it into an extradimensional space, and
it appears whenever you create your pact weapon thereafter. You can't
affect an artifact or a sentient weapon in this way. The weapon ceases
being your pact weapon if you die, if you perform the 1 hour ritual on a
different weapon, or if you use a 1 hour ritual to break your bond to
it. The weapon appears at your feet if it is in the extradimensional
space when the bond breaks.

\hypertarget{pact-of-the-tome}{%
\paragraph{Pact of the Tome}\label{pact-of-the-tome}}

Your patron gives you a grimoire called a Book of Shadows. When you gain
this feature, choose three cantrips from any class's spell list (the
three needn't be from the same list). While the book is on your person,
you can cast those cantrips at will. They don't count against your
number of cantrips known. If they don't appear on the warlock spell
list, they are nonetheless warlock spells for you.

If you lose your Book of Shadows, you can perform a 1 hour ceremony to
receive a replacement from your patron. This ceremony can be performed
during a short or long rest, and it destroys the previous book. The book
turns to ash when you die.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{mystic-arcanum}{%
\subsubsection{Mystic Arcanum}\label{mystic-arcanum}}

At 11th level, your patron bestows upon you a magical secret called an
arcanum. Choose one 6th level spell from the warlock spell list as this
arcanum. You can cast your arcanum spell once without expending a spell
slot. You must finish a long rest before you can do so again.

At higher levels, you gain more warlock spells of your choice that can
be cast in this way: one 7th level spell at 13th level, one 8th level
spell at 15th level, and one 9th level spell at 17th level. You regain
all uses of your Mystic Arcanum when you finish a long rest.

\hypertarget{eldritch-master}{%
\subsubsection{Eldritch Master}\label{eldritch-master}}

At 20th level, you can draw on your inner reserve of mystical power
while entreating your patron to regain expended spell slots. You can
spend 1 minute entreating your patron for aid to regain all your
expended spell slots from your Pact Magic feature. Once you regain spell
slots with this feature, you must finish a long rest before you can do
so again.

\#\#Eldritch Invocations

If an eldritch invocation has prerequisites, you must meet them to learn
it. You can learn the invocation at the same time that you meet its
prerequisites. A level prerequisite refers to your level in this class.

\hypertarget{agonizing-blast}{%
\paragraph{Agonizing Blast}\label{agonizing-blast}}

*Prerequisite: *eldritch blast \emph{cantrip} When you cast
\emph{eldritch blast}, add your Charisma modifier to the damage it deals
on a hit.

\hypertarget{armor-of-shadows}{%
\paragraph{Armor of Shadows}\label{armor-of-shadows}}

You can cast \emph{mage armor} on yourself at will, without expending a
spell slot or material components.

\hypertarget{ascendant-step}{%
\paragraph{Ascendant Step}\label{ascendant-step}}

\emph{Prerequisite: 9th level} You can cast \emph{levitate} on yourself
at will, without expending a spell slot or material components.

\hypertarget{beast-speech}{%
\paragraph{Beast Speech}\label{beast-speech}}

You can cast \emph{speak with animals} at will, without expending a
spell slot.

\hypertarget{beguiling-influence}{%
\paragraph{Beguiling Influence}\label{beguiling-influence}}

You gain proficiency in the Deception and Persuasion skills.

\hypertarget{bewitching-whispers}{%
\paragraph{Bewitching Whispers}\label{bewitching-whispers}}

\emph{Prerequisite: 7th level}

You can cast \emph{compulsion} once using a warlock spell slot. You
can't do so again until you finish a long rest.

\hypertarget{book-of-ancient-secrets}{%
\paragraph{Book of Ancient Secrets}\label{book-of-ancient-secrets}}

\emph{Prerequisite: Pact of the Tome feature} You can now inscribe
magical rituals in your Book of Shadows. Choose two 1st level spells
that have the ritual tag from any class's spell list (the two needn't be
from the same list). The spells appear in the book and don't count
against the number of spells you know. With your Book of Shadows in
hand, you can cast the chosen spells as rituals. You can't cast the
spells except as rituals, unless you've learned them by some other
means. You can also cast a warlock spell you know as a ritual if it has
the ritual tag.

On your adventures, you can add other ritual spells to your Book of
Shadows. When you find such a spell, you can add it to the book if the
spell's level is equal to or less than half your warlock level (rounded
up) and if you can spare the time to transcribe the spell. For each
level of the spell, the transcription process takes 2 hours and costs 50
gp for the rare inks needed to inscribe it.

\hypertarget{chains-of-carceri}{%
\paragraph{Chains of Carceri}\label{chains-of-carceri}}

\emph{Prerequisite: 15th level, Pact of the Chain feature} You can cast
\emph{hold monster} at will---targeting a celestial, fiend, or
elemental---without expending a spell slot or material components. You
must finish a long rest before you can use this invocation on the same
creature again.

\hypertarget{devils-sight}{%
\paragraph{Devil's Sight}\label{devils-sight}}

You can see normally in darkness, both magical and nonmagical, to a
distance of 120 feet.

\hypertarget{dreadful-word}{%
\paragraph{Dreadful Word}\label{dreadful-word}}

\emph{Prerequisite: 7th level} You can cast \emph{confusion} once using
a warlock spell slot. You can't do so again until you finish a long
rest.

\hypertarget{eldritch-sight}{%
\paragraph{Eldritch Sight}\label{eldritch-sight}}

You can cast \emph{detect magic} at will, without expending a spell
slot.

\hypertarget{eldritch-spear}{%
\paragraph{Eldritch Spear}\label{eldritch-spear}}

*Prerequisite: *eldritch blast \emph{cantrip} When you cast
\emph{eldritch blast}, its range is 300 feet.

\hypertarget{eyes-of-the-rune-keeper}{%
\paragraph{Eyes of the Rune Keeper}\label{eyes-of-the-rune-keeper}}

You can read all writing.

\hypertarget{fiendish-vigor}{%
\paragraph{Fiendish Vigor}\label{fiendish-vigor}}

You can cast \emph{false life} on yourself at will as a 1st level spell,
without expending a spell slot or material components.

\hypertarget{gaze-of-two-minds}{%
\paragraph{Gaze of Two Minds}\label{gaze-of-two-minds}}

You can use your action to touch a willing humanoid and perceive through
its senses until the end of your next turn. As long as the creature is
on the same plane of existence as you, you can use your action on
subsequent turns to maintain this connection, extending the duration
until the end of your next turn. While perceiving through the other
creature's senses, you benefit from any special senses possessed by that
creature, and you are blinded and deafened to your own surroundings.

\hypertarget{lifedrinker}{%
\paragraph{Lifedrinker}\label{lifedrinker}}

\emph{Prerequisite: 12th level, Pact of the Blade feature} When you hit
a creature with your pact weapon, the creature takes extra necrotic
damage equal to your Charisma modifier (minimum 1).

\hypertarget{mask-of-many-faces}{%
\paragraph{Mask of Many Faces}\label{mask-of-many-faces}}

You can cast \emph{disguise self} at will, without expending a spell
slot.

\hypertarget{master-of-myriad-forms}{%
\paragraph{Master of Myriad Forms}\label{master-of-myriad-forms}}

\emph{Prerequisite: 15th level}

You can cast \emph{alter self} at will, without expending a spell slot.

\hypertarget{minions-of-chaos}{%
\paragraph{Minions of Chaos}\label{minions-of-chaos}}

\emph{Prerequisite: 9th level}

You can cast \emph{conjure elemental} once using a warlock spell slot.
You can't do so again until you finish a long rest.

\hypertarget{mire-the-mind}{%
\paragraph{Mire the Mind}\label{mire-the-mind}}

\emph{Prerequisite: 5th level} You can cast \emph{slow} once using a
warlock spell slot. You can't do so again until you finish a long rest.

\#\#\#\#Misty Visions

You can cast \emph{silent image} at will, without expending a spell slot
or material components.

\hypertarget{one-with-shadows}{%
\paragraph{One with Shadows}\label{one-with-shadows}}

\emph{Prerequisite: 5th level} When you are in an area of dim light or
darkness, you can use your action to become invisible until you move or
take an action or a reaction.

\hypertarget{otherworldly-leap}{%
\paragraph{Otherworldly Leap}\label{otherworldly-leap}}

\emph{Prerequisite: 9th level}

You can cast \emph{jump} on yourself at will, without expending a spell
slot or material components.

\hypertarget{repelling-blast}{%
\paragraph{Repelling Blast}\label{repelling-blast}}

*Prerequisite: *eldritch blast \emph{cantrip}

When you hit a creature with eldritch blast, you can push the creature
up to 10 feet away from you in a straight line.

\hypertarget{sculptor-of-flesh}{%
\paragraph{Sculptor of Flesh}\label{sculptor-of-flesh}}

\emph{Prerequisite: 7th level} You can cast \emph{polymorph} once using
a warlock spell slot. You can't do so again until you finish a long
rest.

\hypertarget{sign-of-ill-omen}{%
\paragraph{Sign of Ill Omen}\label{sign-of-ill-omen}}

\emph{Prerequisite: 5th level}

You can cast \emph{bestow curse} once using a warlock spell slot. You
can't do so again until you finish a long rest.

\hypertarget{thief-of-five-fates}{%
\paragraph{Thief of Five Fates}\label{thief-of-five-fates}}

You can cast \emph{bane} once using a warlock spell slot. You can't do
so again until you finish a long rest.

\hypertarget{thirsting-blade}{%
\paragraph{Thirsting Blade}\label{thirsting-blade}}

\emph{Prerequisite: 5th level, Pact of the Blade feature}

You can attack with your pact weapon twice, instead of once, whenever
you take the Attack action on your turn.

\hypertarget{visions-of-distant-realms}{%
\paragraph{Visions of Distant Realms}\label{visions-of-distant-realms}}

\emph{Prerequisite: 15th level}

You can cast \emph{arcane eye} at will, without expending a spell slot.

\hypertarget{voice-of-the-chain-master}{%
\paragraph{Voice of the Chain Master}\label{voice-of-the-chain-master}}

\emph{Prerequisite: Pact of the Chain feature}

You can communicate telepathically with your familiar and perceive
through your familiar's senses as long as you are on the same plane of
existence. Additionally, while perceiving through your familiar's
senses, you can also speak through your familiar in your own voice, even
if your familiar is normally incapable of speech.

\hypertarget{whispers-of-the-grave}{%
\paragraph{Whispers of the Grave}\label{whispers-of-the-grave}}

\emph{Prerequisite: 9th level}

You can cast \emph{speak with dead} at will, without expending a spell
slot.

\hypertarget{witch-sight}{%
\paragraph{Witch Sight}\label{witch-sight}}

\emph{Prerequisite: 15th level}

You can see the true form of any shapechanger or creature concealed by
illusion or transmutation magic while the creature is within 30 feet of
you and within line of sight.

\hypertarget{otherworldly-patrons}{%
\subsection{Otherworldly Patrons}\label{otherworldly-patrons}}

The beings that serve as patrons for warlocks are mighty inhabitants of
other planes of existence---not gods, but almost godlike in their power.
Various patrons give their warlocks access to different powers and
invocations, and expect significant favors in return.

Some patrons collect warlocks, doling out mystic knowledge relatively
freely or boasting of their ability to bind mortals to their will. Other
patrons bestow their power only grudgingly, and might make a pact with
only one warlock. Warlocks who serve the same patron might view each
other as allies, siblings, or rivals.

\hypertarget{fiend}{%
\subsubsection{Fiend}\label{fiend}}

You have made a pact with a fiend from the lower planes of existence, a
being whose aims are evil, even if you strive against those aims. Such
beings desire the corruption or destruction of all things, ultimately
including you. Fiends powerful enough to forge a pact include demon
lords such as Demogorgon, Orcus, Fraz'Urb luu, and Baphomet; archdevils
such as Asmodeus, Dispater, Mephistopheles, and Belial; pit fiends and
balors that are especially mighty; and ultroloths and other lords of the
yugoloths.

\hypertarget{expanded-spell-list}{%
\paragraph{Expanded Spell List}\label{expanded-spell-list}}

The Fiend lets you choose from an expanded list of spells when you learn
a warlock spell. The following spells are added to the warlock spell
list for you.

\hypertarget{fiend-expanded-spells}{%
\paragraph{Fiend Expanded Spells}\label{fiend-expanded-spells}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Spell Level & Spells\tabularnewline
\midrule
\endhead
1st & \emph{burning hands}, \emph{command}\tabularnewline
2nd & \emph{blindness/deafness}, \emph{scorching ray}\tabularnewline
3rd & \emph{fireball}, \emph{stinking cloud}\tabularnewline
4th & \emph{fire shield}, \emph{wall of fire}\tabularnewline
5th & \emph{flame strike}, \emph{hallow}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{dark-ones-blessing}{%
\paragraph{Dark One's Blessing}\label{dark-ones-blessing}}

Starting at 1st level, when you reduce a hostile creature to 0 hit
points, you gain temporary hit points equal to your Charisma modifier +
your warlock level (minimum of 1).

\hypertarget{dark-ones-own-luck}{%
\paragraph{Dark One's Own Luck}\label{dark-ones-own-luck}}

Starting at 6th level, you can call on your patron to alter fate in your
favor. When you make an ability check or a saving throw, you can use
this feature toa d10 to your roll. You can do so after seeing the
initial roll but before any of the roll's effects occur.

Once you use this feature, you can't use it again until you finish a
short or long rest.

\hypertarget{fiendish-resilience}{%
\paragraph{Fiendish Resilience}\label{fiendish-resilience}}

Starting at 10th level, you can choose one damage type when you finish a
short or long rest. You gain resistance to that damage type until you
choose a different one with this feature. Damage from magical weapons or
silver weapons ignores this resistance.

\hypertarget{hurl-through-hell}{%
\paragraph{Hurl Through Hell}\label{hurl-through-hell}}

Starting at 14th level, when you hit a creature with an attack, you can
use this feature to instantly transport the target through the lower
planes. The creature disappears and hurtles through a nightmare
landscape.

At the end of your next turn, the target returns to the space it
previously occupied, or the nearest unoccupied space. If the target is
not a fiend, it takes 10d10 psychic damage as it reels from its horrific
experience.

Once you use this feature, you can't use it again until you finish a
long rest.

\begin{quote}
\mbox{}%
\hypertarget{your-pact-boon}{%
\paragraph{Your Pact Boon}\label{your-pact-boon}}
\end{quote}

Each Pact Boon option produces a special creature or an object that
reflects your patron's nature.

\begin{quote}
\textbf{Pact of the Chain.} Your familiar is more cunning than a typical
familiar. Its default form can be a reflection of your patron, with imps
and quasits tied to the Fiend.

\textbf{Pact of the Blade.} If you serve the Fiend, your weapon could be
an axe made of black metal and adorned with decorative flames.

\textbf{Pact of the Tome.} Your Book of Shadows could be a weighty tome
bound in demon hide studded with iron, holding spells of conjuration and
a wealth of forbidden lore about the sinister regions of the cosmos, a
gift of the Fiend.
\end{quote}

\end{document}
