% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

\begin{document}

\hypertarget{wizard}{%
\section{Wizard}\label{wizard}}

\hypertarget{class-features}{%
\subsection{Class Features}\label{class-features}}

As a wizard, you gain the following class features.

\hypertarget{hit-points}{%
\paragraph{Hit Points}\label{hit-points}}

\textbf{Hit Dice:} 1d6 per wizard level

\textbf{Hit Points at 1st Level:} 6 + your Constitution modifier

\textbf{Hit Points at Higher Levels:} 1d6 (or 4) + your Constitution
modifier per wizard level after 1st

\hypertarget{proficiencies}{%
\paragraph{Proficiencies}\label{proficiencies}}

\textbf{Armor:} None

\textbf{Weapons:} Daggers, darts, slings, quarterstaffs, light crossbows

\textbf{Tools:} None

\textbf{Saving Throws:} Intelligence, Wisdom

\textbf{Skills:} Choose two from Arcana, History, Insight,
Investigation, Medicine, and Religion

\hypertarget{equipment}{%
\paragraph{Equipment}\label{equipment}}

You start with the following equipment, in addition to the equipment
granted by your background:

\begin{itemize}
\tightlist
\item
  (\emph{a}) a quarterstaff or (\emph{b}) a dagger
\item
  (\emph{a}) a component pouch or (\emph{b}) an arcane focus
\item
  (\emph{a}) a scholar's pack or (\emph{b}) an explorer's pack
\item
  A spellbook
\end{itemize}

\hypertarget{the-wizard}{%
\paragraph{The Wizard}\label{the-wizard}}

\begin{longtable}[]{@{}lllllllllllll@{}}
\toprule
Level & Proficiency Bonus & Features & Cantrips Known & 1st & 2nd & 3rd
& 4th & 5th & 6th & 7th & 8th & 9th\tabularnewline
\midrule
\endhead
1st & +2 & Spellcasting, Arcane Recovery & 3 & 2 & --- & --- & --- & ---
& --- & --- & --- & ---\tabularnewline
2nd & +2 & Arcane Tradition & 3 & 3 & --- & --- & --- & --- & --- & ---
& --- & ---\tabularnewline
3rd & +2 & --- & 3 & 4 & 2 & --- & --- & --- & --- & --- & --- &
---\tabularnewline
4th & +2 & Ability Score Improvement & 4 & 4 & 3 & --- & --- & --- & ---
& --- & --- & ---\tabularnewline
5th & +3 & --- & 4 & 4 & 3 & 2 & --- & --- & --- & --- & --- &
---\tabularnewline
6th & +3 & Arcane Tradition feature & 4 & 4 & 3 & 3 & --- & --- & --- &
--- & --- & ---\tabularnewline
7th & +3 & --- & 4 & 4 & 3 & 3 & 1 & --- & --- & --- & --- &
---\tabularnewline
8th & +3 & Ability Score Improvement & 4 & 4 & 3 & 3 & 2 & --- & --- &
--- & --- & ---\tabularnewline
9th & +4 & --- & 4 & 4 & 3 & 3 & 3 & 1 & --- & --- & --- &
---\tabularnewline
10th & +4 & Arcane Tradition feature & 5 & 4 & 3 & 3 & 3 & 2 & --- & ---
& --- & ---\tabularnewline
11th & +4 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & --- & --- &
---\tabularnewline
12th & +4 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 2 & 1 & ---
& --- & ---\tabularnewline
13th & +5 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & --- &
---\tabularnewline
14th & +5 & Arcane Tradition feature & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 &
--- & ---\tabularnewline
15th & +5 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & ---\tabularnewline
16th & +5 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 &
1 & ---\tabularnewline
17th & +6 & --- & 5 & 4 & 3 & 3 & 3 & 2 & 1 & 1 & 1 & 1\tabularnewline
18th & +6 & Spell Mastery & 5 & 4 & 3 & 3 & 3 & 3 & 1 & 1 & 1 &
1\tabularnewline
19th & +6 & Ability Score Improvement & 5 & 4 & 3 & 3 & 3 & 3 & 2 & 1 &
1 & 1\tabularnewline
20th & +6 & Signature Spell & 5 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 1 &
1\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{spellcasting}{%
\subsubsection{Spellcasting}\label{spellcasting}}

As a student of arcane magic, you have a spellbook containing spells
that show the first glimmerings of your true power.

\hypertarget{cantrips}{%
\paragraph{Cantrips}\label{cantrips}}

At 1st level, you know three cantrips of your choice from the wizard
spell list. You learn additional wizard cantrips of your choice at
higher levels, as shown in the Cantrips Known column of the Wizard
table.

\hypertarget{spellbook}{%
\paragraph{Spellbook}\label{spellbook}}

At 1st level, you have a spellbook containing six 1st level wizard
spells of your choice. Your spellbook is the repository of the wizard
spells you know, except your cantrips, which are fixed in your mind.

\hypertarget{preparing-and-casting-spells}{%
\paragraph{Preparing and Casting
Spells}\label{preparing-and-casting-spells}}

The Wizard table shows how many spell slots you have to cast your spells
of 1st level and higher. To cast one of these spells, you must expend a
slot of the spell's level or higher. You regain all expended spell slots
when you finish a long rest. You prepare the list of wizard spells that
are available for you to cast. To do so, choose a number of wizard
spells from your spellbook equal to your Intelligence modifier + your
wizard level (minimum of one spell). The spells must be of a level for
which you have spell slots.

For example, if you're a 3rd level wizard, you have four 1st level and
two 2nd level spell slots. With an Intelligence of 16, your list of
prepared spells can include six spells of 1st or 2nd level, in any
combination, chosen from your spellbook. If you prepare the 1st level
spell \emph{magic missile}, you can cast it using a 1st level or a 2nd
level slot. Casting the spell doesn't remove it from your list of
prepared spells. You can change your list of prepared spells when you
finish a long rest. Preparing a new list of wizard spells requires time
spent studying your spellbook and memorizing the incantations and
gestures you must make to cast the spell: at least 1 minute per spell
level for each spell on your list.

\hypertarget{spellcasting-ability}{%
\paragraph{Spellcasting Ability}\label{spellcasting-ability}}

Intelligence is your spellcasting ability for your wizard spells, since
you learn your spells through dedicated study and memorization. You use
your Intelligence whenever a spell refers to your spellcasting ability.
In addition, you use your Intelligence modifier when setting the saving
throw DC for a wizard spell you cast and when making an attack roll with
one.

\textbf{Spell save DC} = 8 + your proficiency bonus + your Intelligence
modifier

\textbf{Spell attack modifier} = your proficiency bonus + your
Intelligence modifier

\hypertarget{ritual-casting}{%
\paragraph{Ritual Casting}\label{ritual-casting}}

You can cast a wizard spell as a ritual if that spell has the ritual tag
and you have the spell in your spellbook. You don't need to have the
spell prepared.

\hypertarget{spellcasting-focus}{%
\paragraph{Spellcasting Focus}\label{spellcasting-focus}}

You can use an arcane focus as a spellcasting focus for your wizard
spells.

\hypertarget{learning-spells-of-1st-level-and-higher}{%
\paragraph{Learning Spells of 1st Level and
Higher}\label{learning-spells-of-1st-level-and-higher}}

Each time you gain a wizard level, you can add two wizard spells of your
choice to your spellbook for free. Each of these spells must be of a
level for which you have spell slots, as shown on the Wizard table. On
your adventures, you might find other spells that you can add to your
spellbook (see the ``Your Spellbook'' sidebar).

\hypertarget{arcane-recovery}{%
\subsubsection{Arcane Recovery}\label{arcane-recovery}}

You have learned to regain some of your magical energy by studying your
spellbook. Once per day when you finish a short rest, you can choose
expended spell slots to recover. The spell slots can have a combined
level that is equal to or less than half your wizard level (rounded up),
and none of the slots can be 6th level or higher. For example, if you're
a 4th level wizard, you can recover up to two levels worth of spell
slots. You can recover either a 2nd level spell slot or two 1st level
spell slots.

\hypertarget{arcane-tradition}{%
\subsubsection{Arcane Tradition}\label{arcane-tradition}}

When you reach 2nd level, you choose an arcane tradition, shaping your
practice of magic through one of eight schools, such as Evocation.

Your choice grants you features at 2nd level and again at 6th, 10th, and
14th level.

\hypertarget{ability-score-improvement}{%
\subsubsection{Ability Score
Improvement}\label{ability-score-improvement}}

When you reach 4th level, and again at 8th, 12th, 16th, and 19th level,
you can increase one ability score of your choice by 2, or you can
increase two ability scores of your choice by 1. As normal, you can't
increase an ability score above 20 using this feature.

\hypertarget{spell-mastery}{%
\subsubsection{Spell Mastery}\label{spell-mastery}}

At 18th level, you have achieved such mastery over certain spells that
you can cast them at will. Choose a 1st level wizard spell and a 2nd
level wizard spell that are in your spellbook. You can cast those spells
at their lowest level without expending a spell slot when you have them
prepared. If you want to cast either spell at a higher level, you must
expend a spell slot as normal.

By spending 8 hours in study, you can exchange one or both of the spells
you chose for different spells of the same levels.

\hypertarget{signature-spells}{%
\subsubsection{Signature Spells}\label{signature-spells}}

When you reach 20th level, you gain mastery over two powerful spells and
can cast them with little effort. Choose two 3rd level wizard spells in
your spellbook as your signature spells. You always have these spells
prepared, they don't count against the number of spells you have
prepared, and you can cast each of them once at 3rd level without
expending a spell slot. When you do so, you can't do so again until you
finish a short or long rest. If you want to cast either spell at a
higher level, you must expend a spell slot as normal.

\hypertarget{arcane-traditions}{%
\subsection{Arcane Traditions}\label{arcane-traditions}}

The study of wizardry is ancient, stretching back to the earliest mortal
discoveries of magic. It is firmly established in fantasy gaming worlds,
with various traditions dedicated to its complex study.

The most common arcane traditions in the multiverse revolve around the
schools of magic. Wizards through the ages have cataloged thousands of
spells, grouping them into eight categories called schools. In some
places, these traditions are literally schools. In other institutions,
the schools are more like academic departments, with rival faculties
competing for students and funding. Even wizards who train apprentices
in the solitude of their own towers use the division of magic into
schools as a learning device, since the spells of each school require
mastery of different techniques.

\hypertarget{school-of-evocation}{%
\subsubsection{School of Evocation}\label{school-of-evocation}}

You focus your study on magic that creates powerful elemental effects
such as bitter cold, searing flame, rolling thunder, crackling
lightning, and burning acid. Some evokers find employment in military
forces, serving as artillery to blast enemy armies from afar. Others use
their spectacular power to protect the weak, while some seek their own
gain as bandits, adventurers, or aspiring tyrants.

\hypertarget{evocation-savant}{%
\paragraph{Evocation Savant}\label{evocation-savant}}

Beginning when you select this school at 2nd level, the gold and time
you must spend to copy an evocation spell into your spellbook is halved.

\hypertarget{sculpt-spells}{%
\paragraph{Sculpt Spells}\label{sculpt-spells}}

Beginning at 2nd level, you can create pockets of relative safety within
the effects of your evocation spells. When you cast an evocation spell
that affects other creatures that you can see, you can choose a number
of them equal to 1 + the spell's level. The chosen creatures
automatically succeed on their saving throws against the spell, and they
take no damage if they would normally take half damage on a successful
save.

\hypertarget{potent-cantrip}{%
\paragraph{Potent Cantrip}\label{potent-cantrip}}

Starting at 6th level, your damaging cantrips affect even creatures that
avoid the brunt of the effect. When a creature succeeds on a saving
throw against your cantrip, the creature takes half the cantrip's damage
(if any) but suffers no additional effect from the cantrip. Empowered
Evocation

Beginning at 10th level, you can add your Intelligence modifier to one
damage roll of any wizard evocation spell you cast.

\hypertarget{overchannel}{%
\paragraph{Overchannel}\label{overchannel}}

Starting at 14th level, you can increase the power of your simpler
spells. When you cast a wizard spell of 1st through 5th level that deals
damage, you can deal maximum damage with that spell.

The first time you do so, you suffer no adverse effect. If you use this
feature again before you finish a long rest, you take 2d12 necrotic
damage for each level of the spell, immediately after you cast it. Each
time you use this feature again before finishing a long rest, the
necrotic damage per spell level increases by 1d12. This damage ignores
resistance and immunity.

\begin{quote}
\mbox{}%
\hypertarget{your-spellbook}{%
\paragraph{Your Spellbook}\label{your-spellbook}}
\end{quote}

The spells that you add to your spellbook as you gain levels reflect the
arcane research you conduct on your own, as well as intellectual
breakthroughs you have had about the nature of the multiverse. You might
find other spells during your adventures. You could discover a spell
recorded on a scroll in an evil wizard's chest, for example, or in a
dusty tome in an ancient library.

\begin{quote}
\textbf{Copying a Spell into the Book.} When you find a wizard spell of
1st level or higher, you can add it to your spellbook if it is of a
spell level you can prepare and if you can spare the time to decipher
and copy it.

Copying that spell into your spellbook involves reproducing the basic
form of the spell, then deciphering the unique system of notation used
by the wizard who wrote it. You must practice the spell until you
understand the sounds or gestures required, then transcribe it into your
spellbook using your own notation.

For each level of the spell, the process takes 2 hours and costs 50 gp.
The cost represents material components you expend as you experiment
with the spell to master it, as well as the fine inks you need to record
it. Once you have spent this time and money, you can prepare the spell
just like your other spells.

\textbf{Replacing the Book.} You can copy a spell from your own
spellbook into another book---for example, if you want to make a backup
copy of your spellbook. This is just like copying a new spell into your
spellbook, but faster and easier, since you understand your own notation
and already know how to cast the spell. You need spend only 1 hour and
10 gp for each level of the copied spell.

If you lose your spellbook, you can use the same procedure to transcribe
the spells that you have prepared into a new spellbook. Filling out the
remainder of your spellbook requires you to find new spells to do so, as
normal. For this reason, many wizards keep backup spellbooks in a safe
place.

\textbf{The Book's Appearance.} Your spellbook is a unique compilation
of spells, with its own decorative flourishes and margin notes. It might
be a plain, functional leather volume that you received as a gift from
your master, a finely bound gilt-edged tome you found in an ancient
library, or even a loose collection of notes scrounged together after
you lost your previous spellbook in a mishap.
\end{quote}

\end{document}
